### 2023-12-22 whittaker.tex
initial commit

%edited starting 8/27/17 for re-submission to Duke
\documentclass[10pt,leqno]{article}
\usepackage{verbatim}
\usepackage{amssymb}
\usepackage{mathtools}
%\usepackage{amsrefs}
\usepackage{rotating}
\usepackage{amsmath}
%\usepackage{showkeys}
\usepackage{tabularx}
\setlength\extrarowheight{4pt}   %spacing in tables
\usepackage{theorem}
\usepackage[matrix,tips,frame,color,line,poly,curve]{xy}
\renewcommand{\labelenumi}{(\arabic{enumi})}
\newcommand\kappaarrow[2]{#1\overset\kappa\rightarrow#2}
\newtheorem{theorem}[equation]{Theorem}
\newtheorem{corollary}[equation]{Corollary}
\newtheorem{definition}[equation]{Definition}
\newtheorem{lemma}[equation]{Lemma}
\newtheorem{desideratum}[equation]{Desideratum}
\newtheorem{conjecture}[equation]{Conjecture}
\newtheorem{proposition}[equation]{Proposition}
\newtheorem{remark}[equation]{Remark}
{\theorembodyfont{\rmfamily}\newtheorem{theoremplain}[equation]{Theorem}
\newtheorem{remarkplain}[equation]{Remark}
\newtheorem{editorialremarkplain}[equation]{Editorial Remark}
\newtheorem{exampleplain}[equation]{Example}
\newtheorem{corollaryplain}[equation]{Corollary}
\newtheorem{mytable}[equation]{Table}
}

\renewcommand{\sec}[1]{\section{#1}
\renewcommand{\theequation}{\thesection.\arabic{equation}}
  \setcounter{equation}{0}}
\newcommand{\subsec}[1]{\subsection{#1}
\renewcommand{\theequation}{\thesubsection.\arabic{equation}}
  \setcounter{equation}{0}}

\newcommand{\subsubsec}[1]{\subsubsection{#1}
\renewcommand{\theequation}{\thesubsection.\arabic{equation}}
  \setcounter{equation}{0}}

% Danger, Will Robinson!
\def\danger{\begin{trivlist}\item[]\noindent%
\begingroup\hangindent=3pc\hangafter=-2%\clubpenalty=10000%
\def\par{\endgraf\endgroup}%
\hbox to0pt{\hskip-\hangindent\dbend\hfill}\ignorespaces}
\def\enddanger{\par\end{trivlist}}

\newcommand{\Gext}{\negthinspace\negthinspace\phantom{a}^\delta G}
\newcommand{\thetaG}{\negthinspace\negthinspace\phantom{a}^\theta
  G(\C)}
\newcommand{\thetaK}{\negthinspace\negthinspace\phantom{a}^\theta K(\C)}
\newcommand{\qed}{\hfill $\square$ \medskip}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\qed}
\newcommand\exact[3]{1\rightarrow #1\rightarrow #2\rightarrow #3\rightarrow1}
\newcommand{\Aut}{\mathrm{Aut}}
\newcommand{\Inv}{\mathrm{Invol}}
\newcommand{\sgn}{\mathrm{sgn}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\gr}{\mathrm{gr}}
\newcommand{\Out}{\mathrm{Out}}
\newcommand{\Int}{\mathrm{Int}}
\renewcommand{\int}{\mathrm{int}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\kernel}{\mathrm{kernel}}
\newcommand{\Ad}{\mathrm{Ad}}
\newcommand{\zinv}{\mathrm{inv}}
\newcommand{\SRF}{\mathrm{SRF}}
\newcommand{\Gad}{G_\mathrm{ad}}
\newcommand{\Gsc}{G_\mathrm{sc}}
\newcommand{\Zsc}{Z_\mathrm{sc}}
\newcommand{\Ztor}{Z_\mathrm{tor}}
\newcommand{\Gbar}{\overline G}
\newcommand{\Kad}{K_\mathrm{ad}}
\newcommand{\Gal}{\mathrm{Gal}}
\newcommand{\Norm}{\mathrm{Norm}}
\newcommand{\Cent}{\mathrm{Cent}}
\newcommand{\Stab}{\mathrm{Stab}}
\newcommand{\I}{\mathcal I}
\renewcommand{\O}{\mathcal O}
\newcommand{\R}{\mathbb R}
\newcommand{\C}{\mathbb C}
\newcommand{\Z}{\mathbb Z}
\newcommand{\W}{\mathbb W}
\newcommand{\Ztwo}{\mathbb Z_2}
\newcommand{\N}{\mathcal N}
\newcommand{\Q}{\mathbb Q}
\newcommand{\E}{\mathbb E}
\newcommand{\G}{G}
\renewcommand{\H}{\mathbb H}
\newcommand{\h}{\mathfrak h}
\newcommand{\n}{\mathfrak n}
\renewcommand{\sl}{\mathfrak s\mathfrak l}
\renewcommand{\P}{\mathfrak p}
\renewcommand{\a}{\mathfrak a}
\newcommand{\zk}{\mathfrak z_\mathfrak k}
\newcommand{\A}{\mathbb A}
\newcommand{\K}{\mathcal K}
\newcommand{\B}{\mathcal B}
\renewcommand{\k}{\mathfrak k}
\newcommand{\spint}{\widetilde{Spin}}
\newcommand{\ch}[1]{#1^\vee}
\newcommand\sigmaqc{\sigma_{\text{qc}}}
\newcommand\thetaqc{\theta_{\text{qc}}}
\newcommand{\Fgal}{F_{\text{gal}}}
\newcommand{\Falg}{F_{\text{alg}}}
\newcommand{\cl}{\mathit{cl}}
\newcommand{\Lie}{\mathrm{Lie}}
\newcommand{\opp}{\text{-opp}}

\renewcommand{\t}{\mathfrak t}
\newcommand{\su}{\mathfrak s\mathfrak u}
\newcommand{\g}{\mathfrak g}
\newcommand\inv{^{-1}}
\newcommand\wh{\widehat}
\newcommand{\GL}{\text{GL}}
\newcommand{\SL}{\text{SL}}
\newcommand{\SO}{\text{SO}}
\newcommand{\SU}{\text{SU}}
\newcommand{\Spin}{\text{Spin}}
\newcommand{\chGGamma}{\phantom{a}^\vee G^\Gamma}
\newcommand{\GGamma}{G^\Gamma}
\newcommand{\s}{\mathfrak s}
\newcommand{\w}{\mathfrak w}
\newcommand{\AV}{\mathrm{AV}}
\newcommand{\WF}{\mathrm{WF}}
\newcommand{\AVann}{\mathrm{AV}_{\mathrm{ann}}}
\newcommand{\GK}{\mathrm{GK}}
\newcommand{\Op}{\O_p}
\begin{document}
\title{Whittaker Models for Real Groups}
\author{Jeffrey Adams}
\maketitle

Let $G$ be a connected, complex reductive group, defined over $\R$, and suppose $G(\R)$ is quasisplit.
We fix some notation.

Let $\g=\Lie(G), \g(\R)=\Lie(G(\R))$. Choose a Cartan involution $\theta$ for $G$. This means:
$\theta$ is an algebraic involution; commuting with the anti-holomorphic involution $\sigma$ defining $G(\R)$;
and $G(\R)^\theta$ is a maximal compact subgroup of $G(\R)$. Set $K=G^\theta$, $K(\R)=G(\R)^\theta=K^\sigma$.
Let $\s$ be the $-1$ eigenspace of $\theta$ acting on $\g$.

We assume $G(\R)$ has discrete series representations, and fix an L-packet $\Pi$ of discrete series representations.

By a  {\it Whittaker datum} we mean a $G(\R)$-conjugacy class of pairs  $(B(\R),\eta)$ where $B(\R)$ is a
Borel subgroup of $G(\R)$, and $\eta$
and $\eta$ is a non-degenerate character of the nilpotent radical $N(\R)$ of $B(\R)$. Non-degenerate means: non-trivial on each simple root space.

Let $\N$ be the set of nilpotent elements of $G$ on $\g$.
This is the closure of the principal nilpotent orbit $\Op$.

Suppose $\pi$ is an irreducible $(\g,K)$-module. Let $I_\pi$ be the annihlator of $\pi$ in the universal enveloping algebra.
Let $\AVann(\pi)$ be the associated variety of $I_\pi$. 
This is the closure of a single complex nilpotent orbit $\O$.
Write $\GK(\pi)$ for the Gelfand-Kirillov dimension of $\pi$
\cite{vogan-gelfand-kirillov}. 
All dimensions are complex unless otherwise stated.
The associated variety of $\pi$, denoted $\AV(\pi)$, is the  the union of a set of
$K$-orbits on $\O\cap\s$.
We have
Then
$$
GK(\pi)=\dim(AV(\pi))=\frac12\dim(\AVann(\pi)
$$
For all of these facts see \cite{vogan_bowdoin}, in particular Corollary 4.7 and Theorem 8.4.

Set $N=\dim(\N)=\dim(G)-\mathrm{rank}(G)$. The maximal Gelfand-Kirillov dimension of a representation is $N/2$.
We say $\pi$ is {\it large} if $\GK(\pi)=N/2$. See \cite[Section 6]{Vogan78}.

The wave-front set of $\pi$, written $\WF(\pi)$, is the union of a (finite) set of nilpotent $G(\R)$ orbits in
$i\g(\R)^*=i\Hom_\R(\g(\R),\R)$. See \cite{howe_wave_front}, \cite{bv_local_structure}.

\begin{lemma}
  \label{l:large}
  The following conditions are equivalent.
  \begin{enumerate}
    \item $\pi$ is large;
\item $\AVann(\pi)=\N=\overline{\Op}$;
\item $\dim(\AVann(\pi))=N$;
  \item $\dim(AV(\pi))=N/2$;
\item $\GK(\pi)=N/2$;

\end{enumerate}
\end{lemma}
See \cite{vogan_bowdoin}.

Let $Z=Z(G)$ be the center of $G$, and $\Gad=G/Z$.
Then $Z$ and $\Gad$ are defined over $\R$, and $Z(\R)=Z(G(\R))$.
Set $G(\R)_{\mathrm{ad}}=G(\R)/Z(\R)$.
Define
$$
Q(\R)=\Gad(\R)/G(\R)_{\mathrm{ad}}
$$
Thus $\Gad(\R)$ is the set of inner automorphisms of $G$ which are defined over $\R$, containing
$G(\R)_{\mathrm{ad}}=G(\R)/Z(\R)$ as a normal subgroup. This is a subgroup of $\Out(G(\R))$,
and therefore acts on representations, conjugacy classes, etc.

\begin{lemma}
  \label{l:Q}
  $Q(\R)\simeq\kernel(H^1(\Gamma,Z)\rightarrow H^1(\Gamma,G))$
\end{lemma}

This is well known:
the exact sequence $1\rightarrow Z \rightarrow G \rightarrow \Gad\rightarrow 1$
gives rise to the long exact sequence:
$$
1\rightarrow Z(\R) \rightarrow G(\R) \rightarrow \Gad(\R) \rightarrow H^1(\Gamma,Z)\rightarrow H^1(\Gamma,G)\rightarrow\dots
$$.
\section{The Main Result}

We're in the setting of the previous section:  $G(\R)$ is quasisplit, and has discrete series representations.

\begin{theorem}
  \label{t:main}
There are canonical bijections between the following sets.

\begin{enumerate}
\item Large discrete series representations in $\Pi$
\item Whittaker data for $G(\R)$
\item $(\Op\cap \s)/K$
\item  $(\Op\cap \g(\R))/G(\R)$
\end{enumerate}

The group $Q(\R)$ acts simply transitively on each of these sets, and the bijections commute with this action.
\end{theorem}

This is mostly an exercise in looking up some references.

\medskip

\begin{proof}
Suppose $\pi$ is a large discrete series representation.
We will show:
\begin{enumerate}
\item $\pi$ admits a Whittaker model for a unique choice of Whittaker datum;
\item $AV(\pi)$ is the closure of a $K$-orbit on $\Op\cap\s$;
\item $WF(\pi)$ is the closure of a $G(\R)$-orbit on $\Op\cap i\g(\R)$.
\end{enumerate}
This defines the maps from (1) to (2,3,4). The fact these are all bijections will follow from the action of $Q(\R)$.

By \cite{Vogan78} and \cite{kostant_whittaker}
a representation $\pi$ is large if and only if it admits a Whittaker model for some Whittaker datum,
and by \cite[Lemma 14.14]{abv} a  large discrete series representation admits a unique Whittaker datum.
This defines the map (1)$\mapsto$(2).

Suppose $\pi$ is a large irreducible representation.
By Lemma \ref{l:large} $\AV(\pi)$ is the union of a set of $K$-orbits on $\Op\cap\s$.
If $\pi$ is a discrete series representation $AV(\pi)$ is the closure of a single $K$-orbit on $\s$.
This defines the map (1)$\mapsto$(3).

By \cite{rossmann_limit_orbits}, $\WF(\pi)$ is the closure of a single orbit
so $\pi\mapsto WF(\pi)$ gives  (1)$\mapsto$(4).

The group $Q(\R)$ acts on  $(\g,K)$-modules, and preserves $\Pi$ and the property of being large.
Therefore, by \cite[(14.15)(d)]{abv}, it acts simply transitively on the set (1).
By \cite[(14.15)(c)]{abv} $Q(\R)$ acts simply transitively on the set (2).

It is well known that if $X\in\g$ is nilpotent then  $G\cdot X\cap \g(\R)/G(\R)$ is in bijection with
$\kernel(H^1(\Gamma,\Stab_G(X)) \rightarrow H^1(\Gamma,G))$. For example see \cite[Lemma 5.2]{galois}.
In the case of the principal nilpotent orbit $\Op$, $\Stab_G(X)$ is $Z(G)$ times a unipotent group,
which implies $H^1(\Gamma,\Stab_G(X))=H^1(\Gamma,Z)$. Therefore by Lemma \ref{l:Q} $Q(\R)$ acts simply transitively
on (4).
Finally the Kostant-Sekiguchi correspondence \cite{sekiguchi} is a bijection between (3) and (4).

Therefore $Q(\R)$ acts on the sets (1-4), and simply transitively on (1). The maps clearly commute with this action. This completes the proof.
\end{proof}

There is one obvious shortcoming of this result: we'd like to know that the Sekiguchi correspondence takes $\AV(\pi)$ to $\WF(\pi)$.
This is true by \cite{SV1} (and also follows in this special case by more elementary arguments). More generally we would like to describe the maps between the various sets more explicitly.

\section{Further results}

We describe maps between the sets (1-4) of Theorem \ref{t:main}.

\medskip

\noindent (2)$\leftrightarrow$(4)

First we describe the set of Whittaker data more explicitly.
Let $B$ be a Borel subgroup of $G$. Let $N$ be the nilradical of $B$, and $\overline N$ the opposite
nilpotent subgroup. Let $\n,\overline\n$ be the Lie algebras of $N,\overline N$.
If $B$ is defined over $\R$ we consider $N(\R),\n(\R), \overline\n(\R)$, etc.
Let $\kappa(\,,\,)$  be the Killing form. 
For $X\in i\overline \n(\R)$ define a unitary character $\psi_X$ of $N(\R)$ by:
$$
\psi_X(e^Y))=e^{2\pi \kappa(X,Y)}\quad(Y\in \n(\R)).
$$
The map $X\rightarrow \psi_X$ is an isomorphism between $i\overline\n(\R)$ and the unitary characters of $N(\R)$.
It is easy to see $\psi_X$ is non-degenerate if and only if $iX\in i\g(\R)$ is a principal nilpotent element.
In this case we write $(B(\R),X)$for the Whittaker datum $(B(\R),\psi_X)$.
It is clear that $(B(\R),X)\mapsto G(\R)\cdot X$ is a bijection between Whittaker data and
$(\Op(\R)\cap i\g(\R))/G(\R)$.

The main result of \cite{matumoto} (Theorem A) says:

\begin{lemma}[(2)$\leftrightarrow$(4)]  
The bijection (2)$\leftrightarrow$(4) takes the Whittaker datum $(B(\R),X)$ to
the principal orbit $G(\R)\cdot X\subset \Op\cap i\g(\R)$. 
 \end{lemma}

\medskip

\noindent (1)$\leftrightarrow$(3)
Suppose $\pi(\lambda)$ is a  discrete series representation. Choose a compact Cartan subgroup $T$, and let
$\lambda\in\t^*$ be the Harish-Chandra parameter of $\pi$. Let $\Delta$ be the set of roots of $\t$ in $\g$, and 
let $\Delta^+(\lambda)=\{\alpha\mid \langle\lambda,\ch\alpha\rangle>0$,
and let $S(\lambda)\in\Delta^+(\lambda)$ be the simple roots.
For $\alpha\in \Delta$ let $\g_\alpha$ be the corresponding root space, and choose a non-zero element $X_\alpha\in\g_\alpha$ for each $\alpha$.

\begin{lemma}[(1)$\leftrightarrow$(3)]
Suppose $\pi$ is a large discrete series representation with Harish-Chandra parameter $\lambda\in\t^*$.
Set

\begin{equation}
  \label{e:Epi}
  E_\pi=\sum_{\alpha\in S(\lambda)}X_\alpha\in \N.
\end{equation}

Then $E_\pi\in\s$ is a regular nilpotent element, and
$$
\AV(\pi)=\overline{K\cdot E_\pi}.
$$
\end{lemma}

\begin{proof}
If $\pi$ is any discrete series representation, with Harish-Chandra parameter $\lambda$, let
$\n=\sum_{\alpha\in\Delta^+(\lambda)}\g_\alpha$.
Then by \cite[Proposition 6.8]{vogan_irreducibility} $AV(\pi)=K\cdot(\n\cap\s)$.

Now assume $\pi$ is large. This implies $X_\alpha\in\s$ for all $\alpha\in S(\lambda)$, so $E_\pi\in \s$. 
By \cite{kostant_tds} $E_\alpha$ is a regular nilpotent element, so the closure of $K\cdot E_\alpha$ in $\s$ is $K\cdot(\n\cap\s)$. 
\end{proof}

\medskip

\noindent (3)$\leftrightarrow$(4)

This is the Kostant-Sekiguchi correspondence. We make this explicit, following \cite[Section 1]{avav}.

Suppose $E_\R\in \Op\cap i\g(\R)$. Then we may choose an $SL(2)$-triple $(H_\R,E_\R,F_\R)$ with $F_\R$  contained in $i\g(\R)$,
which implies $H_\R\in \g(\R)$. 
After conjugating by $G(\R)$ we may further assume $\theta(E_\R)=-F_\R$.
The Sekiguchi correspondence takes
$$
\Op\cap i\g(\R)\ni E_\R\mapsto E_\theta=\frac12(-iE_\R-iF_\R+H_\R)\in \N\cap \s.
$$

The map in the other direction of course the inverse. Given 
$E_\theta\in \Op\cap\s$, choose $(H_\theta,E_\theta,F_\theta)$, with
$F_\theta\in\s$, which implies $H_\theta\in\k$. After conjugating by $K$ we may further assume $\sigma(E_\theta)=F_\theta$.
The correspondence takes
$$
\Op\cap\s\ni E_\theta\mapsto E_\R=\frac i2(E_\theta-F_\theta-H_\theta)\in\N\cap i\g(\R).
$$

\medskip

\noindent (1)$\leftrightarrow$(4)

There are several ways to describe this bijection. We choose to compose the maps (1)$\leftrightarrow$(3)$\leftrightarrow$(4).
Here is the conclusion.

\begin{lemma}
  Let $\pi$ be a large discrete series representation.
Choose a compact Cartan subgroup $T$ and let $\lambda\in \t^*$ be the Harish-Chandra parameter of $\pi$.
Define $E_\theta=E_\pi$ as in \eqref{e:Epi}, and choose an $SL(2)$-triple $(H_\theta,E_\theta,F_\theta)$ as usual.
After conjugating by $K$ we may assume $\sigma(E_\theta)=F_\theta$.  Then
$$
\WF(\pi)=G(\R)\cdot\frac i2(E_\theta-F_\theta-H_\theta)\in\N\cap i\g(\R)
$$
Conversely if $E_\R\in \Op\cap i\g(\R)$, choose an $SL(2)$-triple $(H_\R,E_\R,F_\R)$ which (after conjugating by $G(\R)$) satisfies $\theta(E_\R)=-F_\R$.
Let
$$
H_\theta=E_\R-F_\R.
$$
Then $H_\theta\in\k$ is a regular semisimple element.
Set $\t=\Cent_{\g}(H_\theta)$, and let
$$
\Delta^+=\{\alpha\in\Delta(T,G)\mid  \alpha(H_\theta)>0\}
$$
Then $\pi$ is the discrete series representation in $\Pi$ whose Harish-Chandra parameter is dominant for $\Delta^+$. 
\end{lemma}

We can also express (1)$\mapsto$(4) using the {\it Kostant section}.

Suppose $\pi$ is a discrete series representation.
Choose a compact Cartan subgroup $T$, and let $\lambda\in\t^*$ be the Harish-Chandra parameter of $\pi$.
Identify $\lambda$ with an element $H_\pi\in i\t\subset i\g$ using the isomorphism $\t\simeq \t^*$ induced by the Killing form. 
Let $\O^{ss}_\pi=G(\R)\cdot H_\pi\subset i\g(\R)$. We write $ss$ to emphasize this is a semisimple orbit.

\begin{lemma}
  Suppose $\pi$ is a discrete series representation, and $E_\R\in\Op\cap i\g(\R)$.

  Then $WF(\pi)=\G(\R)\cdot E_\R$ if and only if
$\O^{ss}_\pi$ meets the Kostant section of $E_\R$.
\end{lemma}

\begin{proof}
  This is a simple restatement of the previous Lemma.  [details...]
\end{proof}

This confirms that  the corresponding statement  in the p-adic case \cite{debacker_reeder_generic} and \cite{kaletha_epipelagic}
applies to the real case as well.
\bibliographystyle{plain}
\bibliography{Refs}

\end{document}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: s_{1}:0 -> -1 6

### 2023-12-22 whittaker.tex
typos, Adams/Kaletha reference

@@
 Let $\g=\Lie(G), \g(\R)=\Lie(G(\R))$. Choose a Cartan involution $\theta$ for $G$. This means:
-$\theta$ is an algebraic involution; commuting with the anti-holomorphic involution $\sigma$ defining $G(\R)$;
+$\theta$ is an algebraic involution, commuting with the anti-holomorphic involution $\sigma$ defining $G(\R)$,
 and $G(\R)^\theta$ is a maximal compact subgroup of $G(\R)$. Set $K=G^\theta$, $K(\R)=G(\R)^\theta=K^\sigma$.
@@
 By a  {\it Whittaker datum} we mean a $G(\R)$-conjugacy class of pairs  $(B(\R),\eta)$ where $B(\R)$ is a
-Borel subgroup of $G(\R)$, and $\eta$
+Borel subgroup of $G(\R)$, 
 and $\eta$ is a non-degenerate character of the nilpotent radical $N(\R)$ of $B(\R)$. Non-degenerate means: non-trivial on each simple root space.
@@
 $K$-orbits on $\O\cap\s$.
-We have
 Then
@@
 $$
-\psi_X(e^Y))=e^{2\pi \kappa(X,Y)}\quad(Y\in \n(\R)).
+\psi_X(e^Y)=e^{2\pi \kappa(X,Y)}\quad(Y\in \n(\R)).
 $$
 The map $X\rightarrow \psi_X$ is an isomorphism between $i\overline\n(\R)$ and the unitary characters of $N(\R)$.
-It is easy to see $\psi_X$ is non-degenerate if and only if $iX\in i\g(\R)$ is a principal nilpotent element.
+It is easy to see $\psi_X$ is non-degenerate if and only if $X\in i\g(\R)$ is a principal nilpotent element.
 In this case we write $(B(\R),X)$for the Whittaker datum $(B(\R),\psi_X)$.
@@
 Suppose $\pi(\lambda)$ is a  discrete series representation. Choose a compact Cartan subgroup $T$, and let
-$\lambda\in\t^*$ be the Harish-Chandra parameter of $\pi$. Let $\Delta$ be the set of roots of $\t$ in $\g$, and 
-let $\Delta^+(\lambda)=\{\alpha\mid \langle\lambda,\ch\alpha\rangle>0$,
+$\lambda\in\t^*$ be the Harish-Chandra parameter of $\pi$. Let $\Delta$ be the set of roots of $\t$ in $\g$, 
+let $\Delta^+(\lambda)=\{\alpha\mid \langle\lambda,\ch\alpha\rangle>0\}$,
 and let $S(\lambda)\in\Delta^+(\lambda)$ be the simple roots.
@@
 Now assume $\pi$ is large. This implies $X_\alpha\in\s$ for all $\alpha\in S(\lambda)$, so $E_\pi\in \s$. 
-By \cite{kostant_tds} $E_\alpha$ is a regular nilpotent element, so the closure of $K\cdot E_\alpha$ in $\s$ is $K\cdot(\n\cap\s)$. 
+By \cite{kostant_tds} $E_\pi$ is a regular nilpotent element, so the closure of $K\cdot E_\pi$ in $\s$ is $K\cdot(\n\cap\s)$. 
 \end{proof}
@@
 
-The map in the other direction of course the inverse. Given 
+Computing the map in the other direction goes as follows.
 $E_\theta\in \Op\cap\s$, choose $(H_\theta,E_\theta,F_\theta)$, with
@@
 Identify $\lambda$ with an element $H_\pi\in i\t\subset i\g$ using the isomorphism $\t\simeq \t^*$ induced by the Killing form.
-Let $\O^{ss}_\pi=G(\R)\cdot H_\pi\subset i\g(\R)$. We write $ss$ to emphasize this is a semisimple orbit.
 
-\begin{lemma}
-  Suppose $\pi$ is a discrete series representation, and $E_\R\in\Op\cap i\g(\R)$.
-
-  Then $WF(\pi)=\G(\R)\cdot E_\R$ if and only if
-$\O^{ss}_\pi$ meets the Kostant section of $E_\R$.
-\end{lemma}
-
-\begin{proof}
-  This is a simple restatement of the previous Lemma.  [details...]
-\end{proof}
+\begin{proposition}[\cite{adams_kaletha}]
+Suppose $\pi$ is a generic discrete series representation. Then $\pi$ is $\w$-generic
+for a unique Whittaker datum $\w$.
+Write $\w=\w_X$ for some regular nilpotent element $X\in i\g(\R)$.
+Then $H_\pi$ is $G(\R)$-conjugate to an element of the Kostant section of $X$.
+\end{proposition}
 

### 2024-02-20 whittaker.tex
Test for new branch
Details added, slight reorganization, and questions

@@
 \usepackage{rotating}
+\usepackage{xcolor}
 \usepackage{amsmath}
+\usepackage{enumerate}
+\usepackage[colorlinks=true, linktoc=page, citecolor=blue, linkcolor=blue, urlcolor=blue]{hyperref}
+
 %\usepackage{showkeys}
@@
 \title{Whittaker Models for Real Groups}
-\author{Jeffrey Adams}
+\author{Jeffrey Adams + AA}
 \maketitle
 
-Let $G$ be a connected, complex reductive group, defined over $\R$, and suppose $G(\R)$ is quasisplit.
-We fix some notation.
-
-Let $\g=\Lie(G), \g(\R)=\Lie(G(\R))$. Choose a Cartan involution $\theta$ for $G$. This means:
-$\theta$ is an algebraic involution, commuting with the anti-holomorphic involution $\sigma$ defining $G(\R)$,
-and $G(\R)^\theta$ is a maximal compact subgroup of $G(\R)$. Set $K=G^\theta$, $K(\R)=G(\R)^\theta=K^\sigma$.
-Let $\s$ be the $-1$ eigenspace of $\theta$ acting on $\g$.
+Let $G$ be a connected complex reductive group, defined over $\R$, and suppose $G(\R)$ is quasisplit.
 
@@
 
+TODO: write about generic/large representations, and explain what's in the paper...
+
+\section{Some invariants of irreducible $(\g, K)$-modules}
+
+Suppose $\pi$ is an irreducible $(\g,K)$-module.
+Then we can associate to~$\pi$ several invariants, which depend only on the equivalence class of~$\pi$: the associated variety, the Gelfand---Kirillov dimension, and the wavefront set.
+We do not give full definitions, but try to point to convenient places in the literature.\footnote{AA 20-II-2024: of course if we write this, we should maybe add a few basic references for the notions.}
+
+\subsection{Some notation}
+
+Let~$\sigma$ be the anti-holomorphic involution defining~$G(\R)$. 
+Let $\g=\Lie(G), \g(\R)=\Lie(G(\R))$. Choose a Cartan involution $\theta$ for $G$. This means:
+$\theta$ is an algebraic involution, commuting with~$\sigma$,
+and $G(\R)^\theta$ is a maximal compact subgroup of~$G(\R)$. Set $K=G^\theta$, $K(\R)=G(\R)^\theta=K^\sigma$.
+Let $\s$ be the $-1$ eigenspace of $\theta$ acting on~$\g$.
+
 Let $\N$ be the set of nilpotent elements of $G$ on $\g$.
@@
 
-Suppose $\pi$ is an irreducible $(\g,K)$-module. Let $I_\pi$ be the annihlator of $\pi$ in the universal enveloping algebra.
+ \subsection{The invariants}
+
+Let $I_\pi$ be the annihlator of $\pi$ in the universal enveloping algebra.
 Let $\AVann(\pi)$ be the associated variety of $I_\pi$. 
 This is the closure of a single complex nilpotent orbit $\O$.
-Write $\GK(\pi)$ for the Gelfand-Kirillov dimension of $\pi$
-\cite{vogan-gelfand-kirillov}. 
-All dimensions are complex unless otherwise stated.
+
 The associated variety of $\pi$, denoted $\AV(\pi)$, is the  the union of a set of
 $K$-orbits on $\O\cap\s$.
-Then
+
+The Gelfand---Kirillov dimension~$\GK(\pi)$ of~$\pi$ can be defined in several different ways~\cite{vogan-gelfand-kirillov}; but one of them is
 $$
-GK(\pi)=\dim(AV(\pi))=\frac12\dim(\AVann(\pi)
+GK(\pi)=\dim(\AV(\pi))=\frac12\dim(\AVann(\pi)).
 $$
+(All dimensions are complex unless otherwise stated.)
+
 For all of these facts see \cite{vogan_bowdoin}, in particular Corollary 4.7 and Theorem 8.4.
 
-Set $N=\dim(\N)=\dim(G)-\mathrm{rank}(G)$. The maximal Gelfand-Kirillov dimension of a representation is $N/2$.
-We say $\pi$ is {\it large} if $\GK(\pi)=N/2$. See \cite[Section 6]{Vogan78}.
+Another invariant of an irreducible $(\g, K)$-module~$\pi$ is the \emph{wave-front set} of $\pi$, written $\WF(\pi)$. It is the union of a (finite) set of nilpotent $G(\R)$ orbits in
+$i\g(\R)^*=i\Hom_\R(\g(\R),\R)$.
+See \cite{howe_wave_front}, \cite{bv_local_structure}.\footnote{AA 14-II-2024: another convenient reference  for definitions re~$\WF(\pi)$ seems to be  Harris--He--Olafsson (Duke 2016).}
 
-The wave-front set of $\pi$, written $\WF(\pi)$, is the union of a (finite) set of nilpotent $G(\R)$ orbits in
-$i\g(\R)^*=i\Hom_\R(\g(\R),\R)$. See \cite{howe_wave_front}, \cite{bv_local_structure}.
+\subsection{Large representations} Set $N=\dim(\N)=\dim(G)-\mathrm{rank}(G)$. The maximal Gelfand--Kirillov dimension of a representation is $N/2$.
+We say $\pi$ is {\it large} if $\GK(\pi)=N/2$. See \cite[Section~6]{Vogan78}.
 
@@
 \item $\dim(\AVann(\pi))=N$;
-  \item $\dim(AV(\pi))=N/2$;
+  \item $\dim(\AV(\pi))=N/2$;
 \item $\GK(\pi)=N/2$;
@@
 
-Let $Z=Z(G)$ be the center of $G$, and $\Gad=G/Z$.
-Then $Z$ and $\Gad$ are defined over $\R$, and $Z(\R)=Z(G(\R))$.
-Set $G(\R)_{\mathrm{ad}}=G(\R)/Z(\R)$.
+\section{The dictionary for large discrete series}
+
+\subsection{Statement of the results}
+
+The following uses rather deep results of representation theory:
+\begin{proposition} Let~$\pi$ be the $(\g, K)$-module for a large discrete series representation of~$G(\R)$.  
+\begin{enumerate}[(a)]
+\item There is a unique Whittaker datum~$\mathfrak{w}$ such that~$\pi$ is $\mathfrak{w}$-generic.
+\item $\AV(\pi)$ is the closure of a single $K$-orbit on~$\mathcal{O}_p \cap \mathfrak{s}$.
+\item  $\WF(\pi)$ is the closure of a single $G(\R)$-orbit on $\mathcal{O}_p \cap  i \g(\R)$.
+\end{enumerate}
+\end{proposition}
+
+\begin{proof} For (a), by \cite{vogan-gelfand-kirillov} and \cite{kostant_whittaker}
+a representation $\pi$ is large if and only if it admits a Whittaker model for some Whittaker datum,
+and by \cite[Lemma 14.14]{abv} a  large discrete series representation admits a unique Whittaker datum.
+
+Part~(b) is one of the main results of~\cite{vogan_bowdoin}: see \cite[Theorem ?]{vogan_bowdoin}.\footnote{AA 19-II-2024: I'd welcome some help in navigating~\cite{vogan_bowdoin}: the relevant places seem to be  Sections 4, 5 and 8, but I have a few questions.}
+
+Part~(c) follows from~\cite{rossmann_limit_orbits}.\footnote{AA 14-II-2024: maybe a little more detail would be welcome, the Rossmann paper does not seem to state the result in these terms.}
+\end{proof}
+
+Given a large discrete series representation~$\pi$ we consider the invariants of~$\pi$ defined by the Proposition: a Whittaker datum  $\mathfrak{w}(\pi) \in \mathfrak{W}(G(\R))$, a $K$-orbit $\AV^\flat(\pi) \in (\mathcal{O}_p \cap \mathfrak{s})/K$  and a nilpotent $G(\R)$-orbit $\WF^\flat(\pi) \in (\mathcal{O}_p \cap  i \g(\R))/G(\R)$.
+
+Here is our main statement.
+
+\begin{theorem} \label{th:main} Suppose~$\Pi$ is an $L$-packet of discrete series for~$G(\R)$. 
+The maps $\pi \mapsto \mathfrak{w}(\pi)$, $\pi \mapsto \AV^\flat(\pi)$ and $\pi\mapsto \WF^\flat(\pi)$ induce bijections between:
+\begin{enumerate}
+\item[(1)] The set~$\Pi_{\mathrm{large}}$ of large discrete series representations in~$\Pi$ ;
+\item[(2)] The set of Whittaker data for $G(\R)$ ;
+\item[(3)] The set $(\Op \cap \s)/K$ of~$K$-orbits on $\mathcal{O}_p \cap \s$.
+\item[(4)] The set $(\Op \cap i\g(\R))/G(\R)$ of~$G(\R)$-orbits on $\mathcal{O}_p \cap  i \g(\R)$.
+\end{enumerate}
+\end{theorem}
+
+Before embarking on the proof, let us point out that the bijections are defined using rather deep results of representation theory.
+However, we shall prove in Section~\ref{sec:explicit} that all bijections $(i) \leftrightarrow (j)$, for $i,j \in \{(1), \dots, (4)\}$, can be spelled out in elementary terms.
+Furthermore we shall prove, using elementary arguments, that (3) $\leftrightarrow$ (4) coincides with the Kostant--Sekiguchi correspondence.
+
+Let us now explain the strategy of the proof, which is mainly an exercise in putting together some references that are rather scattered in the literature.
+What we shall actually do is: introduce a finite group~$Q(\R)$, and point out that
+\begin{itemize}
+\item[(i)] it acts simply transitively on the sets~(1)--(4), and 
+\item[(ii)] the maps $\pi \mapsto \mathfrak{w}(\pi)$, $\pi \mapsto \AV^\flat(\pi)$ and $\pi\mapsto \WF^\flat(\pi)$  are equivariant for these actions.
+\end{itemize}
+The theorem follows immediately from these two observations.
+
+\subsection{The group $Q(\R)$ and its actions} Let $Z=Z(G)$ be the center of $G$, and let $\Gad$ be the complex reductive group~$G/Z$.
+Then $Z$ and $\Gad$ are defined over $\R$, and $Z(\R)$ is equal to the center of $G(\R)$.
+We may view~$\Gad(\R)$ as the set of inner automorphisms of~$G$ which are defined over~$\R$, and this contains the group $G(\R)_{\mathrm{ad}}=G(\R)/Z(\R)$ as a normal subgroup of finite index\footnote{AA 15-II-2024: is there a trivial way to explain why finite index?}
 Define 
 $$
-Q(\R)=\Gad(\R)/G(\R)_{\mathrm{ad}}
+Q(\R)=\Gad(\R)/G(\R)_{\mathrm{ad}}.
 $$
-Thus $\Gad(\R)$ is the set of inner automorphisms of $G$ which are defined over $\R$, containing
-$G(\R)_{\mathrm{ad}}=G(\R)/Z(\R)$ as a normal subgroup. This is a subgroup of $\Out(G(\R))$,
-and therefore acts on representations, conjugacy classes, etc.
+This finite group may be viewed as a group of outer automorphisms of~$G(\R)$.
+
+\paragraph*{$\bullet$ Action on~(1)} Since~$Q(\R)$ can be viewed as a group of automorphisms of~$G(\R)$,  it has a canonical action on equivalence classes of $(\g, K)$-modules.\footnote{AA 15-II-2024: probably better to spell out the action.} This action preserves  the property of being large\footnote{AA 15-II-2024: should say something about this using the fact that it comes from automorphisms, either here or in the section on large reps}.
+It also preserves $L$-packets by~\cite[Lemma 6.18]{Contragredient}.
+
+\paragraph*{$\bullet$ Action on~(2)}  By definition of Whittaker data, the action of~$Q(\R)$ on $G(\R)$ induces a canonical action on the set of Whittaker data.
+By \cite[(14.15)]{abv} this action is simply transitive.
+
+It is an immediate consequence of the definitions that the map $\pi \mapsto \w(\pi)$, taking a large discrete series representation to the Whittaker datum for which it has a Whittaker model, is equivariant for the actions of $Q(\R)$ on (1) and (2).
+
+\paragraph*{$\bullet$ Action on~(4)} The actions of $Q(\R)$ on (3) and (4) both use an interpretation of $Q(\R)$ in terms of group cohomology.
+We begin with the action on (4), because the underlying ideas in Galois cohomology may be more familiar to some readers.
+
+We first recall some notation from group cohomology.
+Let~$\Gamma$ be the Galois group~$\Z/2\Z$ of~$\R$.
+When~$A$ is a group and $\tau$ is an involutive automorphism of~$A$, we may consider the cohomology sets $H^0_\tau(\Gamma, A)$ and $H^1_\tau(\Gamma, A)$ attached to the action of~$\Gamma$ on~$G$ using~$\tau$.
+These are pointed sets, and not groups in general if~$A$ isn't abelian.
+We may view $H^0_\tau(\Gamma, A)$ as the fixed-point-set $A^{\tau}$, and $H^1_\tau(\Gamma,A)$ as the quotient of $A^{-\tau} = \{ a \in A, a\tau(a)=1\}$ by the equivalence relation~$\sim$ generated by $a \sim x a \tau(x^{-1})$ for all $x \in G$.
+
+Let us now define the action of $Q(\R)$ on~(4). By definition we have the exact sequence $1\rightarrow Z \rightarrow G \rightarrow \Gad\rightarrow 1$. It 
+gives rise to a long exact sequence of pointed sets:
+\begin{equation} \label{long_ptset}
+1\rightarrow Z(\R) \rightarrow G(\R) \rightarrow \Gad(\R) \rightarrow H^1_\sigma(\Gamma,Z)\rightarrow H^1_\sigma(\Gamma,G)\rightarrow H^1_\sigma(\Gamma,\Gad).
+\end{equation}
+By definition the connecting map  $ \Gad(\R) \rightarrow H^1_\sigma(\Gamma,Z)$ sends $g \in \Gad(\R)$ to the equivalence class of $g \sigma(g^{-1})$ in $H^1_\sigma(\Gamma, Z)$.
+Going through the definitions we see that   two elements  $g_1, g_2$ have the same image if and only if $g_1 g_{2}\inv \in G(\R)_{\mathrm{ad}}$; therefore the image of the connecting map is in canonical bijection with $Q(\R)=\Gad(\R)/G(\R)_{\mathrm{ad}}$, and by exactness of~\eqref{long_ptset} we get:
 
@@
   \label{l:Q}
-  $Q(\R)\simeq\kernel(H^1(\Gamma,Z)\rightarrow H^1(\Gamma,G))$
+The above discussion determines a canonical bijection 
+ \[ Q(\R) \simeq\kernel(H^1_\sigma(\Gamma,Z)\rightarrow H^1_\sigma(\Gamma,G)).\]
 \end{lemma}
 
-This is well known:
-the exact sequence $1\rightarrow Z \rightarrow G \rightarrow \Gad\rightarrow 1$
-gives rise to the long exact sequence:
+Using this we define an action of~$Q(\R)$ on $(\Op \cap i\g(\R))/G(\R)$.
+Suppose~$X \in \g$ is nilpotent.
+Consider the intersection of the orbit $\Omega_X=\mathrm{Ad}(G) \cdot X$ with $\g(\R)$, and its decomposition into $G(\R)$-orbits.
+The map
+\begin{align*} (\Omega_{X} \cap \g(\R))/G(\R) & \to \kernel\left(H^1_\sigma(\Gamma,\mathrm{Stab}_G(X))\rightarrow H^1_\sigma(\Gamma,G)\right) \\ \mathrm{Ad}(g) \cdot X & \mapsto \text{class of $g^{-1} \sigma(g)$ in $H^1_\sigma(\Gamma,\mathrm{Stab}_G(X))$} \end{align*} is a bijection: see \cite[Lemma 5.2]{galois}.
+In the case where $X$ lies on the principal nilpotent orbit $\Op$, the stabilizer $\mathrm{Stab}_G(X)$ is the direct product of $Z(G)$ with a unipotent group\footnote{AA 19-II-2024: should we insert a reference?}, which implies $H^1(\Gamma, \mathrm{Stab}_G(X)) =H^1(\Gamma,Z)$.
+Using Lemma~\ref{l:Q}, we get a bijection $Q(\R) \leftrightarrow (\Op \cap i\g(\R))/G(\R)$, which depends only on the choice of~$X \in \Op$; and a simply transitive action of~$Q(\R)$ on~$(\Op \cap i\g(\R))/G(\R)$, which is entirely canonical.\footnote{AA 19-II-2023: we should say why the map $\pi \mapsto \WF(\pi)$ is equivariant for the action of $Q(\R)$ on both sides.
+You wrote this is obvious, but is it really obvious if we choose this description of the action?
+}
+
+\paragraph*{$\bullet$ Action on~(3)} The action of~$Q(\R)$ on (3) is defined similarly, using the version of group cohomology attached to the Cartan involution~$\theta$.
+As above the exact sequence $1\rightarrow Z \rightarrow G \rightarrow \Gad\rightarrow 1$
+gives rise to a long exact sequence of pointed sets
 $$
-1\rightarrow Z(\R) \rightarrow G(\R) \rightarrow \Gad(\R) \rightarrow H^1(\Gamma,Z)\rightarrow H^1(\Gamma,G)\rightarrow\dots
-$$.
-\section{The Main Result}
+1\rightarrow Z(\R) \rightarrow G(\R) \rightarrow \Gad(\R) \rightarrow H^1_\theta(\Gamma,Z)\rightarrow H^1_\theta(\Gamma,G)\rightarrow H^1_\theta(\Gamma,\Gad)
+$$
+and induces a canonical bijection $Q(\R) \simeq\kernel(H^1_\tau(\Gamma,Z)\rightarrow H^1_\tau(\Gamma,G))$ as in Lemma~\ref{l:Q}.
+We can use this to define an action of~$Q(\R)$ on $(\Op \cap \s)/K$: if~$X \in \Op \cap \s$ and we use the notation above, then by  \cite[Lemma 5.2]{galois} (applied using the Cartan involution~$\theta$ on~$G$, and the opposite of its differential on~$\mathfrak{s}$), the map
+\begin{align*} (\Op \cap \s)/K & \to \kernel\left(H^1_\theta(\Gamma,\mathrm{Stab}_G(X))\rightarrow H^1_\theta(\Gamma,G)\right) \\ \mathrm{Ad}^\ast(g) \cdot X & \mapsto \text{class of $g^{-1} \theta(g)$ in $H^1_\theta(\Gamma,\mathrm{Stab}_G(X))$} \end{align*} is a bijection.
+Putting this together we get a simply transitive action of~$Q(\R)$ on~$(\Op \cap\s)/K$.
+\footnote{AA 19-II-2023: should also say why the maps are equivariant. Is it obvious? At the moment I can't see it. We could always use Lemma~\ref{l:pi_to_av}.}
 
-We're in the setting of the previous section:  $G(\R)$ is quasisplit, and has discrete series representations.
+\section{Explicit versions of the dictionary}\label{sec:explicit}
 
-\begin{theorem}
-  \label{t:main}
-There are canonical bijections between the following sets.
-
-\begin{enumerate}
-\item Large discrete series representations in $\Pi$
-\item Whittaker data for $G(\R)$
-\item $(\Op\cap \s)/K$
-\item  $(\Op\cap \g(\R))/G(\R)$
-\end{enumerate}
-
-The group $Q(\R)$ acts simply transitively on each of these sets, and the bijections commute with this action.
-\end{theorem}
-
-This is mostly an exercise in looking up some references.
-
-\medskip
-
-\begin{proof}
-Suppose $\pi$ is a large discrete series representation.
-We will show:
-\begin{enumerate}
-\item $\pi$ admits a Whittaker model for a unique choice of Whittaker datum;
-\item $AV(\pi)$ is the closure of a $K$-orbit on $\Op\cap\s$;
-\item $WF(\pi)$ is the closure of a $G(\R)$-orbit on $\Op\cap i\g(\R)$.
-\end{enumerate}
-This defines the maps from (1) to (2,3,4). The fact these are all bijections will follow from the action of $Q(\R)$.
-
-By \cite{Vogan78} and \cite{kostant_whittaker}
-a representation $\pi$ is large if and only if it admits a Whittaker model for some Whittaker datum,
-and by \cite[Lemma 14.14]{abv} a  large discrete series representation admits a unique Whittaker datum.
-This defines the map (1)$\mapsto$(2).
-
-Suppose $\pi$ is a large irreducible representation.
-By Lemma \ref{l:large} $\AV(\pi)$ is the union of a set of $K$-orbits on $\Op\cap\s$.
-If $\pi$ is a discrete series representation $AV(\pi)$ is the closure of a single $K$-orbit on $\s$.
-This defines the map (1)$\mapsto$(3).
-
-By \cite{rossmann_limit_orbits}, $\WF(\pi)$ is the closure of a single orbit
-so $\pi\mapsto WF(\pi)$ gives  (1)$\mapsto$(4).
-
-The group $Q(\R)$ acts on  $(\g,K)$-modules, and preserves $\Pi$ and the property of being large.
-Therefore, by \cite[(14.15)(d)]{abv}, it acts simply transitively on the set (1).
-By \cite[(14.15)(c)]{abv} $Q(\R)$ acts simply transitively on the set (2).
-
-It is well known that if $X\in\g$ is nilpotent then  $G\cdot X\cap \g(\R)/G(\R)$ is in bijection with
-$\kernel(H^1(\Gamma,\Stab_G(X)) \rightarrow H^1(\Gamma,G))$. For example see \cite[Lemma 5.2]{galois}.
-In the case of the principal nilpotent orbit $\Op$, $\Stab_G(X)$ is $Z(G)$ times a unipotent group,
-which implies $H^1(\Gamma,\Stab_G(X))=H^1(\Gamma,Z)$. Therefore by Lemma \ref{l:Q} $Q(\R)$ acts simply transitively
-on (4).
-Finally the Kostant-Sekiguchi correspondence \cite{sekiguchi} is a bijection between (3) and (4).
-
-Therefore $Q(\R)$ acts on the sets (1-4), and simply transitively on (1). The maps clearly commute with this action. This completes the proof.
-\end{proof}
-
-There is one obvious shortcoming of this result: we'd like to know that the Sekiguchi correspondence takes $\AV(\pi)$ to $\WF(\pi)$.
-This is true by \cite{SV1} (and also follows in this special case by more elementary arguments). More generally we would like to describe the maps between the various sets more explicitly.
-
-\section{Further results}
-
-We describe maps between the sets (1-4) of Theorem \ref{t:main}.
-
-\medskip
-
-\noindent (2)$\leftrightarrow$(4)
+\subsection{From Whittaker data to real orbits ((2) $\leftrightarrow$ (4))}
 
@@
 It is easy to see $\psi_X$ is non-degenerate if and only if $X\in i\g(\R)$ is a principal nilpotent element.
-In this case we write $(B(\R),X)$for the Whittaker datum $(B(\R),\psi_X)$.
+In this case we write $(B(\R),X)$ for the Whittaker datum $(B(\R),\psi_X)$.
+
 It is clear that $(B(\R),X)\mapsto G(\R)\cdot X$ is a bijection between Whittaker data and
-$(\Op(\R)\cap i\g(\R))/G(\R)$.
+$(\Op(\R)\cap i\g(\R))/G(\R)$. The main result of \cite{matumoto} (Theorem A) says:
 
-The main result of \cite{matumoto} (Theorem A) says:
-
-\begin{lemma}[(2)$\leftrightarrow$(4)]  
+\begin{lemma}
 The bijection (2)$\leftrightarrow$(4) takes the Whittaker datum $(B(\R),X)$ to
-the principal orbit $G(\R)\cdot X\subset \Op\cap i\g(\R)$. 
+the principal orbit $G(\R)\cdot X$. 
  \end{lemma}
 
-\medskip
+\subsection{Connection between ((3) $\leftrightarrow$ (4)) and the Kostant--Sekiguchi correspondence }
 
-\noindent (1)$\leftrightarrow$(3)
+\begin{lemma} The bijection (3)--(4) is induced by the Kostant--Sekiguchi correspondence.
+\end{lemma}
+
+\begin{proof} If we allow ourselves to use deep results, then this is a particular case of the main theorem of~\cite{SV1} (Theorem 1.4).
+In a perfect world, we could also give a more elementary argument, using the description of the Kostant--Sekiguchi correspondence in~\cite{galois} and the descriptions of the actions above; but  I'm not sure it's possible to do it without encountering a basepoint issue.\end{proof}
+
+As a consequence we can make the bijection (3) $\leftrightarrow$ (4) explicit, following \cite[Section~1]{avav}.
+
+Concerning the second point, suppose $E_\R\in \Op\cap i\g(\R)$. Then we may choose an $SL(2)$-triple $(H_\R,E_\R,F_\R)$ with $F_\R$  contained in $i\g(\R)$,
+which implies $H_\R\in \g(\R)$. 
+After conjugating by $G(\R)$ we may further assume $\theta(E_\R)=-F_\R$.
+The Sekiguchi correspondence takes
+$$
+\Op\cap i\g(\R)\ni E_\R\mapsto E_\theta=\frac12(-iE_\R-iF_\R+H_\R)\in \N\cap \s.
+$$
+
+Computing the map in the other direction goes as follows.
+$E_\theta\in \Op\cap\s$, choose $(H_\theta,E_\theta,F_\theta)$, with
+$F_\theta\in\s$, which implies $H_\theta\in\k$. After conjugating by $K$ we may further assume $\sigma(E_\theta)=F_\theta$.
+The correspondence takes
+$$
+\Op\cap\s\ni E_\theta\mapsto E_\R=\frac i2(E_\theta-F_\theta-H_\theta)\in\N\cap i\g(\R).
+$$
+
+\subsection{From large discrete series to $K$-orbits ((1) $\leftrightarrow$ (3))}
+
 Suppose $\pi(\lambda)$ is a  discrete series representation. Choose a compact Cartan subgroup $T$, and let
@@
 
-\begin{lemma}[(1)$\leftrightarrow$(3)]
+\begin{lemma}[(1)$\leftrightarrow$(3)]\label{l:pi_to_av}
 Suppose $\pi$ is a large discrete series representation with Harish-Chandra parameter $\lambda\in\t^*$.
@@
 If $\pi$ is any discrete series representation, with Harish-Chandra parameter $\lambda$, let
-$\n=\sum_{\alpha\in\Delta^+(\lambda)}\g_\alpha$.
-Then by \cite[Proposition 6.8]{vogan_irreducibility} $AV(\pi)=K\cdot(\n\cap\s)$.
+$\n_{\lambda}=\sum_{\alpha\in\Delta^+(\lambda)}\g_\alpha$.
+Then by \cite[Proposition 6.8]{vogan_irreducibility} $AV(\pi)=K\cdot(\n_\lambda\cap\s)$.
 
 Now assume $\pi$ is large. This implies $X_\alpha\in\s$ for all $\alpha\in S(\lambda)$, so $E_\pi\in \s$. 
-By \cite{kostant_tds} $E_\pi$ is a regular nilpotent element, so the closure of $K\cdot E_\pi$ in $\s$ is $K\cdot(\n\cap\s)$. 
+By~\cite{kostant_tds} $E_\pi$ is a regular nilpotent element, so the closure of $K\cdot E_\pi$ in $\s$ is equal to $K\cdot(\n_\lambda\cap\s)$. 
 \end{proof}
 
-\medskip
-
-\noindent (3)$\leftrightarrow$(4)
-
-This is the Kostant-Sekiguchi correspondence. We make this explicit, following \cite[Section 1]{avav}.
-
-Suppose $E_\R\in \Op\cap i\g(\R)$. Then we may choose an $SL(2)$-triple $(H_\R,E_\R,F_\R)$ with $F_\R$  contained in $i\g(\R)$,
-which implies $H_\R\in \g(\R)$. 
-After conjugating by $G(\R)$ we may further assume $\theta(E_\R)=-F_\R$.
-The Sekiguchi correspondence takes
-$$
-\Op\cap i\g(\R)\ni E_\R\mapsto E_\theta=\frac12(-iE_\R-iF_\R+H_\R)\in \N\cap \s.
-$$
-
-Computing the map in the other direction goes as follows.
-$E_\theta\in \Op\cap\s$, choose $(H_\theta,E_\theta,F_\theta)$, with
-$F_\theta\in\s$, which implies $H_\theta\in\k$. After conjugating by $K$ we may further assume $\sigma(E_\theta)=F_\theta$.
-The correspondence takes
-$$
-\Op\cap\s\ni E_\theta\mapsto E_\R=\frac i2(E_\theta-F_\theta-H_\theta)\in\N\cap i\g(\R).
-$$
-
-\medskip
-
-\noindent (1)$\leftrightarrow$(4)
+\subsection{From large discrete series to real orbits ((1) $\leftrightarrow$ (4))}
 
@@
 Define $E_\theta=E_\pi$ as in \eqref{e:Epi}, and choose an $SL(2)$-triple $(H_\theta,E_\theta,F_\theta)$ as usual.
-After conjugating by $K$ we may assume $\sigma(E_\theta)=F_\theta$.  Then
+After conjugating by $K$ we may assume $\sigma(E_\theta)=F_\theta$.  Then\footnote{AA 14-II-2023: no closure?}
 $$
@@
 
-We can also express (1)$\mapsto$(4) using the {\it Kostant section}.
+We can also express (1)$\mapsto$(4) using the {\it Kostant section}.\footnote{14-II-2024: we could spell out the definition, it seems this can be done quickly as in Adams--Kaletha. }
 
@@
 
-This confirms that  the corresponding statement  in the p-adic case \cite{debacker_reeder_generic} and \cite{kaletha_epipelagic}
+This confirms that  the corresponding statement  in the $p$-adic case \cite{debacker_reeder_generic, kaletha_epipelagic}
 applies to the real case as well.
+
 \bibliographystyle{plain}

### 2024-02-23 whittaker.tex
Add small comments

@@
 \newcommand{\Op}{\O_p}
+\newcommand{\Kostant}[1]{\mathcal{K}(#1)}
+
 \begin{document}
@@
 
-There are several ways to describe this bijection. We choose to compose the maps (1)$\leftrightarrow$(3)$\leftrightarrow$(4).
+There are several ways to describe this bijection.\footnote{AA 23-II-2024: it might be nice to mention the version with the asymptotic cone of the orbit of~$H_\pi$, which is extremely clean and concrete.
+} We choose to compose the maps (1)$\leftrightarrow$(3)$\leftrightarrow$(4).
 Here is the conclusion.
@@
 
-We can also express (1)$\mapsto$(4) using the {\it Kostant section}.\footnote{14-II-2024: we could spell out the definition, it seems this can be done quickly as in Adams--Kaletha. }
+We can also express (1)$\mapsto$(4) using the {\it Kostant section}.
+Recall that if~$X$ is a regular nilpotent element of~$\g$ and fits into an $\SL(2)$-triple $(X, H, Y)$, the Kostant section~$\Kostant{X}$ is the affine subspace $X + \mathrm{Cent}_{\g}(Y)$ of~$\g$.
+It depends on the choice of $\SL(2)$-triple, but if $X \in \g(\R)$, then the $G(\R)$-conjugacy class of~$\Kostant{X}$ depends only on the $G(\R)$-conjugacy class of~$X$.
 
@@
 Write $\w=\w_X$ for some regular nilpotent element $X\in i\g(\R)$.
-Then $H_\pi$ is $G(\R)$-conjugate to an element of the Kostant section of $X$.
+Then $H_\pi$ is $G(\R)$-conjugate to an element of the Kostant section of $X$.\footnote{AA 23-II-2024: would probably be useful to explain the connection with $\pi \mapsto \WF(\pi)$ in more detail...}
 \end{proposition}

### 2024-02-23 whittaker.tex
Tiny tinkering

@@
 
-Let $\N$ be the set of nilpotent elements of $G$ on $\g$.
+Let $\N$ be the set of nilpotent elements of $\g$.
 This is the closure of the principal nilpotent orbit $\Op$.
@@
 \begin{proof} If we allow ourselves to use deep results, then this is a particular case of the main theorem of~\cite{SV1} (Theorem 1.4).
-In a perfect world, we could also give a more elementary argument, using the description of the Kostant--Sekiguchi correspondence in~\cite{galois} and the descriptions of the actions above; but  I'm not sure it's possible to do it without encountering a basepoint issue.\end{proof}
+In a perfect world, we could also give a more elementary argument, using the description of the Kostant--Sekiguchi correspondence in~\cite{galois} and the descriptions of the actions above; but  I'm not sure it's possible to do it without encountering a basepoint issue.
+Another possibility, suggested by Jeff, is to extract it from some arguments in Adams--Kaletha (e.g.
+the fact that $\WF(\pi)$ is the asymptotic cone of the $G(\R)$-orbit of the HC parameter of~$\pi$, or the connection with the Kostant section).
+\end{proof}
 
@@
 
-Concerning the second point, suppose $E_\R\in \Op\cap i\g(\R)$. Then we may choose an $SL(2)$-triple $(H_\R,E_\R,F_\R)$ with $F_\R$  contained in $i\g(\R)$,
+Suppose $E_\R\in \Op\cap i\g(\R)$. Then we may choose an $SL(2)$-triple $(H_\R,E_\R,F_\R)$ with $F_\R$  contained in $i\g(\R)$,
 which implies $H_\R\in \g(\R)$. 
-After conjugating by $G(\R)$ we may further assume $\theta(E_\R)=-F_\R$.
-The Sekiguchi correspondence takes
+After conjugating by~$G(\R)$ we may further assume $\theta(E_\R)=-F_\R$.
+The Sekiguchi correspondence takes the $G(\R)$-orbit of~$E_\R$ to the $K$-orbit of
 $$
-\Op\cap i\g(\R)\ni E_\R\mapsto E_\theta=\frac12(-iE_\R-iF_\R+H_\R)\in \N\cap \s.
+E_\theta=\frac12(-iE_\R-iF_\R+H_\R)\in \N\cap \s.
 $$
@@
 Computing the map in the other direction goes as follows.
-$E_\theta\in \Op\cap\s$, choose $(H_\theta,E_\theta,F_\theta)$, with
+Suppose $E_\theta\in \Op\cap\s$. Choose an $SL(2)$-triple  $(E_\theta H_\theta,F_\theta)$ with
 $F_\theta\in\s$, which implies $H_\theta\in\k$. After conjugating by $K$ we may further assume $\sigma(E_\theta)=F_\theta$.
-The correspondence takes
+Then the Sekiguchi correspondence takes the $K$-orbit of $E_\theta$ to the $G(\R)$-orbit of 
 $$
-\Op\cap\s\ni E_\theta\mapsto E_\R=\frac i2(E_\theta-F_\theta-H_\theta)\in\N\cap i\g(\R).
+E_\R=\frac i2(E_\theta-F_\theta-H_\theta)\in\N\cap i\g(\R).
 $$
@@
 
-Suppose $\pi(\lambda)$ is a  discrete series representation. Choose a compact Cartan subgroup $T$, and let
+Suppose $\pi$ is a  discrete series representation. Choose a compact Cartan subgroup $T$, and let
 $\lambda\in\t^*$ be the Harish-Chandra parameter of $\pi$. Let $\Delta$ be the set of roots of $\t$ in $\g$, 

### 2024-02-23 whittaker.tex
Significant update to the action of Q(R) on real orbits

@@
 \title{Whittaker Models for Real Groups}
-\author{Jeffrey Adams + AA}
+\author{Jeffrey Adams \& Alexandre Afgoustidis}
 \maketitle
@@
 
-Before embarking on the proof, let us point out that the bijections are defined using rather deep results of representation theory.
+Before embarking on the proof, let us point out that the maps in the theorem are defined using rather deep results of representation theory.
 However, we shall prove in Section~\ref{sec:explicit} that all bijections $(i) \leftrightarrow (j)$, for $i,j \in \{(1), \dots, (4)\}$, can be spelled out in elementary terms.
@@
 
-\paragraph*{$\bullet$ Action on~(4)} The actions of $Q(\R)$ on (3) and (4) both use an interpretation of $Q(\R)$ in terms of group cohomology.
-We begin with the action on (4), because the underlying ideas in Galois cohomology may be more familiar to some readers.
+\paragraph*{$\bullet$ Action on~(4)} The actions of $Q(\R)$ on (3) and (4) are quite similar, and the proof that they are simply transitive use an interpretation of $Q(\R)$ in terms of group cohomology.
 
-We first recall some notation from group cohomology.
+We begin with the case of the wave-front set (4), because the underlying ideas in Galois cohomology may be more familiar to some readers.
+
+To define the action of~$Q(\R)$ on~(4), first observe that~$\Gad$ acts on~$\g$ by the adjoint action.
+This action preserves~$\Op$, and the restriction to~$\Gad(\R)$ preserves~$\Op\cap (i\g(\R))$.
+Since elements on a given~$G(\R)_{\mathrm{ad}}$-orbit are in the same~$G(\R)$-orbit, this induces an action of $Q(\R)=\Gad(\R)/G(\R)_{\mathrm{ad}}$ on~$\Op\cap (i\g(\R))/G(\R)$.
+
+\begin{proposition}
+\begin{enumerate} 
+\item The action of~$Q(\R)$ on $\Op\cap (i\g(\R))/G(\R)$ is simply transitive.
+\item The map $\pi \mapsto \WF(\pi)$ is $Q(\R)$-equivariant.
+\end{enumerate}
+\end{proposition}
+
+The proof of~(1) uses group comology, and we first recall some general notation.
 Let~$\Gamma$ be the Galois group~$\Z/2\Z$ of~$\R$.
@@
 
-Let us now define the action of $Q(\R)$ on~(4). By definition we have the exact sequence $1\rightarrow Z \rightarrow G \rightarrow \Gad\rightarrow 1$. It 
+We can use group cohomology to define an action of $Q(\R)$ on~(4). By definition we have the exact sequence $1\rightarrow Z \rightarrow G \rightarrow \Gad\rightarrow 1$. It 
 gives rise to a long exact sequence of pointed sets:
@@
 The above discussion determines a canonical bijection 
- \[ Q(\R) \simeq\kernel(H^1_\sigma(\Gamma,Z)\rightarrow H^1_\sigma(\Gamma,G)).\]
+ \begin{equation}\label{bij_q_1} Q(\R) \leftrightarrow \kernel(H^1_\sigma(\Gamma,Z)\rightarrow H^1_\sigma(\Gamma,G)).\end{equation}
 \end{lemma}
@@
 The map
-\begin{align*} (\Omega_{X} \cap \g(\R))/G(\R) & \to \kernel\left(H^1_\sigma(\Gamma,\mathrm{Stab}_G(X))\rightarrow H^1_\sigma(\Gamma,G)\right) \\ \mathrm{Ad}(g) \cdot X & \mapsto \text{class of $g^{-1} \sigma(g)$ in $H^1_\sigma(\Gamma,\mathrm{Stab}_G(X))$} \end{align*} is a bijection: see \cite[Lemma 5.2]{galois}.
+\begin{align} \label{bij_q_2}\beta_X\colon (\Omega_{X} \cap \g(\R))/G(\R) & \to \kernel\left(H^1_\sigma(\Gamma,\mathrm{Stab}_G(X))\rightarrow H^1_\sigma(\Gamma,G)\right) \\ \mathrm{Ad}(g) \cdot X & \mapsto \text{class of $ g\sigma(g^{-1})$ in $H^1_\sigma(\Gamma,\mathrm{Stab}_G(X))$} \nonumber \end{align}
+is a bijection: see \cite[Lemma 5.2]{galois}. 
 In the case where $X$ lies on the principal nilpotent orbit $\Op$, the stabilizer $\mathrm{Stab}_G(X)$ is the direct product of $Z(G)$ with a unipotent group\footnote{AA 19-II-2024: should we insert a reference?}, which implies $H^1(\Gamma, \mathrm{Stab}_G(X)) =H^1(\Gamma,Z)$.
-Using Lemma~\ref{l:Q}, we get a bijection $Q(\R) \leftrightarrow (\Op \cap i\g(\R))/G(\R)$, which depends only on the choice of~$X \in \Op$; and a simply transitive action of~$Q(\R)$ on~$(\Op \cap i\g(\R))/G(\R)$, which is entirely canonical.\footnote{AA 19-II-2023: we should say why the map $\pi \mapsto \WF(\pi)$ is equivariant for the action of $Q(\R)$ on both sides.
-You wrote this is obvious, but is it really obvious if we choose this description of the action?
-}
+Using Lemma~\ref{l:Q}, we get a bijection
+\[\Delta_X\colon (\Op \cap i\g(\R))/G(\R) \leftrightarrow Q(\R).\]
+This bijection depends  on the choice of~$X \in \Op$; but it defines a simply transitive action of~$Q(\R)$ on~$(\Op \cap i\g(\R))/G(\R)$, which is independent of the choice of~$X$.
+
+Let us now prove the Proposition.
+
+First we prove that~$Q(\R)$ acts freely on the set a  $(\Op \cap i\g(\R))/G(\R)$ of orbits.
+Let~$\omega$ be an orbit, and let~$X$ be a point of~$\omega$.
+If~$q$ is an element of~$Q(\R)$, then going through the definitions of~\eqref{bij_q_1}--\eqref{bij_q_2} we see that~$\Delta_X(q \cdot \omega) = q$; therefore if~$q\cdot \omega=\omega$, then~$q=1$.
+
+Next we prove that the action is transitive.
+Let~$\omega, \omega'$ be $G(\R)$-orbits in  $(\Op \cap i\g(\R))$.
+Fix an element~$X$ of~$\omega$ and consider the bijections~$\beta_X$ and~$\Delta_X$ above.
+Let~$q \in Q(\R)$ be the element~$\Delta_X(\omega')$.
+We have seen that $q = \Delta_X(q \cdot \omega)$, therefore \mbox{$\Delta_X(q \cdot \omega)=\Delta_X(\omega')$}, which proves~$q \cdot \omega = \omega'$ and concludes the proof of~(1).
+
+For the proof of part~(2) of the proposition, use the asymptotic cone.
 

### 2024-03-27 whittaker.tex
Wrote up the action of Q(R) on K-orbits, and the Cartan cohomology argument

@@
 \usepackage{amsmath}
+\usepackage{mathrsfs}
 \usepackage{enumerate}
@@
 \newcommand{\Ad}{\mathrm{Ad}}
+\newcommand{\ad}{\mathrm{ad}}
 \newcommand{\zinv}{\mathrm{inv}}
@@
 \newcommand{\WF}{\mathrm{WF}}
+\newcommand{\AC}{\mathrm{AC}}
 \newcommand{\AVann}{\mathrm{AV}_{\mathrm{ann}}}
@@
 Then $Z$ and $\Gad$ are defined over $\R$, and $Z(\R)$ is equal to the center of $G(\R)$.
-We may view~$\Gad(\R)$ as the set of inner automorphisms of~$G$ which are defined over~$\R$, and this contains the group $G(\R)_{\mathrm{ad}}=G(\R)/Z(\R)$ as a normal subgroup of finite index\footnote{AA 15-II-2024: is there a trivial way to explain why finite index?}
+We may view~$\Gad(\R)$ as the set of inner automorphisms of~$G$ which are defined over~$\R$, and this contains the group $G(\R)_{\mathrm{ad}}=G(\R)/Z(\R)$ as a normal subgroup of finite index\footnote{AA 15-II-2024: is there a trivial way to explain why finite index?}.
 Define 
@@
 \paragraph*{$\bullet$ Action on~(4)} The actions of $Q(\R)$ on (3) and (4) are quite similar, and the proof that they are simply transitive use an interpretation of $Q(\R)$ in terms of group cohomology.
-
-We begin with the case of the wave-front set (4), because the underlying ideas in Galois cohomology may be more familiar to some readers.
+We begin with the case of the wave-front set (4), because the argument a more familiar version of  Galois cohomology.
 
 To define the action of~$Q(\R)$ on~(4), first observe that~$\Gad$ acts on~$\g$ by the adjoint action.
-This action preserves~$\Op$, and the restriction to~$\Gad(\R)$ preserves~$\Op\cap (i\g(\R))$.
+This action preserves~$\Op$, and its restriction to~$\Gad(\R)$ preserves~$\Op\cap (i\g(\R))$.
 Since elements on a given~$G(\R)_{\mathrm{ad}}$-orbit are in the same~$G(\R)$-orbit, this induces an action of $Q(\R)=\Gad(\R)/G(\R)_{\mathrm{ad}}$ on~$\Op\cap (i\g(\R))/G(\R)$.
 
-\begin{proposition}
+\begin{proposition}\label{prop:action_on_real_orbits}
 \begin{enumerate} 
@@
 
-The proof of~(1) uses group comology, and we first recall some general notation.
+The proof of~(1) uses group cohomology, and we first recall some general notation.
 Let~$\Gamma$ be the Galois group~$\Z/2\Z$ of~$\R$.
@@
 
+An important point is that this action coincides with that defined before the statement of the Proposition.
+\textcolor{blue}{TODO: explain why.
+Basically the reason is that if we hit $X$ with $q_1q_2$ on the LHS of~\eqref{bij_q_2}, then then going through the definitions this goes to the element~$q_1q_2$ of~$Q(\R)$.}
+
 Let us now prove the Proposition.
@@
 
-For the proof of part~(2) of the proposition, use the asymptotic cone.
+Part~(2) of the proposition is comes from general properties of the wavefront set in microlocal analysis, and from the fact that the action of $Q(\R)$ comes from automorphisms of~$G(\R)$.
+More precisely, if~$q$ is an element of~$Q(\R)$ and $\tilde{q}$ is a representative of~$q$ in $\Gad(\R)$, then the action of~$q$ on equivalence classes of $(\g, K)$-modules comes from the action of the automorphism $\mathrm{int}(\tilde{q})$ of~$G(\R)$ on $(\g, K)$-modules.
+Now the wavefront set of a distribution on a manifold satisfies general covariance properties under diffeomorphisms of the manifold: this follows from Hörmander's original definitions, see e.g.
+\cite[Section 2, p.~800]{HarrisHeOlafsson}.
+Applying this to the present situation, and going through the basics as in   \cite[Section 2]{HarrisHeOlafsson}, it immediately follows that $\pi \mapsto \WF(\pi)$ is equivariant under $Q(\R)$, and this concludes the proof of Proposition~\ref{prop:action_on_K_orbits}.
 
-\paragraph*{$\bullet$ Action on~(3)} The action of~$Q(\R)$ on (3) is defined similarly, using the version of group cohomology attached to the Cartan involution~$\theta$.
-As above the exact sequence $1\rightarrow Z \rightarrow G \rightarrow \Gad\rightarrow 1$
-gives rise to a long exact sequence of pointed sets
-$$
-1\rightarrow Z(\R) \rightarrow G(\R) \rightarrow \Gad(\R) \rightarrow H^1_\theta(\Gamma,Z)\rightarrow H^1_\theta(\Gamma,G)\rightarrow H^1_\theta(\Gamma,\Gad)
-$$
-and induces a canonical bijection $Q(\R) \simeq\kernel(H^1_\tau(\Gamma,Z)\rightarrow H^1_\tau(\Gamma,G))$ as in Lemma~\ref{l:Q}.
-We can use this to define an action of~$Q(\R)$ on $(\Op \cap \s)/K$: if~$X \in \Op \cap \s$ and we use the notation above, then by  \cite[Lemma 5.2]{galois} (applied using the Cartan involution~$\theta$ on~$G$, and the opposite of its differential on~$\mathfrak{s}$), the map
-\begin{align*} (\Op \cap \s)/K & \to \kernel\left(H^1_\theta(\Gamma,\mathrm{Stab}_G(X))\rightarrow H^1_\theta(\Gamma,G)\right) \\ \mathrm{Ad}^\ast(g) \cdot X & \mapsto \text{class of $g^{-1} \theta(g)$ in $H^1_\theta(\Gamma,\mathrm{Stab}_G(X))$} \end{align*} is a bijection.
-Putting this together we get a simply transitive action of~$Q(\R)$ on~$(\Op \cap\s)/K$.
-\footnote{AA 19-II-2023: should also say why the maps are equivariant. Is it obvious? At the moment I can't see it. We could always use Lemma~\ref{l:pi_to_av}.}
+\paragraph*{$\bullet$ Action on~(3)} We turn to the action of~$Q(\R)$ on $(\Op \cap \s)/K$, and to the associated variety.
+For this it is convenient to use an isomorphic variant of~$Q(\R)$, defined in terms of~$K$ rather than~$G(\R)$.
+
+Since the Cartan involution $\theta$ is an automorphism of~$G$, it preserves the center~$Z=Z(G)$, and induces an involution~$\theta_{\ad}$ of~$\Gad=G/Z$.
+Let $Z_K$ be the intersection $Z \cap K$, and let $K_{\ad}$ be the quotient $K/Z_K$.
+The natural map $K \mapsto \Gad$, induced by the inclusion $K \hookrightarrow G$, maps~$K$ to a subgroup of~$\Gad^{\theta_{\ad}}$, and has kernel~$Z_K$.
+Therefore it factors to an injective morphism $\iota\colon \Kad \hookrightarrow\Gad^{\theta_{\ad}} $.
+The image of~$\iota$ is a normal subgroup of~$\Gad^{\theta_{\ad}}$; using it we will identify $\Kad$ with a normal subgroup of $\Gad^{\theta_{\ad}}$.
+Define
+\[ Q'(\R) = \Gad^{\theta_{\ad}}/\Kad.\]
+
+\begin{lemma}\label{lem:q_and_qprime}
+\begin{enumerate}
+\item Every element of $Q(R)=\Gad(\R)/G(\R)_{\ad}$ has a $\theta_\ad$-invariant representative in $\Gad(\R)$.
+\item Given $q \in Q(\R)$, and a $\theta_{\ad}$-invariant representative~$\tilde{q}$ of~$q$, the image of~$\tilde{q}$ in~$Q'(\R)$ depends only on~$q$ and not on the choice of~$\tilde{q}$.
+Denote this image by~$\Psi(q)$; then $q \mapsto \Psi(q)$ is an isomorphism between $Q(\R)$ and~$Q'(\R)$.
+\end{enumerate}
+\end{lemma}
+
+\begin{proof} \textcolor{red}{TODO!}\end{proof}
+
+To define the  action of~$Q(\R)$ on $(\Op \cap \s)/K$, we point out that $Q'(\R)$ acts on $\Op \cap \s$ and that this action preserves the $K$-orbits.
+First, the adjoint action of~$\Gad$ on~$\g$ preserves both $\Op$ and~$\s$.
+Second, the action of~$K$ on $\Op \cap \s$ is trivial on~$Z_K$, and factors through an action of~$\Kad$.
+It is then easy to check that if two elements of $\Op \cap \s$ lie in on the same $\Kad$-orbit, then for every $g \in \Gad^{\theta_{\ad}}$, the elements  $\tilde{g} \cdot x$ and $\tilde{g} \cdot y$ lie on the same $\Kad$-orbit.
+This determines an action of~$Q'(\R)$ on~$(\Op \cap \s)/K$, and by Lemma~\ref{lem:q_and_qprime} we get an action of~$Q(\R)$ on~$(\Op \cap \s)/K$.
+This is the action featured in the following statement:
+
+\begin{proposition}\label{prop:action_on_K_orbits}
+\begin{enumerate} 
+\item The action of~$Q(\R)$ on $(\Op \cap \s)/K$ is simply transitive.
+\item The map $\pi \mapsto \AV(\pi)$ is $Q(\R)$-equivariant.
+\end{enumerate}
+\end{proposition}
+
+The proof is similar to that of Proposition~\ref{prop:action_on_real_orbits}, but we need to use the version of Galois cohomology attached to the Cartan involution $\theta$.
+Taking up the above notation on Galois cohomology, the exact sequence $1\rightarrow Z \rightarrow G \rightarrow \Gad\rightarrow 1$ gives rise to a long exact sequence of pointed sets:
+\begin{equation} \label{long_ptset_theta}
+1\rightarrow Z_K \rightarrow K \rightarrow \Gad^{\theta_{\ad}} \rightarrow H^1_\theta(\Gamma,Z)\rightarrow H^1_\theta(\Gamma,G)\rightarrow H^1_{\theta_{\ad}}(\Gamma,\Gad).
+\end{equation}
+As in Lemma~\ref{l:Q}  this determines a bijection $Q'(\R) \leftrightarrow \kernel(H^1_\theta(\Gamma,Z)\rightarrow H^1_{\theta}(\Gamma,G))$.
+The argument for part~(1) of Proposition~\ref{prop:action_on_real_orbits} works seamlessly if we replace~$\sigma$ with~$\theta$, and proves that the action of~$Q'(\R)$ on $(\Op \cap \s)/K$ is simply transitive.
+Since the action of~$Q(\R)$ is defined by transport of structure from that of~$Q'(\R)$, this proves~(1).
+
+As for~(2), it is again an immediate consequence of the precise definition of the associated variety.
+Stating this needs a little more care, since it is not obvious that $\Gad$ acts on representations of~$G(\R)$.
+However, the adjoint action of~$\Gad^{\theta_{\ad}}$ on $G$ preserves $K$; this this induces an action of~$\Gad^{\theta_{\ad}}$ on $(\g, K)$-modules.
+The restriction of that action to~$\Kad$ is trivial, and this gives an action of $Q'(\R)$ acts on equivalence classes of $(\g, K)$-modules.
+Now, the definition of the associated variety uses filtrations (see the Introduction of~\cite{vogan_bowdoin}) which are all invariant under $\Gad^{\theta_\ad}$, and inspecting the definitions it becomes clear that the map $\pi \mapsto \AV(\pi)$, taking a large discrete series $(\g,K)$-module  (or rather its equivalence class) to its associated variety, is equivariant under~$Q'(\R)$.
+In view of the relationship between the actions of $Q'(\R)$ and $Q(\R)$ on $(\Op \cap \s)/K$, this proves part~(2) of Proposition~\ref{prop:action_on_K_orbits}.
+\qed
 
@@
 In a perfect world, we could also give a more elementary argument, using the description of the Kostant--Sekiguchi correspondence in~\cite{galois} and the descriptions of the actions above; but  I'm not sure it's possible to do it without encountering a basepoint issue.
-Another possibility, suggested by Jeff, is to extract it from some arguments in Adams--Kaletha (e.g.
-the fact that $\WF(\pi)$ is the asymptotic cone of the $G(\R)$-orbit of the HC parameter of~$\pi$, or the connection with the Kostant section).
-\end{proof}
+Another possibility, suggested by Jeff, is to extract it from  arguments in Adams--Kaletha (e.g.
+the fact that $\WF(\pi)$ is the asymptotic cone of the $G(\R)$-orbit of the HC parameter of~$\pi$, and the connection with the Kostant section).
+\textcolor{red}{AA (27-III-2024): I think this last strategy should indeed work, but there are details to discuss with Jeff to complete the argument, and if everything turns out OK then  I'll write up the proof here.}\end{proof}
 
@@
 
-There are several ways to describe this bijection.\footnote{AA 23-II-2024: it might be nice to mention the version with the asymptotic cone of the orbit of~$H_\pi$, which is extremely clean and concrete.
+There are several ways to describe this bijection.\footnote{AA 23-II-2024: I think we should mention the version with the asymptotic cone of the orbit of~$H_\pi$, which is extremely clean and concrete.
 } We choose to compose the maps (1)$\leftrightarrow$(3)$\leftrightarrow$(4).
@@
 Write $\w=\w_X$ for some regular nilpotent element $X\in i\g(\R)$.
-Then $H_\pi$ is $G(\R)$-conjugate to an element of the Kostant section of $X$.\footnote{AA 23-II-2024: would probably be useful to explain the connection with $\pi \mapsto \WF(\pi)$ in more detail...}
+Then $H_\pi$ is $G(\R)$-conjugate to an element of the Kostant section of $X$.\footnote{AA 23-II-2024: would probably be useful to explain the connection with $\pi \mapsto \WF(\pi)$ in more detail...\\ AA 27-III-2024: furthermore, if the Kostant section is used in the proof that $\AV \leftrightarrow \WF$ coincides with Sekiguchi, then we should move this subsection to an earlier place, and then probably this discussion will have to be reworked.
+}
 \end{proposition}

### 2024-03-29 whittaker.tex
some changes around Galois cohomology stuff

@@
 Let us now explain the strategy of the proof, which is mainly an exercise in putting together some references that are rather scattered in the literature.
-What we shall actually do is: introduce a finite group~$Q(\R)$, and point out that
+What we shall actually do is: introduce a finite group~$Q(G(\R))$, and point out that
 \begin{itemize}
@@
 
-\subsection{The group $Q(\R)$ and its actions} Let $Z=Z(G)$ be the center of $G$, and let $\Gad$ be the complex reductive group~$G/Z$.
+\subsection{The group $Q(G(\R))$ and its actions} Let $Z=Z(G)$ be the center of $G$, and let $\Gad$ be the complex reductive group~$G/Z$.
 Then $Z$ and $\Gad$ are defined over $\R$, and $Z(\R)$ is equal to the center of $G(\R)$.
@@
 $$
-Q(\R)=\Gad(\R)/G(\R)_{\mathrm{ad}}.
+Q(G(\R))=\Gad(\R)/G(\R)_{\mathrm{ad}}.
 $$
@@
 
-\paragraph*{$\bullet$ Action on~(1)} Since~$Q(\R)$ can be viewed as a group of automorphisms of~$G(\R)$,  it has a canonical action on equivalence classes of $(\g, K)$-modules.\footnote{AA 15-II-2024: probably better to spell out the action.} This action preserves  the property of being large\footnote{AA 15-II-2024: should say something about this using the fact that it comes from automorphisms, either here or in the section on large reps}.
+\paragraph*{$\bullet$ Action on~(1)} Since~$Q(G(\R))$ can be viewed as a group of automorphisms of~$G(\R)$,  it has a canonical action on equivalence classes of $(\g, K)$-modules.\footnote{AA 15-II-2024: probably better to spell out the action.} This action preserves  the property of being large\footnote{AA 15-II-2024: should say something about this using the fact that it comes from automorphisms, either here or in the section on large reps}.
 It also preserves $L$-packets by~\cite[Lemma 6.18]{Contragredient}.
 
-\paragraph*{$\bullet$ Action on~(2)}  By definition of Whittaker data, the action of~$Q(\R)$ on $G(\R)$ induces a canonical action on the set of Whittaker data.
+\paragraph*{$\bullet$ Action on~(2)}  By definition of Whittaker data, the action of~$Q(G(\R))$ on $G(\R)$ induces a canonical action on the set of Whittaker data.
 By \cite[(14.15)]{abv} this action is simply transitive.
 
-It is an immediate consequence of the definitions that the map $\pi \mapsto \w(\pi)$, taking a large discrete series representation to the Whittaker datum for which it has a Whittaker model, is equivariant for the actions of $Q(\R)$ on (1) and (2).
+It is an immediate consequence of the definitions that the map $\pi \mapsto \w(\pi)$, taking a large discrete series representation to the Whittaker datum for which it has a Whittaker model, is equivariant for the actions of $Q(G(\R))$ on (1) and (2).
 
-\paragraph*{$\bullet$ Action on~(4)} The actions of $Q(\R)$ on (3) and (4) are quite similar, and the proof that they are simply transitive use an interpretation of $Q(\R)$ in terms of group cohomology.
+\paragraph*{$\bullet$ Action on~(4)} The actions of $Q(G(\R))$ on (3) and (4) are quite similar, and the proof that they are simply transitive use an interpretation of $Q(G(\R))$ in terms of group cohomology.
 We begin with the case of the wave-front set (4), because the argument a more familiar version of  Galois cohomology.
 
-To define the action of~$Q(\R)$ on~(4), first observe that~$\Gad$ acts on~$\g$ by the adjoint action.
-This action preserves~$\Op$, and its restriction to~$\Gad(\R)$ preserves~$\Op\cap (i\g(\R))$.
-Since elements on a given~$G(\R)_{\mathrm{ad}}$-orbit are in the same~$G(\R)$-orbit, this induces an action of $Q(\R)=\Gad(\R)/G(\R)_{\mathrm{ad}}$ on~$\Op\cap (i\g(\R))/G(\R)$.
+To define the action of~$Q(G(\R))$ on~(4), first observe that~$\Gad$ acts on~$\g$ by the adjoint action.
+This action preserves~$\Op$, and its restriction to~$\Gad(\R)$ preserves~$\Op\cap i\g(\R)$.
+Since elements on a given~$G(\R)_{\mathrm{ad}}$-orbit are in the same~$G(\R)$-orbit, this induces an action of $Q(G(\R))=\Gad(\R)/G(\R)_{\mathrm{ad}}$ on~$(\Op\cap i\g(\R))/G(\R)$.
 
@@
 \begin{enumerate} 
-\item The action of~$Q(\R)$ on $\Op\cap (i\g(\R))/G(\R)$ is simply transitive.
-\item The map $\pi \mapsto \WF(\pi)$ is $Q(\R)$-equivariant.
+\item The action of~$Q(G(\R))$ on $(\Op\cap i\g(\R))/G(\R)$ is simply transitive.
+\item The map $\pi \mapsto \WF(\pi)$ is $Q(G(\R))$-equivariant.
 \end{enumerate}
@@
 
-The proof of~(1) uses group cohomology, and we first recall some general notation.
-Let~$\Gamma$ be the Galois group~$\Z/2\Z$ of~$\R$.
-When~$A$ is a group and $\tau$ is an involutive automorphism of~$A$, we may consider the cohomology sets $H^0_\tau(\Gamma, A)$ and $H^1_\tau(\Gamma, A)$ attached to the action of~$\Gamma$ on~$G$ using~$\tau$.
-These are pointed sets, and not groups in general if~$A$ isn't abelian.
-We may view $H^0_\tau(\Gamma, A)$ as the fixed-point-set $A^{\tau}$, and $H^1_\tau(\Gamma,A)$ as the quotient of $A^{-\tau} = \{ a \in A, a\tau(a)=1\}$ by the equivalence relation~$\sim$ generated by $a \sim x a \tau(x^{-1})$ for all $x \in G$.
+\begin{proof}
+The proof of~(1) is a standard argument in group cohomology. Suppose $\omega,\omega'$ are $G(\R)$ orbits in $\Op\cap i\g(\R)$,
+and choose $X\in \omega,X'\in\omega'$. Then there exists $g\in G$ such that $\Ad(g)(X)=X'$. Since $X\in \g(\R)$ the condition $X'\in i\g(\R)$ 
+is $g\inv \sigma(g)\in \Stab_G(X)$.  Since $X$ is principal $\Stab_G(X)=ZU$ where $U$ is a unipotent group. 
+A standard fact is that $H^1(\sigma,U)=1$, and from this we see that, after multiplying $g$ on the right by an element of $u$, we can assume $g\inv \sigma(g)\in Z$.
+This is equivalent to: the image of $g$ in $\Gad$ is in $\Gad(\R)$.
+On the other hand $\omega=\omega'$
+if and only if $X'=\Ad(g)X$ for some $g\in G(\R)$. This competes the proof of (1).
 
-We can use group cohomology to define an action of $Q(\R)$ on~(4). By definition we have the exact sequence $1\rightarrow Z \rightarrow G \rightarrow \Gad\rightarrow 1$. It 
-gives rise to a long exact sequence of pointed sets:
+Part~(2) of the proposition is comes from general properties of the wavefront set in microlocal analysis, and from the fact that the action of $Q(G(\R))$ comes from automorphisms of~$G(\R)$.
+More precisely, if~$q$ is an element of~$Q(G(\R))$ and $\tilde{q}$ is a representative of~$q$ in $\Gad(\R)$, then the action of~$q$ on equivalence classes of $(\g, K)$-modules comes from the action of the automorphism $\mathrm{int}(\tilde{q})$ of~$G(\R)$ on $(\g, K)$-modules.
+Now the wavefront set of a distribution on a manifold satisfies general covariance properties under diffeomorphisms of the manifold: this follows from Hörmander's original definitions, see e.g.
+\cite[Section 2, p.~800]{HarrisHeOlafsson}.
+Applying this to the present situation, and going through the basics as in   \cite[Section 2]{HarrisHeOlafsson}, it immediately follows that $\pi \mapsto \WF(\pi)$ is equivariant under $Q(G(\R))$.
+\end{proof}
+
+This can be said more succintly as follows.
+The exact sequence $1\rightarrow Z \rightarrow G \rightarrow \Gad\rightarrow 1$ gives 
+gives rise to a long exact cohomology sequence
 \begin{equation} \label{long_ptset}
@@
 \end{equation}
-By definition the connecting map  $ \Gad(\R) \rightarrow H^1_\sigma(\Gamma,Z)$ sends $g \in \Gad(\R)$ to the equivalence class of $g \sigma(g^{-1})$ in $H^1_\sigma(\Gamma, Z)$.
-Going through the definitions we see that   two elements  $g_1, g_2$ have the same image if and only if $g_1 g_{2}\inv \in G(\R)_{\mathrm{ad}}$; therefore the image of the connecting map is in canonical bijection with $Q(\R)=\Gad(\R)/G(\R)_{\mathrm{ad}}$, and by exactness of~\eqref{long_ptset} we get:
+Therefore
+$$
+Q(\R)=\ker(H^1_\sigma(\Gamma,Z)\rightarrow H^1_\sigma(\Gamma,G).
+$$
+Then:
+$$
+\begin{aligned}
+(\Op\cap i\g(\R))/G(\R)&\leftrightarrow \ker(H^1_\sigma(\Gamma,\Stab_G(X))\rightarrow H^1_\sigma(\Gamma,G)\\
+&=
+\ker(H^1_\sigma(\Gamma,ZU)\rightarrow H^1_\sigma(\Gamma,G)\\
+&=
+\ker(H^1_\sigma(\Gamma,Z)\rightarrow H^1_\sigma(\Gamma,G)\\
+&=Q(G(\R))
+\end{aligned}
+$$
 
-\begin{lemma}
-  \label{l:Q}
-The above discussion determines a canonical bijection 
- \begin{equation}\label{bij_q_1} Q(\R) \leftrightarrow \kernel(H^1_\sigma(\Gamma,Z)\rightarrow H^1_\sigma(\Gamma,G)).\end{equation}
-\end{lemma}
-
-Using this we define an action of~$Q(\R)$ on $(\Op \cap i\g(\R))/G(\R)$.
-Suppose~$X \in \g$ is nilpotent.
-Consider the intersection of the orbit $\Omega_X=\mathrm{Ad}(G) \cdot X$ with $\g(\R)$, and its decomposition into $G(\R)$-orbits.
-The map
-\begin{align} \label{bij_q_2}\beta_X\colon (\Omega_{X} \cap \g(\R))/G(\R) & \to \kernel\left(H^1_\sigma(\Gamma,\mathrm{Stab}_G(X))\rightarrow H^1_\sigma(\Gamma,G)\right) \\ \mathrm{Ad}(g) \cdot X & \mapsto \text{class of $ g\sigma(g^{-1})$ in $H^1_\sigma(\Gamma,\mathrm{Stab}_G(X))$} \nonumber \end{align}
-is a bijection: see \cite[Lemma 5.2]{galois}. 
-In the case where $X$ lies on the principal nilpotent orbit $\Op$, the stabilizer $\mathrm{Stab}_G(X)$ is the direct product of $Z(G)$ with a unipotent group\footnote{AA 19-II-2024: should we insert a reference?}, which implies $H^1(\Gamma, \mathrm{Stab}_G(X)) =H^1(\Gamma,Z)$.
-Using Lemma~\ref{l:Q}, we get a bijection
-\[\Delta_X\colon (\Op \cap i\g(\R))/G(\R) \leftrightarrow Q(\R).\]
-This bijection depends  on the choice of~$X \in \Op$; but it defines a simply transitive action of~$Q(\R)$ on~$(\Op \cap i\g(\R))/G(\R)$, which is independent of the choice of~$X$.
-
-An important point is that this action coincides with that defined before the statement of the Proposition.
-\textcolor{blue}{TODO: explain why.
-Basically the reason is that if we hit $X$ with $q_1q_2$ on the LHS of~\eqref{bij_q_2}, then then going through the definitions this goes to the element~$q_1q_2$ of~$Q(\R)$.}
-
-Let us now prove the Proposition.
-
-First we prove that~$Q(\R)$ acts freely on the set a  $(\Op \cap i\g(\R))/G(\R)$ of orbits.
-Let~$\omega$ be an orbit, and let~$X$ be a point of~$\omega$.
-If~$q$ is an element of~$Q(\R)$, then going through the definitions of~\eqref{bij_q_1}--\eqref{bij_q_2} we see that~$\Delta_X(q \cdot \omega) = q$; therefore if~$q\cdot \omega=\omega$, then~$q=1$.
-
-Next we prove that the action is transitive.
-Let~$\omega, \omega'$ be $G(\R)$-orbits in  $(\Op \cap i\g(\R))$.
-Fix an element~$X$ of~$\omega$ and consider the bijections~$\beta_X$ and~$\Delta_X$ above.
-Let~$q \in Q(\R)$ be the element~$\Delta_X(\omega')$.
-We have seen that $q = \Delta_X(q \cdot \omega)$, therefore \mbox{$\Delta_X(q \cdot \omega)=\Delta_X(\omega')$}, which proves~$q \cdot \omega = \omega'$ and concludes the proof of~(1).
-
-Part~(2) of the proposition is comes from general properties of the wavefront set in microlocal analysis, and from the fact that the action of $Q(\R)$ comes from automorphisms of~$G(\R)$.
-More precisely, if~$q$ is an element of~$Q(\R)$ and $\tilde{q}$ is a representative of~$q$ in $\Gad(\R)$, then the action of~$q$ on equivalence classes of $(\g, K)$-modules comes from the action of the automorphism $\mathrm{int}(\tilde{q})$ of~$G(\R)$ on $(\g, K)$-modules.
-Now the wavefront set of a distribution on a manifold satisfies general covariance properties under diffeomorphisms of the manifold: this follows from Hörmander's original definitions, see e.g.
-\cite[Section 2, p.~800]{HarrisHeOlafsson}.
-Applying this to the present situation, and going through the basics as in   \cite[Section 2]{HarrisHeOlafsson}, it immediately follows that $\pi \mapsto \WF(\pi)$ is equivariant under $Q(\R)$, and this concludes the proof of Proposition~\ref{prop:action_on_K_orbits}.
-
-\paragraph*{$\bullet$ Action on~(3)} We turn to the action of~$Q(\R)$ on $(\Op \cap \s)/K$, and to the associated variety.
-For this it is convenient to use an isomorphic variant of~$Q(\R)$, defined in terms of~$K$ rather than~$G(\R)$.
+\paragraph*{$\bullet$ Action on~(3)} We turn to the action of~$Q(G(\R))$ on $(\Op \cap \s)/K$, and to the associated variety.
+For this it is convenient to use an isomorphic variant of~$Q(G(\R))$, defined in terms of~$K$ rather than~$G(\R)$.
 
@@
 \item Every element of $Q(R)=\Gad(\R)/G(\R)_{\ad}$ has a $\theta_\ad$-invariant representative in $\Gad(\R)$.
-\item Given $q \in Q(\R)$, and a $\theta_{\ad}$-invariant representative~$\tilde{q}$ of~$q$, the image of~$\tilde{q}$ in~$Q'(\R)$ depends only on~$q$ and not on the choice of~$\tilde{q}$.
-Denote this image by~$\Psi(q)$; then $q \mapsto \Psi(q)$ is an isomorphism between $Q(\R)$ and~$Q'(\R)$.
+\item Given $q \in Q(G(\R))$, and a $\theta_{\ad}$-invariant representative~$\tilde{q}$ of~$q$, the image of~$\tilde{q}$ in~$Q'(\R)$ depends only on~$q$ and not on the choice of~$\tilde{q}$.
+Denote this image by~$\Psi(q)$; then $q \mapsto \Psi(q)$ is an isomorphism between $Q(G(\R))$ and~$Q'(\R)$.
 \end{enumerate}
@@
 
-\begin{proof} \textcolor{red}{TODO!}\end{proof}
+\begin{proof} \textcolor{red}{TODO!}
+Here are the main points.
 
-To define the  action of~$Q(\R)$ on $(\Op \cap \s)/K$, we point out that $Q'(\R)$ acts on $\Op \cap \s$ and that this action preserves the $K$-orbits.
+$$
+\begin{aligned}
+Q_\sigma(G(\R))&=\ker(H^1_\sigma(\Gamma,Z)\rightarrow H^1_\sigma(\Gamma,G))\\
+Q_\theta(G(\R))&=\ker(H^1_\theta(\Gamma,Z)\rightarrow H^1_\theta(\Gamma,G))\\
+H^1_\sigma(\Gamma,Z)&\simeq H^1_\sigma(\Gamma,Z^{\sigma\theta})\simeq H^1_\theta(\Gamma,Z^{\sigma\theta})\simeq H^1_\theta(\Gamma,Z)\\
+H^1_\sigma(\Gamma,G)&\simeq H^1_\sigma(\Gamma,G^{\sigma\theta})\simeq H^1_\theta(\Gamma,G^{\sigma\theta})\simeq H^1_\theta(\Gamma,G)\\
+\end{aligned}
+$$
+The first and last isomorphisms in the last two rows are induced by inclusion $Z^{\sigma\theta}\hookrightarrow Z$ and $G^{\sigma\theta}\hookrightarrow G$.
+
+\end{proof}
+
+To define the  action of~$Q(G(\R))$ on $(\Op \cap \s)/K$, we point out that $Q'(\R)$ acts on $\Op \cap \s$ and that this action preserves the $K$-orbits.
 First, the adjoint action of~$\Gad$ on~$\g$ preserves both $\Op$ and~$\s$.
@@
 It is then easy to check that if two elements of $\Op \cap \s$ lie in on the same $\Kad$-orbit, then for every $g \in \Gad^{\theta_{\ad}}$, the elements  $\tilde{g} \cdot x$ and $\tilde{g} \cdot y$ lie on the same $\Kad$-orbit.
-This determines an action of~$Q'(\R)$ on~$(\Op \cap \s)/K$, and by Lemma~\ref{lem:q_and_qprime} we get an action of~$Q(\R)$ on~$(\Op \cap \s)/K$.
+This determines an action of~$Q'(\R)$ on~$(\Op \cap \s)/K$, and by Lemma~\ref{lem:q_and_qprime} we get an action of~$Q(G(\R))$ on~$(\Op \cap \s)/K$.
 This is the action featured in the following statement:
@@
 \begin{enumerate} 
-\item The action of~$Q(\R)$ on $(\Op \cap \s)/K$ is simply transitive.
-\item The map $\pi \mapsto \AV(\pi)$ is $Q(\R)$-equivariant.
+\item The action of~$Q(G(\R))$ on $(\Op \cap \s)/K$ is simply transitive.
+\item The map $\pi \mapsto \AV(\pi)$ is $Q(G(\R))$-equivariant.
 \end{enumerate}
@@
 The argument for part~(1) of Proposition~\ref{prop:action_on_real_orbits} works seamlessly if we replace~$\sigma$ with~$\theta$, and proves that the action of~$Q'(\R)$ on $(\Op \cap \s)/K$ is simply transitive.
-Since the action of~$Q(\R)$ is defined by transport of structure from that of~$Q'(\R)$, this proves~(1).
+Since the action of~$Q(G(\R))$ is defined by transport of structure from that of~$Q'(\R)$, this proves~(1).
 
@@
 Now, the definition of the associated variety uses filtrations (see the Introduction of~\cite{vogan_bowdoin}) which are all invariant under $\Gad^{\theta_\ad}$, and inspecting the definitions it becomes clear that the map $\pi \mapsto \AV(\pi)$, taking a large discrete series $(\g,K)$-module  (or rather its equivalence class) to its associated variety, is equivariant under~$Q'(\R)$.
-In view of the relationship between the actions of $Q'(\R)$ and $Q(\R)$ on $(\Op \cap \s)/K$, this proves part~(2) of Proposition~\ref{prop:action_on_K_orbits}.
+In view of the relationship between the actions of $Q'(\R)$ and $Q(G(\R))$ on $(\Op \cap \s)/K$, this proves part~(2) of Proposition~\ref{prop:action_on_K_orbits}.
 \qed

### 2024-04-01 whittaker.tex
Tried to rewrite Section 2 to clarify Q_sigma versus Q_theta and make it more self-contained

@@
 \usepackage{verbatim}
-\usepackage{amssymb}
+\usepackage{amssymb, amscd}
 \usepackage{mathtools}
@@
 Let us now explain the strategy of the proof, which is mainly an exercise in putting together some references that are rather scattered in the literature.
-What we shall actually do is: introduce a finite group~$Q(G(\R))$, and point out that
+What we shall actually do is: introduce a finite group~$Q_\sigma(G)$, and point out that
 \begin{itemize}
@@
 \end{itemize}
-The theorem follows immediately from these two observations.
+The theorem follows immediately from these two observations.\footnote{AA 01-IV-2024 --- perhaps it would be reader-friendly to point out the basic fact on group actions that we are using here: suppose a group $Q$ acts on two sets $A, B$ and let $f\colon A \to B$ be an equivariant map.
+If $Q$ acts transitively on~$B$  then~$f$ is surjective, and if $Q$ acts transitively on~$A$ and freely on~$B$ then~$f$ is injective.
+}
 
-\subsection{The group $Q(G(\R))$ and its actions} Let $Z=Z(G)$ be the center of $G$, and let $\Gad$ be the complex reductive group~$G/Z$.
-Then $Z$ and $\Gad$ are defined over $\R$, and $Z(\R)$ is equal to the center of $G(\R)$.
-We may view~$\Gad(\R)$ as the set of inner automorphisms of~$G$ which are defined over~$\R$, and this contains the group $G(\R)_{\mathrm{ad}}=G(\R)/Z(\R)$ as a normal subgroup of finite index\footnote{AA 15-II-2024: is there a trivial way to explain why finite index?}.
+\subsection{The groups $Q_\sigma(G)$ and $Q_{\theta}(G)$}
+
+\subsubsection{Definition of the two groups}Let $Z=Z(G)$ be the center of $G$, and let $\Gad$ be the complex reductive group~$G/Z$.
+The group $Z(\R)=Z^{\sigma}$ is equal to the center of $G(\R)$.
+The automorphism~$\sigma$ of~$G$ preserves $Z$, and descends to an automorphism~$\sigma_{\ad}$ of~$\Gad$.
+We set $\Gad(\R)=\Gad^{\sigma_{\ad}}$; we may view it as the set of inner automorphisms of~$G$ which are defined over~$\R$, and this contains the group $G(\R)_{\mathrm{ad}}=G(\R)/Z(\R)$ as a normal subgroup of finite index\footnote{AA 15-II-2024: is there a trivial way to explain why finite index?}.
 Define 
 $$
-Q(G(\R))=\Gad(\R)/G(\R)_{\mathrm{ad}}.
+Q_\sigma(G)=\Gad(\R)/G(\R)_{\mathrm{ad}}.
 $$
@@
 
-\paragraph*{$\bullet$ Action on~(1)} Since~$Q(G(\R))$ can be viewed as a group of automorphisms of~$G(\R)$,  it has a canonical action on equivalence classes of $(\g, K)$-modules.\footnote{AA 15-II-2024: probably better to spell out the action.} This action preserves  the property of being large\footnote{AA 15-II-2024: should say something about this using the fact that it comes from automorphisms, either here or in the section on large reps}.
-It also preserves $L$-packets by~\cite[Lemma 6.18]{Contragredient}.
+We shall need a variant of~$Q_{\sigma}(\R)$ in which we replace the real form~$\sigma$ by the Cartan involution~$\theta$.
+As above, since~$\theta$ is an automorphism of~$G$, it preserves~$Z$,  and induces an involution~$\theta_{\ad}$ of~$\Gad$.
+Recall $K=G^{\theta}$; consider the intersection $Z_K=Z \cap K$, and set  $K_{\ad}=K/Z_K$.
+The inclusion  $K \hookrightarrow G$ induces a map $K \to \Gad$, whose image is a subgroup of~$\Gad^{\theta_{\ad}}$ and whose kernel is~$Z_K$.
+Therefore it factors to an injective morphism $\iota\colon \Kad \hookrightarrow\Gad^{\theta_{\ad}} $, whose image is a normal subgroup of~$\Gad^{\theta_{\ad}}$.
+Using it we will identify $\Kad$ with a normal subgroup of $\Gad^{\theta_{\ad}}$.
+Define
+\[ Q_\theta(G) = \Gad^{\theta_{\ad}}/\Kad.\]
+Unlike $Q_{\sigma}(G)$, this group does not have an obvious action on~$G(\R)$.
+Nevertheless the groups $Q_{\sigma}(G)$ and $Q_{\theta}(G)$ are isomorphic.
+We will spell out an explicit isomorphism below, using group cohomology arguments.
 
-\paragraph*{$\bullet$ Action on~(2)}  By definition of Whittaker data, the action of~$Q(G(\R))$ on $G(\R)$ induces a canonical action on the set of Whittaker data.
+\subsubsection{Interpretation in terms of group cohomology}
+
+The groups $Q_{\sigma}(G)$ and $Q_{\theta}(G)$ are instances of the following construction: if~$\tau$ is an involutive automorphism of~$G$, then it preserves~$Z$ and induces an involution~$\tau_{\ad}$ of~$\Gad$; we may then set $Q_{\tau}(G)=\Gad^{\tau_{\ad}}/(G^{\tau})_{\ad}$, where $(G^{\tau})_{\ad}$ is the image of~$G^{\tau}$ in~$\Gad$.
+In this situation~$Q_{\tau}(G)$ has a simple interpretation in Galois cohomology, which we now recall.
+
+Let us first set up some notation.
+Let~$\Gamma$ be the Galois group~$\Z/2\Z$ of~$\R$.
+When~$A$ is a group and $\tau$ is an involutive automorphism of~$A$, we may consider the cohomology sets $H^0_\tau(\Gamma, A)$ and $H^1_\tau(\Gamma, A)$ attached to the action of~$\Gamma$ on~$G$ using~$\tau$.
+These are pointed sets, and not groups in general if~$A$ isn't abelian.
+We may view $H^0_\tau(\Gamma, A)$ as the fixed-point-set $A^{\tau}$, and $H^1_\tau(\Gamma,A)$ as the quotient of $A^{-\tau} = \{ a \in A, a\tau(a)=1\}$ by the equivalence relation~$\sim$ generated by $a \sim x a \tau(x^{-1})$ for all $x \in G$.
+
+We now take~$A=G$, and continue to assume~$\tau$ is an involutive automorphism. Then the short exact sequence $1\rightarrow Z \rightarrow G \rightarrow \Gad\rightarrow 1$ 
+gives rise to a ``long" exact sequence of pointed sets:
+\begin{equation} \label{long_ptset}
+1\rightarrow Z^\tau \rightarrow G^\tau \rightarrow \Gad^{\tau_{\ad}} \rightarrow H^1_\tau(\Gamma,Z)\rightarrow H^1_\tau(\Gamma,G)\rightarrow H^1_{\tau_\ad}(\Gamma,\Gad).
+\end{equation}
+By definition the connecting map  $ \Gad^{\tau_{\ad}} \rightarrow H^1_\tau(\Gamma,Z)$ sends $g \in \Gad^{\tau_{\ad}}$ to the equivalence class of $g \tau_{\ad}(g^{-1})$ in $H^1_\tau(\Gamma, Z)$, and the meaning of all the other maps is obvious.
+Going through the definitions we see that  two elements  $g_1, g_2$ have the same image if and only if $g_1 g_{2}\inv \in (G^\tau)_{\ad}$. 
+Therefore the image of the connecting map is in canonical bijection with $Q_\tau(G)$, and by exactness of~\eqref{long_ptset} we get a canonical bijection
+\begin{equation} \label{interp_q_cohomology} Q_{\tau}(G) \simeq \ker(H^1_\tau(\Gamma,Z)\rightarrow H^1_\tau(\Gamma,G)).\end{equation}
+The previous argument is in the category of pointed sets, and one should keep in mind on the right-hand side $H^1_\tau(\Gamma,G))$  is not a group in general, therefore~\eqref{interp_q_cohomology} is at first sight only a set-theoretic bijection.
+However,
+$H^1_\tau(\Gamma,Z)$ is a group since $Z$ is abelian; therefore both sides of~\eqref{interp_q_cohomology} have canonical abelian group structures, and chasing definitions one easily sees that~\eqref{interp_q_cohomology} is actually an isomorphism of abelian groups.
+
+\subsubsection{Isomorphism between $Q_{\sigma}(G)$ and $Q_{\theta}(G)$}
+
+Using the group cohomology interpretation in the previous paragraph, we can construct a canonical  isomorphism between $Q_{\sigma}(G)$ and $Q_{\theta}(G)$.
+For this recall $\theta\sigma = \sigma\theta$ and $G^{\sigma\theta}$ is a compact real form of~$G$.
+Furthermore $\sigma$ and $\theta$ coincide on $G^{\sigma\theta}$, therefore  $H_{\sigma}(\Gamma, G^{\sigma\theta})$ and  $H_{\sigma}(\Gamma, G^{\sigma\theta})$ are the same set, which we will denote by  $H_{\sigma\mid\theta}(\Gamma, G^{\sigma\theta})$.
+Now the inclusion $G^{\sigma\theta} \hookrightarrow G$ induces canonical maps
+\begin{equation} \label{bij_cohom} H^{1}_{\sigma}(\Gamma, G) \longleftarrow H_{\sigma\mid\theta}(\Gamma, G^{\sigma\theta}) \longrightarrow H^{1}_{\theta}(\Gamma, G).\end{equation}
+By \cite[Corollary~4.4 and Corollary 4.7]{galois}, both of these maps are \emph{bijections}.
+Replacing~$G$ by $Z$ we get bijections $H^{1}_{\sigma}(\Gamma, Z) \leftarrow H_{\sigma\mid\theta}(\Gamma, Z^{\sigma\theta}) \rightarrow H^{1}_{\theta}(\Gamma, Z)$, and these fit with the bijections~\eqref{bij_cohom} into a commutative diagram
+\[
+\begin{CD}
+H^{1}_{\sigma}(\Gamma, Z) @<<< H_{\sigma\mid\theta}(\Gamma, Z^{\sigma\theta})@>>> H^{1}_{\theta}(\Gamma, Z)
+ \\
+@V{\varphi_{\sigma}}VV @VVV @V{\varphi_{\theta}}VV  \\
+H^{1}_{\sigma}(\Gamma, G) @<<< H_{\sigma\mid\theta}(\Gamma, G^{\sigma\theta})@>>> H^{1}_{\theta}(\Gamma, G)
+\end{CD}
+\]
+where $\varphi_{\sigma}$ and $\varphi_{\theta}$ are induced by the inclusion $Z \hookrightarrow G$.
+Since the horizontal arrows are isomorphisms in the category of pointed sets, they induce a canonical bijection between the kernels of $\varphi_{\sigma}$ and $\varphi_{\theta}$; by~\eqref{interp_q_cohomology} this gives a canonical bijection
+\[ Q_{\sigma}(G) \simeq Q_{\theta}(G).\] 
+As discussed after~\eqref{interp_q_cohomology}, this is actually an isomorphism of abelian groups.
+
+\subsection{Actions of $Q_\sigma(G)$ on representations and invariants}
+
+\subsubsection*{On representations} 
+Since~$Q_\sigma(G)$ can be viewed as a group of automorphisms of~$G(\R)$,  it has a canonical action on equivalence classes of representations of~$G(\R)$, and therefore on~$(\g, K)$-modules.
+This action preserves  the property of being large\footnote{AA 15-II-2024: should say something about this using the fact that it comes from automorphisms, either here or in the section on large reps}.
+It also preserves $L$-packets by~\cite[Lemma 6.18]{Contragredient}, and acts transitively on an~$L$-packet\footnote{AA 01-IV-2023: this point was missing, I think it's easy using Harish-Chandra's parametrization, the fact that every element of~$Q_{\sigma}(G)$ has a representative in the Weyl group, plus the description of discrete series L-packets in the Congragredient paper.
+The point about the action preserving $L$-packets also follows from this, it's perhaps a better argument than [Contragredient, Lemma 6.18] which may be better suited to the $\theta$-version.}
+
+\subsubsection*{On~Whittaker data}  By definition of Whittaker data, the action of~$Q_{\sigma}(G)$ on $G(\R)$ induces a canonical action on the set of Whittaker data.
 By \cite[(14.15)]{abv} this action is simply transitive.
 
-It is an immediate consequence of the definitions that the map $\pi \mapsto \w(\pi)$, taking a large discrete series representation to the Whittaker datum for which it has a Whittaker model, is equivariant for the actions of $Q(G(\R))$ on (1) and (2).
+It is an immediate consequence of the definitions that the map $\pi \mapsto \w(\pi)$, taking a large discrete series representation to the Whittaker datum for which it has a Whittaker model, is equivariant for the actions of $Q_{\sigma}(G)$ on (1)--(2).
 
-\paragraph*{$\bullet$ Action on~(4)} The actions of $Q(G(\R))$ on (3) and (4) are quite similar, and the proof that they are simply transitive use an interpretation of $Q(G(\R))$ in terms of group cohomology.
-We begin with the case of the wave-front set (4), because the argument a more familiar version of  Galois cohomology.
+\subsubsection*{On real nilpotent orbits}
 
-To define the action of~$Q(G(\R))$ on~(4), first observe that~$\Gad$ acts on~$\g$ by the adjoint action.
+To define the action of~$Q_{\sigma}(G)$ on~(4), first observe that~$\Gad$ acts on~$\g$ by the adjoint action.
 This action preserves~$\Op$, and its restriction to~$\Gad(\R)$ preserves~$\Op\cap i\g(\R)$.
-Since elements on a given~$G(\R)_{\mathrm{ad}}$-orbit are in the same~$G(\R)$-orbit, this induces an action of $Q(G(\R))=\Gad(\R)/G(\R)_{\mathrm{ad}}$ on~$(\Op\cap i\g(\R))/G(\R)$.
+Since elements on a given~$G(\R)_{\mathrm{ad}}$-orbit are in the same~$G(\R)$-orbit, this induces an action of $Q_{\sigma}(G)=\Gad(\R)/G(\R)_{\mathrm{ad}}$ on~$(\Op\cap i\g(\R))/G(\R)$.
 
@@
 \begin{enumerate} 
-\item The action of~$Q(G(\R))$ on $(\Op\cap i\g(\R))/G(\R)$ is simply transitive.
-\item The map $\pi \mapsto \WF(\pi)$ is $Q(G(\R))$-equivariant.
+\item The action of~$Q_{\sigma}(G)$ on $(\Op\cap i\g(\R))/G(\R)$ is simply transitive.
+\item The map $\pi \mapsto \WF(\pi)$ is $Q_{\sigma}(G)$-equivariant.
 \end{enumerate}
@@
 
-Part~(2) of the proposition is comes from general properties of the wavefront set in microlocal analysis, and from the fact that the action of $Q(G(\R))$ comes from automorphisms of~$G(\R)$.
-More precisely, if~$q$ is an element of~$Q(G(\R))$ and $\tilde{q}$ is a representative of~$q$ in $\Gad(\R)$, then the action of~$q$ on equivalence classes of $(\g, K)$-modules comes from the action of the automorphism $\mathrm{int}(\tilde{q})$ of~$G(\R)$ on $(\g, K)$-modules.
+Part~(2) of the proposition is comes from general properties of the wavefront set in microlocal analysis, and from the fact that the action of $Q_{\sigma}(G)$ comes from automorphisms of~$G(\R)$.
+More precisely, if~$q$ is an element of~$Q_{\sigma}(G)$ and $\tilde{q}$ is a representative of~$q$ in $\Gad(\R)$, then the action of~$q$ on equivalence classes of $(\g, K)$-modules comes from the action of the automorphism $\mathrm{int}(\tilde{q})$ of~$G(\R)$ on $(\g, K)$-modules.
 Now the wavefront set of a distribution on a manifold satisfies general covariance properties under diffeomorphisms of the manifold: this follows from Hörmander's original definitions, see e.g.
 \cite[Section 2, p.~800]{HarrisHeOlafsson}.
-Applying this to the present situation, and going through the basics as in   \cite[Section 2]{HarrisHeOlafsson}, it immediately follows that $\pi \mapsto \WF(\pi)$ is equivariant under $Q(G(\R))$.
+Applying this to the present situation, and going through the basics as in   \cite[Section~2]{HarrisHeOlafsson}, it immediately follows that $\pi \mapsto \WF(\pi)$ is equivariant under $Q_{\sigma}(G)$.
 \end{proof}
 
-This can be said more succintly as follows.
-The exact sequence $1\rightarrow Z \rightarrow G \rightarrow \Gad\rightarrow 1$ gives 
-gives rise to a long exact cohomology sequence
-\begin{equation} \label{long_ptset}
-1\rightarrow Z(\R) \rightarrow G(\R) \rightarrow \Gad(\R) \rightarrow H^1_\sigma(\Gamma,Z)\rightarrow H^1_\sigma(\Gamma,G)\rightarrow H^1_\sigma(\Gamma,\Gad).
-\end{equation}
-Therefore
-$$
-Q(\R)=\ker(H^1_\sigma(\Gamma,Z)\rightarrow H^1_\sigma(\Gamma,G).
-$$
-Then:
+It may be interesting to point out a variant on the proof of~(1). Given $X \in \Op \cap i\g(\R)$, the map 
+\begin{align} \label{bij_q_2} (\Omega_{X} \cap i\g(\R))/G(\R) & \to \kernel\left(H^1_\sigma(\Gamma,\mathrm{Stab}_G(X))\rightarrow H^1_\sigma(\Gamma,G)\right) \\ \mathrm{Ad}(g) \cdot X & \mapsto \text{class of $ g\sigma(g^{-1})$ in $H^1_\sigma(\Gamma,\mathrm{Stab}_G(X))$} \nonumber \end{align}
+is a bijection: see \cite[Lemma 5.2]{galois}. 
+Using this we get bijections
 $$
 \begin{aligned}
-(\Op\cap i\g(\R))/G(\R)&\leftrightarrow \ker(H^1_\sigma(\Gamma,\Stab_G(X))\rightarrow H^1_\sigma(\Gamma,G)\\
+(\Op\cap i\g(\R))/G(\R)&\simeq \ker(H^1_\sigma(\Gamma,\Stab_G(X))\rightarrow H^1_\sigma(\Gamma,G))\\
 &=
-\ker(H^1_\sigma(\Gamma,ZU)\rightarrow H^1_\sigma(\Gamma,G)\\
-&=
-\ker(H^1_\sigma(\Gamma,Z)\rightarrow H^1_\sigma(\Gamma,G)\\
-&=Q(G(\R))
+\ker(H^1_\sigma(\Gamma,Z)\rightarrow H^1_\sigma(\Gamma,G))\\
+&\simeq Q_{\sigma}(G)
 \end{aligned}
 $$
+where the middle line uses $H^1_\sigma(\Gamma,\Stab_G(X))=H^1_\sigma(\Gamma,ZU)=H^1_\sigma(\Gamma,Z)$ as explained in the proof.
+The resulting bijection  $(\Op\cap i\g(\R))/G(\R)\simeq Q_\sigma(\R)$ is equivariant (for the actions of $Q_\sigma(G)$ on $(\Op\cap i\g(\R))/G(\R)$ described above, and the action of  $Q_\sigma(G)$ on itself by multiplication), and this gives another proof of~(1).
 
-\paragraph*{$\bullet$ Action on~(3)} We turn to the action of~$Q(G(\R))$ on $(\Op \cap \s)/K$, and to the associated variety.
-For this it is convenient to use an isomorphic variant of~$Q(G(\R))$, defined in terms of~$K$ rather than~$G(\R)$.
+\subsection{Actions of $Q_\theta(G)$ on representations and invariants}
 
-Since the Cartan involution $\theta$ is an automorphism of~$G$, it preserves the center~$Z=Z(G)$, and induces an involution~$\theta_{\ad}$ of~$\Gad=G/Z$.
-Let $Z_K$ be the intersection $Z \cap K$, and let $K_{\ad}$ be the quotient $K/Z_K$.
-The natural map $K \mapsto \Gad$, induced by the inclusion $K \hookrightarrow G$, maps~$K$ to a subgroup of~$\Gad^{\theta_{\ad}}$, and has kernel~$Z_K$.
-Therefore it factors to an injective morphism $\iota\colon \Kad \hookrightarrow\Gad^{\theta_{\ad}} $.
-The image of~$\iota$ is a normal subgroup of~$\Gad^{\theta_{\ad}}$; using it we will identify $\Kad$ with a normal subgroup of $\Gad^{\theta_{\ad}}$.
-Define
-\[ Q'(\R) = \Gad^{\theta_{\ad}}/\Kad.\]
+To discuss the map taking a $(\g, K)$-module to the associated variety, it seems better to use $Q_{\theta}(G)$ rather than~$Q_{\sigma}(G)$.
 
-\begin{lemma}\label{lem:q_and_qprime}
-\begin{enumerate}
-\item Every element of $Q(R)=\Gad(\R)/G(\R)_{\ad}$ has a $\theta_\ad$-invariant representative in $\Gad(\R)$.
-\item Given $q \in Q(G(\R))$, and a $\theta_{\ad}$-invariant representative~$\tilde{q}$ of~$q$, the image of~$\tilde{q}$ in~$Q'(\R)$ depends only on~$q$ and not on the choice of~$\tilde{q}$.
-Denote this image by~$\Psi(q)$; then $q \mapsto \Psi(q)$ is an isomorphism between $Q(G(\R))$ and~$Q'(\R)$.
-\end{enumerate}
-\end{lemma}
+ \subsubsection*{On $(\g, K)$-modules}
 
-\begin{proof} \textcolor{red}{TODO!}
-Here are the main points.
+ Recall $Q_{\theta}(\R)=\Gad^{\theta_{\ad}}/\Kad$.
+By definition $\Gad^{\theta_{\ad}}$ is contained in the normalizer $\mathrm{Norm}_G(K)$; therefore it acts on~$(\g, K)$-modules.
+Any element of~$\Kad$ takes a $(\g,K)$-module to an equivalent one, therefore $Q_{\theta}(\R)$ acts on~$(\g, K)$-module.
+This preserves the property of being a discrete series, and of being large.
+Furthermore, by \cite[Lemma 6.18 and Remark 6.19]{Contragredient} the action preserves $L$-packets.
+Therefore $Q_{\theta}(\R)$ acts transitively on the large representations in a discrete series $L$-packet.
 
-$$
-\begin{aligned}
-Q_\sigma(G(\R))&=\ker(H^1_\sigma(\Gamma,Z)\rightarrow H^1_\sigma(\Gamma,G))\\
-Q_\theta(G(\R))&=\ker(H^1_\theta(\Gamma,Z)\rightarrow H^1_\theta(\Gamma,G))\\
-H^1_\sigma(\Gamma,Z)&\simeq H^1_\sigma(\Gamma,Z^{\sigma\theta})\simeq H^1_\theta(\Gamma,Z^{\sigma\theta})\simeq H^1_\theta(\Gamma,Z)\\
-H^1_\sigma(\Gamma,G)&\simeq H^1_\sigma(\Gamma,G^{\sigma\theta})\simeq H^1_\theta(\Gamma,G^{\sigma\theta})\simeq H^1_\theta(\Gamma,G)\\
-\end{aligned}
-$$
-The first and last isomorphisms in the last two rows are induced by inclusion $Z^{\sigma\theta}\hookrightarrow Z$ and $G^{\sigma\theta}\hookrightarrow G$.
+\subsubsection*{On nilpotent $K$-orbits.}
 
-\end{proof}
-
-To define the  action of~$Q(G(\R))$ on $(\Op \cap \s)/K$, we point out that $Q'(\R)$ acts on $\Op \cap \s$ and that this action preserves the $K$-orbits.
+Let us define an action of~$Q_{\theta}(G)$ on $(\Op \cap \s)/K$.
 First, the adjoint action of~$\Gad$ on~$\g$ preserves both $\Op$ and~$\s$.
-Second, the action of~$K$ on $\Op \cap \s$ is trivial on~$Z_K$, and factors through an action of~$\Kad$.
+Second, the action of~$K=G^\theta$ on $\Op \cap \s$ is trivial on~$Z_K=Z^\theta$, and factors through an action of~$\Kad$.
 It is then easy to check that if two elements of $\Op \cap \s$ lie in on the same $\Kad$-orbit, then for every $g \in \Gad^{\theta_{\ad}}$, the elements  $\tilde{g} \cdot x$ and $\tilde{g} \cdot y$ lie on the same $\Kad$-orbit.
-This determines an action of~$Q'(\R)$ on~$(\Op \cap \s)/K$, and by Lemma~\ref{lem:q_and_qprime} we get an action of~$Q(G(\R))$ on~$(\Op \cap \s)/K$.
-This is the action featured in the following statement:
+This determines an action of~$Q_\theta(G)$ on $(\Op \cap \s)/K$, which is the one featured in the next statement.
 
@@
 \begin{enumerate} 
-\item The action of~$Q(G(\R))$ on $(\Op \cap \s)/K$ is simply transitive.
-\item The map $\pi \mapsto \AV(\pi)$ is $Q(G(\R))$-equivariant.
+\item The action of~$Q_{\theta}(G)$ on $(\Op \cap \s)/K$ is simply transitive.
+\item The map $\pi \mapsto \AV(\pi)$ is $Q_{\theta}(G)$-equivariant.
 \end{enumerate}
@@
 
-The proof is similar to that of Proposition~\ref{prop:action_on_real_orbits}, but we need to use the version of Galois cohomology attached to the Cartan involution $\theta$.
-Taking up the above notation on Galois cohomology, the exact sequence $1\rightarrow Z \rightarrow G \rightarrow \Gad\rightarrow 1$ gives rise to a long exact sequence of pointed sets:
-\begin{equation} \label{long_ptset_theta}
-1\rightarrow Z_K \rightarrow K \rightarrow \Gad^{\theta_{\ad}} \rightarrow H^1_\theta(\Gamma,Z)\rightarrow H^1_\theta(\Gamma,G)\rightarrow H^1_{\theta_{\ad}}(\Gamma,\Gad).
-\end{equation}
-As in Lemma~\ref{l:Q}  this determines a bijection $Q'(\R) \leftrightarrow \kernel(H^1_\theta(\Gamma,Z)\rightarrow H^1_{\theta}(\Gamma,G))$.
-The argument for part~(1) of Proposition~\ref{prop:action_on_real_orbits} works seamlessly if we replace~$\sigma$ with~$\theta$, and proves that the action of~$Q'(\R)$ on $(\Op \cap \s)/K$ is simply transitive.
-Since the action of~$Q(G(\R))$ is defined by transport of structure from that of~$Q'(\R)$, this proves~(1).
+The proof of~(1) is exactly the same as that  to that of Proposition~\ref{prop:action_on_real_orbits}(1), replacing~$\sigma$ by the Cartan involution $\theta$.
 
-As for~(2), it is again an immediate consequence of the precise definition of the associated variety.
-Stating this needs a little more care, since it is not obvious that $\Gad$ acts on representations of~$G(\R)$.
-However, the adjoint action of~$\Gad^{\theta_{\ad}}$ on $G$ preserves $K$; this this induces an action of~$\Gad^{\theta_{\ad}}$ on $(\g, K)$-modules.
-The restriction of that action to~$\Kad$ is trivial, and this gives an action of $Q'(\R)$ acts on equivalence classes of $(\g, K)$-modules.
-Now, the definition of the associated variety uses filtrations (see the Introduction of~\cite{vogan_bowdoin}) which are all invariant under $\Gad^{\theta_\ad}$, and inspecting the definitions it becomes clear that the map $\pi \mapsto \AV(\pi)$, taking a large discrete series $(\g,K)$-module  (or rather its equivalence class) to its associated variety, is equivariant under~$Q'(\R)$.
-In view of the relationship between the actions of $Q'(\R)$ and $Q(G(\R))$ on $(\Op \cap \s)/K$, this proves part~(2) of Proposition~\ref{prop:action_on_K_orbits}.
+As for~(2), it is a consequence of the precise definition of the associated variety.
+This uses filtrations of the universal enveloping algebra of~$\g$ which are all invariant under $\Gad^{\theta_{\ad}}$: see for instance the Introduction of~\cite{vogan_bowdoin}.
+Inspecting the definitions in \emph{loc.
+cit.} it becomes clear that the map $\pi \mapsto \AV(\pi)$, taking a large discrete series $(\g,K)$-module  (or rather its equivalence class) to its associated variety, is equivariant under~$Q_{\theta}(G)$, proving~(2).
 \qed

### 2024-04-01 whittaker.tex
Small typos

@@
 Going through the definitions we see that  two elements  $g_1, g_2$ have the same image if and only if $g_1 g_{2}\inv \in (G^\tau)_{\ad}$. 
-Therefore the image of the connecting map is in canonical bijection with $Q_\tau(G)$, and by exactness of~\eqref{long_ptset} we get a canonical bijection
+Therefore the image of the connecting map is in canonical bijection with $Q_\tau(G)$. Since~\eqref{long_ptset} is exact we get a canonical bijection
 \begin{equation} \label{interp_q_cohomology} Q_{\tau}(G) \simeq \ker(H^1_\tau(\Gamma,Z)\rightarrow H^1_\tau(\Gamma,G)).\end{equation}
-The previous argument is in the category of pointed sets, and one should keep in mind on the right-hand side $H^1_\tau(\Gamma,G))$  is not a group in general, therefore~\eqref{interp_q_cohomology} is at first sight only a set-theoretic bijection.
+The previous argument is in the category of pointed sets, and on the right-hand side $H^1_\tau(\Gamma,G))$  is not a group in general.
+Therefore, at first sight, the map~\eqref{interp_q_cohomology} is only a set-theoretic bijection.
 However,
-$H^1_\tau(\Gamma,Z)$ is a group since $Z$ is abelian; therefore both sides of~\eqref{interp_q_cohomology} have canonical abelian group structures, and chasing definitions one easily sees that~\eqref{interp_q_cohomology} is actually an isomorphism of abelian groups.
+$H^1_\tau(\Gamma,Z)$ is a group since $Z$ is abelian; thus both sides of~\eqref{interp_q_cohomology} have canonical abelian group structures, and chasing definitions one easily sees that~\eqref{interp_q_cohomology} is actually an isomorphism of abelian groups.
 
@@
 For this recall $\theta\sigma = \sigma\theta$ and $G^{\sigma\theta}$ is a compact real form of~$G$.
-Furthermore $\sigma$ and $\theta$ coincide on $G^{\sigma\theta}$, therefore  $H_{\sigma}(\Gamma, G^{\sigma\theta})$ and  $H_{\sigma}(\Gamma, G^{\sigma\theta})$ are the same set, which we will denote by  $H_{\sigma\mid\theta}(\Gamma, G^{\sigma\theta})$.
+Furthermore $\sigma$ and $\theta$ coincide on $G^{\sigma\theta}$,
+therefore  $H_{\sigma}(\Gamma, G^{\sigma\theta})$ and  $H_{\sigma}(\Gamma, G^{\sigma\theta})$ are the same set,
+which we will denote by  $H_{\sigma\mid\theta}(\Gamma, G^{\sigma\theta})$.
 Now the inclusion $G^{\sigma\theta} \hookrightarrow G$ induces canonical maps 
@@
 By \cite[Corollary~4.4 and Corollary 4.7]{galois}, both of these maps are \emph{bijections}.
-Replacing~$G$ by $Z$ we get bijections $H^{1}_{\sigma}(\Gamma, Z) \leftarrow H_{\sigma\mid\theta}(\Gamma, Z^{\sigma\theta}) \rightarrow H^{1}_{\theta}(\Gamma, Z)$, and these fit with the bijections~\eqref{bij_cohom} into a commutative diagram
+Replacing~$G$ by $Z$ we get bijections $H^{1}_{\sigma}(\Gamma, Z) \leftarrow H_{\sigma\mid\theta}(\Gamma, Z^{\sigma\theta}) \rightarrow H^{1}_{\theta}(\Gamma, Z)$.
+These fit with the bijections~\eqref{bij_cohom} into a commutative diagram
 \[
@@
 This action preserves  the property of being large\footnote{AA 15-II-2024: should say something about this using the fact that it comes from automorphisms, either here or in the section on large reps}.
-It also preserves $L$-packets by~\cite[Lemma 6.18]{Contragredient}, and acts transitively on an~$L$-packet\footnote{AA 01-IV-2023: this point was missing, I think it's easy using Harish-Chandra's parametrization, the fact that every element of~$Q_{\sigma}(G)$ has a representative in the Weyl group, plus the description of discrete series L-packets in the Congragredient paper.
-The point about the action preserving $L$-packets also follows from this, it's perhaps a better argument than [Contragredient, Lemma 6.18] which may be better suited to the $\theta$-version.}
+It also preserves $L$-packets by~\cite[Lemma 6.18]{Contragredient}, and acts transitively on an~$L$-packet\footnote{AA 01-IV-2023: this point was missing, and I think details should be included.
+I think the transitivity is easy using  the description of discrete series L-packets in the Congragredient paper in terms of Harish-Chandra parameters, plus the fact that every element of~$Q_{\sigma}(G)$ has a representative in the Weyl group of a given elliptic maximal torus.
+The point about the action preserving $L$-packets also follows from this, I think; and perhaps it gives a better argument for the preservation of $L$-packets than [Contragredient, Lemma 6.18], which may be better suited to the $\theta$-version.}.
 

### 2024-04-01 whittaker.tex
Added reference to Serre's Galois cohomology textbook for H^1(sigma, U)

@@
 is $g\inv \sigma(g)\in \Stab_G(X)$.  Since $X$ is principal $\Stab_G(X)=ZU$ where $U$ is a unipotent group. 
-A standard fact is that $H^1(\sigma,U)=1$, and from this we see that, after multiplying $g$ on the right by an element of $u$, we can assume $g\inv \sigma(g)\in Z$.
+A standard fact is that $H^1_\sigma(\Gamma,U)=1$ \cite[Chap.~III, Proposition~6]{Serre_Galois}, and from this we see that, after multiplying $g$ on the right by an element of $u$, we can assume $g\inv \sigma(g)\in Z$.
 This is equivalent to: the image of $g$ in $\Gad$ is in $\Gad(\R)$.

### 2024-04-01 whittaker.tex
Further small typos

@@
  Recall $Q_{\theta}(\R)=\Gad^{\theta_{\ad}}/\Kad$.
-By definition $\Gad^{\theta_{\ad}}$ is contained in the normalizer $\mathrm{Norm}_G(K)$; therefore it acts on~$(\g, K)$-modules.
-Any element of~$\Kad$ takes a $(\g,K)$-module to an equivalent one, therefore $Q_{\theta}(\R)$ acts on~$(\g, K)$-module.
+By definition $\Gad^{\theta_{\ad}}$ is contained in the normalizer $\mathrm{Norm}_G(K)$; this determines a canonical action of $\Gad^{\theta_{\ad}}$ on~$(\g, K)$-modules.
+ Any element of~$\Kad$ takes a $(\g,K)$-module to an equivalent one, and this gives an action of $Q_{\theta}(\R)$ on equivalence classes of irreducible $(\g, K)$-modules.
  This preserves the property of being a discrete series, and of being large.

### 2024-04-01 whittaker.tex
Tiny changes

@@
 I think the transitivity is easy using  the description of discrete series L-packets in the Congragredient paper in terms of Harish-Chandra parameters, plus the fact that every element of~$Q_{\sigma}(G)$ has a representative in the Weyl group of a given elliptic maximal torus.
-The point about the action preserving $L$-packets also follows from this, I think; and perhaps it gives a better argument for the preservation of $L$-packets than [Contragredient, Lemma 6.18], which may be better suited to the $\theta$-version.}.
+The point about the action preserving $L$-packets also follows from this, I think; and perhaps it gives a better argument for the preservation of $L$-packets than [Contragredient, Lemma 6.18], which looks better suited to the $\theta$-version.}.
 
@@
 \cite[Section 2, p.~800]{HarrisHeOlafsson}.
-Applying this to the present situation, and going through the basics as in   \cite[Section~2]{HarrisHeOlafsson}, it immediately follows that $\pi \mapsto \WF(\pi)$ is equivariant under $Q_{\sigma}(G)$.
+Applying this to the present situation, and going through the basics as in   \cite[Section~2]{HarrisHeOlafsson}, it follows that $\pi \mapsto \WF(\pi)$ is equivariant under $Q_{\sigma}(G)$.
 \end{proof}

### 2024-04-02 whittaker.tex
First sketch for an introduction

@@
 
-Let $G$ be a connected complex reductive group, defined over $\R$, and suppose $G(\R)$ is quasisplit.
+Let $G$ be a connected complex reductive group, defined over $\R$, and consider the group $G(\R)$ of real points.
 
-We assume $G(\R)$ has discrete series representations, and fix an L-packet $\Pi$ of discrete series representations.
+Suppose $\pi$ is an irreducible representation of~$G(\R)$. Recall $\pi$ \emph{has a Whittaker model} when there exists a pair $(B(\R), \chi)$ where 
+\begin{enumerate}[(i)]
+\item $B$ is a Borel subgroup of~$G$ defined over~$\R$, with real points $B(\R)$;
+\item $\eta$ is a character of the nilpotent radical~$N(\R)$ of~$B(\R)$, subject to the condition that~$\eta$ is nontrivial on each simple root space;
+\end{enumerate}
+such that~$\pi$ embeds into the induced representation $\mathrm{Ind}_{N(\R)}^{G(\R)}(\chi)$.
+Of course this can happen if and only if there exists a Borel subgroup $B \subset G$ satisfying~(i); by definition this means~$G$ is \emph{quasisplit}, which we assume from now on.
 
-By a  {\it Whittaker datum} we mean a $G(\R)$-conjugacy class of pairs  $(B(\R),\eta)$ where $B(\R)$ is a
-Borel subgroup of $G(\R)$, 
-and $\eta$ is a non-degenerate character of the nilpotent radical $N(\R)$ of $B(\R)$. Non-degenerate means: non-trivial on each simple root space.
+We also say~$\pi$ is \emph{generic} when it has a Whittaker model.
+In that case, the pair $(B, \chi)$ is not uniquely determined by~$\chi$.
+However the $G(\R)$-conjugacy class of $(B(\R), \eta)$ is uniquely determined by the equivalence class of~$\pi$.
+We will call it the Whittaker datum attached to~$\pi$, denoted $\mathfrak{w}(\pi)$.
+More generally, by a  {\it Whittaker datum} we will mean a $G(\R)$-conjugacy class of pairs  $(B(\R),\eta)$ satisfying (i)-(ii).
 
-TODO: write about generic/large representations, and explain what's in the paper...
+We may view $\mathfrak{w}(\pi)$ as a useful invariant of generic representations.
+For instance, suppose~$\pi$ is a discrete series representation of~$G(\R)$.
+Then $\mathfrak{w}(\pi)$ singles out~$\pi$ among the discrete series representations of~$G(\R)$ having  the same infinitesimal and central characters.
+In the language of the local Langlands correspondence this means the Whittaker datum singles out~$\pi$ within its $L$-packet.
+
+More generally, Whittaker data play a subtle but key role in the local Langlands correspondence for reductive groups over arbitrary local fields (including the nonarchimedean case).
+For instance, given a Whittaker datum~$\mathfrak{w}$, it is expected that every tempered $L$-packet contains precisely one $\mathfrak{w}$-generic representation, which can be used as a basepoint for the internal structure of the $L$-packet.
+(Here insert refs to the work of Tasho and others.)
+
+Returning to real groups, there are of course other invariants that one may attach to an irreducible representation~$\pi$.
+We shall be concerned with two of them, defined using very different (and rather subtle) ideas.
+The first is the \emph{wavefront set}, which originally comes from microlocal analysis of the matrix coefficients.
+The second is the \emph{associated variety}, which is defined using algebro-geometric methods.
+Both consist of nilpotent elements of the dual of the Lie algebra of~$G$, and are defined as coadjoint orbits (of two different kinds).
+
+Now suppose~$\pi$ is a generic discrete series representation of~$G(\R)$.
+Then the Whittaker datum $\mathfrak{w}(\pi)$, the wavefront set $\WF(\pi)$ and the associated variety $\AV(\pi)$ basically contain the same information: given one of the three invariants, it is possible to reconstruct the other two.
+This is well known to the experts, but not so easy to extract from the literature, especially not if one wants to be explicit about how to pass back and forth between the three invariants.
+We have felt it worthwhile to give an account of the matter here.
+
+We shall do two things: 
+\begin{enumerate}
+\item Give an elementary proof that passage from~$\pi$ to $\mathfrak{w}(\pi)$, $\WF(\pi)$ and $\AV(\pi)$ defines bijections between generic discrete series in an $L$-packet for $G(\R)$, Whittaker data for $G(\R)$, and the appropriate sets of nilpotent orbits;
+\item Given one of the invariants $\mathfrak{w}(\pi)$, $\WF(\pi)$ and~$\AV(\pi)$, explain in the simplest possible terms how to reconstruct the other two. 
+\end{enumerate}
+Most statements in this note were already known, and we have tried to give new and simplified proofs for as many of them as we could.
+In the cases where we had to call on more difficult statements from the literature, we tried to give convenient references.
 
 \section{Some invariants of irreducible $(\g, K)$-modules}
+
+\footnote{AA 02-IV-2024: should of course rewrite this section once the rest is stable.}
 
@@
 Another invariant of an irreducible $(\g, K)$-module~$\pi$ is the \emph{wave-front set} of $\pi$, written $\WF(\pi)$. It is the union of a (finite) set of nilpotent $G(\R)$ orbits in
-$i\g(\R)^*=i\Hom_\R(\g(\R),\R)$.
-See \cite{howe_wave_front}, \cite{bv_local_structure}.\footnote{AA 14-II-2024: another convenient reference  for definitions re~$\WF(\pi)$ seems to be  Harris--He--Olafsson (Duke 2016).}
+$i\g(\R)^*=i\Hom_\R(\g(\R),\R)$. See \cite{howe_wave_front}, \cite{bv_local_structure}, \cite{HarrisHeOlafsson}.
 
@@
 
-Given a large discrete series representation~$\pi$ we consider the invariants of~$\pi$ defined by the Proposition: a Whittaker datum  $\mathfrak{w}(\pi) \in \mathfrak{W}(G(\R))$, a $K$-orbit $\AV^\flat(\pi) \in (\mathcal{O}_p \cap \mathfrak{s})/K$  and a nilpotent $G(\R)$-orbit $\WF^\flat(\pi) \in (\mathcal{O}_p \cap  i \g(\R))/G(\R)$.
+Given a large discrete series representation~$\pi$ we consider the invariants of~$\pi$ defined by the Proposition: a Whittaker datum  $\mathfrak{w}(\pi)$, a $K$-orbit $\AV^\flat(\pi) \in (\mathcal{O}_p \cap \mathfrak{s})/K$  and a nilpotent $G(\R)$-orbit $\WF^\flat(\pi) \in (\mathcal{O}_p \cap  i \g(\R))/G(\R)$.
 
@@
 
-It may be interesting to point out a variant on the proof of~(1). Given $X \in \Op \cap i\g(\R)$, the map 
+It may be interesting to point out a variant on the proof of~(1).\footnote{AA 01-IV-2024: well, is it interesting to keep it in the paper, or should we comment it out...?
+} Given $X \in \Op \cap i\g(\R)$, the map
 \begin{align} \label{bij_q_2} (\Omega_{X} \cap i\g(\R))/G(\R) & \to \kernel\left(H^1_\sigma(\Gamma,\mathrm{Stab}_G(X))\rightarrow H^1_\sigma(\Gamma,G)\right) \\ \mathrm{Ad}(g) \cdot X & \mapsto \text{class of $ g\sigma(g^{-1})$ in $H^1_\sigma(\Gamma,\mathrm{Stab}_G(X))$} \nonumber \end{align}
@@
 $$
-where the middle line uses $H^1_\sigma(\Gamma,\Stab_G(X))=H^1_\sigma(\Gamma,ZU)=H^1_\sigma(\Gamma,Z)$ as explained in the proof.
+where the middle line uses the equality $H^1_\sigma(\Gamma,\Stab_G(X))=H^1_\sigma(\Gamma,Z)$, which comes from the fact that $\Stab_G(X)=ZU$  as explained in the proof.
 The resulting bijection  $(\Op\cap i\g(\R))/G(\R)\simeq Q_\sigma(\R)$ is equivariant (for the actions of $Q_\sigma(G)$ on $(\Op\cap i\g(\R))/G(\R)$ described above, and the action of  $Q_\sigma(G)$ on itself by multiplication), and this gives another proof of~(1).

### 2024-04-02 whittaker.tex
Small typos

@@
 
-Suppose $\pi$ is an irreducible representation of~$G(\R)$. Recall $\pi$ \emph{has a Whittaker model} when there exists a pair $(B(\R), \chi)$ where 
+Suppose $\pi$ is an irreducible representation of~$G(\R)$. Recall $\pi$ has a \emph{Whittaker model} when there exists a pair $(B(\R), \chi)$ where 
 \begin{enumerate}[(i)]
@@
 Then $\mathfrak{w}(\pi)$ singles out~$\pi$ among the discrete series representations of~$G(\R)$ having  the same infinitesimal and central characters.
-In the language of the local Langlands correspondence this means the Whittaker datum singles out~$\pi$ within its $L$-packet.
+In the language of the local Langlands correspondence \cite{Langlands_CIRRAC, Contragredient}, this means the Whittaker datum singles out~$\pi$ within its $L$-packet.
 
-More generally, Whittaker data play a subtle but key role in the local Langlands correspondence for reductive groups over arbitrary local fields (including the nonarchimedean case).
-For instance, given a Whittaker datum~$\mathfrak{w}$, it is expected that every tempered $L$-packet contains precisely one $\mathfrak{w}$-generic representation, which can be used as a basepoint for the internal structure of the $L$-packet.
-(Here insert refs to the work of Tasho and others.)
+More generally, Whittaker data play a subtle but key role in the local Langlands correspondence for reductive groups over arbitrary local fields \cite{Borel, Kaletha_Taibi}, including the nonarchimedean case.
+For instance, given a Whittaker datum~$\mathfrak{w}$, it is expected that every tempered $L$-packet contains precisely one $\mathfrak{w}$-generic representation, which can be used as a basepoint for the internal structure of the $L$-packet~\cite{Kaletha_genericity}.
 
@@
 
-\section{The dictionary for large discrete series}
+\subsection{The invariants for large discrete series}
 
-\subsection{Statement of the results}
+The following uses rather deep results of representation theory.
 
-The following uses rather deep results of representation theory:
-\begin{proposition} Let~$\pi$ be the $(\g, K)$-module for a large discrete series representation of~$G(\R)$.  
+\begin{proposition} \label{invariants_ds}
+Let~$\pi$ be the $(\g, K)$-module for a large discrete series representation of~$G(\R)$.  
 \begin{enumerate}[(a)]
@@
 
-Given a large discrete series representation~$\pi$ we consider the invariants of~$\pi$ defined by the Proposition: a Whittaker datum  $\mathfrak{w}(\pi)$, a $K$-orbit $\AV^\flat(\pi) \in (\mathcal{O}_p \cap \mathfrak{s})/K$  and a nilpotent $G(\R)$-orbit $\WF^\flat(\pi) \in (\mathcal{O}_p \cap  i \g(\R))/G(\R)$.
+\section{The dictionary for large discrete series}
+
+\subsection{Statement of the results}
+
+Given a large discrete series representation~$\pi$ we consider the invariants of~$\pi$ defined by Proposition~\ref{invariants_ds}: a Whittaker datum  $\mathfrak{w}(\pi)$, a $K$-orbit $\AV^\flat(\pi)$ in $\mathcal{O}_p \cap \mathfrak{s}$, and a $G(\R)$-orbit $\WF^\flat(\pi)$ in $(\mathcal{O}_p \cap  i \g(\R))$.
 
@@
 Furthermore $\sigma$ and $\theta$ coincide on $G^{\sigma\theta}$,
-therefore  $H_{\sigma}(\Gamma, G^{\sigma\theta})$ and  $H_{\sigma}(\Gamma, G^{\sigma\theta})$ are the same set,
+therefore  $H_{\sigma}(\Gamma, G^{\sigma\theta})$ and  $H_{\theta}(\Gamma, G^{\sigma\theta})$ are the same set,
 which we will denote by  $H_{\sigma\mid\theta}(\Gamma, G^{\sigma\theta})$.

### 2024-04-15 whittaker.tex
First attempt at writing up our Sekiguchi proof

@@
 Second, the action of~$K=G^\theta$ on $\Op \cap \s$ is trivial on~$Z_K=Z^\theta$, and factors through an action of~$\Kad$.
-It is then easy to check that if two elements of $\Op \cap \s$ lie in on the same $\Kad$-orbit, then for every $g \in \Gad^{\theta_{\ad}}$, the elements  $\tilde{g} \cdot x$ and $\tilde{g} \cdot y$ lie on the same $\Kad$-orbit.
+It is then easy to check that if two elements of $\Op \cap \s$ lie in on the same $\Kad$-orbit, then for every $g \in \Gad^{\theta_{\ad}}$, the elements  ${g} \cdot x$ and ${g} \cdot y$ lie on the same $\Kad$-orbit.
 This determines an action of~$Q_\theta(G)$ on $(\Op \cap \s)/K$, which is the one featured in the next statement.
@@
 
-As for~(2), it is a consequence of the precise definition of the associated variety.
+As for~(2), it follows directly from the definition of the associated variety.
 This uses filtrations of the universal enveloping algebra of~$\g$ which are all invariant under $\Gad^{\theta_{\ad}}$: see for instance the Introduction of~\cite{vogan_bowdoin}.
@@
 
-\subsection{From Whittaker data to real orbits ((2) $\leftrightarrow$ (4))}
+\subsection{Whittaker data to real orbits ((2) $\leftrightarrow$ (4))}
 
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:matumoto}
 The bijection (2)$\leftrightarrow$(4) takes the Whittaker datum $(B(\R),X)$ to
@@
 
-\subsection{Connection between ((3) $\leftrightarrow$ (4)) and the Kostant--Sekiguchi correspondence }
-
-\begin{lemma} The bijection (3)--(4) is induced by the Kostant--Sekiguchi correspondence.
-\end{lemma}
-
-\begin{proof} If we allow ourselves to use deep results, then this is a particular case of the main theorem of~\cite{SV1} (Theorem 1.4).
-In a perfect world, we could also give a more elementary argument, using the description of the Kostant--Sekiguchi correspondence in~\cite{galois} and the descriptions of the actions above; but  I'm not sure it's possible to do it without encountering a basepoint issue.
-Another possibility, suggested by Jeff, is to extract it from  arguments in Adams--Kaletha (e.g.
-the fact that $\WF(\pi)$ is the asymptotic cone of the $G(\R)$-orbit of the HC parameter of~$\pi$, and the connection with the Kostant section).
-\textcolor{red}{AA (27-III-2024): I think this last strategy should indeed work, but there are details to discuss with Jeff to complete the argument, and if everything turns out OK then  I'll write up the proof here.}\end{proof}
-
-As a consequence we can make the bijection (3) $\leftrightarrow$ (4) explicit, following \cite[Section~1]{avav}.
-
-Suppose $E_\R\in \Op\cap i\g(\R)$. Then we may choose an $SL(2)$-triple $(H_\R,E_\R,F_\R)$ with $F_\R$  contained in $i\g(\R)$,
-which implies $H_\R\in \g(\R)$. 
-After conjugating by~$G(\R)$ we may further assume $\theta(E_\R)=-F_\R$.
-The Sekiguchi correspondence takes the $G(\R)$-orbit of~$E_\R$ to the $K$-orbit of
-$$
-E_\theta=\frac12(-iE_\R-iF_\R+H_\R)\in \N\cap \s.
-$$
-
-Computing the map in the other direction goes as follows.
-Suppose $E_\theta\in \Op\cap\s$. Choose an $SL(2)$-triple  $(E_\theta H_\theta,F_\theta)$ with
-$F_\theta\in\s$, which implies $H_\theta\in\k$. After conjugating by $K$ we may further assume $\sigma(E_\theta)=F_\theta$.
-Then the Sekiguchi correspondence takes the $K$-orbit of $E_\theta$ to the $G(\R)$-orbit of 
-$$
-E_\R=\frac i2(E_\theta-F_\theta-H_\theta)\in\N\cap i\g(\R).
-$$
-
-\subsection{From large discrete series to $K$-orbits ((1) $\leftrightarrow$ (3))}
+\subsection{Large discrete series to $K$-orbits ((1) $\leftrightarrow$ (3))}
 
@@
 
-\subsection{From large discrete series to real orbits ((1) $\leftrightarrow$ (4))}
+\subsection{Large discrete series to real orbits ((1) $\leftrightarrow$ (4))}
+
+Suppose $\pi$ is a discrete series representation.
+Choose a compact Cartan subgroup $T$, and let $\lambda\in\t^*$ be the Harish-Chandra parameter of $\pi$.
+Identify $\lambda$ with an element $H_\pi\in i\t\subset i\g$ using the isomorphism $\t\simeq \t^*$ induced by the Killing form. 
+Define
+\begin{equation} \label{semisimple_orbit_HC} \mathcal{O}_{\pi}=\quad \text{$G(\R)$-orbit of the Harish-Chandra parameter $H_\pi$}.\end{equation}
+
+Consider the \emph{asymptotic cone} of $\mathcal{O}_\pi$:
+\[ \AC(\mathcal{O}_\pi) = \dots \]
+
+\begin{lemma} \label{lem:WF_and_AC}
+Let~$\pi$ be a discrete series representation of $G(\R)$. The wave-front set $\WF(\pi)$ is equal to the asymptotic cone $\AC(\mathcal{O}_\pi)$.
+\end{lemma}
+
+\subsection{Large discrete series to Whittaker data ((1) $\leftrightarrow$ (2))}
+
+We recall a recent result of the first author (JDA) and Kaletha, which spells out the connection between large discrete series and Whittaker data using  {\it Kostant sections}.
+Let~$X$ be a regular nilpotent element of~$\g$, and suppose~$X$ fits into an $\SL(2)$-triple $(X, H, Y)$.
+The Kostant section~$\Kostant{X}$ is the affine subspace $X + \mathrm{Cent}_{\g}(Y)$ of~$\g$.
+It depends on the choice of $\SL(2)$-triple, but if $X \in \g(\R)$, then the $G(\R)$-conjugacy class of~$\Kostant{X}$ depends only on the $G(\R)$-conjugacy class of~$X$.
+
+\begin{proposition}[\cite{adams_kaletha}]\label{JeffTasho_criterion}
+Suppose $\pi$ is a generic discrete series representation of~$G(\R)$. Suppose~$\pi$ be a Whittaker datum for~$G(\R)$, and let~$X \in i\g(\R)$ be a regular nilpotent element such that $\w = \w_X$. 
+Then $\pi$ is $\w$-generic if and only if $\Kostant{X}$ meets $\mathcal{O}_\pi$. 
+\end{proposition}
+
+This confirms that  the corresponding statement  in the $p$-adic case \cite{debacker_reeder_generic, kaletha_epipelagic}
+applies to the real case as well.
+
+\subsection{Connection between ((3) $\leftrightarrow$ (4)) and the Kostant--Sekiguchi correspondence }
+
+Theorem~\ref{th:main} gives a bijection between the set $(\Op \cap \s)/K$ of principal nilpotent~$K$-orbits and the set $(\Op \cap i\g(\R))/G(\R)$ of principal nilpotent~$G(\R)$-orbits.
+
+It is well known that a natural bijection between nilpotent $K$-orbits and nilpotent $G(\R)$-orbits can be defined in more elementary terms.
+This is the Kostant--Sekiguchi correspondence~\cite{}.
+Furthermore, it is a deep result of Schmid and Vilonen (the main result of~\cite{SV1}) that the wavefront set and the associated variety are exchanged by this correspondence.
+(As a historical aside, the Kostant--Sekiguchi correspondence was discovered on the basis that the correspondence $\AV(\pi) \leftrightarrow \WF(\pi)$ might be expressed in elementary terms.)
+
+Therefore, a particular case of Schmid and Vilonen's theorem says: 
+\begin{proposition} \label{Sekiguchi_result} The bijection (3)--(4) is induced by the Kostant--Sekiguchi correspondence.
+\end{proposition} 
+We shall do two things here.
+First, we will quote a result of \cite{AVAV} which makes this case of the Kostant--Sekiguchi correspondence completely explicit.
+Second, we shall give a new and elementary proof of Proposition~\ref{Sekiguchi_result}: this avoids the use of Schmid and Vilonen's difficult results, and instead uses the results above (in particular Proposition~\ref{JeffTasho_criterion}).
+
+\subsubsection{The Sekiguchi correspondence for principal nilpotent orbits}
+
+Let spell out the special case of the Sekiguchi correspondence which is of interest here. 
+Suppose $E_\R\in \Op\cap i\g(\R)$. Then we may choose an $SL(2)$-triple $(H_\R,E_\R,F_\R)$ with $F_\R$  contained in $i\g(\R)$,
+which implies $H_\R\in \g(\R)$. 
+After conjugating by~$G(\R)$ we may further assume $\theta(E_\R)=-F_\R$.
+The Sekiguchi correspondence takes the $G(\R)$-orbit of~$E_\R$ to the $K$-orbit of
+$$
+E_\theta=\frac12(-iE_\R-iF_\R+H_\R)\in \N\cap \s.
+$$
+
+Computing the map in the other direction goes as follows.
+Suppose $E_\theta\in \Op\cap\s$. Choose an $SL(2)$-triple  $(E_\theta H_\theta,F_\theta)$ with
+$F_\theta\in\s$, which implies $H_\theta\in\k$. After conjugating by $K$ we may further assume $\sigma(E_\theta)=F_\theta$.
+Then the Sekiguchi correspondence takes the $K$-orbit of $E_\theta$ to the $G(\R)$-orbit of 
+\begin{equation}\label{def_E_R}
+E_\R=\frac i2(E_\theta-F_\theta-H_\theta)\in\N\cap i\g(\R).
+\end{equation}
+
+\subsubsection{A simple proof of Proposition~\ref{Sekiguchi_result}}
+
+Consider the principal nilpotent element~$E_\pi$ defined in~\eqref{e:Epi}.
+We define another regular nilpotent element  $E_\R$ by using $E_\pi$ as $E_\theta$ in~\eqref{def_E_R}.
+We know that the associated variety of $\pi$ is the closure of $K \cdot E_\pi$ (Proposition~\ref{}), so the image of $\AV(\pi)$ by the Sekiguchi correspondence is the closure of the $G(\R)$-orbit of $E_\R$.
+We want to check that $\WF(\pi)$
+
+By Lemma~\ref{lem:matumoto} it is enough to check that $\pi$ is $\w$-generic for the Whittaker datum $\w$ corresponding to~$E_\R$.
+By Proposition~\ref{JeffTasho_criterion} this is the case if and only if the Kostant section $\Kostant{E_\R}$ meets $\mathcal{O}_\pi$.
+
+Now, we know that $\Kostant{E_\R}=E_\R+\mathrm{Cent}_\g(F_\R)$ contains $E_\R-F_\R = H_\theta$.
+In general the orbits $\mathcal{O}_\pi$ and $G(\R) \cdot H_\theta$ are disjoint.
+Nevertheless $H_{\lambda}$ and $H_\theta=[E_\theta, F_\theta]$ are in the same Weyl chamber.
+Therefore the result follows from:
+
+\begin{proposition}\label{prop:AC_chamber} Let $\mathcal{C} \subset \t$ be a large open Weyl chamber.
+If $H$ and $H'$ are two points of~$\mathcal{C}$ and if $\mathcal{O}, \mathcal{O}'$ are the   $G(\R)$-orbits of $H$ and $H'$, then $\AC(\mathcal{O})=\AC(\mathcal{O}')$.
+\end{proposition}
+
+We shall prove this in the rest of this section, based on the following lemma.
+
+\begin{lemma}\label{lem:Kost_and_AC} Let $\mathcal{O}$ be a regular semisimple orbit and  let $X$ be a regular nilpotent element.
+Then $\Kostant{X}$ meets~$\mathcal{O}$ if and only if $X$ is in the asymptotic cone~$\AC(\mathcal{O})$.
+\end{lemma}
+\begin{proof} \textcolor{red}{See if we spell it all out (keeping in mind that half of it is in the paper with Tasho, but should probably be included for convenience since part of the arguments are similar).
+Or maybe it's actually possible to give just a reference to Fresse--Mehdi.} \end{proof}
+
+\begin{lemma}\label{lem:AC_containment} Let~$\Omega$ be a regular nilpotent $G(\R)$-orbit, and let $\mathcal{E}_\Omega \subset \g$ be the union of all regular semisimple orbits~$\mathcal{O}$ such that $\AC(\mathcal{O})$ contains~$\Omega$.
+Then $\mathcal{E}_\Omega$ is open.
+\end{lemma}
+
+\begin{proof}
+Let $F$ be an element of~$\Omega$, and let $\mathcal{O}$  be a regular semisimple orbit such that $\AC(\mathcal{O})$ contains~$\Omega$.
+Then $\Kostant{F}$ meets $\mathcal{O}$ by  Lemma~\ref{lem:Kost_and_AC}. 
+Fix $X$ in $\mathcal{O} \cap \Kostant{F}$.
+We have $X =F+Y$ where $Y$ belongs to the centralizer $\mathrm{Cent}_\g(F)$.
+Since this centralizer is transverse to the $G(\R)$-orbits and has dimension $\dim(\g(\R))-\dim(\t(\R))$,
+there exists an open neighborhood of~$X$ consisting of (regular semisimple) orbits  which meet $\Kostant(F)$.
+Using Lemma~\ref{lem:Kost_and_AC} again, we see that all those orbits $\mathcal{O}'$ satisfy $F \in \AC(\mathcal{O}')$,
+which implies that $\Omega = G(\R) \cdot F$ is contained in $\AC(\mathcal{O}')$.
+This proves that $\mathcal{E}_\Omega$ contains an open neighborhood of any of its points, hence is open.   \end{proof}
+
+Let us prove Proposition~\ref{prop:AC_chamber}.
+
+Given an element $H$ of $\mathcal{C}$ we shall write $\mathcal{O}_H$ for the $G(\R)$-orbit of~$H$.
+For any regular nilpotent orbit~$\Omega$ let $E^{\mathcal{C}}_\Omega$  denote the set of $H \in \mathcal{C}$ such that $\AC(\mathcal{O}_H)$ contains $\Omega$; byLemma~\ref{lem:AC_containment}  we know that   $E^{\mathcal{C}}_\Omega$ is an open subset of~$\mathcal{C}$.
+
+Now let $\mathcal{S}$ be the unit sphere of $\t$ for the norm induced by the Killing form, and $\mathcal{S} \cap \mathcal{C}$ be the intersection of $\mathcal{S}$ with the given chamber.
+This is an open subset of $\mathcal{S}$.
+The previous arguments show that the the radial projection $\mathcal{S}_{\Omega}$ of  $E^{\mathcal{C}}_\Omega$ on $\mathcal{S}$ is an open subset of $\mathcal{S} \cap \mathcal{C}$.
+
+Given regular nilpotent orbits $\Omega$ and $\Omega'$, we deduce that $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$ is an open subset of the $\mathcal{S} \cap \mathcal{C}$.
+
+Now consider the set $\Sigma$ of all points on $\mathcal{S} \cap \mathcal{C}$ which arise as the radial projection of the Harish-Chandra parameter~$H$ of some large discrete series representation.
+Since the Harish-Chandra parameters for discrete series are (a translate of) an integral lattice, the set $\Sigma$ is dense in $\mathcal{S} \cap \mathcal{C}$.
+Therefore if the open set $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$ is nonempty, there must exist at least one large discrete series representation~$\pi$ whose Harish-Chandra projects to $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$.
+By Lemma~\ref{lem:WF_and_AC} this means $\Omega$ and $\Omega'$ must be contained in $\WF(\pi)$, which implies $\Omega = \Omega'$ since the wavefront set is the closure of a single orbit.
+
+We conclude that if $\Omega \neq \Omega'$, then $\mathcal{S}_\Omega$ and $\mathcal{S}_\Omega$ are disjoint, and therefore $\mathcal{E}^\t_{\Omega}$ and $\mathcal{E}^t_{\Omega'}$ are disjoint open subsets of~$\mathcal{C}$.
+Since $\mathcal{C}$ is connected and equal to the union of all subsets $\mathcal{E}^{\mathcal{C}}_{\Omega}$, the chamber $\mathcal{C}$ must be equal to a single $\mathcal{E}^\t_\Omega$.
+This concludes the proof of Proposition~\ref{prop:AC_chamber}, and therefore also of Proposition~\ref{Sekiguchi_result}.
+
+\subsection{Where to put this, if we keep it?}
 
@@
 
-We can also express (1)$\mapsto$(4) using the {\it Kostant section}.
-Recall that if~$X$ is a regular nilpotent element of~$\g$ and fits into an $\SL(2)$-triple $(X, H, Y)$, the Kostant section~$\Kostant{X}$ is the affine subspace $X + \mathrm{Cent}_{\g}(Y)$ of~$\g$.
-It depends on the choice of $\SL(2)$-triple, but if $X \in \g(\R)$, then the $G(\R)$-conjugacy class of~$\Kostant{X}$ depends only on the $G(\R)$-conjugacy class of~$X$.
-
-Suppose $\pi$ is a discrete series representation.
-Choose a compact Cartan subgroup $T$, and let $\lambda\in\t^*$ be the Harish-Chandra parameter of $\pi$.
-Identify $\lambda$ with an element $H_\pi\in i\t\subset i\g$ using the isomorphism $\t\simeq \t^*$ induced by the Killing form.
-
-\begin{proposition}[\cite{adams_kaletha}]
-Suppose $\pi$ is a generic discrete series representation. Then $\pi$ is $\w$-generic
-for a unique Whittaker datum $\w$.
-Write $\w=\w_X$ for some regular nilpotent element $X\in i\g(\R)$.
-Then $H_\pi$ is $G(\R)$-conjugate to an element of the Kostant section of $X$.\footnote{AA 23-II-2024: would probably be useful to explain the connection with $\pi \mapsto \WF(\pi)$ in more detail...\\ AA 27-III-2024: furthermore, if the Kostant section is used in the proof that $\AV \leftrightarrow \WF$ coincides with Sekiguchi, then we should move this subsection to an earlier place, and then probably this discussion will have to be reworked.
-}
-\end{proposition}
-
-This confirms that  the corresponding statement  in the $p$-adic case \cite{debacker_reeder_generic, kaletha_epipelagic}
-applies to the real case as well.
-
 \bibliographystyle{plain}

### 2024-04-15 whittaker.tex
Small edits

@@
 It is well known that a natural bijection between nilpotent $K$-orbits and nilpotent $G(\R)$-orbits can be defined in more elementary terms.
-This is the Kostant--Sekiguchi correspondence~\cite{}.
-Furthermore, it is a deep result of Schmid and Vilonen (the main result of~\cite{SV1}) that the wavefront set and the associated variety are exchanged by this correspondence.
+This is the Kostant--Sekiguchi correspondence~\cite{sekiguchi}.
+Furthermore, it is a deep theorem of Schmid and Vilonen (the main result of~\cite{SV1}) that the wavefront set and the associated variety are exchanged by this correspondence.
 (As a historical aside, the Kostant--Sekiguchi correspondence was discovered on the basis that the correspondence $\AV(\pi) \leftrightarrow \WF(\pi)$ might be expressed in elementary terms.)
@@
 First, we will quote a result of \cite{AVAV} which makes this case of the Kostant--Sekiguchi correspondence completely explicit.
-Second, we shall give a new and elementary proof of Proposition~\ref{Sekiguchi_result}: this avoids the use of Schmid and Vilonen's difficult results, and instead uses the results above (in particular Proposition~\ref{JeffTasho_criterion}).
+Second, we shall give a new and elementary proof of Proposition~\ref{Sekiguchi_result}: this avoids the use of Schmid and Vilonen's difficult results, and instead uses the results above (in particular Proposition~\ref{JeffTasho_criterion}) as the main ingredients.
 
-\subsubsection{The Sekiguchi correspondence for principal nilpotent orbits}
-
-Let spell out the special case of the Sekiguchi correspondence which is of interest here. 
+\subsubsection{The Sekiguchi correspondence for principal nilpotent orbits}\label{sec:concrete_sek}
+\footnote{AA 2024-IV-15: should correct the formulas here.}
+Let us spell out the special case of the Sekiguchi correspondence which is of interest here. 
 Suppose $E_\R\in \Op\cap i\g(\R)$. Then we may choose an $SL(2)$-triple $(H_\R,E_\R,F_\R)$ with $F_\R$  contained in $i\g(\R)$,
@@
 
-\subsubsection{A simple proof of Proposition~\ref{Sekiguchi_result}}
+\subsubsection{A simple proof of Proposition~\ref{Sekiguchi_result}}\label{sec:sekiguchi_proof}
 
@@
 We define another regular nilpotent element  $E_\R$ by using $E_\pi$ as $E_\theta$ in~\eqref{def_E_R}.
-We know that the associated variety of $\pi$ is the closure of $K \cdot E_\pi$ (Proposition~\ref{}), so the image of $\AV(\pi)$ by the Sekiguchi correspondence is the closure of the $G(\R)$-orbit of $E_\R$.
+We know that the associated variety of $\pi$ is the closure of $K \cdot E_\pi$ (Lemma~\ref{l:pi_to_av}), so the image of $\AV(\pi)$ by the Sekiguchi correspondence is the closure of the $G(\R)$-orbit of $E_\R$.
 We want to check that $\WF(\pi)$
@@
 
-Now, we know that $\Kostant{E_\R}=E_\R+\mathrm{Cent}_\g(F_\R)$ contains $E_\R-F_\R = H_\theta$.
+Now, we know that $\Kostant{E_\R}=E_\R+\mathrm{Cent}_\g(F_\R)$ contains $E_\R-F_\R = H_\theta$\footnote{AA 2024-IV-15: insert the correct version once we've checked the Sekiguchi formulas in the previous paragraph.
+}
+.
 In general the orbits $\mathcal{O}_\pi$ and $G(\R) \cdot H_\theta$ are disjoint.
@@
 \begin{proposition}\label{prop:AC_chamber} Let $\mathcal{C} \subset \t$ be a large open Weyl chamber.
-If $H$ and $H'$ are two points of~$\mathcal{C}$ and if $\mathcal{O}, \mathcal{O}'$ are the   $G(\R)$-orbits of $H$ and $H'$, then $\AC(\mathcal{O})=\AC(\mathcal{O}')$.
+If $H$ and $H'$ are  points of~$\mathcal{C}$ and $\mathcal{O}, \mathcal{O}'$ are the   $G(\R)$-orbits of $H$ and $H'$, then $\AC(\mathcal{O})=\AC(\mathcal{O}')$.
 \end{proposition}
@@
 \end{lemma}
-\begin{proof} \textcolor{red}{See if we spell it all out (keeping in mind that half of it is in the paper with Tasho, but should probably be included for convenience since part of the arguments are similar).
-Or maybe it's actually possible to give just a reference to Fresse--Mehdi.} \end{proof}
+\begin{proof} See if we spell it  out (one direction is in Adams--Kaletha, but parts of the arguments are similar so it might be more convenient include both directions...).
+Maybe it's actually possible just refer to Fresse--Mehdi with pointers.
+\end{proof}
 
@@
 Let us prove Proposition~\ref{prop:AC_chamber}.
-
 Given an element $H$ of $\mathcal{C}$ we shall write $\mathcal{O}_H$ for the $G(\R)$-orbit of~$H$.
-For any regular nilpotent orbit~$\Omega$ let $E^{\mathcal{C}}_\Omega$  denote the set of $H \in \mathcal{C}$ such that $\AC(\mathcal{O}_H)$ contains $\Omega$; byLemma~\ref{lem:AC_containment}  we know that   $E^{\mathcal{C}}_\Omega$ is an open subset of~$\mathcal{C}$.
+For any regular nilpotent orbit~$\Omega$ let $E^{\mathcal{C}}_\Omega$  denote the set of $H \in \mathcal{C}$ such that $\AC(\mathcal{O}_H)$ contains $\Omega$; by Lemma~\ref{lem:AC_containment}  we know that   $E^{\mathcal{C}}_\Omega$ is an open subset of~$\mathcal{C}$.
 
@@
 
-\subsection{Where to put this, if we keep it?}
+\subsubsection{Where to put this, if we keep it?}
 
-There are several ways to describe this bijection.\footnote{AA 23-II-2024: I think we should mention the version with the asymptotic cone of the orbit of~$H_\pi$, which is extremely clean and concrete.
-} We choose to compose the maps (1)$\leftrightarrow$(3)$\leftrightarrow$(4).
-Here is the conclusion.
+As we saw the correspondence $\pi \leftrightarrow \WF(\pi)$ can be described using the asymptotic cone of the semisimple orbit of the Harish-Chandra parameter.
+We used this in the proof of Proposition~\ref{Sekiguchi_result}.
+Now, the results of Sections~\ref{sec:concrete_sek} and~\ref{sec:sekiguchi_proof} provide another description of $\WF(\pi)$ from the Harish-Chandra parameter: we can compose the maps (1)$\leftrightarrow$(3)$\leftrightarrow$(4).
+This gives the following rather concrete conclusion.
 

### 2024-04-15 whittaker.tex
More tinkering

@@
 \begin{enumerate}[(i)]
-\item $B$ is a Borel subgroup of~$G$ defined over~$\R$, with real points $B(\R)$;
-\item $\eta$ is a character of the nilpotent radical~$N(\R)$ of~$B(\R)$, subject to the condition that~$\eta$ is nontrivial on each simple root space;
+\item $B$ is a Borel subgroup of~$G$ defined over~$\R$, with real points $B(\R)$,
+\item $\eta$ is a character of the nilpotent radical~$N(\R)$ of~$B(\R)$, subject to the condition that~$\eta$ is nontrivial on each simple root space,
 \end{enumerate}
 such that~$\pi$ embeds into the induced representation $\mathrm{Ind}_{N(\R)}^{G(\R)}(\chi)$.
-Of course this can happen if and only if there exists a Borel subgroup $B \subset G$ satisfying~(i); by definition this means~$G$ is \emph{quasisplit}, which we assume from now on.
+Of course this can happen if and only if there exists a Borel subgroup $B \subset G$ satisfying~(i); by definition this condition means~$G$ is \emph{quasisplit}, which we assume from now on.
 
@@
 Then the Whittaker datum $\mathfrak{w}(\pi)$, the wavefront set $\WF(\pi)$ and the associated variety $\AV(\pi)$ basically contain the same information: given one of the three invariants, it is possible to reconstruct the other two.
-This is well known to the experts, but not so easy to extract from the literature, especially not if one wants to be explicit about how to pass back and forth between the three invariants.
+This is well known to the experts, but some aspects of this discussion are not  easy to extract from the literature, especially not if one wants to be explicit about how to pass back and forth between the three invariants.
 We have felt it worthwhile to give an account of the matter here.
@@
 
-\footnote{AA 02-IV-2024: should of course rewrite this section once the rest is stable.}
+\footnote{AA 02-IV-2024: I didn't make any effort at polishing this in recent weeks; we should of course rewrite this section once the rest is stable.}
 
@@
 Now, we know that $\Kostant{E_\R}=E_\R+\mathrm{Cent}_\g(F_\R)$ contains $E_\R-F_\R = H_\theta$\footnote{AA 2024-IV-15: insert the correct version once we've checked the Sekiguchi formulas in the previous paragraph.
-}
-.
+}.
 In general the orbits $\mathcal{O}_\pi$ and $G(\R) \cdot H_\theta$ are disjoint. 
-Nevertheless $H_{\lambda}$ and $H_\theta=[E_\theta, F_\theta]$ are in the same Weyl chamber.
+Nevertheless $H_{\lambda}$ and $H_\theta=[E_\theta, F_\theta]$ are in the same Weyl chamber\footnote{AA 2024-IV-15: should probably explain a bit more why this is correct.}.
 Therefore the result follows from:
@@
 \end{proof}
+
+The connection between Lemma~\ref{lem:Kost_and_AC} and Proposition~\ref{prop:AC_chamber} is that Lemma~\ref{lem:Kost_and_AC}  implies the  following observation on the behavior of the asymptotic cone of regular semisimple orbits:
 

### 2024-04-16 whittaker.tex
Typos and more tinkering

@@
 \newcommand{\Kostant}[1]{\mathcal{K}(#1)}
-
+\newcommand{\ECom}{\mathcal{E}^{\mathcal{C}}_\Omega}
 \begin{document}
@@
 
-Consider the \emph{asymptotic cone} of $\mathcal{O}_\pi$:
-\[ \AC(\mathcal{O}_\pi) = \dots \]
+Consider the \emph{asymptotic cone} of $\mathcal{O}_\pi$ (see e.g. \cite[Section 3]{AVAV}) :
+\[ \AC(\mathcal{O}_\pi) = \left\{ v \in \g \ : \ \text{$\exists (\varepsilon_n, x_n)\in (\R_+ \times \mathcal{O}_\pi)^\mathbb{N}$ such that $\varepsilon_n \to 0$ and $\varepsilon_n x_n \to v$}  \right\}.
+\]
 
@@
 \end{lemma}
+
+In Section~\ref{sec:alternate_WF} below we will  give another simple description of~$\WF(\pi)$, based on the description of $\AV(\pi)$ in the previous paragraph and on the Sekiguchi correspondence.
 
@@
 \footnote{AA 2024-IV-15: should correct the formulas here.}
-Let us spell out the special case of the Sekiguchi correspondence which is of interest here. 
+Let us spell out the special case of the Sekiguchi correspondence which is of interest here. We follow~\cite[Section~2]{AVAV}.
+
 Suppose $E_\R\in \Op\cap i\g(\R)$. Then we may choose an $SL(2)$-triple $(H_\R,E_\R,F_\R)$ with $F_\R$  contained in $i\g(\R)$,
@@
 Given an element $H$ of $\mathcal{C}$ we shall write $\mathcal{O}_H$ for the $G(\R)$-orbit of~$H$.
-For any regular nilpotent orbit~$\Omega$ let $E^{\mathcal{C}}_\Omega$  denote the set of $H \in \mathcal{C}$ such that $\AC(\mathcal{O}_H)$ contains $\Omega$; by Lemma~\ref{lem:AC_containment}  we know that   $E^{\mathcal{C}}_\Omega$ is an open subset of~$\mathcal{C}$.
+For any regular nilpotent orbit~$\Omega$ let $\ECom$  denote the set of $H \in \mathcal{C}$ such that $\AC(\mathcal{O}_H)$ contains $\Omega$; by Lemma~\ref{lem:AC_containment}  we know that   $\ECom$ is an open subset of~$\mathcal{C}$.
 
@@
 Therefore if the open set $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$ is nonempty, there must exist at least one large discrete series representation~$\pi$ whose Harish-Chandra projects to $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$.
-By Lemma~\ref{lem:WF_and_AC} this means $\Omega$ and $\Omega'$ must be contained in $\WF(\pi)$, which implies $\Omega = \Omega'$ since the wavefront set is the closure of a single orbit.
+By Lemma~\ref{lem:WF_and_AC} this means $\Omega$ and $\Omega'$ must be contained in $\WF(\pi)$, which implies $\Omega = \Omega'$ since the wavefront set is the closure of a single orbit if $\pi$ is a large discrete series.
 
-We conclude that if $\Omega \neq \Omega'$, then $\mathcal{S}_\Omega$ and $\mathcal{S}_\Omega$ are disjoint, and therefore $\mathcal{E}^\t_{\Omega}$ and $\mathcal{E}^t_{\Omega'}$ are disjoint open subsets of~$\mathcal{C}$.
-Since $\mathcal{C}$ is connected and equal to the union of all subsets $\mathcal{E}^{\mathcal{C}}_{\Omega}$, the chamber $\mathcal{C}$ must be equal to a single $\mathcal{E}^\t_\Omega$.
+We conclude that if $\Omega \neq \Omega'$, then $\mathcal{S}_\Omega$ and $\mathcal{S}_\Omega$ are disjoint, and therefore $\ECom$ and $\mathcal{E}^{\mathcal{C}}_{\Omega'}$ are disjoint open subsets of~$\mathcal{C}$.
+Since $\mathcal{C}$ is connected and equal to the union of all subsets $\mathcal{E}^{\mathcal{C}}_{\Omega}$, the chamber $\mathcal{C}$ must be equal to a single $\ECom$.
 This concludes the proof of Proposition~\ref{prop:AC_chamber}, and therefore also of Proposition~\ref{Sekiguchi_result}.
 
-\subsubsection{Where to put this, if we keep it?}
+\subsubsection{A simple description of the wavefront set}\label{sec:alternate_WF}
 

### 2024-04-25 whittaker.tex
in the middle of many changes

@@
 \newcommand{\AV}{\mathrm{AV}}
+\newcommand{\Wh}{\mathrm{Wh}}
 \newcommand{\WF}{\mathrm{WF}}
@@
 
-Suppose $\pi$ is an irreducible representation of~$G(\R)$. Recall $\pi$ has a \emph{Whittaker model} when there exists a pair $(B(\R), \chi)$ where 
+Suppose $\pi$ is an irreducible representation of~$G(\R)$.
+We say $\pi$ has a {\it Whittaker model}, or is {\it generic},  if
+$\pi$ embeds into the induced
+representation $\mathrm{Ind}_{N(\R)}^{G(\R)}(\chi)$ for some $(B,\eta)$ satisfying:
+We consider pairs
 \begin{enumerate}[(i)]
 \item $B$ is a Borel subgroup of~$G$ defined over~$\R$, with real points $B(\R)$,
-\item $\eta$ is a character of the nilpotent radical~$N(\R)$ of~$B(\R)$, subject to the condition that~$\eta$ is nontrivial on each simple root space,
+\item $\eta$ is a character of the nilpotent radical~$N(\R)$ of~$B(\R)$, subject to the condition that~$\eta$ is nontrivial on each simple root space.
 \end{enumerate}
-such that~$\pi$ embeds into the induced representation $\mathrm{Ind}_{N(\R)}^{G(\R)}(\chi)$.
-Of course this can happen if and only if there exists a Borel subgroup $B \subset G$ satisfying~(i); by definition this condition means~$G$ is \emph{quasisplit}, which we assume from now on.
+The existence of a Borel subgroup satisfying (i) is the definition of $G$ being quasisplit, which we assume holds from now on.
+Clearly this condition only depends on the conjugacy class of the pair
+so we refer to consider pairs $(B,\eta)$ modulo conjugation by $G(\R)$, and refer to such a conjugacy class as a 
+as a {\it Whittaker datum}.
+This is a small finite set.
+If $\w$ is a Whittaker datum, it makes sense to talk about $\pi$ having a $\w$-Whittaker model. We let $\Wh(\pi)$  be the set of
+Whittaker data $\w$ such that $\pi$ has a $\w$-Whittaker model.
 
-We also say~$\pi$ is \emph{generic} when it has a Whittaker model.
-In that case, the pair $(B, \chi)$ is not uniquely determined by~$\chi$.
-However the $G(\R)$-conjugacy class of $(B(\R), \eta)$ is uniquely determined by the equivalence class of~$\pi$.
-We will call it the Whittaker datum attached to~$\pi$, denoted $\mathfrak{w}(\pi)$.
-More generally, by a  {\it Whittaker datum} we will mean a $G(\R)$-conjugacy class of pairs  $(B(\R),\eta)$ satisfying (i)-(ii).
+The set $\Wh(\pi)$ is
+a useful invariant of generic representations.
+For instance if $\Pi$ is a tempered $L$-packet for $G(\R)$ and $\w$ is a Whittaker datum then $\Pi$ contains a unique representation $\pi$
+having a $\w$-Whittaker model. This plays a role in describing the internal structure of $L$-packets.
+If $\Pi$ is a discrete series $L$-packet then each generic representation in the packet has a unique
+Whittaker model, so the generic representation in $\Pi$ are parametrized by their Whittaker models.
+It is conjectured that these properties hold in the $p$-adic case as well, and this is known in many cases.
 
-We may view $\mathfrak{w}(\pi)$ as a useful invariant of generic representations.
-For instance, suppose~$\pi$ is a discrete series representation of~$G(\R)$.
-Then $\mathfrak{w}(\pi)$ singles out~$\pi$ among the discrete series representations of~$G(\R)$ having  the same infinitesimal and central characters.
-In the language of the local Langlands correspondence \cite{Langlands_CIRRAC, Contragredient}, this means the Whittaker datum singles out~$\pi$ within its $L$-packet.
+In the case of real groups there are other invariants attached to an
+irreducible representation $\pi$.  We will be concerned with two of
+them, defined very differently. The first is the \emph{wavefront set} $\WF(\pi)$
+which is an analytic invariant determined by the global character of $\pi$ near the identity.
+The second is the \emph{associated variety} $\AV(\pi)$, which is
+defined  algebraically.
+Both consist of nilpotent elements of the dual of the Lie algebra of~$G$, and are defined as
+coadjoint orbits (of two different kinds).
+The invariants $\Wh(\pi), \WF(\pi)$ and $\AV(\pi)$ are closely related to each other.
 
-More generally, Whittaker data play a subtle but key role in the local Langlands correspondence for reductive groups over arbitrary local fields \cite{Borel, Kaletha_Taibi}, including the nonarchimedean case.
-For instance, given a Whittaker datum~$\mathfrak{w}$, it is expected that every tempered $L$-packet contains precisely one $\mathfrak{w}$-generic representation, which can be used as a basepoint for the internal structure of the $L$-packet~\cite{Kaletha_genericity}.
+We now focus on the case of a generic discrete series representation
+$\pi$ of $G(\R)$, so $\Wh(\pi)$ is a single Whittaker datum.  In this
+case the invariants $\Wh(\pi), \WF(\pi)$ and $\AV(\pi)$ determine each
+other. This is well known to experts, but not so easy to to extract
+from the literature, especially not if one wants to be explicit about
+how to pass back and forth between the three invariants. The purpose
+of this paper is to give a self-contained account of these matters.
 
-Returning to real groups, there are of course other invariants that one may attach to an irreducible representation~$\pi$.
-We shall be concerned with two of them, defined using very different (and rather subtle) ideas.
-The first is the \emph{wavefront set}, which originally comes from microlocal analysis of the matrix coefficients.
-The second is the \emph{associated variety}, which is defined using algebro-geometric methods.
-Both consist of nilpotent elements of the dual of the Lie algebra of~$G$, and are defined as coadjoint orbits (of two different kinds).
-
-Now suppose~$\pi$ is a generic discrete series representation of~$G(\R)$.
-Then the Whittaker datum $\mathfrak{w}(\pi)$, the wavefront set $\WF(\pi)$ and the associated variety $\AV(\pi)$ basically contain the same information: given one of the three invariants, it is possible to reconstruct the other two.
-This is well known to the experts, but some aspects of this discussion are not  easy to extract from the literature, especially not if one wants to be explicit about how to pass back and forth between the three invariants.
-We have felt it worthwhile to give an account of the matter here.
-
-We shall do two things: 
+More precisely, we will do two things:
 \begin{enumerate}
 \item Give an elementary proof that passage from~$\pi$ to $\mathfrak{w}(\pi)$, $\WF(\pi)$ and $\AV(\pi)$ defines bijections between generic discrete series in an $L$-packet for $G(\R)$, Whittaker data for $G(\R)$, and the appropriate sets of nilpotent orbits;
-\item Given one of the invariants $\mathfrak{w}(\pi)$, $\WF(\pi)$ and~$\AV(\pi)$, explain in the simplest possible terms how to reconstruct the other two. 
+\item Given one of the invariants $\Wh(\pi)$, $\WF(\pi)$ or $\AV(\pi)$, explain in the simplest possible terms how to explicitly reconstruct the other two.
 \end{enumerate}
-Most statements in this note were already known, and we have tried to give new and simplified proofs for as many of them as we could.
-In the cases where we had to call on more difficult statements from the literature, we tried to give convenient references.
+Many results in this note are well known. We have tried to give new and simplified proofs for as many of them as we could, and otherwise give convenient references.
 
-\section{Some invariants of irreducible $(\g, K)$-modules}
-
-\footnote{AA 02-IV-2024: I didn't make any effort at polishing this in recent weeks; we should of course rewrite this section once the rest is stable.}
-
-Suppose $\pi$ is an irreducible $(\g,K)$-module.
-Then we can associate to~$\pi$ several invariants, which depend only on the equivalence class of~$\pi$: the associated variety, the Gelfand---Kirillov dimension, and the wavefront set.
-We do not give full definitions, but try to point to convenient places in the literature.\footnote{AA 20-II-2024: of course if we write this, we should maybe add a few basic references for the notions.}
+\section{Some invariants of irreducible representations}
 
@@
 Let~$\sigma$ be the anti-holomorphic involution defining~$G(\R)$.
-Let $\g=\Lie(G), \g(\R)=\Lie(G(\R))$. Choose a Cartan involution $\theta$ for $G$. This means:
+Let $\g=\Lie(G), \g(\R)=\Lie(G(\R))$. 
+Choose a Cartan involution $\theta$ for $G$. This means:
 $\theta$ is an algebraic involution, commuting with~$\sigma$,
 and $G(\R)^\theta$ is a maximal compact subgroup of~$G(\R)$. Set $K=G^\theta$, $K(\R)=G(\R)^\theta=K^\sigma$.
-Let $\s$ be the $-1$ eigenspace of $\theta$ acting on~$\g$.
+Let $\s$ be the $-1$ eigenspace of $\theta$ acting on~$\g$
+(we use the same notation for $\sigma,\theta$ lifted to $\g$).
 
@@
 This is the closure of the principal nilpotent orbit $\Op$.
+
+We work main in the setting of $(\g,K)$-modules.
 
@@
 
+\subsection{The invariants for generic discrete series}
+
+\begin{proposition} \label{invariants_ds}
+  Suppose $\pi$ is a generic discrete series representation of $G(\R)$. Then:
+\begin{enumerate}[(a)]
+\item $\Wh(\pi)$ is a single Whittaker datum;
+\item $\AV(\pi)$ is the closure of a single $K$-orbit on~$\mathcal{O}_p \cap \mathfrak{s}$;
+\item  $\WF(\pi)$ is the closure of a single $G(\R)$-orbit on $\mathcal{O}_p \cap  i \g(\R)^*$.
+\end{enumerate}
+\end{proposition}
+
+\begin{proof} For (a), by \cite{vogan-gelfand-kirillov} and \cite{kostant_whittaker}
+a representation $\pi$ is large if and only if it admits a Whittaker model for some Whittaker datum,
+and by \cite[Lemma 14.14]{abv} a  large discrete series representation admits a unique Whittaker datum.
+
+Part~(b) is one of the main results of~\cite{vogan_bowdoin}: see \cite[Theorem ?]{vogan_bowdoin}.\footnote{AA 19-II-2024: I'd welcome some help in navigating~\cite{vogan_bowdoin}: the relevant places seem to be  Sections 4, 5 and 8, but I have a few questions.}
+
+Part~(c) follows from~\cite{rossmann_limit_orbits}.\footnote{AA 14-II-2024: maybe a little more detail would be welcome, the Rossmann paper does not seem to state the result in these terms.}
+\end{proof}
+
+Because of this result we abuse notation slightly as follows. We say $AV(\pi)=\O$ if $AV(\pi)$ is the closure of the $K$-orbit $\O\subset \s$.
+Similarly we write $\WF(\pi)=\O$ to indicate that $\WF(\pi)$ is the closure of the $G(\R)$-orbit $\O\subset i\g(\R)^*$.
+
 \subsection{Large representations} Set $N=\dim(\N)=\dim(G)-\mathrm{rank}(G)$. The maximal Gelfand--Kirillov dimension of a representation is $N/2$.
@@
   \item $\GK(\pi)=N/2$;
+    \item $\pi$ is generic.
 
@@
 
-\subsection{The invariants for large discrete series}
-
-The following uses rather deep results of representation theory.
-
-\begin{proposition} \label{invariants_ds}
-Let~$\pi$ be the $(\g, K)$-module for a large discrete series representation of~$G(\R)$.  
-\begin{enumerate}[(a)]
-\item There is a unique Whittaker datum~$\mathfrak{w}$ such that~$\pi$ is $\mathfrak{w}$-generic.
-\item $\AV(\pi)$ is the closure of a single $K$-orbit on~$\mathcal{O}_p \cap \mathfrak{s}$.
-\item  $\WF(\pi)$ is the closure of a single $G(\R)$-orbit on $\mathcal{O}_p \cap  i \g(\R)$.
-\end{enumerate}
-\end{proposition}
-
-\begin{proof} For (a), by \cite{vogan-gelfand-kirillov} and \cite{kostant_whittaker}
-a representation $\pi$ is large if and only if it admits a Whittaker model for some Whittaker datum,
-and by \cite[Lemma 14.14]{abv} a  large discrete series representation admits a unique Whittaker datum.
-
-Part~(b) is one of the main results of~\cite{vogan_bowdoin}: see \cite[Theorem ?]{vogan_bowdoin}.\footnote{AA 19-II-2024: I'd welcome some help in navigating~\cite{vogan_bowdoin}: the relevant places seem to be  Sections 4, 5 and 8, but I have a few questions.}
-
-Part~(c) follows from~\cite{rossmann_limit_orbits}.\footnote{AA 14-II-2024: maybe a little more detail would be welcome, the Rossmann paper does not seem to state the result in these terms.}
-\end{proof}
-
-\section{The dictionary for large discrete series}
+\section{The dictionary for generic discrete series}
 
@@
 
-Given a large discrete series representation~$\pi$ we consider the invariants of~$\pi$ defined by Proposition~\ref{invariants_ds}: a Whittaker datum  $\mathfrak{w}(\pi)$, a $K$-orbit $\AV^\flat(\pi)$ in $\mathcal{O}_p \cap \mathfrak{s}$, and a $G(\R)$-orbit $\WF^\flat(\pi)$ in $(\mathcal{O}_p \cap  i \g(\R))$.
+Given a generic discrete series representation~$\pi$ we consider the invariants of~$\pi$ defined by Proposition~\ref{invariants_ds}: a Whittaker datum  $\Wh(\pi)$, a $K$-orbit $\AV(\pi)$ in $\mathcal{O}_p \cap \mathfrak{s}$, and a $G(\R)$-orbit $\WF(\pi)$ in $(\mathcal{O}_p \cap  i \g(\R))$.
 
@@
 \begin{theorem} \label{th:main} Suppose~$\Pi$ is an $L$-packet of discrete series for~$G(\R)$. 
-The maps $\pi \mapsto \mathfrak{w}(\pi)$, $\pi \mapsto \AV^\flat(\pi)$ and $\pi\mapsto \WF^\flat(\pi)$ induce bijections between:
+The maps $\pi \mapsto \Wh(\pi)$, $\pi \mapsto \AV(\pi)$ and $\pi\mapsto \WF(\pi)$ induce bijections between:
 \begin{enumerate}
-\item[(1)] The set~$\Pi_{\mathrm{large}}$ of large discrete series representations in~$\Pi$ ;
+\item[(1)] The set~$\Pi_{\mathrm{gen}}$ of generic discrete series representations in~$\Pi$ ;
 \item[(2)] The set of Whittaker data for $G(\R)$ ;
-\item[(3)] The set $(\Op \cap \s)/K$ of~$K$-orbits on $\mathcal{O}_p \cap \s$.
-\item[(4)] The set $(\Op \cap i\g(\R))/G(\R)$ of~$G(\R)$-orbits on $\mathcal{O}_p \cap  i \g(\R)$.
+\item[(3)] The set of~$K$-orbits on $\mathcal{O}_p \cap \s$.
+\item[(4)] The set of~$G(\R)$-orbits on $\mathcal{O}_p \cap  i \g(\R)^*$.
 \end{enumerate}
@@
 \item[(i)] it acts simply transitively on the sets~(1)--(4), and 
-\item[(ii)] the maps $\pi \mapsto \mathfrak{w}(\pi)$, $\pi \mapsto \AV^\flat(\pi)$ and $\pi\mapsto \WF^\flat(\pi)$  are equivariant for these actions.
+\item[(ii)] the maps $\pi \mapsto \Wh(\pi)$, $\pi \mapsto \AV(\pi)$ and $\pi\mapsto \WF(\pi)$  are equivariant for these actions.
 \end{itemize}
@@
 \subsubsection{Definition of the two groups}Let $Z=Z(G)$ be the center of $G$, and let $\Gad$ be the complex reductive group~$G/Z$.
-The group $Z(\R)=Z^{\sigma}$ is equal to the center of $G(\R)$.
-The automorphism~$\sigma$ of~$G$ preserves $Z$, and descends to an automorphism~$\sigma_{\ad}$ of~$\Gad$.
-We set $\Gad(\R)=\Gad^{\sigma_{\ad}}$; we may view it as the set of inner automorphisms of~$G$ which are defined over~$\R$, and this contains the group $G(\R)_{\mathrm{ad}}=G(\R)/Z(\R)$ as a normal subgroup of finite index\footnote{AA 15-II-2024: is there a trivial way to explain why finite index?}.
-Define 
+Then $Z(\R)=Z^\sigma$ is the center of $G(\R)$, so we set $\G(\R)_\ad=G(\R)/Z(\R)$.
+On the other hand  $\sigma$ factors to an automorphism, still denoted $\sigma$, of $\Gad$, and we let  $\Gad(\R)=(\Gad)^\sigma$.
+The canononical map $G\rightarrow G/Z$ restricts to a map $G^\sigma\rightarrow (G/Z)^\sigma$, with kernel $Z^\sigma$.
+Hence there is a
+natural injective map $(G^\sigma)_\ad\hookrightarrow (\Gad)^\sigma$, and we define
 $$
-Q_\sigma(G)=\Gad(\R)/G(\R)_{\mathrm{ad}}.
+Q_\sigma(G)=(\Gad)^\sigma/(G^\sigma)_\ad=\Gad(\R)/\G(\R)_\ad.
 $$
@@
 
-We shall need a variant of~$Q_{\sigma}(\R)$ in which we replace the real form~$\sigma$ by the Cartan involution~$\theta$.
-As above, since~$\theta$ is an automorphism of~$G$, it preserves~$Z$,  and induces an involution~$\theta_{\ad}$ of~$\Gad$.
-Recall $K=G^{\theta}$; consider the intersection $Z_K=Z \cap K$, and set  $K_{\ad}=K/Z_K$.
-The inclusion  $K \hookrightarrow G$ induces a map $K \to \Gad$, whose image is a subgroup of~$\Gad^{\theta_{\ad}}$ and whose kernel is~$Z_K$.
-Therefore it factors to an injective morphism $\iota\colon \Kad \hookrightarrow\Gad^{\theta_{\ad}} $, whose image is a normal subgroup of~$\Gad^{\theta_{\ad}}$.
-Using it we will identify $\Kad$ with a normal subgroup of $\Gad^{\theta_{\ad}}$.
-Define
-\[ Q_\theta(G) = \Gad^{\theta_{\ad}}/\Kad.\]
-Unlike $Q_{\sigma}(G)$, this group does not have an obvious action on~$G(\R)$.
-Nevertheless the groups $Q_{\sigma}(G)$ and $Q_{\theta}(G)$ are isomorphic.
-We will spell out an explicit isomorphism below, using group cohomology arguments.
+A similar discussion applies to the involution $\theta$.
+Then $Z^\theta$ is the center of $K=G^\theta$ and  $\theta$ factors to $\Gad$.
+We define $(G^\theta)_\ad=G^\theta/Z^\theta$ and
+$$
+Q_\theta(G)=(\Gad)^\theta/(G^\theta)_\ad =(\Gad)^\theta/\Kad.
+$$
+This is a group of outer automorphisms of $K$.
+
+An important fact is that $Q_\sigma(G)$ and $Q_\theta(G)$ are canonically isomorphic. This is a generalization of the well known fact that
+$G(\R)/G(\R)_0\simeq K/K_0$ where the subscript $0$ denotes identity component.
 

### 2024-04-25 whittaker.tex
intermediate commit

@@
 
+\subsubsection*{Representations}
+
+We work mostly in the  algebraic setting of
+$(\g,K)$-modules. However, mainly for the analytic wave front set
+invariant we need to consider representations of $G(\R)$ on a Banach
+space. Suppose $(\pi,V)$ is an irreducible representation of $G(\R)$ 
+ where $V$ is a Banach space. The underlying
+$(\g,K)$-module is on the space of $K$-finite vectors in
+$V$. Conversely if $\pi$ is an irreducible $(\g,K)$-module it can be
+realized as the $K$-finite vectors of some  Banach space
+representation.
+
  \subsection{The invariants}
@@
 
-Another invariant of an irreducible $(\g, K)$-module~$\pi$ is the \emph{wave-front set} of $\pi$, written $\WF(\pi)$. It is the union of a (finite) set of nilpotent $G(\R)$ orbits in
-$i\g(\R)^*=i\Hom_\R(\g(\R),\R)$. See \cite{howe_wave_front}, \cite{bv_local_structure}, \cite{HarrisHeOlafsson}.
+Now suppose $(\pi,V)$ is an irreducible representation of $G(\R)$. 
+See \cite{howe_wave_front}, \cite{bv_local_structure},
+\cite{HarrisHeOlafsson} for the definition of the \emph{wave-front
+  set} $\WF(\pi)$. This is an analytic invariant determined by the
+singularities of the global character of $\pi$ near the identity. 
+It is a closed $G(\R)$-invariant subset of the nilpotent cone in
+$i\g(\R)^*$. As such it is the union of a finite number of nilpotent $G(\R)$-orbits.
 
@@
 
+\begin{lemma}
+There is a canonical isomorphism $\phi:Q_\sigma(G)\simeq Q_\theta(G)$ defined as follows.
+Suppose $x\in Q_\sigma(G)=(\Gad)^\sigma/(G^\sigma)_\ad$.
+We can choose a representative $g\in (\Gad)^\sigma$ of $x$ which is also in $(\Gad)^\theta$.
+Define $\phi(x)$ to be the image of $g$ in $Q_\theta(G)=(\Gad)^\theta/(G^\theta)_\ad$.
+This is independent of the choice of $g$ and $\phi$ is an isomorphism of pointed sets.
+\end{lemma}
+
+Based on the Lemma we define $Q(G)$ to be $Q_\sigma(G)$ or $Q_\theta(G)$, depending on the setting.
+
+[This is an explicit version of the group cohomology argument. Some detail here...]
+
 \subsubsection{Interpretation in terms of group cohomology}
@@
 
-\subsection{Actions of $Q_\sigma(G)$ on representations and invariants}
+\subsection{Action of $Q(G)$ on representations and invariants}
 
-\subsubsection*{On representations} 
 Since~$Q_\sigma(G)$ can be viewed as a group of automorphisms of~$G(\R)$,  it has a canonical action on equivalence classes of representations of~$G(\R)$, and therefore on~$(\g, K)$-modules.

### 2024-04-25 whittaker.tex
more changes in progress

@@
 
-Suppose $\pi$ is an irreducible representation of~$G(\R)$.
-We say $\pi$ has a {\it Whittaker model}, or is {\it generic},  if
-$\pi$ embeds into the induced
-representation $\mathrm{Ind}_{N(\R)}^{G(\R)}(\chi)$ for some $(B,\eta)$ satisfying:
 We consider pairs
@@
 The existence of a Borel subgroup satisfying (i) is the definition of $G$ being quasisplit, which we assume holds from now on.
-Clearly this condition only depends on the conjugacy class of the pair
-so we refer to consider pairs $(B,\eta)$ modulo conjugation by $G(\R)$, and refer to such a conjugacy class as a 
+
+We recall what it means for a representation $\pi$ to have a $(B,\eta)$-Whittaker model in Section ?.
+This condition only depends on the conjugacy class of the pair, 
+so we  consider pairs $(B,\eta)$ modulo conjugation by $G(\R)$, and refer to such a conjugacy class as a 
 as a {\it Whittaker datum}.
@@
 If $\w$ is a Whittaker datum, it makes sense to talk about $\pi$ having a $\w$-Whittaker model. We let $\Wh(\pi)$  be the set of
-Whittaker data $\w$ such that $\pi$ has a $\w$-Whittaker model.
+Whittaker data $\w$ such that $\pi$ has a $\w$-Whittaker model. We say $\pi$ is {\it generic} if $\Wh(\pi)$ is non-empty.
 
@@
 
-We work main in the setting of $(\g,K)$-modules.
-
 \subsubsection*{Representations}
 
-We work mostly in the  algebraic setting of
-$(\g,K)$-modules. However, mainly for the analytic wave front set
-invariant we need to consider representations of $G(\R)$ on a Banach
-space. Suppose $(\pi,V)$ is an irreducible representation of $G(\R)$ 
- where $V$ is a Banach space. The underlying
+We need to pass back and forth between representations of $G(\R)$ and $(\g,K)$-modules. 
+See ? for details.
+
+Suppose $(\pi,V)$ is an irreducible representation of $G(\R)$  on a Hilbert space. 
+The underlying
 $(\g,K)$-module is on the space of $K$-finite vectors in
 $V$. Conversely if $\pi$ is an irreducible $(\g,K)$-module it can be
-realized as the $K$-finite vectors of some  Banach space
-representation.
+realized as the $K$-finite vectors of a Hilbert space representation, which we 
+refer to as the Hilbert space globalization of $\pi$.
 
@@
 
-Now suppose $(\pi,V)$ is an irreducible representation of $G(\R)$. 
+Now suppose $(\pi,V)$ is an irreducible representation of $G(\R)$ on a Hilbert space. 
 See \cite{howe_wave_front}, \cite{bv_local_structure},
@@
 $i\g(\R)^*$. As such it is the union of a finite number of nilpotent $G(\R)$-orbits.
+
+If $\pi$ is an irreducible $(\g,K)$-module we define $\WF(\pi)$ to be the wave-front set of 
+the Hilbert space globalization of $\pi$. 
+In the other direction if $\pi$ is an irreducible representation of $G(\R)$ we define $\AV(\pi)$ to be the associated variety 
+of its underlying $(\g,K)$-module.
+
+[Need a paragraph explaining $\Wh(\pi)$, following Matsumoto]
 
@@
 
-Based on the Lemma we define $Q(G)$ to be $Q_\sigma(G)$ or $Q_\theta(G)$, depending on the setting.
+[This is an explicit version of the group cohomology argument. Some detail here...]
 
-[This is an explicit version of the group cohomology argument. Some detail here...]
+Note that $Q_\sigma(G)$ is a set of automorphisms of $G(\R)$. It therefore acts on representations of $G(\R)$. 
+Similarly $Q_\theta(G)$ is a set of automorphisms of $(\g,K)$, and acts on $(\g,K)$-modules.
+
+\begin{lemma}
+Suppose $\pi$ is an irreducible  Hilbert space representation of $G(\R)$.
+Suppose $g\in Q_\sigma(G)$. 
+Then $(\pi^g)_K\simeq (\pi_K)^{\phi(g)}$.
+\end{lemma}
+
+\begin{proof}
+straightforward
+\end{proof}
+
+Based on these two Lemmas we write $Q(G)$ for the group $Q_\sigma(G)$ or $Q_\theta(G)$, depending on the situation.
 

### 2024-04-25 whittaker.tex
more rolling changes...

@@
 \newcommand{\I}{\mathcal I}
+\newcommand{\mH}{\mathcal H}
 \renewcommand{\O}{\mathcal O}
@@
 
-We consider pairs
+We consider pairs $(B,\eta)$ where 
 \begin{enumerate}[(i)]
@@
 them, defined very differently. The first is the \emph{wavefront set} $\WF(\pi)$
-which is an analytic invariant determined by the global character of $\pi$ near the identity.
+which is an analytic invariant.
 The second is the \emph{associated variety} $\AV(\pi)$, which is
@@
 other. This is well known to experts, but not so easy to to extract
-from the literature, especially not if one wants to be explicit about
-how to pass back and forth between the three invariants. The purpose
+from the literature. The purpose
 of this paper is to give a self-contained account of these matters.
@@
 We need to pass back and forth between representations of $G(\R)$ and $(\g,K)$-modules.
-See ? for details.
+See \cite{greenbook} for details.
 
-Suppose $(\pi,V)$ is an irreducible representation of $G(\R)$  on a Hilbert space. 
+Suppose $\pi$ is an irreducible admissible representation of $G(\R)$  on a Hilbert space. 
 The underlying
@@
 \subsection{The invariants}
+We recall some results from,  \cite{vogan_bowdoin}, in particular Corollary 4.7 and Theorem 8.4.
 
+Suppose $\pi$ is an irreducible $(\g,KL)$-module.
 Let $I_\pi$ be the annihlator of $\pi$ in the universal enveloping algebra.
@@
 This is the closure of a single complex nilpotent orbit $\O$.
-
-The associated variety of $\pi$, denoted $\AV(\pi)$, is the  the union of a set of
-$K$-orbits on $\O\cap\s$.
+The associated variety of $\pi$, denoted $\AV(\pi)$, is a closed, $K$-invariant set in $\s$, so it is a finite union of
+nilpotent $K$-orbits on $\s$.
 
@@
 
-For all of these facts see \cite{vogan_bowdoin}, in particular Corollary 4.7 and Theorem 8.4.
-
-Now suppose $(\pi,V)$ is an irreducible representation of $G(\R)$ on a Hilbert space. 
+Now suppose $\pi$ is an irreducible admissible representation of $G(\R)$ on a Hilbert space $\mH$. 
 See \cite{howe_wave_front}, \cite{bv_local_structure},
@@
 
+We consider the space $\mH^\infty$ of smooth vectors in $\mH$, and its dual $\mH^{-\infty}$. We say $\pi$ has a $(B,\eta)$-Whittaker model
+if there exists $v\in \mH^{-\infty}$ such that $\pi(n)(v)=\eta(n)v$ for all $n$ in the nilradical $N(\R)$ of $B(\R)$.
+See \cite{matumoto}.
+
 If $\pi$ is an irreducible $(\g,K)$-module we define $\WF(\pi)$ to be the wave-front set of 
-the Hilbert space globalization of $\pi$. 
-In the other direction if $\pi$ is an irreducible representation of $G(\R)$ we define $\AV(\pi)$ to be the associated variety 
+the Hilbert space globalization of $\pi$, and similarly $\Wh(\pi)$. 
+In the other direction if $\pi$ is an irreducible Hilbert space representation of $G(\R)$ we define $\AV(\pi)$ to be the associated variety 
 of its underlying $(\g,K)$-module.
-
-[Need a paragraph explaining $\Wh(\pi)$, following Matsumoto]
 
@@
 
-Note that $Q_\sigma(G)$ is a set of automorphisms of $G(\R)$. It therefore acts on representations of $G(\R)$. 
-Similarly $Q_\theta(G)$ is a set of automorphisms of $(\g,K)$, and acts on $(\g,K)$-modules.
+Note that $Q_\sigma(G)$ is a group of automorphisms of $G(\R)$. It therefore acts on representations of $G(\R)$. 
+Similarly $Q_\theta(G)$ is a group of automorphisms of $(\g,K)$, and acts on $(\g,K)$-modules.
 
@@
 \[ Q_{\sigma}(G) \simeq Q_{\theta}(G).\]
-As discussed after~\eqref{interp_q_cohomology}, this is actually an isomorphism of abelian groups.
-
-\subsection{Action of $Q(G)$ on representations and invariants}
-
-Since~$Q_\sigma(G)$ can be viewed as a group of automorphisms of~$G(\R)$,  it has a canonical action on equivalence classes of representations of~$G(\R)$, and therefore on~$(\g, K)$-modules.
-This action preserves  the property of being large\footnote{AA 15-II-2024: should say something about this using the fact that it comes from automorphisms, either here or in the section on large reps}.
-It also preserves $L$-packets by~\cite[Lemma 6.18]{Contragredient}, and acts transitively on an~$L$-packet\footnote{AA 01-IV-2023: this point was missing, and I think details should be included.
-I think the transitivity is easy using  the description of discrete series L-packets in the Congragredient paper in terms of Harish-Chandra parameters, plus the fact that every element of~$Q_{\sigma}(G)$ has a representative in the Weyl group of a given elliptic maximal torus.
-The point about the action preserving $L$-packets also follows from this, I think; and perhaps it gives a better argument for the preservation of $L$-packets than [Contragredient, Lemma 6.18], which looks better suited to the $\theta$-version.}.
-
-\subsubsection*{On~Whittaker data}  By definition of Whittaker data, the action of~$Q_{\sigma}(G)$ on $G(\R)$ induces a canonical action on the set of Whittaker data.
-By \cite[(14.15)]{abv} this action is simply transitive.
-
-It is an immediate consequence of the definitions that the map $\pi \mapsto \w(\pi)$, taking a large discrete series representation to the Whittaker datum for which it has a Whittaker model, is equivariant for the actions of $Q_{\sigma}(G)$ on (1)--(2).
+This action preserves $L$-packets by 
+by~\cite[Lemma 6.18]{Contragredient}.
 
@@
 
-\subsection{Actions of $Q_\theta(G)$ on representations and invariants}
-
-To discuss the map taking a $(\g, K)$-module to the associated variety, it seems better to use $Q_{\theta}(G)$ rather than~$Q_{\sigma}(G)$.
-
- \subsubsection*{On $(\g, K)$-modules}
-
- Recall $Q_{\theta}(\R)=\Gad^{\theta_{\ad}}/\Kad$.
-By definition $\Gad^{\theta_{\ad}}$ is contained in the normalizer $\mathrm{Norm}_G(K)$; this determines a canonical action of $\Gad^{\theta_{\ad}}$ on~$(\g, K)$-modules.
- Any element of~$\Kad$ takes a $(\g,K)$-module to an equivalent one, and this gives an action of $Q_{\theta}(\R)$ on equivalence classes of irreducible $(\g, K)$-modules.
- This preserves the property of being a discrete series, and of being large.
- Furthermore, by \cite[Lemma 6.18 and Remark 6.19]{Contragredient} the action preserves $L$-packets.
- Therefore $Q_{\theta}(\R)$ acts transitively on the large representations in a discrete series $L$-packet.
-
-\subsubsection*{On nilpotent $K$-orbits.}
-
-Let us define an action of~$Q_{\theta}(G)$ on $(\Op \cap \s)/K$.
-First, the adjoint action of~$\Gad$ on~$\g$ preserves both $\Op$ and~$\s$.
-Second, the action of~$K=G^\theta$ on $\Op \cap \s$ is trivial on~$Z_K=Z^\theta$, and factors through an action of~$\Kad$.
-It is then easy to check that if two elements of $\Op \cap \s$ lie in on the same $\Kad$-orbit, then for every $g \in \Gad^{\theta_{\ad}}$, the elements  ${g} \cdot x$ and ${g} \cdot y$ lie on the same $\Kad$-orbit.
-This determines an action of~$Q_\theta(G)$ on $(\Op \cap \s)/K$, which is the one featured in the next statement.
+On the other hand $Q(G)$, realized as $Q_\theta(G)$ is a group of automorphisms of $(\g,K)$.
+It induces actions on $\s$, $\Op$ and $\Op\cap\s$, and on $(\g,K)$-modules.
 
@@
 \begin{enumerate} 
-\item The action of~$Q_{\theta}(G)$ on $(\Op \cap \s)/K$ is simply transitive.
-\item The map $\pi \mapsto \AV(\pi)$ is $Q_{\theta}(G)$-equivariant.
+\item The action of~$Q(G)$ on $(\Op \cap \s)/K$ is simply transitive.
+\item The map $\pi \mapsto \AV(\pi)$ is $Q(G)$-equivariant.
 \end{enumerate}

### 2024-04-30 whittaker.tex
In the middle of some changes, added invariant representatives proof

@@
 
-We recall what it means for a representation $\pi$ to have a $(B,\eta)$-Whittaker model in Section ?.
+We recall what it means for a representation $\pi$ to have a $(B,\eta)$-Whittaker model in Section~\ref{sec:invariants}.
 This condition only depends on the conjugacy class of the pair, 
@@
 
+\subsubsection*{Involutions}
+
 Let~$\sigma$ be the anti-holomorphic involution defining~$G(\R)$.
@@
 (we use the same notation for $\sigma,\theta$ lifted to $\g$).
+
+\subsubsection*{Nilpotent orbits}
 
@@
 
-\subsection{The invariants}
+\subsection{The invariants}\label{sec:invariants}
+
+\subsubsection*{Associated variety and Gelfand--Kirillov dimension}
+
 We recall some results from,  \cite{vogan_bowdoin}, in particular Corollary 4.7 and Theorem 8.4.
 
-Suppose $\pi$ is an irreducible $(\g,KL)$-module.
+Suppose $\pi$ is an irreducible $(\g,K)$-module.
 Let $I_\pi$ be the annihlator of $\pi$ in the universal enveloping algebra.
@@
 
+If we do not start with a $(\g, K)$-module but with a Hilbert space representation~$\pi$ of $G(\R)$,  we define $\AV(\pi)$ to be the associated variety 
+of its underlying $(\g,K)$-module.
+
+\subsubsection*{Wavefront set}
+
 Now suppose $\pi$ is an irreducible admissible representation of $G(\R)$ on a Hilbert space $\mH$. 
-See \cite{howe_wave_front}, \cite{bv_local_structure},
-\cite{HarrisHeOlafsson} for the definition of the \emph{wave-front
-  set} $\WF(\pi)$. This is an analytic invariant determined by the
-singularities of the global character of $\pi$ near the identity. 
+The \emph{wave-front
+  set} $\WF(\pi)$ is an analytic invariant determined by the
+singularities of the global character of $\pi$ near the identity. See \cite{howe_wave_front}, \cite{bv_local_structure},
+\cite{HarrisHeOlafsson} for the definition. 
 It is a closed $G(\R)$-invariant subset of the nilpotent cone in
 $i\g(\R)^*$. As such it is the union of a finite number of nilpotent $G(\R)$-orbits.
+
+If $\pi$ is an irreducible $(\g,K)$-module we define $\WF(\pi)$ to be the wave-front set of 
+the Hilbert space globalization of $\pi$.
+
+\subsubsection*{Whittaker models}
 
@@
 
-If $\pi$ is an irreducible $(\g,K)$-module we define $\WF(\pi)$ to be the wave-front set of 
-the Hilbert space globalization of $\pi$, and similarly $\Wh(\pi)$. 
-In the other direction if $\pi$ is an irreducible Hilbert space representation of $G(\R)$ we define $\AV(\pi)$ to be the associated variety 
-of its underlying $(\g,K)$-module.
+We write $\Wh(\pi)$ for the set of Whittaker data~$\w$ such that If $\pi$ is an irreducible $(\g,K)$-module we define $\Wh(\pi)$ to be the set of 
+the Hilbert space globalization of $\pi$.
 
@@
 
-Because of this result we abuse notation slightly as follows. We say $AV(\pi)=\O$ if $AV(\pi)$ is the closure of the $K$-orbit $\O\subset \s$.
+Because of this result we abuse notation slightly as follows.
+If~$\pi$ is a generic discrete series representation of~$G(\R)$, we write $AV(\pi)=\O$ to indicate that $AV(\pi)$ is the closure of the $K$-orbit $\O\subset \s$.
 Similarly we write $\WF(\pi)=\O$ to indicate that $\WF(\pi)$ is the closure of the $G(\R)$-orbit $\O\subset i\g(\R)^*$.
 
-\subsection{Large representations} Set $N=\dim(\N)=\dim(G)-\mathrm{rank}(G)$. The maximal Gelfand--Kirillov dimension of a representation is $N/2$.
-We say $\pi$ is {\it large} if $\GK(\pi)=N/2$. See \cite[Section~6]{Vogan78}.
+\subsection{Large representations} Set $N=\dim(G)-\mathrm{rank}(G)$. This is the dimension of the nilpotent cone~$\N$. The maximal Gelfand--Kirillov dimension of a representation is $N/2$.
+We say $\pi$ is {\it large} if $\GK(\pi)=N/2$. See \cite[Section~6]{vogan-gelfand-kirillov}.
 
@@
 
-\subsection{Statement of the results}
+\subsection{Statement of the dictionary}
 
 Given a generic discrete series representation~$\pi$ we consider the invariants of~$\pi$ defined by Proposition~\ref{invariants_ds}: a Whittaker datum  $\Wh(\pi)$, a $K$-orbit $\AV(\pi)$ in $\mathcal{O}_p \cap \mathfrak{s}$, and a $G(\R)$-orbit $\WF(\pi)$ in $(\mathcal{O}_p \cap  i \g(\R))$.
-
-Here is our main statement.
 
@@
 Let us now explain the strategy of the proof, which is mainly an exercise in putting together some references that are rather scattered in the literature.
-What we shall actually do is: introduce a finite group~$Q_\sigma(G)$, and point out that
+What we shall actually do is: introduce a finite group~$Q(G)$, and point out that
 \begin{itemize}
-\item[(i)] it acts simply transitively on the sets~(1)--(4), and 
+\item[(i)] it acts transitively on~(1), and simply transitively on (2)--(4);
 \item[(ii)] the maps $\pi \mapsto \Wh(\pi)$, $\pi \mapsto \AV(\pi)$ and $\pi\mapsto \WF(\pi)$  are equivariant for these actions.
 \end{itemize}
-The theorem follows immediately from these two observations.\footnote{AA 01-IV-2024 --- perhaps it would be reader-friendly to point out the basic fact on group actions that we are using here: suppose a group $Q$ acts on two sets $A, B$ and let $f\colon A \to B$ be an equivariant map.
-If $Q$ acts transitively on~$B$  then~$f$ is surjective, and if $Q$ acts transitively on~$A$ and freely on~$B$ then~$f$ is injective.
-}
+The theorem follows immediately from these two observations, and from the following basic fact on group actions.
+
+\begin{lemma} Suppose a group $Q$ acts on two sets $A, B$ and let $f\colon A \to B$ be an equivariant map. 
+\begin{itemize}
+\item[(a)] If $Q$ acts transitively on~$B$  then~$f$ is surjective;
+\item[(b)] If $Q$ acts transitively on~$A$ and freely on~$B$, then~$f$ is injective.
+\end{itemize}
+In particular, if~$Q$ acts transitively on~$A$ and simply transitively on~$B$, then~$f$ is a bijection and the action of~$Q$ on~$A$ is simply transitive.
+\end{lemma}
 
@@
 
-\subsubsection{Definition of the two groups}Let $Z=Z(G)$ be the center of $G$, and let $\Gad$ be the complex reductive group~$G/Z$.
-Then $Z(\R)=Z^\sigma$ is the center of $G(\R)$, so we set $\G(\R)_\ad=G(\R)/Z(\R)$.
-On the other hand  $\sigma$ factors to an automorphism, still denoted $\sigma$, of $\Gad$, and we let  $\Gad(\R)=(\Gad)^\sigma$.
-The canononical map $G\rightarrow G/Z$ restricts to a map $G^\sigma\rightarrow (G/Z)^\sigma$, with kernel $Z^\sigma$.
-Hence there is a
-natural injective map $(G^\sigma)_\ad\hookrightarrow (\Gad)^\sigma$, and we define
+\subsubsection{Definition of the two groups, and canonical isomorphism}
+
+Let $Z=Z(G)$ be the center of $G$, and let $\Gad$ be the complex reductive group~$G/Z$.
+Then $Z(\R)=Z^\sigma$ is the center of $G(\R)$. We set $\G(\R)_\ad=G(\R)/Z(\R)$.
+On the other hand  $\sigma$ factors to an automorphism  of $\Gad$, still denoted~$\sigma$, and we let  $\Gad(\R)=(\Gad)^\sigma$.
+The projection $G\rightarrow \Gad$ restricts to a map $G^\sigma\rightarrow (G/Z)^\sigma$, with kernel $Z^\sigma$.
+This induces a canonical injection $(G^\sigma)_\ad\hookrightarrow (\Gad)^\sigma$, and we define
 $$
@@
 
-\begin{lemma}
-There is a canonical isomorphism $\phi:Q_\sigma(G)\simeq Q_\theta(G)$ defined as follows.
-Suppose $x\in Q_\sigma(G)=(\Gad)^\sigma/(G^\sigma)_\ad$.
-We can choose a representative $g\in (\Gad)^\sigma$ of $x$ which is also in $(\Gad)^\theta$.
-Define $\phi(x)$ to be the image of $g$ in $Q_\theta(G)=(\Gad)^\theta/(G^\theta)_\ad$.
-This is independent of the choice of $g$ and $\phi$ is an isomorphism of pointed sets.
+\begin{lemma}\label{lem:iso_q}
+\begin{itemize}
+\item[(a)] 
+Every element of $Q_\sigma(G)=(\Gad)^\sigma/(G^\sigma)_\ad$ has a representative in $(\Gad)^\sigma$ which is also in $(\Gad)^\theta$.
+\item[(b)] Given $x \in Q_{\sigma}(G)$, and a representative $g\in (\Gad)^\sigma \cap (\Gad)^\theta$ as in~(a), the image of~$g$ in  $Q_\theta(G)$ depends only on~$x$, and not on  the choice of~$g$.
+The corresponding map $x \mapsto \phi(x)$, from $Q_{\sigma}(G)$ to $Q_{\theta}(G)$, is a group isomorphism.
+\end{itemize}
 \end{lemma}
 
-[This is an explicit version of the group cohomology argument. Some detail here...]
+The proof uses an interpretation of $Q_\sigma(G)$ and $Q_\theta(G)$ in terms of group cohomology, which we now spell out.
+
+\subsubsection{Interpretation in terms of group cohomology}
+
+The groups $Q_{\sigma}(G)$ and $Q_{\theta}(G)$ are instances of the following construction: if~$\tau$ is an involutive automorphism of~$G$, then it preserves~$Z$ and induces an involution of~$\Gad$, still denoted $\tau$; we may then set $Q_{\tau}(G)=(\Gad)^{\tau}/(G^{\tau})_{\ad}$, where $(G^{\tau})_{\ad}$ is the image of~$G^{\tau}$ in~$\Gad$.
+In this situation~$Q_{\tau}(G)$ has a simple interpretation in Galois cohomology, which we now recall.
+
+Let us first set up some general notation.
+When~$A$ is a group and $\tau$ is an involutive automorphism of~$A$, consider the cohomology sets $H^0(\tau, A)$ and $H^1(\tau, A)$ attached to the action of $\Z/2\Z$ on~$A$ by~$\tau$.
+We shall view   $H^0(\tau, A)$ as the fixed-point-set $A^{\tau}$, and $H^1(\tau,A)$ as the quotient of $A^{-\tau} = \{ a \in A, \tau(a)=a^{-1}\}$ by the equivalence relation $a \sim x a \tau(x^{-1})$ for all $x \in A$.
+The set $H^1(\tau, A)$ has a distinguished point $1$, coming from the identity of~$A$; but in general it just a pointed set, and not a group if~$A$ is nonabelian.
+
+We now take~$A=G$, and continue to assume~$\tau$ is an involutive automorphism. Then the short exact sequence $1\rightarrow Z \rightarrow G \rightarrow \Gad\rightarrow 1$ 
+gives rise to a ``long" exact sequence of pointed sets:
+\begin{equation} \label{long_ptset}
+1\rightarrow Z^\tau \rightarrow G^\tau \rightarrow \Gad^{\tau} \overset{\psi_\tau}{\longrightarrow} H^1(\tau,Z)\to H^1(\tau,G)\rightarrow H^1(\tau,\Gad).
+\end{equation}
+In~\eqref{long_ptset} the connecting map  $ \psi_\tau\colon \Gad^{\tau} \rightarrow H^1(\tau,Z)$ is defined as follows: if $\gamma \in \Gad^{\tau}$ is the coset $gZ$, then $g\tau(g^{-1}) \in Z^{-\tau}$, and the connecting map sends~$\gamma$ to the class of $g \tau(g^{-1})$ in $H^1(\tau, Z)$.
+The kernel of~$\psi_\tau$ is $(G^\tau)_{\ad}$.
+Since~\eqref{long_ptset} is exact we deduce that $\psi_\tau$ induces a canonical  bijection
+\begin{equation} \label{interp_q_cohomology} Q_{\tau}(G) \to  \ker\left(H^1(\tau,Z)\overset{\varphi_\tau}{\longrightarrow} H^1(\tau,G)\right)\end{equation}
+where $\varphi_\tau$ is induced by the inclusion $Z^{-\tau} \hookrightarrow G^{-\tau}$.
+
+%The previous argument is in the category of pointed sets, and on the right-hand side $H^1(\tau,G)$  is not a group in general.
+Therefore, at first sight, the map~\eqref{interp_q_cohomology} is only a set-theoretic bijection.
+However,
+%$H^1(\tau,Z)$ is a group since $Z$ is abelian; thus both sides of~\eqref{interp_q_cohomology} have canonical abelian group structures, and chasing definitions one easily sees that~\eqref{interp_q_cohomology} is actually an isomorphism of abelian groups.
+
+%We can spell out the inverse of~\eqref{interp_q_cohomology} as follows.
+Suppose~$\zeta \in H^1(\tau, Z)$ is the equivalence class of  $z \in Z^{-\tau}$.
+By definition we have $\varphi_\tau(\zeta)=1$ if and only if there exists $g \in G$ such that $z = g \tau(g^{-1})$.
+In that case $\tau(g) =z^{-1}g$, therefore the projection of~$g$ in $\Gad=G/Z$ is an element $\tilde{q}$ of~$\Gad^{\tau}$.
+It follows immediately from the definitions that the class of $\tilde{q}$ in $Q_{\tau}(G)=\Gad^\tau/(G^\tau)_\ad$ depends only on $\zeta$ and not on the choice of $g$ or $z$.
+If $q$ denotes this equivalence class, then the map $\zeta \to q$ is the inverse of~\eqref{interp_q_cohomology}.
+
+\subsubsection{Proof of Lemma~\ref{lem:iso_q}}
+
+The proof of Lemma~\ref{lem:iso_q} uses Galois cohomology for the compact real form.  Recall $\theta\sigma = \sigma\theta$, and $G^{\sigma\theta}$ is a compact real form of~$G$. 
+The involutions $\sigma$ and $\theta$ coincide on $G^{\sigma\theta}$,
+therefore  $H^1(\sigma, G^{\sigma\theta})$ and  $H^1(\theta, G^{\sigma\theta})$ are the same set,
+which we will denote by  $H(\ast, G^{\sigma\theta})$.
+Now the inclusion $G^{\sigma\theta} \hookrightarrow G$ induces canonical maps 
+\begin{equation} \label{bij_cohom} H^{1}(\sigma,  G) \longleftarrow H(\ast, G^{\sigma\theta}) \longrightarrow H^{1}(\theta,  G).\end{equation}
+By \cite[Corollary~4.4 and Corollary 4.7]{galois}, both of these maps are \emph{bijections}.
+Replacing~$G$ by $Z$ we get bijections $H^{1}(\sigma, Z) \leftarrow H(\ast, Z^{\sigma\theta}) \rightarrow H^{1}_{\theta}(\Gamma, Z)$.
+These fit with the bijections~\eqref{bij_cohom} into a commutative diagram
+\[
+\begin{CD}
+H^{1}(\sigma, Z) @<<< H^1(\ast, Z^{\sigma\theta})@>>> H^{1}(\theta, Z)
+ \\
+@V{\varphi_{\sigma}}VV @VVV @V{\varphi_{\theta}}VV  \\
+H^{1}(\sigma, G) @<<< H^1(\ast, G^{\sigma\theta})@>>> H^{1}(\theta,  G)
+\end{CD}
+\]
+where $\varphi_\sigma$, $\varphi_\theta$ are the maps in \eqref{interp_q_cohomology}.
+
+Let us now prove part~(a) of Lemma~\ref{lem:iso_q}.
+Let $\gamma$ be an element of $(\Gad)^\sigma$; what we need to show is that there exists $\gamma_0 \in (G^\sigma)_{\ad}$ such that $\gamma \gamma_0^{-1}$ is $\theta$-invariant.
+
+Let $g$ be an element of $G$ such that $\gamma = gZ$; then $z=g \sigma(g^{-1})$ is an element of $Z^{-\sigma}$.
+Let $\zeta$ be its class in $H^{1}(\theta, Z)$.
+Let $\zeta_c$ be the inverse image of $\zeta$ under the bijection $H(\ast, Z^{\sigma\theta})\to H^{1}(\sigma, Z) $, and let $z_c\in (Z^{\sigma\theta})^{-\sigma}$ be a representative of $\zeta_c$.
+By definition there exists $z_0 \in Z$ such that $z = z_0 z_c \sigma(z_0^{-1})$.
+Since $\zeta_c$ is in the kernel of the map $H^1(\ast, Z^{\sigma\theta}) \to H^1(\ast, G^{\sigma\theta})$, there must exist  $k \in G^{\sigma\theta}$  such that $z_c = k \sigma(k^{-1})$.
+We see that $z = g \sigma(g)^{-1}$ is equal to $z_0 k \sigma((z_0k)^{-1})$, in other words
+\[ z_0^{-1} k^{-1} g \in G^{\sigma}.\]
+Let $\gamma_0$ be the image of $z_0^{-1} k^{-1} g$ in $\Gad$.
+Then $\gamma_0 \in (G^{\sigma})_\ad$, and $\gamma_0$ is equal to the image of $k^{-1} g$ in $\Gad$.
+The element $\kappa=\gamma \gamma_0^{-1}$ of $\Gad$  is therefore $\sigma$-invariant, and since $\kappa=kZ$, we also have $(\theta\sigma)(\kappa)=\kappa$; we conclude that $\theta(\kappa) = \kappa$, q.e.d.
+
+\textcolor{red}{TODO: prove that this induces a map $Q_{\sigma}(G)\to Q_{\theta}(G)$. Once this is done the  inverse map is clear, so it is a bijection.}
+
+%where $\varphi_{\sigma}$ and $\varphi_{\theta}$ are induced by the inclusion $Z \hookrightarrow G$.
+Since the horizontal arrows are isomorphisms in the category of pointed sets, they induce a canonical bijection between the kernels of $\varphi_{\sigma}$ and $\varphi_{\theta}$.
+%
+%; by~\eqref{interp_q_cohomology} this gives a canonical bijection 
+%\[ Q_{\sigma}(G) \simeq Q_{\theta}(G).\]
+
+\subsection{Actions of~$Q(G)$}
+
+\subsubsection*{On representations}
 
 Note that $Q_\sigma(G)$ is a group of automorphisms of $G(\R)$. It therefore acts on representations of $G(\R)$. 
-Similarly $Q_\theta(G)$ is a group of automorphisms of $(\g,K)$, and acts on $(\g,K)$-modules.
+Similarly $Q_\theta(G)$ is a group of automorphisms of $(\g,K)$, and acts on $(\g,K)$-modules.\footnote{AA 30-IV-2024: shouldn't this be:  $\Gad^\sigma$ and $\Gad^\theta$  act on $G(\R)$-representations or $(\g,K)$-modules respectively, and this induces actions of $Q_{\sigma}(G)$ and $Q_{\theta}(G)$ on equivalence classes...?}
+These two actions are intertwined by the isomorphism of Lemma~\ref{lem:iso_q}:
 
-\begin{lemma}
+\begin{lemma}\label{lem:action_q}
 Suppose $\pi$ is an irreducible  Hilbert space representation of $G(\R)$.
@@
 
-Based on these two Lemmas we write $Q(G)$ for the group $Q_\sigma(G)$ or $Q_\theta(G)$, depending on the situation.
-
-\subsubsection{Interpretation in terms of group cohomology}
-
-The groups $Q_{\sigma}(G)$ and $Q_{\theta}(G)$ are instances of the following construction: if~$\tau$ is an involutive automorphism of~$G$, then it preserves~$Z$ and induces an involution~$\tau_{\ad}$ of~$\Gad$; we may then set $Q_{\tau}(G)=\Gad^{\tau_{\ad}}/(G^{\tau})_{\ad}$, where $(G^{\tau})_{\ad}$ is the image of~$G^{\tau}$ in~$\Gad$.
-In this situation~$Q_{\tau}(G)$ has a simple interpretation in Galois cohomology, which we now recall.
-
-Let us first set up some notation.
-Let~$\Gamma$ be the Galois group~$\Z/2\Z$ of~$\R$.
-When~$A$ is a group and $\tau$ is an involutive automorphism of~$A$, we may consider the cohomology sets $H^0_\tau(\Gamma, A)$ and $H^1_\tau(\Gamma, A)$ attached to the action of~$\Gamma$ on~$G$ using~$\tau$.
-These are pointed sets, and not groups in general if~$A$ isn't abelian.
-We may view $H^0_\tau(\Gamma, A)$ as the fixed-point-set $A^{\tau}$, and $H^1_\tau(\Gamma,A)$ as the quotient of $A^{-\tau} = \{ a \in A, a\tau(a)=1\}$ by the equivalence relation~$\sim$ generated by $a \sim x a \tau(x^{-1})$ for all $x \in G$.
-
-We now take~$A=G$, and continue to assume~$\tau$ is an involutive automorphism. Then the short exact sequence $1\rightarrow Z \rightarrow G \rightarrow \Gad\rightarrow 1$ 
-gives rise to a ``long" exact sequence of pointed sets:
-\begin{equation} \label{long_ptset}
-1\rightarrow Z^\tau \rightarrow G^\tau \rightarrow \Gad^{\tau_{\ad}} \rightarrow H^1_\tau(\Gamma,Z)\rightarrow H^1_\tau(\Gamma,G)\rightarrow H^1_{\tau_\ad}(\Gamma,\Gad).
-\end{equation}
-By definition the connecting map  $ \Gad^{\tau_{\ad}} \rightarrow H^1_\tau(\Gamma,Z)$ sends $g \in \Gad^{\tau_{\ad}}$ to the equivalence class of $g \tau_{\ad}(g^{-1})$ in $H^1_\tau(\Gamma, Z)$, and the meaning of all the other maps is obvious.
-Going through the definitions we see that  two elements  $g_1, g_2$ have the same image if and only if $g_1 g_{2}\inv \in (G^\tau)_{\ad}$. 
-Therefore the image of the connecting map is in canonical bijection with $Q_\tau(G)$. Since~\eqref{long_ptset} is exact we get a canonical bijection
-\begin{equation} \label{interp_q_cohomology} Q_{\tau}(G) \simeq \ker(H^1_\tau(\Gamma,Z)\rightarrow H^1_\tau(\Gamma,G)).\end{equation}
-The previous argument is in the category of pointed sets, and on the right-hand side $H^1_\tau(\Gamma,G))$  is not a group in general.
-Therefore, at first sight, the map~\eqref{interp_q_cohomology} is only a set-theoretic bijection.
-However,
-$H^1_\tau(\Gamma,Z)$ is a group since $Z$ is abelian; thus both sides of~\eqref{interp_q_cohomology} have canonical abelian group structures, and chasing definitions one easily sees that~\eqref{interp_q_cohomology} is actually an isomorphism of abelian groups.
-
-\subsubsection{Isomorphism between $Q_{\sigma}(G)$ and $Q_{\theta}(G)$}
-
-Using the group cohomology interpretation in the previous paragraph, we can construct a canonical  isomorphism between $Q_{\sigma}(G)$ and $Q_{\theta}(G)$.
-For this recall $\theta\sigma = \sigma\theta$ and $G^{\sigma\theta}$ is a compact real form of~$G$.
-Furthermore $\sigma$ and $\theta$ coincide on $G^{\sigma\theta}$,
-therefore  $H_{\sigma}(\Gamma, G^{\sigma\theta})$ and  $H_{\theta}(\Gamma, G^{\sigma\theta})$ are the same set,
-which we will denote by  $H_{\sigma\mid\theta}(\Gamma, G^{\sigma\theta})$.
-Now the inclusion $G^{\sigma\theta} \hookrightarrow G$ induces canonical maps 
-\begin{equation} \label{bij_cohom} H^{1}_{\sigma}(\Gamma, G) \longleftarrow H_{\sigma\mid\theta}(\Gamma, G^{\sigma\theta}) \longrightarrow H^{1}_{\theta}(\Gamma, G).\end{equation}
-By \cite[Corollary~4.4 and Corollary 4.7]{galois}, both of these maps are \emph{bijections}.
-Replacing~$G$ by $Z$ we get bijections $H^{1}_{\sigma}(\Gamma, Z) \leftarrow H_{\sigma\mid\theta}(\Gamma, Z^{\sigma\theta}) \rightarrow H^{1}_{\theta}(\Gamma, Z)$.
-These fit with the bijections~\eqref{bij_cohom} into a commutative diagram
-\[
-\begin{CD}
-H^{1}_{\sigma}(\Gamma, Z) @<<< H_{\sigma\mid\theta}(\Gamma, Z^{\sigma\theta})@>>> H^{1}_{\theta}(\Gamma, Z)
- \\
-@V{\varphi_{\sigma}}VV @VVV @V{\varphi_{\theta}}VV  \\
-H^{1}_{\sigma}(\Gamma, G) @<<< H_{\sigma\mid\theta}(\Gamma, G^{\sigma\theta})@>>> H^{1}_{\theta}(\Gamma, G)
-\end{CD}
-\]
-where $\varphi_{\sigma}$ and $\varphi_{\theta}$ are induced by the inclusion $Z \hookrightarrow G$.
-Since the horizontal arrows are isomorphisms in the category of pointed sets, they induce a canonical bijection between the kernels of $\varphi_{\sigma}$ and $\varphi_{\theta}$; by~\eqref{interp_q_cohomology} this gives a canonical bijection
-\[ Q_{\sigma}(G) \simeq Q_{\theta}(G).\]
-This action preserves $L$-packets by 
-by~\cite[Lemma 6.18]{Contragredient}.
+Because of Lemmas~\ref{lem:iso_q} and \ref{lem:action_q}, we write $Q(G)$ for the group $Q_\sigma(G)$ or $Q_\theta(G)$, depending on the situation.
 
@@
 is $g\inv \sigma(g)\in \Stab_G(X)$.  Since $X$ is principal $\Stab_G(X)=ZU$ where $U$ is a unipotent group. 
-A standard fact is that $H^1_\sigma(\Gamma,U)=1$ \cite[Chap.~III, Proposition~6]{Serre_Galois}, and from this we see that, after multiplying $g$ on the right by an element of $u$, we can assume $g\inv \sigma(g)\in Z$.
+A standard fact is that $H^1(\sigma, U)=1$ \cite[Chap.~III, Proposition~6]{Serre_Galois}, and from this we see that, after multiplying $g$ on the right by an element of $u$, we can assume $g\inv \sigma(g)\in Z$.
 This is equivalent to: the image of $g$ in $\Gad$ is in $\Gad(\R)$.
@@
 
-It may be interesting to point out a variant on the proof of~(1).\footnote{AA 01-IV-2024: well, is it interesting to keep it in the paper, or should we comment it out...?
+%It may be interesting to point out a variant on the proof of~(1).\footnote{AA 01-IV-2024: well, is it interesting to keep it in the paper, or should we comment it out...?
 } Given $X \in \Op \cap i\g(\R)$, the map
-\begin{align} \label{bij_q_2} (\Omega_{X} \cap i\g(\R))/G(\R) & \to \kernel\left(H^1_\sigma(\Gamma,\mathrm{Stab}_G(X))\rightarrow H^1_\sigma(\Gamma,G)\right) \\ \mathrm{Ad}(g) \cdot X & \mapsto \text{class of $ g\sigma(g^{-1})$ in $H^1_\sigma(\Gamma,\mathrm{Stab}_G(X))$} \nonumber \end{align}
-is a bijection: see \cite[Lemma 5.2]{galois}. 
-Using this we get bijections
-$$
-\begin{aligned}
-(\Op\cap i\g(\R))/G(\R)&\simeq \ker(H^1_\sigma(\Gamma,\Stab_G(X))\rightarrow H^1_\sigma(\Gamma,G))\\
-&=
-\ker(H^1_\sigma(\Gamma,Z)\rightarrow H^1_\sigma(\Gamma,G))\\
-&\simeq Q_{\sigma}(G)
-\end{aligned}
-$$
-where the middle line uses the equality $H^1_\sigma(\Gamma,\Stab_G(X))=H^1_\sigma(\Gamma,Z)$, which comes from the fact that $\Stab_G(X)=ZU$  as explained in the proof.
+%\begin{align} \label{bij_q_2} (\Omega_{X} \cap i\g(\R))/G(\R) & \to \kernel\left(H^1_\sigma(\Gamma,\mathrm{Stab}_G(X))\rightarrow H^1_\sigma(\Gamma,G)\right) \\ \mathrm{Ad}(g) \cdot X & \mapsto \text{class of $ g\sigma(g^{-1})$ in $H^1_\sigma(\Gamma,\mathrm{Stab}_G(X))$} \nonumber \end{align}
+%is a bijection: see \cite[Lemma 5.2]{galois}. 
+%Using this we get bijections
+%$$
+%\begin{aligned}
+%(\Op\cap i\g(\R))/G(\R)&\simeq \ker(H^1_\sigma(\Gamma,\Stab_G(X))\rightarrow H^1_\sigma(\Gamma,G))\\
+%&=
+%\ker(H^1_\sigma(\Gamma,Z)\rightarrow H^1_\sigma(\Gamma,G))\\
+%&\simeq Q_{\sigma}(G)
+%\end{aligned}
+%$$
+%where the middle line uses the equality $H^1_\sigma(\Gamma,\Stab_G(X))=H^1_\sigma(\Gamma,Z)$, which comes from the fact that $\Stab_G(X)=ZU$  as explained in the proof.
 The resulting bijection  $(\Op\cap i\g(\R))/G(\R)\simeq Q_\sigma(\R)$ is equivariant (for the actions of $Q_\sigma(G)$ on $(\Op\cap i\g(\R))/G(\R)$ described above, and the action of  $Q_\sigma(G)$ on itself by multiplication), and this gives another proof of~(1).

### 2024-05-01 whittaker.tex
Tiny changes and added todos

@@
 
-In the case of real groups there are other invariants attached to an
+There are other invariants attached to an
 irreducible representation $\pi$.  We will be concerned with two of
@@
 
-\subsection{Some notation}
+\subsection{Basic notation}
 
@@
 Let $\N$ be the set of nilpotent elements of $\g$.
-This is the closure of the principal nilpotent orbit $\Op$.
+This is the closure of the principal nilpotent orbit $\Op$.\footnote{(AA 2024-V-1) Todo: give nice references...}
 
@@
 
+\footnote{(AA 2024-V-1) Todo: add notation $\pi_K$ and quickly discuss notions of equivalence?}
+
 \subsection{The invariants}\label{sec:invariants}
@@
 \subsubsection*{Associated variety and Gelfand--Kirillov dimension}
-
-We recall some results from,  \cite{vogan_bowdoin}, in particular Corollary 4.7 and Theorem 8.4.
 
@@
 The associated variety of $\pi$, denoted $\AV(\pi)$, is a closed, $K$-invariant set in $\s$, so it is a finite union of
-nilpotent $K$-orbits on $\s$.
+nilpotent $K$-orbits on $\s$.\footnote{(AA 2024-V-1) Todo: give nice references, Vogan's Bowdoin paper and others...}.
 
@@
 
-Part~(b) is one of the main results of~\cite{vogan_bowdoin}: see \cite[Theorem ?]{vogan_bowdoin}.\footnote{AA 19-II-2024: I'd welcome some help in navigating~\cite{vogan_bowdoin}: the relevant places seem to be  Sections 4, 5 and 8, but I have a few questions.}
+Part~(b) is one of the main results of~\cite{vogan_bowdoin}: see \cite[Theorem ?]{vogan_bowdoin}.
 
-Part~(c) follows from~\cite{rossmann_limit_orbits}.\footnote{AA 14-II-2024: maybe a little more detail would be welcome, the Rossmann paper does not seem to state the result in these terms.}
+Part~(c) follows from~\cite{rossmann_limit_orbits}. (Where?)
+
+\footnote{\textcolor{red}{(AA, 2024-V-1) : TODO -- find the right references, I tried but quickly got lost...}}
+
 \end{proof}
@@
 \end{lemma}
-See \cite{vogan_bowdoin}.
+See \cite{vogan_bowdoin}, in particular Corollary 4.7 and Theorem 8.4.
 
@@
 \begin{lemma}\label{lem:action_q}
-Suppose $\pi$ is an irreducible  Hilbert space representation of $G(\R)$.
-Suppose $g\in Q_\sigma(G)$. 
-Then $(\pi^g)_K\simeq (\pi_K)^{\phi(g)}$.
+Suppose $\pi$ is the equivalence class of an irreducible Hilbert space representation of $G(\R)$. 
+Suppose $q\in Q_\sigma(G)$. 
+Then $(\pi^q)_K\simeq (\pi_K)^{\phi(g)}$.
 \end{lemma}
@@
 \begin{proof}
-straightforward
+Immediate from Lemma~\ref{lem:iso_q} and the definition of the actions.
 \end{proof}

### 2024-05-01 whittaker.tex
Added proof for the consistency statement using AdamsTaibi prop 5.4

@@
 \item[(b)] Given $x \in Q_{\sigma}(G)$, and a representative $g\in (\Gad)^\sigma \cap (\Gad)^\theta$ as in~(a), the image of~$g$ in  $Q_\theta(G)$ depends only on~$x$, and not on  the choice of~$g$.
-The corresponding map $x \mapsto \phi(x)$, from $Q_{\sigma}(G)$ to $Q_{\theta}(G)$, is a group isomorphism.
+The corresponding map $x \mapsto \varphi(x)$, from $Q_{\sigma}(G)$ to $Q_{\theta}(G)$, is a group isomorphism.
 \end{itemize}
@@
 
-\textcolor{red}{TODO: prove that this induces a map $Q_{\sigma}(G)\to Q_{\theta}(G)$. Once this is done the  inverse map is clear, so it is a bijection.}
+Let us prove~(b).
+To show that when $g\in (\Gad)^\sigma \cap (\Gad)^\theta$ is a representative of $x \in Q_{\sigma}(G)$,  the image of~$g$ in  $Q_\theta(G)$ depends only on~$x$, it is enough to show that  $(G^\sigma)_\ad \cap (\Gad)^\theta \subset (G^\theta)_{\ad}$.
+This follows from \cite[Proposition 5.4]{galois}, applied to the action of~$G$ on~$\Gad$ and the obvious involutions.
+We conclude that taking $x \in Q_{\sigma}(G)$ to the image $\varphi(x)$ of $g$ in $Q_{\theta}(G)$ gives a well-defined map $\varphi\colon Q_{\sigma}(G)\to Q_{\theta}(G)$, which is clearly a group homomorphism.
+Exchanging the roles of $\sigma$ and $\theta$, we get a well-defined map $Q_{\theta}(G) \to Q_{\sigma}(G)$, which is the inverse of $\varphi$; therefore $\varphi$ is an isomorphism.
 

### 2024-05-01 whittaker.tex
added missing ingredient

--- 2024-05-01 whittaker.tex
@@
 
+\subsection{Missing ingredient?}
+
+We want to know that if $\pi_1=\pi(\lambda_1),\pi_2=\pi(\lambda_2)$ are large discrete series, then $\Wh(\pi_1)=\Wh(\pi_2)$ if and only $\lambda_1,\lambda_2$
+are in the same Weyl chamber.
+
+More precisely, $W$ and $W_K=\Norm_K(T)$ act on $T$, and $\pi(\lambda)=\pi(w\lambda)$ if and only if $\lambda\in W_K$.
+So the correct statement is: $\Wh(\pi_1)=\Wh(\pi_2)$ if and only if the Weyl chambers of $\lambda_1,\lambda_2$ are conjugate by $W_K$.
+
+One direction is easy. We need to show:
+$\Wh(\pi(\lambda_1))=\Wh(\pi(\lambda_2)\Rightarrow \mathcal C(\lambda_1)$ is $W_K$-conjugate to  $\mathcal C(\lambda_2)$.
+
+We may as well assume $\pi(\lambda_1),\pi(\lambda_2)$ are in the same $L$-packet, i.e. $\lambda_2=w\lambda_1$ for some $w\in W$.
+We know that $Q$ acts simply transitively on the large discrete series in the $L$-packet, and on principal nilpotent orbits.
+Also: this action is given by the action of $W$, i.e. if $g\in Q$ then $\pi(\lambda)^g=\pi(g\lambda)=\pi(w\lambda)$ for some $w\in W$.
+So
+$$
+\Wh(\pi_1)=\Wh(\pi_2)\Leftrightarrow \pi_1\simeq \pi_2\Leftrightarrow \lambda_1\sim_{W_K}\lambda_2\Leftrightarrow \mathcal C_1\sim_{W_K}\mathcal C_2
+$$
+
 \bibliographystyle{plain}

### 2024-05-22 whittaker.tex
Jolted down the right place in Rossmann, to be completed
Fixed SL(2) formulas; notes in an appendix

--- 2024-05-01 whittaker.tex
@@
 
-Part~(c) follows from~\cite{rossmann_limit_orbits}. (Where?)
+Part~(c) follows from~\cite{rossmann_limit_orbits}.
+Update May 1: it seems the right place is Lemma B, and to go from that to the statement is a matter of chasing definitions and using the asymptotic cone.
+I (=AA) will have a look.
 
@@
 \subsubsection{The Sekiguchi correspondence for principal nilpotent orbits}\label{sec:concrete_sek}
-\footnote{AA 2024-IV-15: should correct the formulas here.}
+\footnote{JA These formulas should be right now, see the Appendix}
 Let us spell out the special case of the Sekiguchi correspondence which is of interest here. We follow~\cite[Section~2]{AVAV}.
@@
 $$
-E_\theta=\frac12(-iE_\R-iF_\R+H_\R)\in \N\cap \s.
+E_\theta=\frac12(E_\R-F_\R+H_\R)\in \N\cap \s.
 $$
@@
 Computing the map in the other direction goes as follows.
-Suppose $E_\theta\in \Op\cap\s$. Choose an $SL(2)$-triple  $(E_\theta H_\theta,F_\theta)$ with
+Suppose $E_\theta\in \Op\cap\s$. Choose an $SL(2)$-triple  $(E_\theta, H_\theta,F_\theta)$ with
 $F_\theta\in\s$, which implies $H_\theta\in\k$. After conjugating by $K$ we may further assume $\sigma(E_\theta)=F_\theta$.
@@
 \begin{equation}\label{def_E_R}
-E_\R=\frac i2(E_\theta-F_\theta-H_\theta)\in\N\cap i\g(\R).
+E_\R=\frac 12(E_\theta-F_\theta-H_\theta)\in\N\cap i\g(\R).
 \end{equation}
@@
 
+\subsection{Appendix: $SL(2,\R)$ calculation}
+
+This is not for publication, just to make sure we have the formulas in Section \ref{sec:concrete_sek} correct.
+These are:
+$$
+E_\theta=\frac12(E_\R-F_\R+H_\R)\in \N\cap \s.
+$$
+and
+$$
+E_\R=\frac 12(E_\theta-F_\theta-H_\theta)\in\N\cap i\g(\R).
+$$
+
+Recall $\sigma(X)=\overline X$ and $\theta(X)=-X^t$.
+
+Take
+$$
+E_\R=\begin{pmatrix}0&i\\0&0\end{pmatrix},
+F_\R=\begin{pmatrix}0&0\\-i&0\end{pmatrix},
+H_\R=\begin{pmatrix}1&0\\0&-1\end{pmatrix}
+$$
+These satisfy the standard $SL(2)$ commutation relations, and $E_\R,F_\R$ are in the $-1$-eigenspace of $\sigma$,
+and $\theta(E_\R)=F_\R, \theta(H_\R)=-H_\R$.
+
+Set $g=\frac 1{\sqrt 2}\begin{pmatrix}1&i\\i&1
+\end{pmatrix}$, and take $E_\theta,F_\theta,H_\theta$ be the conjugates of $E_\R,F_\R,H_\R$ by $g$:
+$$
+E_\theta=\frac12\begin{pmatrix}1&i\\i&-1\end{pmatrix},
+F_\theta=\frac12\begin{pmatrix}1&-i\\-i&-1\end{pmatrix},
+H_\theta=\begin{pmatrix}0&-i\\i&0\end{pmatrix},
+$$
+
+These satisfy the standard $SL(2)$ commutation relations, and $E_\theta,F_\theta$ are in the $-1$-eigenspace of $\theta$.
+Also $\sigma(E_\theta)=F_\theta,\sigma(H_\theta)=-H_\theta$.
+
+Furthermore:
+$$
+\begin{aligned}
+  E_\theta&=\frac12(E_\R-F_\R+H_\R)\\
+  F_\theta&=\frac12(-E_\R+F_\R+H_\R)\\
+  H_\theta&=-E_\R-F_\R
+\end{aligned}
+$$
+and
+$$
+\begin{aligned}
+  E_\R&=\frac12(E_\theta-F_\theta-H_\theta)\\
+  F_\R&=\frac12(-E_\theta+F_\theta-H_\theta)\\
+  H_\R&=E_\theta+F_\theta
+\end{aligned}
+$$
+
 \bibliographystyle{plain}
@@
 \end{document}
-%%% Local Variables: 
-%%% mode: latex
-%%% TeX-master: t
-%%% End: s_{1}:0 -> -1 6

### 2024-05-29 whittaker.tex
Details about why Rossmann's lemma implies WF is a single orbit

@@
 
-Part~(b) is one of the main results of~\cite{vogan_bowdoin}: see \cite[Theorem ?]{vogan_bowdoin}.
+Part~(b) is one of the main results of~\cite{vogan_bowdoin}: see \cite[Theorem ?]{vogan_bowdoin}.\footnote{\textcolor{red}{(AA, 2024-V-1) : TODO -- find the right references, I tried but quickly got lost...}}
 
@@
 Update May 1: it seems the right place is Lemma B, and to go from that to the statement is a matter of chasing definitions and using the asymptotic cone.
-I (=AA) will have a look.
-
-\footnote{\textcolor{red}{(AA, 2024-V-1) : TODO -- find the right references, I tried but quickly got lost...}}
+\textcolor{blue}{Update May 29: by Lemma B in~\cite{rossmann_limit_orbits}, if $\mathfrak{h}^+$ is the large Weyl chamber containing the HC parameter of~$\pi$, then $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ is a single orbit---where $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ is defined in Rossmann's paper.
+What we have to check is that the closure of this $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains $\WF(\pi)$.
+Now, I think that  the equivalence between conditions  (L1) and (L2) on page 2 of~\cite{rossmann_limit_orbits} easily implies that the closure of $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains the asymptotic cone of the orbit of the HC parameter, so the claim seems to follow from the relationship between $\WF(\pi)$ and the asymptotic cone.}
 

### 2024-06-07 whittaker.tex
Restores the lost discussion about Weyl chambers

@@
 What we have to check is that the closure of this $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains $\WF(\pi)$.
-Now, I think that  the equivalence between conditions  (L1) and (L2) on page 2 of~\cite{rossmann_limit_orbits} easily implies that the closure of $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains the asymptotic cone of the orbit of the HC parameter, so the claim seems to follow from the relationship between $\WF(\pi)$ and the asymptotic cone.}
+Now, I think that  the equivalence between conditions  (L1) and (L2) on page 2 of~\cite{rossmann_limit_orbits} easily implies that the closure of $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains the asymptotic cone of the orbit of the HC parameter, so the claim seems to follow from the relationship between $\WF(\pi)$ and the asymptotic cone (Lemma~\ref{lem:WF_and_AC}).}
 
@@
 
+For this see \cite{HarrisHeOlafsson}; in our case the result is due to Rossmann and can be extracted from \cite{RossmannPicard}, Theorem B and C. \qed
+
 In Section~\ref{sec:alternate_WF} below we will  give another simple description of~$\WF(\pi)$, based on the description of $\AV(\pi)$ in the previous paragraph and on the Sekiguchi correspondence.
@@
 
+\subsection{Bonus}
+
+This section uses the arguments above to deduce the ``folklore fact'' stated by  Jeff and Tasho with a reference to the present paper for the proof.
+\footnote{AA 2024-VI-7: I don't remember whether this was the most up-to-date version  of our understanding; I seem to remember that we wanted to know that $Q$ acts simply transitively on the large Weyl chambers, and I haven't thought yet about what the relationship this has with what is written below...}
+
+We want to know that if $\pi_1=\pi(\lambda_1),\pi_2=\pi(\lambda_2)$ are large discrete series, then $\Wh(\pi_1)=\Wh(\pi_2)$ if and only $\lambda_1,\lambda_2$
+are in the same Weyl chamber.
+
+More precisely, $W$ and $W_K=\Norm_K(T)$ act on $T$, and $\pi(\lambda)=\pi(w\lambda)$ if and only if $\lambda\in W_K$.
+So the correct statement is: $\Wh(\pi_1)=\Wh(\pi_2)$ if and only if the Weyl chambers of $\lambda_1,\lambda_2$ are conjugate by $W_K$.
+
+One direction is easy using the above results: we have seen that if $\lambda_1,\lambda_2$
+are in the same Weyl chamber then the wavefront set, therefore the Whittaker model, are the same.
+
+What we need to show:
+$\Wh(\pi(\lambda_1))=\Wh(\pi(\lambda_2)\Rightarrow \mathcal C(\lambda_1)$ is $W_K$-conjugate to  $\mathcal C(\lambda_2)$.
+
+We may as well assume $\pi(\lambda_1),\pi(\lambda_2)$ are in the same $L$-packet, i.e.
+$\lambda_2=w\lambda_1$ for some $w\in W$.We know that $Q$ acts simply transitively on the large discrete series in the $L$-packet, and on principal nilpotent orbits.
+Also: this action is given by the action of $W$, i.e. if $g\in Q$ then $\pi(\lambda)^g=\pi(g\lambda)=\pi(w\lambda)$ for some $w\in W$.
+So
+$$
+\Wh(\pi_1)=\Wh(\pi_2)\Leftrightarrow \pi_1\simeq \pi_2\Leftrightarrow \lambda_1\sim_{W_K}\lambda_2\Leftrightarrow \mathcal C_1\sim_{W_K}\mathcal C_2
+$$
+
 \subsection{Appendix: $SL(2,\R)$ calculation}

### 2024-06-12 whittaker.tex
Fairly serious round of changes
Fixed missing *'s and signs in many places, added some missing proofs
New Fresse/Mehdi reference

@@
 \subsubsection*{Nilpotent orbits} 
+\label{s:nilpotentorbits}
+Let $\N$ be the set of nilpotent elements of $\g$.
 
-Let $\N$ be the set of nilpotent elements of $\g$.
-This is the closure of the principal nilpotent orbit $\Op$.\footnote{(AA 2024-V-1) Todo: give nice references...}
+We need to pass to the dual Lie algebra $\g^*$. We follow  \cite[Section 2]{AVAV}.
+Define $\N^*\subset \g^*$ to be the set of elements whose orbit is a cone.
+We identify $\g$ and $\g^*$ using  a non-degenerate invariant form on $\g$.
+This restricts to an isomorphism $\N\simeq \N^*$. Although this isomorphism depends on the choice of form,
+the bijection on the level of $G$-orbits is canonical.
+
+We define $\O_p$ to be the principal nilpotent orbit in $\N^*$: this is the unique orbit such that $\overline{\O_p}=\N^*$.
+
+In the $\theta$-picture we have an analogous construction. We may assume the form is orthogonal with respect to $\theta$.
+Consequently the decomposition $\g=\mathfrak k+\s$ also gives $\g^*=\mathfrak k^*\oplus \s^*$, and this induces
+a canonical bijection between $K$-orbits on $\s$ and on $\s^*$.
 
@@
 Let $I_\pi$ be the annihlator of $\pi$ in the universal enveloping algebra.
-Let $\AVann(\pi)$ be the associated variety of $I_\pi$.
-This is the closure of a single complex nilpotent orbit $\O$.
-The associated variety of $\pi$, denoted $\AV(\pi)$, is a closed, $K$-invariant set in $\s$, so it is a finite union of
-nilpotent $K$-orbits on $\s$.\footnote{(AA 2024-V-1) Todo: give nice references, Vogan's Bowdoin paper and others...}.
+Let $\AVann(\pi)\subset\N^*\subset \g^*$ be the associated variety of $I_\pi$.
+This is the closure of a single complex nilpotent orbit $\O$
+See \cite[Section 1, Theorem 4.7]{vogan_bowdoin}.
+
+The associated variety of $\pi$, denoted $\AV(\pi)$, is a closed, $K$-invariant set in $\s^*$, so it is a finite union of
+nilpotent $K$-orbits on $\s^*$. See \cite[Section 5]{vogan_bowdoin}.
 
@@
 
-If we do not start with a $(\g, K)$-module but with a Hilbert space representation~$\pi$ of $G(\R)$,  we define $\AV(\pi)$ to be the associated variety 
-of its underlying $(\g,K)$-module.
+We define the associated variety of a Hilbert space representations to be that of  its underlying $(\g,K)$-module.
 
@@
 
-If $\pi$ is an irreducible $(\g,K)$-module we define $\WF(\pi)$ to be the wave-front set of 
-the Hilbert space globalization of $\pi$.
+We define the wave front set of a $(\g,K)$-module to be that of its 
+Hilbert space globalization.
 
@@
 
-We write $\Wh(\pi)$ for the set of Whittaker data~$\w$ such that If $\pi$ is an irreducible $(\g,K)$-module we define $\Wh(\pi)$ to be the set of 
-the Hilbert space globalization of $\pi$.
+We write $\Wh(\pi)$ for the set of Whittaker data~$\w$ such that $\pi$ has a $\w$-Whittaker model.
+
+We define the Whittaker data  of a $(\g,K)$-module to be that of its 
+Hilbert space globalization.
 
@@
 \item $\Wh(\pi)$ is a single Whittaker datum;
-\item $\AV(\pi)$ is the closure of a single $K$-orbit on~$\mathcal{O}_p \cap \mathfrak{s}$;
+\item $\AV(\pi)$ is the closure of a single $K$-orbit on~$\mathcal{O}_p \cap \s^*$;
 \item  $\WF(\pi)$ is the closure of a single $G(\R)$-orbit on $\mathcal{O}_p \cap  i \g(\R)^*$.
@@
 and by \cite[Lemma 14.14]{abv} a  large discrete series representation admits a unique Whittaker datum.
-
-Part~(b) is one of the main results of~\cite{vogan_bowdoin}: see \cite[Theorem ?]{vogan_bowdoin}.\footnote{\textcolor{red}{(AA, 2024-V-1) : TODO -- find the right references, I tried but quickly got lost...}}
+For (b) see \cite[Proposition A.9]{AV1}.
 
@@
 Because of this result we abuse notation slightly as follows.
-If~$\pi$ is a generic discrete series representation of~$G(\R)$, we write $AV(\pi)=\O$ to indicate that $AV(\pi)$ is the closure of the $K$-orbit $\O\subset \s$.
+If~$\pi$ is a generic discrete series representation of~$G(\R)$, we write $AV(\pi)=\O$ to indicate that $AV(\pi)$ is the closure of the $K$-orbit $\O\subset \s^*$.
 Similarly we write $\WF(\pi)=\O$ to indicate that $\WF(\pi)$ is the closure of the $G(\R)$-orbit $\O\subset i\g(\R)^*$.
@@
     \item $\pi$ is large;
-\item $\AVann(\pi)=\N=\overline{\Op}$;
+\item $\AVann(\pi)=\N^*=\overline{\Op}$;
 \item $\dim(\AVann(\pi))=N$;
@@
 
-Given a generic discrete series representation~$\pi$ we consider the invariants of~$\pi$ defined by Proposition~\ref{invariants_ds}: a Whittaker datum  $\Wh(\pi)$, a $K$-orbit $\AV(\pi)$ in $\mathcal{O}_p \cap \mathfrak{s}$, and a $G(\R)$-orbit $\WF(\pi)$ in $(\mathcal{O}_p \cap  i \g(\R))$.
+Given a generic discrete series representation~$\pi$ we consider the invariants of~$\pi$ defined by Proposition~\ref{invariants_ds}: a Whittaker datum  $\Wh(\pi)$, a $K$-orbit $\AV(\pi)$ in $\mathcal{O}_p \cap \s^*$, and a $G(\R)$-orbit $\WF(\pi)$ in $\mathcal{O}_p \cap  i \g(\R)^*$.
 
@@
 \item[(2)] The set of Whittaker data for $G(\R)$ ;
-\item[(3)] The set of~$K$-orbits on $\mathcal{O}_p \cap \s$.
+\item[(3)] The set of~$K$-orbits on $\mathcal{O}_p \cap \s^*$.
 \item[(4)] The set of~$G(\R)$-orbits on $\mathcal{O}_p \cap  i \g(\R)^*$.
 \end{enumerate}
+In particular if $\pi$ is a large discrete series represenation then each of these three invariants of $\pi$ determines the other $2$. 
 \end{theorem}
 
-Before embarking on the proof, let us point out that the maps in the theorem are defined using rather deep results of representation theory.
-However, we shall prove in Section~\ref{sec:explicit} that all bijections $(i) \leftrightarrow (j)$, for $i,j \in \{(1), \dots, (4)\}$, can be spelled out in elementary terms.
+Before embarking on the proof, let us point out that the maps in the Theorem are defined using rather deep results of representation theory.
+However, we shall show in Section~\ref{sec:explicit} that all bijections $(i) \leftrightarrow (j)$, for $i,j \in \{(1), \dots, (4)\}$, can be spelled out in elementary terms.
 Furthermore we shall prove, using elementary arguments, that (3) $\leftrightarrow$ (4) coincides with the Kostant--Sekiguchi correspondence.
@@
 Note that $Q_\sigma(G)$ is a group of automorphisms of $G(\R)$. It therefore acts on representations of $G(\R)$. 
-Similarly $Q_\theta(G)$ is a group of automorphisms of $(\g,K)$, and acts on $(\g,K)$-modules.\footnote{AA 30-IV-2024: shouldn't this be:  $\Gad^\sigma$ and $\Gad^\theta$  act on $G(\R)$-representations or $(\g,K)$-modules respectively, and this induces actions of $Q_{\sigma}(G)$ and $Q_{\theta}(G)$ on equivalence classes...?}
+Similarly $Q_\theta(G)$ is a group of automorphisms of $(\g,K)$, and acts on $(\g,K)$-modules.\footnote{AA 30-IV-2024: shouldn't this be:  $\Gad^\sigma$ and $\Gad^\theta$  act on $G(\R)$-representations or $(\g,K)$-modules respectively, and this induces actions of $Q_{\sigma}(G)$ and $Q_{\theta}(G)$ on equivalence classes...?
+JDA this is the same thing}
 These two actions are intertwined by the isomorphism of Lemma~\ref{lem:iso_q}:
@@
 To define the action of~$Q_{\sigma}(G)$ on~(4), first observe that~$\Gad$ acts on~$\g$ by the adjoint action.
-This action preserves~$\Op$, and its restriction to~$\Gad(\R)$ preserves~$\Op\cap i\g(\R)$.
-Since elements on a given~$G(\R)_{\mathrm{ad}}$-orbit are in the same~$G(\R)$-orbit, this induces an action of $Q_{\sigma}(G)=\Gad(\R)/G(\R)_{\mathrm{ad}}$ on~$(\Op\cap i\g(\R))/G(\R)$.
+This action preserves~$\Op$, and its restriction to~$\Gad(\R)$ preserves~$\Op\cap i\g(\R)^*$.
+Since elements on a given~$G(\R)_{\mathrm{ad}}$-orbit are in the same~$G(\R)$-orbit, this induces an action of $Q_{\sigma}(G)=\Gad(\R)/G(\R)_{\mathrm{ad}}$ on~$(\Op\cap i\g(\R)^*)/G(\R)$.
 
@@
 \begin{enumerate} 
-\item The action of~$Q_{\sigma}(G)$ on $(\Op\cap i\g(\R))/G(\R)$ is simply transitive.
+\item The action of~$Q_{\sigma}(G)$ on $(\Op\cap i\g(\R)^*)/G(\R)$ is simply transitive.
 \item The map $\pi \mapsto \WF(\pi)$ is $Q_{\sigma}(G)$-equivariant.
@@
 \begin{proof}
-The proof of~(1) is a standard argument in group cohomology. Suppose $\omega,\omega'$ are $G(\R)$ orbits in $\Op\cap i\g(\R)$,
-and choose $X\in \omega,X'\in\omega'$. Then there exists $g\in G$ such that $\Ad(g)(X)=X'$. Since $X\in \g(\R)$ the condition $X'\in i\g(\R)$ 
+The proof of~(1) is a standard argument in group cohomology. Suppose $\omega,\omega'$ are $G(\R)$ orbits in $\Op\cap i\g(\R)^*$,
+and choose $X\in \omega,X'\in\omega'$. Then there exists $g\in G$ such that $\Ad(g)(X)=X'$. Since $X\in \g(\R)^*$ the condition $X'\in i\g(\R)^*$ 
 is $g\inv \sigma(g)\in \Stab_G(X)$.  Since $X$ is principal $\Stab_G(X)=ZU$ where $U$ is a unipotent group. 
@@
 On the other hand $Q(G)$, realized as $Q_\theta(G)$ is a group of automorphisms of $(\g,K)$.
-It induces actions on $\s$, $\Op$ and $\Op\cap\s$, and on $(\g,K)$-modules.
+It induces actions on $\s^*$, $\Op$ and $\Op\cap\s^*$, and on $(\g,K)$-modules.
 
@@
 \begin{enumerate} 
-\item The action of~$Q(G)$ on $(\Op \cap \s)/K$ is simply transitive.
+\item The action of~$Q(G)$ on $(\Op \cap \s^*)/K$ is simply transitive.
 \item The map $\pi \mapsto \AV(\pi)$ is $Q(G)$-equivariant.
@@
 If $B$ is defined over $\R$ we consider $N(\R),\n(\R), \overline\n(\R)$, etc.
-Let $\kappa(\,,\,)$  be the Killing form. 
-For $X\in i\overline \n(\R)$ define a unitary character $\psi_X$ of $N(\R)$ by:
+For $X\in i\overline \n(\R)^*$ define a unitary character $\psi_X$ of $N(\R)$ by:
 $$
-\psi_X(e^Y)=e^{2\pi \kappa(X,Y)}\quad(Y\in \n(\R)).
+\psi_X(e^Y)=e^{X(Y)}\quad(Y\in \n(\R)).
 $$
-The map $X\rightarrow \psi_X$ is an isomorphism between $i\overline\n(\R)$ and the unitary characters of $N(\R)$.
-It is easy to see $\psi_X$ is non-degenerate if and only if $X\in i\g(\R)$ is a principal nilpotent element.
+The map $X\rightarrow \psi_X$ is an isomorphism between $i\overline\n(\R)^*$ and the unitary characters of $N(\R)$.
+It is easy to see $\psi_X$ is non-degenerate if and only if $X\in i\g(\R)^*$ is a principal nilpotent element.
 In this case we write $(B(\R),X)$ for the Whittaker datum $(B(\R),\psi_X)$.
@@
 It is clear that $(B(\R),X)\mapsto G(\R)\cdot X$ is a bijection between Whittaker data and
-$(\Op(\R)\cap i\g(\R))/G(\R)$. The main result of \cite{matumoto} (Theorem A) says:
+$(\Op(\R)\cap i\g(\R)^*)/G(\R)$. The main result of \cite{matumoto} (Theorem A) says:
 
@@
 \begin{equation}
-  \label{e:Epi}
-  E_\pi=\sum_{\alpha\in S(\lambda)}X_\alpha\in \N.
+  \label{e:Fpi}
+  F_\pi=\sum_{\alpha\in S(\lambda)}X_{-\alpha}\in \N.
 \end{equation}
 
-Then $E_\pi\in\s$ is a regular nilpotent element, and
+Then $F_\pi\in\s$ is a regular nilpotent element. Let $\xi_\pi\in \N^*$ be the corresponding element (cf. Section \ref{s:nilpotentorbits}).
+Then 
 $$
-\AV(\pi)=\overline{K\cdot E_\pi}.
+\AV(\pi)=\overline{K\cdot \xi_\pi}.
 $$
@@
 
-\begin{proof}
-If $\pi$ is any discrete series representation, with Harish-Chandra parameter $\lambda$, let
-$\n_{\lambda}=\sum_{\alpha\in\Delta^+(\lambda)}\g_\alpha$.
-Then by \cite[Proposition 6.8]{vogan_irreducibility} $AV(\pi)=K\cdot(\n_\lambda\cap\s)$.
-
-Now assume $\pi$ is large. This implies $X_\alpha\in\s$ for all $\alpha\in S(\lambda)$, so $E_\pi\in \s$. 
-By~\cite{kostant_tds} $E_\pi$ is a regular nilpotent element, so the closure of $K\cdot E_\pi$ in $\s$ is equal to $K\cdot(\n_\lambda\cap\s)$. 
-\end{proof}
+See
+\cite[Propositions A.7 and A.9]{AV1}.
 
@@
 Choose a compact Cartan subgroup $T$, and let $\lambda\in\t^*$ be the Harish-Chandra parameter of $\pi$.
-Identify $\lambda$ with an element $H_\pi\in i\t\subset i\g$ using the isomorphism $\t\simeq \t^*$ induced by the Killing form. 
 Define
-\begin{equation} \label{semisimple_orbit_HC} \mathcal{O}_{\pi}=\quad \text{$G(\R)$-orbit of the Harish-Chandra parameter $H_\pi$}.\end{equation}
+\begin{equation} \label{semisimple_orbit_HC} \mathcal{O}_{\pi}=G(\R)\cdot\lambda.\end{equation}
 
 Consider the \emph{asymptotic cone} of $\mathcal{O}_\pi$ (see e.g. \cite[Section 3]{AVAV}) :
-\[ \AC(\mathcal{O}_\pi) = \left\{ v \in \g \ : \ \text{$\exists (\varepsilon_n, x_n)\in (\R_+ \times \mathcal{O}_\pi)^\mathbb{N}$ such that $\varepsilon_n \to 0$ and $\varepsilon_n x_n \to v$}  \right\}.
+\[ \AC(\mathcal{O}_\pi) = \left\{ v \in \g^* \ : \ \text{$\exists (\varepsilon_n, x_n)\in (\R_+ \times \mathcal{O}_\pi)^\mathbb{N}$ such that $\varepsilon_n \to 0$ and $\varepsilon_n x_n \to v$}\}  \right\}.
 \]
+This is a union of nilpotent $G(\R)$-orbits on $i\g(\R)^*$.
 
@@
 
-We recall a recent result of the first author (JDA) and Kaletha, which spells out the connection between large discrete series and Whittaker data using  {\it Kostant sections}.
-Let~$X$ be a regular nilpotent element of~$\g$, and suppose~$X$ fits into an $\SL(2)$-triple $(X, H, Y)$.
+We recall a recent result of the first author and Tasho Kaletha, which spells out the connection between large discrete series and Whittaker data using  {\it Kostant sections}.
+Let~$X$ be a regular nilpotent element of~$\g$, and choose an  $\SL(2)$-triple $(X, H, Y)$.
 The Kostant section~$\Kostant{X}$ is the affine subspace $X + \mathrm{Cent}_{\g}(Y)$ of~$\g$.
-It depends on the choice of $\SL(2)$-triple, but if $X \in \g(\R)$, then the $G(\R)$-conjugacy class of~$\Kostant{X}$ depends only on the $G(\R)$-conjugacy class of~$X$.
+This depends on the choice of $\SL(2)$-triple, but if $X \in \g(\R)^*$, then the $G(\R)$-conjugacy class of~$\Kostant{X}$ depends only on the $G(\R)$-conjugacy class of~$X$.
 
 \begin{proposition}[\cite{adams_kaletha}]\label{JeffTasho_criterion}
-Suppose $\pi$ is a generic discrete series representation of~$G(\R)$. Suppose~$\pi$ be a Whittaker datum for~$G(\R)$, and let~$X \in i\g(\R)$ be a regular nilpotent element such that $\w = \w_X$. 
+Suppose $\pi$ is a generic discrete series representation of~$G(\R)$. Suppose~$\pi$ be a Whittaker datum for~$G(\R)$, and let~$X \in i\g(\R)^*$ be a regular nilpotent element such that $\w = \w_X$. 
 Then $\pi$ is $\w$-generic if and only if $\Kostant{X}$ meets $\mathcal{O}_\pi$. 
@@
 
-Theorem~\ref{th:main} gives a bijection between the set $(\Op \cap \s)/K$ of principal nilpotent~$K$-orbits and the set $(\Op \cap i\g(\R))/G(\R)$ of principal nilpotent~$G(\R)$-orbits.
+Theorem~\ref{th:main} gives a bijection between the set $(\Op \cap \s^*)/K$ of principal nilpotent~$K$-orbits and the set $(\Op \cap i\g(\R)^*/G(\R)$ of principal nilpotent~$G(\R)$-orbits.
 
@@
 
-Suppose $E_\R\in \Op\cap i\g(\R)$. Then we may choose an $SL(2)$-triple $(H_\R,E_\R,F_\R)$ with $F_\R$  contained in $i\g(\R)$,
+{\bf Note:} Need some $*$'s here.
+
+Suppose $F_\R\in \Op\cap i\g(\R)$. Then we may choose an $SL(2)$-triple $(H_\R,E_\R,F_\R)$ with $E_\R$  contained in $i\g(\R)$,
 which implies $H_\R\in \g(\R)$. 
@@
 $$
-E_\theta=\frac12(E_\R-F_\R+H_\R)\in \N\cap \s.
+F_\theta=\frac12(-E_\R+F_\R+H_\R)\in \N\cap \s.
 $$
@@
 Computing the map in the other direction goes as follows.
-Suppose $E_\theta\in \Op\cap\s$. Choose an $SL(2)$-triple  $(E_\theta, H_\theta,F_\theta)$ with
-$F_\theta\in\s$, which implies $H_\theta\in\k$. After conjugating by $K$ we may further assume $\sigma(E_\theta)=F_\theta$.
+Suppose $F_\theta\in \Op\cap\s$. Choose an $SL(2)$-triple  $(E_\theta, H_\theta,F_\theta)$ with
+$E_\theta\in\s$, which implies $H_\theta\in\k$. After conjugating by $K$ we may further assume $\sigma(E_\theta)=F_\theta$.
 Then the Sekiguchi correspondence takes the $K$-orbit of $E_\theta$ to the $G(\R)$-orbit of 
-\begin{equation}\label{def_E_R}
-E_\R=\frac 12(E_\theta-F_\theta-H_\theta)\in\N\cap i\g(\R).
+\begin{equation}\label{def_F_R}
+F_\R=\frac 12(-E_\theta+F_\theta-H_\theta)\in\N\cap i\g(\R).
 \end{equation}
@@
 
-Consider the principal nilpotent element~$E_\pi$ defined in~\eqref{e:Epi}.
-We define another regular nilpotent element  $E_\R$ by using $E_\pi$ as $E_\theta$ in~\eqref{def_E_R}.
-We know that the associated variety of $\pi$ is the closure of $K \cdot E_\pi$ (Lemma~\ref{l:pi_to_av}), so the image of $\AV(\pi)$ by the Sekiguchi correspondence is the closure of the $G(\R)$-orbit of $E_\R$.
-We want to check that $\WF(\pi)$
+Consider the principal nilpotent element~$F_\pi$ defined in~\eqref{e:Fpi}. We define another regular nilpotent element  $F_\R$ using 
+\eqref{def_F_R} using $F_\theta=F_\pi$ on the right hand side. 
+We know that  $\AV(\pi)=K \cdot \xi_\pi$ (where $\xi_\pi\in\g^*$ corresponds to $F_\pi$, see Lemma~\ref{l:pi_to_av}), so the image of $\AV(\pi)$ by the Sekiguchi correspondence is 
+ $G(\R)\cdot F_\R$. We want to check that $\WF(\pi)$
 
-By Lemma~\ref{lem:matumoto} it is enough to check that $\pi$ is $\w$-generic for the Whittaker datum $\w$ corresponding to~$E_\R$.
-By Proposition~\ref{JeffTasho_criterion} this is the case if and only if the Kostant section $\Kostant{E_\R}$ meets $\mathcal{O}_\pi$.
+By Lemma~\ref{lem:matumoto} it is enough to check that $\pi$ is $\w$-generic for the Whittaker datum $\w$ corresponding to~$F_\R$.
+By Proposition~\ref{JeffTasho_criterion} this is the case if and only if the Kostant section $\Kostant{F_\R}$ meets $\mathcal{O}_\pi$.
 
-Now, we know that $\Kostant{E_\R}=E_\R+\mathrm{Cent}_\g(F_\R)$ contains $E_\R-F_\R = H_\theta$\footnote{AA 2024-IV-15: insert the correct version once we've checked the Sekiguchi formulas in the previous paragraph.
+Now, we know that $\Kostant{F_\R}=F_\R+\mathrm{Cent}_\g(F_\R)$ contains $F_\R-F_\R = H_\theta$\footnote{AA 2024-IV-15: insert the correct version once we've checked the Sekiguchi formulas in the previous paragraph.
 }.
 In general the orbits $\mathcal{O}_\pi$ and $G(\R) \cdot H_\theta$ are disjoint. 
-Nevertheless $H_{\lambda}$ and $H_\theta=[E_\theta, F_\theta]$ are in the same Weyl chamber\footnote{AA 2024-IV-15: should probably explain a bit more why this is correct.}.
+Nevertheless $H_{\lambda}$ and $H_\theta=[F_\theta, F_\theta]$ are in the same Weyl chamber\footnote{AA 2024-IV-15: should probably explain a bit more why this is correct.}.
 Therefore the result follows from:
@@
 Then $\Kostant{X}$ meets~$\mathcal{O}$ if and only if $X$ is in the asymptotic cone~$\AC(\mathcal{O})$.
+
+Consequently each of the three invariants $\Wh(\pi),\AV(\pi)$ and $\WF(\pi)$ are constant for $\pi=\pi(\lambda)$ a large discrete series representation, and $\lambda$ in a fixed large Weyl chamber.
 \end{lemma}
-\begin{proof} See if we spell it  out (one direction is in Adams--Kaletha, but parts of the arguments are similar so it might be more convenient include both directions...).
-Maybe it's actually possible just refer to Fresse--Mehdi with pointers.
+\begin{proof} 
+If $X\in \AC(\mathcal O)$ then $\Kostant{X}$ meets $\mathcal O$ by \cite[Lemma 3.2.3]{adams_kaletha}.
+
+Suppose $\Kostant{X}$ meets $\mathcal O$.
+This means there is an $SL(2)$-triple $(H,Y,X)$, and $Z\in \Cent(Y)$ such that $X+Z\in \O$. 
+By the representation theory of $SL(2)$ we know that $Z=\sum_{j=0}^n Z_j$ with $[H,Z_j]=-jZ_j$. 
+Then 
+$$
+\Ad(e^{tH})(X+Z)=e^{2t}(X) + \sum_j e^{-tj}Z_j
+$$
+Taking the limit as $t\rightarrow 0$ gives $\Ad(e^{tH})(X+Z)\rightarrow e^{2t}X$. Therefore
+$$
+\lim_{t\rightarrow 0}e^{-2t}\Ad(e^{tH})(X+Z)=X
+$$ which implies the result.
 \end{proof}
+
+For a closely related result see \cite[Proposition 3.5]{fm}.
 
@@
 Choose a compact Cartan subgroup $T$ and let $\lambda\in \t^*$ be the Harish-Chandra parameter of $\pi$.
-Define $E_\theta=E_\pi$ as in \eqref{e:Epi}, and choose an $SL(2)$-triple $(H_\theta,E_\theta,F_\theta)$ as usual.
+Define $F_\theta=F_\pi$ as in \eqref{e:Fpi}, and choose an $SL(2)$-triple $(H_\theta,E_\theta,F_\theta)$ as usual.
 After conjugating by $K$ we may assume $\sigma(E_\theta)=F_\theta$.  Then\footnote{AA 14-II-2023: no closure?}
@@
 
+Here is another application of Proposition \ref{prop:AC_chamber}.
+
+\begin{lemma}
+\label{l:equalWhittaker}
+Suppose $\pi=\pi(\lambda),\pi'=\pi(\lambda')$ are large discrete series
+representations. Then $\Wh(\pi)=\Wh(\pi')$ if and only if
+$\lambda,\lambda'$ are in the same Weyl chamber (up to the action of
+$W_K$).
+\end{lemma}
+
+\begin{proof}
+If $\lambda,\lambda'$ are in the same Weyl chamber the $\Wh(\pi)=\WF(\pi')$ by Lemma \ref{lem:Kost_and_AC}.
+
+For the other direction, by Theorem \ref{th:main} we can replace
+$\Wh(\pi)$ in the statement with $\WF(\pi)$.  So suppose
+$\WF(\pi)=\WF(\pi')$. By Lemma \ref{lem:Kost_and_AC} we may assume
+$\lambda=w\lambda'$ for some $w\in W$, i.e. $\pi,\pi'$ are contained
+in the same $L$-packet $\Pi$. By Theorem \ref{th:main} 
+we know $\Wh(\pi)=\Wh(\pi')$ if and only if $\pi\simeq \pi'$.
+This holds if and only if $\lambda'=w\lambda$ with $w\in W_K$, 
+i.e. $\mathcal C(\lambda)$ are $\mathcal C(\lambda')$ are $W_K$-conjugate.
+\end{proof}
+\begin{comment}
 \subsection{Bonus}
@@
 $$
-
+\end{comment}
 \subsection{Appendix: $SL(2,\R)$ calculation}

### 2024-06-12 whittaker.tex
Merging with some of my changes

@@
 and by \cite[Lemma 14.14]{abv} a  large discrete series representation admits a unique Whittaker datum.
+
 For (b) see \cite[Proposition A.9]{AV1}.
 
-Part~(c) follows from~\cite{rossmann_limit_orbits}.
-Update May 1: it seems the right place is Lemma B, and to go from that to the statement is a matter of chasing definitions and using the asymptotic cone.
-\textcolor{blue}{Update May 29: by Lemma B in~\cite{rossmann_limit_orbits}, if $\mathfrak{h}^+$ is the large Weyl chamber containing the HC parameter of~$\pi$, then $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ is a single orbit---where $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ is defined in Rossmann's paper.
-What we have to check is that the closure of this $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains $\WF(\pi)$.
-Now, I think that  the equivalence between conditions  (L1) and (L2) on page 2 of~\cite{rossmann_limit_orbits} easily implies that the closure of $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains the asymptotic cone of the orbit of the HC parameter, so the claim seems to follow from the relationship between $\WF(\pi)$ and the asymptotic cone (Lemma~\ref{lem:WF_and_AC}).}
+Part~(c) follows from~\cite[Lemma B]{rossmann_limit_orbits}.
+Let us briefly explain how to go from there to  assertion~(c), using standard facts on the asymptotic cone recalled below in Section~\ref{sec:asymp_cone} below.
+
+Let~$\mathfrak{h}^+$ be a Weyl chamber in~$\mathfrak{h}$ containing a representative for the Harish-Chandra parameter of~$\pi$.
+Write $\lim_{x \to 0(\mathfrak{h}^+)} G(\R)\cdot x$ for the set of all elements $y \in \g$ such that every $G$-invariant neighborhood of~$y$ contains all elements of~$\mathfrak{h}^+$ sufficiently close to zero.
+By Lemma B in~\cite{rossmann_limit_orbits}, if $\mathfrak{h}^+$ is a large Weyl chamber, then $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ is a single $G$-orbit.
+Since this does happen when~$\pi$ is a generic discrete series representation, to prove assertion~(c)  it is enough to check the closure of $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains $\WF(\pi)$ in that case.
+Now, the equivalence between conditions  (L1) and (L2) on page 2 of~\cite{rossmann_limit_orbits} immediately imply that the closure of $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains the asymptotic cone of the orbit of the Harish-Chandra parameter (see  Section~\ref{sec:asymp_cone} below).
+Therefore assertion~(c) follows from the fact that this asymptotic cone is equal to  $\WF(\pi)$  (Lemma~\ref{lem:WF_and_AC} below).
 
@@
 
-\subsection{Large discrete series to real orbits ((1) $\leftrightarrow$ (4))}
+\subsection{Large discrete series to real orbits ((1) $\leftrightarrow$ (4))}\label{sec:asymp_cone}
 

### 2024-06-12 whittaker.tex
Small update merging our recent changes

@@
 Define $\N^*\subset \g^*$ to be the set of elements whose orbit is a cone.
-We identify $\g$ and $\g^*$ using  a non-degenerate invariant form on $\g$.
+We identify $\g$ and $\g^*$ using  a non-degenerate invariant bilinear form on $\g$. Given an element~$X$ in $\g$ we sometimes write $X^\ast$ for the corresponding element of~$\g^\ast$.
+
 This restricts to an isomorphism $\N\simeq \N^*$. Although this isomorphism depends on the choice of form,
@@
 
-We define $\O_p$ to be the principal nilpotent orbit in $\N^*$: this is the unique orbit such that $\overline{\O_p}=\N^*$.
+We define $\O_p$ to be the \emph{principal nilpotent orbit} in $\N^*$: this is the unique orbit whose closure is  $\N^*$.
 
@@
 \subsubsection*{Representations} 
-
 We need to pass back and forth between representations of $G(\R)$ and $(\g,K)$-modules.
@@
 $(\g,K)$-module is on the space of $K$-finite vectors in
-$V$. Conversely if $\pi$ is an irreducible $(\g,K)$-module it can be
+$V$; we will denote it by~$\pi_K$ in this paper.
+
+Conversely if $\pi$ is an irreducible $(\g,K)$-module it can be
 realized as the $K$-finite vectors of a Hilbert space representation, which we
@@
 
-\footnote{(AA 2024-V-1) Todo: add notation $\pi_K$ and quickly discuss notions of equivalence?}
+The notion of equivalence of $(\g, K)$-modules is defined in such a way that two equivalent $(\g, K)$-modules have equivalent Hilbert space globalizations, and that any two equivalent admissible representations of~$G$ have equivalent underlying $(\g, K)$-modules.
 
@@
 
-The associated variety of $\pi$, denoted $\AV(\pi)$, is a closed, $K$-invariant set in $\s^*$, so it is a finite union of
+The associated variety of $\pi$, denoted $\AV(\pi)$, is a closed, $K$-invariant set in~$\s^*$; so it is a finite union of
 nilpotent $K$-orbits on $\s^*$. See \cite[Section 5]{vogan_bowdoin}.
@@
 
+\subsection{Large representations} Set $N=\dim(G)-\mathrm{rank}(G)$. This is the dimension of the nilpotent cone~$\N$. The maximal Gelfand--Kirillov dimension of a representation is $N/2$.
+We say $\pi$ is {\it large} if $\GK(\pi)=N/2$. See \cite[Section~6]{vogan-gelfand-kirillov}.
+
+\begin{lemma}
+  \label{l:large}
+  The following conditions are equivalent.
+  \begin{enumerate}
+    \item $\pi$ is large;
+\item $\AVann(\pi)=\N^*=\overline{\Op}$;
+\item $\dim(\AVann(\pi))=N$;
+  \item $\dim(\AV(\pi))=N/2$;
+  \item $\GK(\pi)=N/2$;
+    \item $\pi$ is generic.
+
+\end{enumerate}
+\end{lemma}
+See \cite{vogan_bowdoin}, in particular Corollary 4.7 and Theorem 8.4.
+
+\subsection{Discrete series and Harish-Chandra parameters}
+
+Recall $G(\R)$ has relative discrete series representations if and only if it has a relatively compact Cartan subgroup.
+From now on, we assume $G(\R)$ does have discrete series representation, and fix a compact Cartan subgroup $H(\R)$ of~$G(\R)$, with complexified Lie algebra~$\mathfrak{h} \subset \g$.
+
+With this choice, any discrete series representation of~$G(\R)$ has a \emph{Harish-Chandra parameter}. Etc etc.
+\begin{itemize}
+\item Harish-Chandra parameter, $W$ and $W_K$
+\item Notion of large Weyl chamber 
+\end{itemize}
+
 \subsection{The invariants for generic discrete series}
@@
 Part~(c) follows from~\cite[Lemma B]{rossmann_limit_orbits}.
-Let us briefly explain how to go from there to  assertion~(c), using standard facts on the asymptotic cone recalled below in Section~\ref{sec:asymp_cone} below.
+Let us explain how to go from there to  assertion~(c), using standard facts on the asymptotic cone recalled below (\S\,{}\ref{sec:asymp_cone}).
 
@@
 Similarly we write $\WF(\pi)=\O$ to indicate that $\WF(\pi)$ is the closure of the $G(\R)$-orbit $\O\subset i\g(\R)^*$.
-
-\subsection{Large representations} Set $N=\dim(G)-\mathrm{rank}(G)$. This is the dimension of the nilpotent cone~$\N$. The maximal Gelfand--Kirillov dimension of a representation is $N/2$.
-We say $\pi$ is {\it large} if $\GK(\pi)=N/2$. See \cite[Section~6]{vogan-gelfand-kirillov}.
-
-\begin{lemma}
-  \label{l:large}
-  The following conditions are equivalent.
-  \begin{enumerate}
-    \item $\pi$ is large;
-\item $\AVann(\pi)=\N^*=\overline{\Op}$;
-\item $\dim(\AVann(\pi))=N$;
-  \item $\dim(\AV(\pi))=N/2$;
-  \item $\GK(\pi)=N/2$;
-    \item $\pi$ is generic.
-
-\end{enumerate}
-\end{lemma}
-See \cite{vogan_bowdoin}, in particular Corollary 4.7 and Theorem 8.4.
 
@@
 \end{enumerate}
-In particular if $\pi$ is a large discrete series represenation then each of these three invariants of $\pi$ determines the other $2$. 
+In particular if $\pi$ is a large discrete series representation then each of these three invariants of $\pi$ determines the other two. 
 \end{theorem}
@@
 
-Then $F_\pi\in\s$ is a regular nilpotent element. Let $\xi_\pi\in \N^*$ be the corresponding element (cf. Section \ref{s:nilpotentorbits}).
+Then $F_\pi\in\s$ is a regular nilpotent element. Let $F_\pi^\ast\in \N^*$ be the corresponding element (cf. Section \ref{s:nilpotentorbits}).
 Then 
 $$
-\AV(\pi)=\overline{K\cdot \xi_\pi}.
+\AV(\pi)=\overline{K\cdot F_\pi^\ast}.
 $$

### 2024-06-12 whittaker.tex
Tinkering

@@
 
-This restricts to an isomorphism $\N\simeq \N^*$. Although this isomorphism depends on the choice of form,
-the bijection on the level of $G$-orbits is canonical.
+The identification $\g \simeq \g^\ast$ restricts to a bijection $\N\simeq \N^*$. Although this correspondence depends on the choice of form,
+the induced bijection on the level of $G$-orbits is canonical.
 
@@
 
-In the $\theta$-picture we have an analogous construction. We may assume the form is orthogonal with respect to $\theta$.
-Consequently the decomposition $\g=\mathfrak k+\s$ also gives $\g^*=\mathfrak k^*\oplus \s^*$, and this induces
+We may assume the chosen bilinear form on~$\g$ is $\theta$-invariant.
+In this case the identification between $\g=\mathfrak k+\s$ and $\g^*=\mathfrak k^*\oplus \s^*$ determines a $K$-equivariant  (but non-canonical) isomorphism between $\s$ and $\s^\ast$.
+This induces
 a canonical bijection between $K$-orbits on $\s$ and on $\s^*$.
@@
 Suppose $\pi$ is an irreducible $(\g,K)$-module.
-Let $I_\pi$ be the annihlator of $\pi$ in the universal enveloping algebra.
-Let $\AVann(\pi)\subset\N^*\subset \g^*$ be the associated variety of $I_\pi$.
-This is the closure of a single complex nilpotent orbit $\O$
-See \cite[Section 1, Theorem 4.7]{vogan_bowdoin}.
 
 The associated variety of $\pi$, denoted $\AV(\pi)$, is a closed, $K$-invariant set in~$\s^*$; so it is a finite union of
-nilpotent $K$-orbits on $\s^*$. See \cite[Section 5]{vogan_bowdoin}.
+nilpotent $K$-orbits on $\s^*$. For the definition, and many properties, see \cite[Section 5]{vogan_bowdoin}.
+
+A slightly different invariant is the associated variety of the annihilator. Let $I_\pi$ be the annihlator of $\pi$ in the universal enveloping algebra.
+Let $\AVann(\pi)\subset\N^*\subset \g^*$ be the associated variety of $I_\pi$.
+This is the closure of a single complex nilpotent orbit $\O$.
+See \cite[Section 1, Theorem 4.7]{vogan_bowdoin}.
 
@@
 
-We define the associated variety of a Hilbert space representations to be that of  its underlying $(\g,K)$-module.
+We define the associated variety of a Hilbert space representation to be that of  its underlying $(\g,K)$-module.
 

### 2024-06-14 whittaker.tex
Adding some stars and checking the Sekiguchi formulas

@@
 Since this does happen when~$\pi$ is a generic discrete series representation, to prove assertion~(c)  it is enough to check the closure of $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains $\WF(\pi)$ in that case.
-Now, the equivalence between conditions  (L1) and (L2) on page 2 of~\cite{rossmann_limit_orbits} immediately imply that the closure of $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains the asymptotic cone of the orbit of the Harish-Chandra parameter (see  Section~\ref{sec:asymp_cone} below).
+Now, the equivalence between conditions  (L1) and (L2) on page 2 of~\cite{rossmann_limit_orbits} implies that the closure of $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains the asymptotic cone of the orbit of the Harish-Chandra parameter (see  Section~\ref{sec:asymp_cone} below).
 Therefore assertion~(c) follows from the fact that this asymptotic cone is equal to  $\WF(\pi)$  (Lemma~\ref{lem:WF_and_AC} below).
@@
 We recall a recent result of the first author and Tasho Kaletha, which spells out the connection between large discrete series and Whittaker data using  {\it Kostant sections}.
-Let~$X$ be a regular nilpotent element of~$\g$, and choose an  $\SL(2)$-triple $(X, H, Y)$.
+Let~$X$ be a regular nilpotent element of~$\g$, and choose elements $H, Y \in \g$ such that $(X,H,Y)$ is an  $\SL(2)$-triple.
 The Kostant section~$\Kostant{X}$ is the affine subspace $X + \mathrm{Cent}_{\g}(Y)$ of~$\g$.
-This depends on the choice of $\SL(2)$-triple, but if $X \in \g(\R)^*$, then the $G(\R)$-conjugacy class of~$\Kostant{X}$ depends only on the $G(\R)$-conjugacy class of~$X$.
+This depends on the choice of $\SL(2)$-triple, but if $X \in \g(\R)$, then the $G(\R)$-conjugacy class of~$\Kostant{X}$ depends only on the $G(\R)$-conjugacy class of~$X$.
 
@@
 \subsubsection{The Sekiguchi correspondence for principal nilpotent orbits}\label{sec:concrete_sek}
-\footnote{JA These formulas should be right now, see the Appendix}
 Let us spell out the special case of the Sekiguchi correspondence which is of interest here. We follow~\cite[Section~2]{AVAV}.
 
-{\bf Note:} Need some $*$'s here.
-
-Suppose $F_\R\in \Op\cap i\g(\R)$. Then we may choose an $SL(2)$-triple $(H_\R,E_\R,F_\R)$ with $E_\R$  contained in $i\g(\R)$,
+Suppose $\xi_\R\in \Op\cap i\g(\R)^\ast$, and write $\xi_\R = F_\R^\ast$ where $F_\R$ is a principal nilpotent element.
+We may choose $H_\R, E_\R \in \g$ such that $(H_\R,E_\R,F_\R)$ is an $\mathrm{SL}(2)$-triple and  $E_\R$  contained in $i\g(\R)$,
 which implies $H_\R\in \g(\R)$. 
-After conjugating by~$G(\R)$ we may further assume $\theta(E_\R)=-F_\R$.
-The Sekiguchi correspondence takes the $G(\R)$-orbit of~$E_\R$ to the $K$-orbit of
-$$
-F_\theta=\frac12(-E_\R+F_\R+H_\R)\in \N\cap \s.
-$$
+After conjugating by~$G(\R)$ we may further assume $\theta(E_\R)=-F_\R$. Set 
+\[   F_\theta=\frac12(-E_\R+F_\R+H_\R).\]
+Then the Sekiguchi correspondence takes the $G(\R)$-orbit of~$\xi_\R$ to the $K$-orbit of $\xi_\theta=F_\theta^\ast$.
 
 Computing the map in the other direction goes as follows.
-Suppose $F_\theta\in \Op\cap\s$. Choose an $SL(2)$-triple  $(E_\theta, H_\theta,F_\theta)$ with
-$E_\theta\in\s$, which implies $H_\theta\in\k$. After conjugating by $K$ we may further assume $\sigma(E_\theta)=F_\theta$.
-Then the Sekiguchi correspondence takes the $K$-orbit of $E_\theta$ to the $G(\R)$-orbit of 
+Suppose $\xi_\theta \in \Op\cap \s^\ast$, and let $F_\theta \in \s$ be such that $\xi_\theta=F_\theta^\ast$.
+Choose $E_\theta, H_\theta \in \g$ such that $(E_\theta, H_\theta, F_\theta)$ is an $SL(2)$-triple with $E_\theta \in \s$,  which implies $H_\theta\in\k$.
+After conjugating by $K$ we may further assume $\sigma(E_\theta)=F_\theta$.
+Define 
 \begin{equation}\label{def_F_R}
-F_\R=\frac 12(-E_\theta+F_\theta-H_\theta)\in\N\cap i\g(\R).
+  F_\R=\frac12(-E_\theta+F_\theta-H_\theta)\\
 \end{equation}
+Then the Sekiguchi correspondence takes the $K$-orbit of $\xi_\theta$ to the $G(\R)$-orbit of $\xi_\R = F_\R^\ast$.
 
@@
 
-Consider the principal nilpotent element~$F_\pi$ defined in~\eqref{e:Fpi}. We define another regular nilpotent element  $F_\R$ using 
-\eqref{def_F_R} using $F_\theta=F_\pi$ on the right hand side. 
+Consider the principal nilpotent element~$F_\pi$ defined in~\eqref{e:Fpi}.
+Let us use this as~$F_\theta$ in the previous subsection: define $E_\theta = \sum_{\alpha \in S(\lambda)}X_\alpha$ and $H_\theta  = [E_\theta, F_\theta]$; then $E_\theta \in \s$ and $(E_\theta, H_\theta, F_\theta)$ is an $\mathrm{SL}(2)$-triple.
+Define another $\mathrm{SL}(2)$-triple $(E_\R, F_\R, H_\R)$ by
+\[ \begin{aligned}
+  F_\R&=\frac12(-E_\theta+F_\theta-H_\theta)\\
+  E_\R&=\frac12(E_\theta-F_\theta-H_\theta)\\
+  H_\R&=E_\theta+F_\theta.
+\end{aligned}\]
+
 We know that  $\AV(\pi)=K \cdot \xi_\pi$ (where $\xi_\pi\in\g^*$ corresponds to $F_\pi$, see Lemma~\ref{l:pi_to_av}), so the image of $\AV(\pi)$ by the Sekiguchi correspondence is 
- $G(\R)\cdot F_\R$. We want to check that $\WF(\pi)$
+ $G(\R)\cdot F_\R$. We want to check that this is equal to $\WF(\pi)$.
 
@@
 
-Now, we know that $\Kostant{F_\R}=F_\R+\mathrm{Cent}_\g(F_\R)$ contains $F_\R-F_\R = H_\theta$\footnote{AA 2024-IV-15: insert the correct version once we've checked the Sekiguchi formulas in the previous paragraph.
-}.
-In general the orbits $\mathcal{O}_\pi$ and $G(\R) \cdot H_\theta$ are disjoint. 
-Nevertheless $H_{\lambda}$ and $H_\theta=[F_\theta, F_\theta]$ are in the same Weyl chamber\footnote{AA 2024-IV-15: should probably explain a bit more why this is correct.}.
+Now, we know that $\Kostant{F_\R}=F_\R+\mathrm{Cent}_\g(E_\R)$ contains $F_\R+E_\R = -H_\theta$.
+In general the orbits $\mathcal{O}_\pi$ and $G(\R) \cdot (-H_\theta)$ are disjoint. 
+Nevertheless $H_{\lambda}$ and $-H_\theta=[F_\theta, E_\theta] = \sum_{\alpha \in S(\lambda)} [X_{-\alpha,} X_\alpha]H_\alpha$ are in the same Weyl chamber. 
 Therefore the result follows from:
@@
 $$
-These satisfy the standard $SL(2)$ commutation relations, and $E_\R,F_\R$ are in the $-1$-eigenspace of $\sigma$,
-and $\theta(E_\R)=F_\R, \theta(H_\R)=-H_\R$.
+These satisfy the standard $SL(2)$ commutation relations: 
+\[ [E_\R, F_\R] = H_\R, \quad [H_\R, E_\R] = 2E_\R, \quad [H_\R, F_\R] = -2F_\R. \]
+
+Furthermore $E_\R,F_\R$ are in the $-1$-eigenspace of $\sigma$,
+and  we have $\theta(E_\R)=F_\R$ and $\theta(H_\R)=-H_\R$.
 
 Set $g=\frac 1{\sqrt 2}\begin{pmatrix}1&i\\i&1
-\end{pmatrix}$, and take $E_\theta,F_\theta,H_\theta$ be the conjugates of $E_\R,F_\R,H_\R$ by $g$:
+\end{pmatrix}$, and take $E_\theta,F_\theta,H_\theta$ be the conjugates of $E_\R,F_\R,H_\R$ by~$g$:
 $$

### 2024-06-14 whittaker.tex
Further small changes

@@
 Choose a compact Cartan subgroup $T$ and let $\lambda\in \t^*$ be the Harish-Chandra parameter of $\pi$.
-Define $F_\theta=F_\pi$ as in \eqref{e:Fpi}, and choose an $SL(2)$-triple $(H_\theta,E_\theta,F_\theta)$ as usual.
-After conjugating by $K$ we may assume $\sigma(E_\theta)=F_\theta$.  Then\footnote{AA 14-II-2023: no closure?}
+Define $F_\theta=F_\pi$ as in \eqref{e:Fpi}, and choose  $E_\theta$, $H_\theta$ such that $(H_\theta,E_\theta,F_\theta)$ is an $\mathrm{SL}(2)$-triple with $\sigma(E_\theta)=F_\theta$.  Then
 $$
-\WF(\pi)=G(\R)\cdot\frac i2(E_\theta-F_\theta-H_\theta)\in\N\cap i\g(\R)
-$$
-Conversely if $E_\R\in \Op\cap i\g(\R)$, choose an $SL(2)$-triple $(H_\R,E_\R,F_\R)$ which (after conjugating by $G(\R)$) satisfies $\theta(E_\R)=-F_\R$.
+\WF(\pi)=G(\R)\cdot F_\R^\ast, \quad \text{where $F_\R = \frac i2(-E_\theta+F_\theta-H_\theta)\in\N\cap i\g(\R)$.}
+$$\end{lemma}
+Conversely, assume we are given an $L$-packet~$\Pi$ of generic discrete series, and consider a regular semisimple orbit~$\Omega$ in~$\Op \cap i\g(\R)^\ast$.
+We can determine the unique element~$\pi \in \Pi$ with $\WF(\pi)=\Omega$ as follows.
+Fix~$\xi_\R \in \Omega$, write $\xi_\R=F_\R^\ast$ with $F_\R \in \g$ and let $E_\R, H_\R \in \g$ be such that $(E_\R, H_\R, F_\R$ is an  $\mathrm{SL}(2)$-triple with $\theta(E_\R)=-F_\R$.
+Set
 Let
@@
 $$
-Then $H_\theta\in\k$ is a regular semisimple element.
-Set $\t=\Cent_{\g}(H_\theta)$, and let
+Then $H_\theta$ is a regular semisimple element, and belongs to~$\k$.
+Define a Cartan subalgebra~$\t$ of~$\g$ by $\t=\Cent_{\g}(H_\theta)$, and a set of positive roots by
 $$
-\Delta^+=\{\alpha\in\Delta(T,G)\mid  \alpha(H_\theta)>0\}
+\Delta^+=\{\alpha\in\Delta(\t,\g)\mid  \alpha(H_\theta)>0\}.
 $$
 Then $\pi$ is the discrete series representation in $\Pi$ whose Harish-Chandra parameter is dominant for $\Delta^+$.
-\end{lemma}
 
-Here is another application of Proposition \ref{prop:AC_chamber}.
+\subsection{Application: Whittaker model and Weyl chamber of the Harish-Chandra parameter}
+
+As an application of the above results, here is a simple proof of a result which is well known to the experts, but not easy to locate in the literature.
 
@@
 \begin{proof}
-If $\lambda,\lambda'$ are in the same Weyl chamber the $\Wh(\pi)=\WF(\pi')$ by Lemma \ref{lem:Kost_and_AC}.
+If $\lambda,\lambda'$ are in the same Weyl chamber the $\Wh(\pi)=\WF(\pi')$ by Lemma~\ref{lem:Kost_and_AC}.
 

### 2024-06-14 whittaker.tex
A small change in the proof of Lemma 21

@@
 Recall $G(\R)$ has relative discrete series representations if and only if it has a relatively compact Cartan subgroup.
-From now on, we assume $G(\R)$ does have discrete series representation, and fix a compact Cartan subgroup $H(\R)$ of~$G(\R)$, with complexified Lie algebra~$\mathfrak{h} \subset \g$.
+From now on, we assume $G(\R)$ does have discrete series representation; fix a compact Cartan subgroup $T(\R)$ of~$G(\R)$, and let~$\mathfrak{t} \subset \g$ be the corresponding Cartan subalgebra of~$\g$ (the complexified Lie algebra of~$T(\R)$).
 
@@
 \begin{itemize}
-\item Harish-Chandra parameter, $W$ and $W_K$
+\item Harish-Chandra parameter, notation $\pi(\lambda)$, discussion of $W$ and $W_K$
 \item Notion of large Weyl chamber 
@@
 Suppose $\Kostant{X}$ meets $\mathcal O$.
-This means there is an $SL(2)$-triple $(H,Y,X)$, and $Z\in \Cent(Y)$ such that $X+Z\in \O$. 
-By the representation theory of $SL(2)$ we know that $Z=\sum_{j=0}^n Z_j$ with $[H,Z_j]=-jZ_j$. 
-Then 
-$$
-\Ad(e^{tH})(X+Z)=e^{2t}(X) + \sum_j e^{-tj}Z_j
-$$
-Taking the limit as $t\rightarrow 0$ gives $\Ad(e^{tH})(X+Z)\rightarrow e^{2t}X$. Therefore
-$$
-\lim_{t\rightarrow 0}e^{-2t}\Ad(e^{tH})(X+Z)=X
-$$ which implies the result.
+This means there is an $SL(2)$-triple $(X,H,Y)$, and an element $Z\in \Cent_\g(Y)$ such that $W=X+Z \in \O$. 
+By \cite{Kostant59}, the centralizer  $\mathrm{Cent}_{\g}(Y)$ is abelian; furthermore there exists a Cartan subalgebra $\mathfrak{h} \subset \g$, and a positive system $\Delta$ for the roots of $\mathfrak{h}$ in $\g$, such that $E$ is contained in the sum of $\Delta$-positive root spaces, while $\mathrm{Cent}_{\g}(F)$ is contained in the sum of $\Delta$-negative roots.
+Therefore, if we set $h(t) = \exp(tH)$ for $t \in \R_+$, then
+\[\begin{cases} \mathrm{Ad}(h(t)) \cdot F \longrightarrow 0 & \text{as $t \to +\infty$, while} \\
+ \mathrm{Ad}(h(t)) \cdot E = f(t) E & \text{ with $f(t) >0$ and $f(t)\to +\infty$ as $t \to \infty$.}\end{cases}\]
+Set $Y(t) = \mathrm{Ad}(h(t)) Y$; then $f(t) \left[ E + Y(t) \right] = \mathrm{Ad}(h(t)) W$ lies on the orbit~$\mathcal{O}$.
+Thus there exists a continuous path in $\R^+ \cdot \mathcal{O}$ with $E=X$ as a limit point; by definition this means $X \in \AC(\mathcal{O})$.%By the representation theory of $SL(2)$ we know that $Z=\sum_{j=0}^n Z_j$ with $[H,Z_j]=-jZ_j$.
+%Then 
+%$$
+%\Ad(e^{tH})(X+Z)=e^{2t}(X) + \sum_j e^{-tj}Z_j
+%$$
+%Taking the limit as $t\rightarrow 0$ gives $\Ad(e^{tH})(X+Z)\rightarrow e^{2t}X$. Therefore
+%$$
+%\lim_{t\rightarrow 0}e^{-2t}\Ad(e^{tH})(X+Z)=X
+%$$ which implies the result.
 \end{proof}

### 2024-06-14 whittaker.tex
First draft of small section on DS and HC parameters

@@
 
-\subsection{Discrete series and Harish-Chandra parameters}
+\subsection{Discrete series and Harish-Chandra parameters} \label{sec:discrete_series}
 
-Recall $G(\R)$ has relative discrete series representations if and only if it has a relatively compact Cartan subgroup.
-From now on, we assume $G(\R)$ does have discrete series representation; fix a compact Cartan subgroup $T(\R)$ of~$G(\R)$, and let~$\mathfrak{t} \subset \g$ be the corresponding Cartan subalgebra of~$\g$ (the complexified Lie algebra of~$T(\R)$).
+Recall $G(\R)$ has relative discrete series representations if and only if it has a relatively compact Cartan subgroup, i.e.
+there exists a $\theta$-stable Cartan subgroup~$T$ of~$G$  such that~$T(\R) \cap G_d$ is  compact, where $G_d$ is the derived group of~$G$.
+From now on, we assume $G(\R)$ does have discrete series representation: we fix  a Cartan subgroup $T \subset G$ satisfying the conditions above, and let~$\mathfrak{t}$ denote the Lie algebra of~$T$, which is a Cartan subalgebra of~$\g$.
 
-With this choice, any discrete series representation of~$G(\R)$ has a \emph{Harish-Chandra parameter}. Etc etc.
-\begin{itemize}
-\item Harish-Chandra parameter, notation $\pi(\lambda)$, discussion of $W$ and $W_K$
-\item Notion of large Weyl chamber 
-\end{itemize}
+Choose a  positive system~$\Delta^+$  for the roots of~$\t$ in~$\g$, and let~$\rho \in \mathfrak{t}^\ast$ be the half-sum of positive roots.
+Let~$\Lambda \subset \mathfrak{t}^\ast$ be the set of elements~$\lambda \in \mathfrak{t}^\ast$ which are \emph{regular} (i.e.
+the linear form $\lambda$ does not vanish on any coroot) and such that $\lambda-\rho$  is the differential of a character of~$T(\R)$.
+The action of the Weyl group~$W=W(\g, \t)$ preserves~$\Lambda$.
+Let~$W_K\subset W$ be the subgroup $\mathrm{Norm}_K(T)/T$.
+
+Then any discrete series representation of~$G(\R)$ has a \emph{Harish-Chandra parameter}, which is an element of~$\Lambda/W_K$.\footnote{AA 2024-VI-14: perhaps we should add that if $\pi$ is a discrete series representation, then the Harish-Chandra parameter and the central character are enough to specify~$\pi$ completely, and refer to \cite[Section 8]{AV1} and \cite{Contragredient} for full details on the parametrization.
+}
+
+Recall that the \emph{Weyl chambers} of~$\mathfrak{t}^\ast$ are the connected components of the set of regular elements.
+Each Weyl chamber specifies a positive root system for the roots of $\mathfrak{t}$ in~$\g$, and we say a Weyl chamber is \emph{large} if the corresponding simple roots are all noncompact.
+
+If~$\lambda \in \mathfrak{t}^\ast$ is a representative for the Harish-Chandra parameter of a discrete series representation $\pi$, then~$\pi$ is generic if and only if the Weyl chamber containing~$\lambda$ is large.
+See~\cite[Section 6]{vogan-gelfand-kirillov}.
 
@@
 
-Let~$\mathfrak{h}^+$ be a Weyl chamber in~$\mathfrak{h}$ containing a representative for the Harish-Chandra parameter of~$\pi$.
-Write $\lim_{x \to 0(\mathfrak{h}^+)} G(\R)\cdot x$ for the set of all elements $y \in \g$ such that every $G$-invariant neighborhood of~$y$ contains all elements of~$\mathfrak{h}^+$ sufficiently close to zero.
-By Lemma B in~\cite{rossmann_limit_orbits}, if $\mathfrak{h}^+$ is a large Weyl chamber, then $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ is a single $G$-orbit.
-Since this does happen when~$\pi$ is a generic discrete series representation, to prove assertion~(c)  it is enough to check the closure of $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains $\WF(\pi)$ in that case.
-Now, the equivalence between conditions  (L1) and (L2) on page 2 of~\cite{rossmann_limit_orbits} implies that the closure of $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains the asymptotic cone of the orbit of the Harish-Chandra parameter (see  Section~\ref{sec:asymp_cone} below).
+Let~$\mathfrak{t}^+$ be a Weyl chamber in~$\mathfrak{t}$ containing a representative for the Harish-Chandra parameter of~$\pi$.
+Write $\lim_{x \to 0(\mathfrak{t}^+)} G(\R)\cdot x$ for the set of all elements $y \in \g$ such that every $G$-invariant neighborhood of~$y$ contains all elements of~$\mathfrak{t}^+$ sufficiently close to zero.
+By Lemma B in~\cite{rossmann_limit_orbits}, if $\mathfrak{t}^+$ is a large Weyl chamber, then $\lim_{x \to 0(\mathfrak{t}^+)} G\cdot x$ is a single $G$-orbit.
+Since this does happen when~$\pi$ is a generic discrete series representation, to prove assertion~(c)  it is enough to check the closure of $\lim_{x \to 0(\mathfrak{t}^+)} G\cdot x$ contains $\WF(\pi)$ in that case.
+Now, the equivalence between conditions  (L1) and (L2) on page 2 of~\cite{rossmann_limit_orbits} implies that the closure of $\lim_{x \to 0(\mathfrak{t}^+)} G\cdot x$ contains the asymptotic cone of the orbit of the Harish-Chandra parameter (see  Section~\ref{sec:asymp_cone} below).
 Therefore assertion~(c) follows from the fact that this asymptotic cone is equal to  $\WF(\pi)$  (Lemma~\ref{lem:WF_and_AC} below).
@@
 
-Suppose $\pi$ is a  discrete series representation. Choose a compact Cartan subgroup $T$, and let
-$\lambda\in\t^*$ be the Harish-Chandra parameter of $\pi$. Let $\Delta$ be the set of roots of $\t$ in $\g$, 
+Suppose $\pi$ is a  discrete series representation. Let
+$\lambda\in\t^*$ be a representative for the Harish-Chandra parameter of $\pi$ (Section~\ref{sec:discrete_series}). Let $\Delta$ be the set of roots of $\t$ in $\g$, 
 let $\Delta^+(\lambda)=\{\alpha\mid \langle\lambda,\ch\alpha\rangle>0\}$,

### 2024-06-14 whittaker.tex
Small tinkering and update to homework

@@
 
-Suppose $\pi$ is a discrete series representation.
-Choose a compact Cartan subgroup $T$, and let $\lambda\in\t^*$ be the Harish-Chandra parameter of $\pi$.
-Define
+Suppose $\pi$ is a discrete series representation. Let $\lambda\in\t^*$ be a representative of the Harish-Chandra parameter of $\pi$.
+Define\footnote{AA 2024-VI-14: should perhaps decide if we fix a large chamber from the start and take the HC parameter to live there, or at least be careful about consistency in notation...}
 \begin{equation} \label{semisimple_orbit_HC} \mathcal{O}_{\pi}=G(\R)\cdot\lambda.\end{equation}

### 2024-06-15 whittaker.tex
Polishing the application to Whittaker models and Weyl chambers

@@
 
-As an application of the above results, here is a simple proof of a result which is well known to the experts, but not easy to locate in the literature.
+As an application of the above results, here is a simple proof of a fact which is well known to the experts, but not easy to locate in the literature.
 
@@
 \label{l:equalWhittaker}
-Suppose $\pi=\pi(\lambda),\pi'=\pi(\lambda')$ are large discrete series
-representations. Then $\Wh(\pi)=\Wh(\pi')$ if and only if
-$\lambda,\lambda'$ are in the same Weyl chamber (up to the action of
-$W_K$).
+Suppose $\pi$, $\pi'$ are large discrete series representations of~$G(\R)$.
+Let~$\lambda, \lambda'$ be representatives for the Harish-Chandra parameters of~$\pi, \pi'$ respectively, and let $\mathscr{C}, \mathscr{C}'$ be the corresponding Weyl chambers.
+
+Then $\Wh(\pi)=\Wh(\pi')$ if and only if $\mathscr{C}, \mathscr{C}'$ are in the same $W_K$-orbit. 
 \end{lemma}
@@
 \begin{proof}
-If $\lambda,\lambda'$ are in the same Weyl chamber the $\Wh(\pi)=\WF(\pi')$ by Lemma~\ref{lem:Kost_and_AC}.
+If  $\mathscr{C}, \mathscr{C}'$ are in the same $W_K$-orbit, then the Harish-Chandra parameters of $\pi$, $\pi'$ have representatives in the same Weyl chamber; therefore $\Wh(\pi)=\Wh(\pi')$ by Lemma~\ref{lem:Kost_and_AC}.
 
@@
 $\lambda=w\lambda'$ for some $w\in W$, i.e. $\pi,\pi'$ are contained
-in the same $L$-packet $\Pi$. By Theorem \ref{th:main} 
+in the same $L$-packet $\Pi$. In that case, by Theorem \ref{th:main} 
 we know $\Wh(\pi)=\Wh(\pi')$ if and only if $\pi\simeq \pi'$.
 This holds if and only if $\lambda'=w\lambda$ with $w\in W_K$, 
-i.e. $\mathcal C(\lambda)$ are $\mathcal C(\lambda')$ are $W_K$-conjugate.
+i.e. $\mathscr{C}$ and $\mathscr{C}'$ are $W_K$-conjugate.
 \end{proof}
-\begin{comment}
-\subsection{Bonus}
 
-This section uses the arguments above to deduce the ``folklore fact'' stated by  Jeff and Tasho with a reference to the present paper for the proof.
-\footnote{AA 2024-VI-7: I don't remember whether this was the most up-to-date version  of our understanding; I seem to remember that we wanted to know that $Q$ acts simply transitively on the large Weyl chambers, and I haven't thought yet about what the relationship this has with what is written below...}
-
-We want to know that if $\pi_1=\pi(\lambda_1),\pi_2=\pi(\lambda_2)$ are large discrete series, then $\Wh(\pi_1)=\Wh(\pi_2)$ if and only $\lambda_1,\lambda_2$
-are in the same Weyl chamber.
-
-More precisely, $W$ and $W_K=\Norm_K(T)$ act on $T$, and $\pi(\lambda)=\pi(w\lambda)$ if and only if $\lambda\in W_K$.
-So the correct statement is: $\Wh(\pi_1)=\Wh(\pi_2)$ if and only if the Weyl chambers of $\lambda_1,\lambda_2$ are conjugate by $W_K$.
-
-One direction is easy using the above results: we have seen that if $\lambda_1,\lambda_2$
-are in the same Weyl chamber then the wavefront set, therefore the Whittaker model, are the same.
-
-What we need to show:
-$\Wh(\pi(\lambda_1))=\Wh(\pi(\lambda_2)\Rightarrow \mathcal C(\lambda_1)$ is $W_K$-conjugate to  $\mathcal C(\lambda_2)$.
-
-We may as well assume $\pi(\lambda_1),\pi(\lambda_2)$ are in the same $L$-packet, i.e.
-$\lambda_2=w\lambda_1$ for some $w\in W$.We know that $Q$ acts simply transitively on the large discrete series in the $L$-packet, and on principal nilpotent orbits.
-Also: this action is given by the action of $W$, i.e. if $g\in Q$ then $\pi(\lambda)^g=\pi(g\lambda)=\pi(w\lambda)$ for some $w\in W$.
-So
-$$
-\Wh(\pi_1)=\Wh(\pi_2)\Leftrightarrow \pi_1\simeq \pi_2\Leftrightarrow \lambda_1\sim_{W_K}\lambda_2\Leftrightarrow \mathcal C_1\sim_{W_K}\mathcal C_2
-$$
-\end{comment}
 \subsection{Appendix: $SL(2,\R)$ calculation}

### 2024-06-19 whittaker.tex
Many small edits

@@
 The notion of equivalence of $(\g, K)$-modules is defined in such a way that two equivalent $(\g, K)$-modules have equivalent Hilbert space globalizations, and that any two equivalent admissible representations of~$G$ have equivalent underlying $(\g, K)$-modules.
+Therefore if~$\pi$ refers an equivalence class of irreducible Hilbert space representations of~$G(\R)$ (as opposed to an actual representation in the equivalence class), then it makes sense to write~$\pi_K$ for the corresponding equivalence class of $(\g, K)$-modules.
 
@@
 Let $\AVann(\pi)\subset\N^*\subset \g^*$ be the associated variety of $I_\pi$.
-This is the closure of a single complex nilpotent orbit $\O$.
-See \cite[Section 1, Theorem 4.7]{vogan_bowdoin}.
+This is the closure of a single complex nilpotent orbit: see \cite[Section 1, Theorem 4.7]{vogan_bowdoin}.
 
-The Gelfand---Kirillov dimension~$\GK(\pi)$ of~$\pi$ can be defined in several different ways~\cite{vogan-gelfand-kirillov}; but one of them is
+The Gelfand--Kirillov dimension~$\GK(\pi)$ of~$\pi$ can be defined in several different ways~\cite{vogan-gelfand-kirillov}; but one of them is
 $$
@@
   set} $\WF(\pi)$ is an analytic invariant determined by the
-singularities of the global character of $\pi$ near the identity. See \cite{howe_wave_front}, \cite{bv_local_structure},
-\cite{HarrisHeOlafsson} for the definition. 
-It is a closed $G(\R)$-invariant subset of the nilpotent cone in
+singularities of the global character of $\pi$ near the identity. See \cite{howe_wave_front, bv_local_structure, HarrisHeOlafsson} for the definition. 
+The set~$\WF(\pi)$  is a closed $G(\R)$-invariant subset of the nilpotent cone in
 $i\g(\R)^*$. As such it is the union of a finite number of nilpotent $G(\R)$-orbits.
@@
 
-We consider the space $\mH^\infty$ of smooth vectors in $\mH$, and its dual $\mH^{-\infty}$. We say $\pi$ has a $(B,\eta)$-Whittaker model
-if there exists $v\in \mH^{-\infty}$ such that $\pi(n)(v)=\eta(n)v$ for all $n$ in the nilradical $N(\R)$ of $B(\R)$.
-See \cite{matumoto}.
+Suppose again that $\pi$ is an irreducible admissible representation of $G(\R)$ on a Hilbert space $\mH$.
+We consider the attached representations of~$\pi$ on the space $\mH^\infty$ of smooth vectors in $\mH$, and on its dual $\mH^{-\infty}$.
+Let~$(B, \eta)$ be a pair satisfying conditions (i)-(ii) of the Introduction.
+We say $\pi$ has a $(B,\eta)$-Whittaker model
+if there exists a nonzero element $v$ in $\mH^{-\infty}$ such that $\pi(n)(v)=\eta(n)v$ for all $n$ in the nilradical $N(\R)$ of $B(\R)$.See \cite{matumoto}.
+If~$\w$ is the corresponding Whittaker datum, i.e.
+the $G(\R)$-conjugacy class of the pair $(B, \eta)$, we say~$\pi$ has a $\w$-Whittaker model.
 
@@
 there exists a $\theta$-stable Cartan subgroup~$T$ of~$G$  such that~$T(\R) \cap G_d$ is  compact, where $G_d$ is the derived group of~$G$.
-From now on, we assume $G(\R)$ does have discrete series representation: we fix  a Cartan subgroup $T \subset G$ satisfying the conditions above, and let~$\mathfrak{t}$ denote the Lie algebra of~$T$, which is a Cartan subalgebra of~$\g$.
+Throughout the paper, we assume $G(\R)$ does have discrete series representation, we fix  a Cartan subgroup $T \subset G$ satisfying the conditions above, and we let~$\mathfrak{t}$ denote the Lie algebra of~$T$, which is a Cartan subalgebra of~$\g$.
 
@@
 Let~$\Lambda \subset \mathfrak{t}^\ast$ be the set of elements~$\lambda \in \mathfrak{t}^\ast$ which are \emph{regular} (i.e.
-the linear form $\lambda$ does not vanish on any coroot) and such that $\lambda-\rho$  is the differential of a character of~$T(\R)$.
+the linear form $\lambda$ does not vanish on any coroot), and such that $\lambda-\rho$  is the differential of a character of~$T(\R)$.
 The action of the Weyl group~$W=W(\g, \t)$ preserves~$\Lambda$.
@@
 
-Then any discrete series representation of~$G(\R)$ has a \emph{Harish-Chandra parameter}, which is an element of~$\Lambda/W_K$.\footnote{AA 2024-VI-14: perhaps we should add that if $\pi$ is a discrete series representation, then the Harish-Chandra parameter and the central character are enough to specify~$\pi$ completely, and refer to \cite[Section 8]{AV1} and \cite{Contragredient} for full details on the parametrization.
-}
+Then any discrete series representation of~$G(\R)$ has a \emph{Harish-Chandra parameter}, which is an element of~$\Lambda/W_K$.
+In fact, suppose~$\lambda$ is an element of~$\Lambda$ and $\zeta$ is a character of the center~$Z(\R)$ of~$G(\R)$ whose differential agrees with~$\lambda-\rho$ on the intersection $T(\R) \cap Z(\R)$; then the pair $(\lambda, \zeta)$  determines a discrete series representation~$\pi_{\lambda, \zeta}$ of~$G(\R)$.
+Every discrete series representation arises in this way, and $\pi_{\lambda, \zeta}=\pi_{\lambda', \zeta'}$ if and only if $\zeta=\zeta'$ and $\lambda, \lambda'$ are $W_K$-conjugate.
+See  \cite[Section 8]{AV1} and \cite{Contragredient} for more on the parametrization.
 
@@
 
-Let~$\mathfrak{t}^+$ be a Weyl chamber in~$\mathfrak{t}$ containing a representative for the Harish-Chandra parameter of~$\pi$.
-Write $\lim_{x \to 0(\mathfrak{t}^+)} G(\R)\cdot x$ for the set of all elements $y \in \g$ such that every $G$-invariant neighborhood of~$y$ contains all elements of~$\mathfrak{t}^+$ sufficiently close to zero.
-By Lemma B in~\cite{rossmann_limit_orbits}, if $\mathfrak{t}^+$ is a large Weyl chamber, then $\lim_{x \to 0(\mathfrak{t}^+)} G\cdot x$ is a single $G$-orbit.
-Since this does happen when~$\pi$ is a generic discrete series representation, to prove assertion~(c)  it is enough to check the closure of $\lim_{x \to 0(\mathfrak{t}^+)} G\cdot x$ contains $\WF(\pi)$ in that case.
-Now, the equivalence between conditions  (L1) and (L2) on page 2 of~\cite{rossmann_limit_orbits} implies that the closure of $\lim_{x \to 0(\mathfrak{t}^+)} G\cdot x$ contains the asymptotic cone of the orbit of the Harish-Chandra parameter (see  Section~\ref{sec:asymp_cone} below).
+Let~$\mathfrak{t}^+$ be a Weyl chamber in~$\mathfrak{t}^\ast$ containing a representative~$\lambda$ for the Harish-Chandra parameter of~$\pi$.
+Write $\lim_{x \to 0(\mathfrak{t}^+)}\left[ G(\R)\cdot x\right]$ for the set of all elements $y \in i\g(\R)^\ast$ such that every $G(\R)$-invariant neighborhood of~$y$ contains all elements of~$\mathfrak{t}^+$ sufficiently close to zero.
+By Lemma B in~\cite{rossmann_limit_orbits}, if $\mathfrak{t}^+$ is a large Weyl chamber, then $\lim_{x \to 0(\mathfrak{t}^+)} \left[G(\R)\cdot x\right]$ is a single $G(\R)$-orbit.
+Since this does happen when~$\pi$ is a generic discrete series representation, to prove assertion~(c)  it is enough to check the closure of $\lim_{x \to 0(\mathfrak{t}^+)} \left[G(\R)\cdot x\right]$ contains $\WF(\pi)$ in that case.
+Now, the equivalence between conditions  (L1) and (L2) on page 2 of~\cite{rossmann_limit_orbits} implies that the closure of $\lim_{x \to 0(\mathfrak{t}^+)} \left[G(\R)\cdot x\right]$ contains the asymptotic cone of the orbit $G(\R)\cdot \lambda$  (see  Section~\ref{sec:asymp_cone} below).
 Therefore assertion~(c) follows from the fact that this asymptotic cone is equal to  $\WF(\pi)$  (Lemma~\ref{lem:WF_and_AC} below).
-
 \end{proof}
 
-Because of this result we abuse notation slightly as follows.
+Because of Proposition~\ref{invariants_ds} we will abuse notation slightly, as follows.
 If~$\pi$ is a generic discrete series representation of~$G(\R)$, we write $AV(\pi)=\O$ to indicate that $AV(\pi)$ is the closure of the $K$-orbit $\O\subset \s^*$.
@@
 \begin{theorem} \label{th:main} Suppose~$\Pi$ is an $L$-packet of discrete series for~$G(\R)$. 
-The maps $\pi \mapsto \Wh(\pi)$, $\pi \mapsto \AV(\pi)$ and $\pi\mapsto \WF(\pi)$ induce bijections between:
+The maps $\pi \mapsto \Wh(\pi)$, $\pi \mapsto \AV(\pi)$ and $\pi\mapsto \WF(\pi)$ induce bijections between\textup{:}
 \begin{enumerate}
-\item[(1)] The set~$\Pi_{\mathrm{gen}}$ of generic discrete series representations in~$\Pi$ ;
-\item[(2)] The set of Whittaker data for $G(\R)$ ;
-\item[(3)] The set of~$K$-orbits on $\mathcal{O}_p \cap \s^*$.
-\item[(4)] The set of~$G(\R)$-orbits on $\mathcal{O}_p \cap  i \g(\R)^*$.
+\item[(1)] The set~$\Pi_{\mathrm{gen}}$ of generic discrete series representations in~$\Pi$\textup{;}
+\item[(2)] The set of Whittaker data for $G(\R)$\textup{;}
+\item[(3)] The set of~$K$-orbits on $\mathcal{O}_p \cap \s^*$\textup{;}
+\item[(4)] The set of~$G(\R)$-orbits on $\mathcal{O}_p \cap  i \g(\R)^*$\textup{.}
 \end{enumerate}
@@
 
-\begin{lemma} Suppose a group $Q$ acts on two sets $A, B$ and let $f\colon A \to B$ be an equivariant map. 
+\begin{lemma} Suppose a group $Q$ acts on two sets $A, B$ and let $f\colon A \to B$ be a~$Q$-equivariant map. 
 \begin{itemize}
-\item[(a)] If $Q$ acts transitively on~$B$  then~$f$ is surjective;
+\item[(a)] If $Q$ acts transitively on~$B$,  then~$f$ is surjective\textup{;}
 \item[(b)] If $Q$ acts transitively on~$A$ and freely on~$B$, then~$f$ is injective.
 \end{itemize}
-In particular, if~$Q$ acts transitively on~$A$ and simply transitively on~$B$, then~$f$ is a bijection and the action of~$Q$ on~$A$ is simply transitive.
+In particular, if~$Q$ acts transitively on~$A$ and simply transitively on~$B$, then~$f$ must be a bijection and the action of~$Q$ on~$A$ must be simply transitive.
 \end{lemma}
@@
 
-\subsubsection{Interpretation in terms of group cohomology}
+\subsubsection{Connection with group cohomology}
 
@@
 We shall view   $H^0(\tau, A)$ as the fixed-point-set $A^{\tau}$, and $H^1(\tau,A)$ as the quotient of $A^{-\tau} = \{ a \in A, \tau(a)=a^{-1}\}$ by the equivalence relation $a \sim x a \tau(x^{-1})$ for all $x \in A$.
-The set $H^1(\tau, A)$ has a distinguished point $1$, coming from the identity of~$A$; but in general it just a pointed set, and not a group if~$A$ is nonabelian.
+The set $H^1(\tau, A)$ has a distinguished point $1$, coming from the identity of~$A$; but in general it is just a pointed set, and not a group if~$A$ is nonabelian.
 
@@
 \end{equation}
-In~\eqref{long_ptset} the connecting map  $ \psi_\tau\colon \Gad^{\tau} \rightarrow H^1(\tau,Z)$ is defined as follows: if $\gamma \in \Gad^{\tau}$ is the coset $gZ$, then $g\tau(g^{-1}) \in Z^{-\tau}$, and the connecting map sends~$\gamma$ to the class of $g \tau(g^{-1})$ in $H^1(\tau, Z)$.
+In~\eqref{long_ptset} the connecting map  $ \psi_\tau\colon \Gad^{\tau} \rightarrow H^1(\tau,Z)$ is defined as follows: if $\gamma \in \Gad^{\tau}$ is the coset $gZ$, then $g\tau(g^{-1}) \in Z^{-\tau}$, and $\psi_\tau$ sends~$\gamma$ to the class of $g \tau(g^{-1})$ in $H^1(\tau, Z)$.
 The kernel of~$\psi_\tau$ is $(G^\tau)_{\ad}$.
 Since~\eqref{long_ptset} is exact we deduce that $\psi_\tau$ induces a canonical  bijection
-\begin{equation} \label{interp_q_cohomology} Q_{\tau}(G) \to  \ker\left(H^1(\tau,Z)\overset{\varphi_\tau}{\longrightarrow} H^1(\tau,G)\right)\end{equation}
+\begin{equation} \label{interp_q_cohomology} Q_{\tau}(G) \overset{\sim}{\longrightarrow}  \ker\left(H^1(\tau,Z)\overset{\varphi_\tau}{\longrightarrow} H^1(\tau,G)\right)\end{equation}
 where $\varphi_\tau$ is induced by the inclusion $Z^{-\tau} \hookrightarrow G^{-\tau}$.
@@
 
-Note that $Q_\sigma(G)$ is a group of automorphisms of $G(\R)$. It therefore acts on representations of $G(\R)$. 
-Similarly $Q_\theta(G)$ is a group of automorphisms of $(\g,K)$, and acts on $(\g,K)$-modules.\footnote{AA 30-IV-2024: shouldn't this be:  $\Gad^\sigma$ and $\Gad^\theta$  act on $G(\R)$-representations or $(\g,K)$-modules respectively, and this induces actions of $Q_{\sigma}(G)$ and $Q_{\theta}(G)$ on equivalence classes...?
-JDA this is the same thing}
+The adjoint action of $\Gad^\sigma$ on~$G(\R)$ induces an action on $G(\R)$-representations, which descends to an action of  $Q_\sigma(G)$ on equivalence class of $G(\R)$-reoresentations.
+If~$q$ is an element of~$Q_\sigma(G)$, we write $\pi \mapsto \pi^q$ for the action of~$q$ on equivalence classes of $G(\R)$-representations.
+
+Similarly the actions of $\Gad^\theta$ on~$\g$ and~$K$ induce an action of $Q_\theta(G)$ on equivalence classes of $(\g,K)$-modules, for which we use analogous notation.
+
 These two actions are intertwined by the isomorphism of Lemma~\ref{lem:iso_q}:
@@
 The map $X\rightarrow \psi_X$ is an isomorphism between $i\overline\n(\R)^*$ and the unitary characters of $N(\R)$.
-It is easy to see $\psi_X$ is non-degenerate if and only if $X\in i\g(\R)^*$ is a principal nilpotent element.
-In this case we write $(B(\R),X)$ for the Whittaker datum $(B(\R),\psi_X)$.
+It is easy to see that $\psi_X$ is nondegenerate (i.e. satisfies condition~(ii) in the Introduction) if and only if $X\in i\g(\R)^*$ is a principal nilpotent element.
+Therefore the pair $(B(\R),X)$ determines a Whittaker datum $\mathfrak{w}_{X}$: the $G(\R)$-conjugacy class of $(B(\R),\psi_X)$.
+We do not keep track of~$B$ in the notation because~$\mathfrak{w}_X$ doesn't depend on this choice: see~\cite[Section~3.1]{adams_kaletha}.
 
-It is clear that $(B(\R),X)\mapsto G(\R)\cdot X$ is a bijection between Whittaker data and
+The correspondence $\mathfrak{w}_{X} \leftrightarrow G(\R)\cdot X$ defines a bijection between Whittaker data and
 $(\Op(\R)\cap i\g(\R)^*)/G(\R)$. The main result of \cite{matumoto} (Theorem A) says:
@@
 \begin{lemma}\label{lem:matumoto}
-The bijection (2)$\leftrightarrow$(4) takes the Whittaker datum $(B(\R),X)$ to
+The bijection (2)$\leftrightarrow$(4) takes the Whittaker datum $\mathfrak{w}_{X}$ to
 the principal orbit $G(\R)\cdot X$. 
@@
 
-Suppose $\pi$ is a  discrete series representation. Let
+Suppose $\pi$ is a  discrete series representation of~$G(\R)$. Let
 $\lambda\in\t^*$ be a representative for the Harish-Chandra parameter of $\pi$ (Section~\ref{sec:discrete_series}). Let $\Delta$ be the set of roots of $\t$ in $\g$, 
-let $\Delta^+(\lambda)=\{\alpha\mid \langle\lambda,\ch\alpha\rangle>0\}$,
-and let $S(\lambda)\in\Delta^+(\lambda)$ be the simple roots.
-For $\alpha\in \Delta$ let $\g_\alpha$ be the corresponding root space, and choose a non-zero element $X_\alpha\in\g_\alpha$ for each $\alpha$.
+let $\Delta^+(\lambda)=\{\alpha \in \Delta \mid \langle\lambda,\ch\alpha\rangle>0\}$,
+and let $S(\lambda)\subset\Delta^+(\lambda)$ be the simple roots.
+For $\alpha\in \Delta$, let $\g_\alpha$ be the corresponding root space, and choose a non-zero element $X_\alpha\in\g_\alpha$ for each $\alpha$.
 
@@
 \end{lemma}
-
 See
@@
 
-Suppose $\pi$ is a discrete series representation. Let $\lambda\in\t^*$ be a representative of the Harish-Chandra parameter of $\pi$.
-Define\footnote{AA 2024-VI-14: should perhaps decide if we fix a large chamber from the start and take the HC parameter to live there, or at least be careful about consistency in notation...}
+Suppose $\pi$ is a discrete series representation of~$G(\R)$, and let $\lambda\in\t^*$ be a representative of the Harish-Chandra parameter of $\pi$.
+Define\footnote{AA 2024-VI-14: should perhaps think about consistency in notation, and decide if we fix a large chamber from the start and take the HC parameter to live there, or add a few words about independence of choices...}
 \begin{equation} \label{semisimple_orbit_HC} \mathcal{O}_{\pi}=G(\R)\cdot\lambda.\end{equation}
@@
 
-For this see \cite{HarrisHeOlafsson}; in our case the result is due to Rossmann and can be extracted from \cite{RossmannPicard}, Theorem B and C. \qed
+For this see \cite{HarrisHeOlafsson}; in the special case considered here, the result is due to Rossmann and can be extracted from \cite{RossmannPicard}, Theorems B and C. \qed
 
@@
 We recall a recent result of the first author and Tasho Kaletha, which spells out the connection between large discrete series and Whittaker data using  {\it Kostant sections}.
-Let~$X$ be a regular nilpotent element of~$\g$, and choose elements $H, Y \in \g$ such that $(X,H,Y)$ is an  $\SL(2)$-triple.
+Let~$X$ be a regular nilpotent element of~$\g$, and choose  $H, Y \in \g$ such that $(X,H,Y)$ is an  $\SL(2)$-triple.
 The Kostant section~$\Kostant{X}$ is the affine subspace $X + \mathrm{Cent}_{\g}(Y)$ of~$\g$.
 This depends on the choice of $\SL(2)$-triple, but if $X \in \g(\R)$, then the $G(\R)$-conjugacy class of~$\Kostant{X}$ depends only on the $G(\R)$-conjugacy class of~$X$.
+
+Using the given identification $\g \simeq \g^\ast$, if $X \in i\g(\R)^\ast$ is a regular nilpotent element, then it makes sense to talk about the Kostant section $\Kostant{X} \subset \g^\ast$.
+The notation hides the dependence on a choice of $\mathrm{SL}(2)$-triple.
 
@@
 
-Theorem~\ref{th:main} gives a bijection between the set $(\Op \cap \s^*)/K$ of principal nilpotent~$K$-orbits and the set $(\Op \cap i\g(\R)^*/G(\R)$ of principal nilpotent~$G(\R)$-orbits.
+Theorem~\ref{th:main} gives a bijection between the set $(\Op \cap \s^*)/K$ of principal nilpotent~$K$-orbits and the set $(\Op \cap i\g(\R)^*)/G(\R)$ of principal nilpotent~$G(\R)$-orbits.
 
@@
 
+Let us fix a generic discrete representation~$\pi$, a representative~$\lambda \in \t^\ast$ for the Harish-Chandra parameter, and we write~$H_\lambda$ for the element of~$\t$ such that $H_\lambda^\ast=\lambda$.
+In the rest of this section we use the identification $\g \simeq \g^\ast$ implicitly, and do not distinguish between adjoint and coadjoint orbits, Weyl chambers in $\t$ and $\t^\ast$, etc.
+
 Consider the principal nilpotent element~$F_\pi$ defined in~\eqref{e:Fpi}.
@@
 
-We know that  $\AV(\pi)=K \cdot \xi_\pi$ (where $\xi_\pi\in\g^*$ corresponds to $F_\pi$, see Lemma~\ref{l:pi_to_av}), so the image of $\AV(\pi)$ by the Sekiguchi correspondence is 
+We know that  $\AV(\pi)=K \cdot F_\pi$, so the image of $\AV(\pi)$ by the Sekiguchi correspondence is 
  $G(\R)\cdot F_\R$. We want to check that this is equal to $\WF(\pi)$.
@@
 Now, we know that $\Kostant{F_\R}=F_\R+\mathrm{Cent}_\g(E_\R)$ contains $F_\R+E_\R = -H_\theta$.
-In general the orbits $\mathcal{O}_\pi$ and $G(\R) \cdot (-H_\theta)$ are disjoint. 
-Nevertheless $H_{\lambda}$ and $-H_\theta=[F_\theta, E_\theta] = \sum_{\alpha \in S(\lambda)} [X_{-\alpha,} X_\alpha]H_\alpha$ are in the same Weyl chamber. 
-Therefore the result follows from:
+However, $H_\theta$ does not have to be on~$\mathcal{O}_\pi$: in general $\mathcal{O}_\pi=G(\R) \cdot H_\lambda$ and $G(\R) \cdot (-H_\theta)$ are disjoint orbits.
+Nevertheless $H_{\lambda}$ and $-H_\theta=[F_\theta, E_\theta] = \sum_{\alpha \in S(\lambda)} [X_{-\alpha,} X_\alpha]$ are in the same Weyl chamber.  Therefore the result follows from:
 
@@
 
-Consequently each of the three invariants $\Wh(\pi),\AV(\pi)$ and $\WF(\pi)$ are constant for $\pi=\pi(\lambda)$ a large discrete series representation, and $\lambda$ in a fixed large Weyl chamber.
+Consequently each of the three invariants $\Wh(\pi),\AV(\pi)$ and $\WF(\pi)$ remain constant if $\pi=\pi_{\lambda, \zeta}$ is a large discrete series representation, and $\lambda$ varies in a fixed large Weyl chamber.
 \end{lemma}
@@
 
+\medskip
+
 The connection between Lemma~\ref{lem:Kost_and_AC} and Proposition~\ref{prop:AC_chamber} is that Lemma~\ref{lem:Kost_and_AC}  implies the  following observation on the behavior of the asymptotic cone of regular semisimple orbits:
@@
 Since this centralizer is transverse to the $G(\R)$-orbits and has dimension $\dim(\g(\R))-\dim(\t(\R))$,
-there exists an open neighborhood of~$X$ consisting of (regular semisimple) orbits  which meet $\Kostant(F)$.
+there exists an open neighborhood of~$X$ consisting of (regular semisimple) orbits  which meet $\Kostant{F}$.
 Using Lemma~\ref{lem:Kost_and_AC} again, we see that all those orbits $\mathcal{O}'$ satisfy $F \in \AC(\mathcal{O}')$,
@@
 Let us prove Proposition~\ref{prop:AC_chamber}.
-Given an element $H$ of $\mathcal{C}$ we shall write $\mathcal{O}_H$ for the $G(\R)$-orbit of~$H$.
+Given an element $H$ of $\mathcal{C}$, we shall write $\mathcal{O}_H$ for the $G(\R)$-orbit of~$H$.
 For any regular nilpotent orbit~$\Omega$ let $\ECom$  denote the set of $H \in \mathcal{C}$ such that $\AC(\mathcal{O}_H)$ contains $\Omega$; by Lemma~\ref{lem:AC_containment}  we know that   $\ECom$ is an open subset of~$\mathcal{C}$.
 
-Now let $\mathcal{S}$ be the unit sphere of $\t$ for the norm induced by the Killing form, and $\mathcal{S} \cap \mathcal{C}$ be the intersection of $\mathcal{S}$ with the given chamber.
+Now let $\mathcal{S}$ be the unit sphere of $\t$ for the norm induced by the given invariant bilinear form on~$\g$, and let $\mathcal{S} \cap \mathcal{C}$ be the intersection of $\mathcal{S}$ with the given chamber.
 This is an open subset of $\mathcal{S}$.
@@
 
-\begin{lemma}
-  Let $\pi$ be a large discrete series representation.
-Choose a compact Cartan subgroup $T$ and let $\lambda\in \t^*$ be the Harish-Chandra parameter of $\pi$.
+\begin{lemma}\label{lem:explicit_WF}
+  Let $\pi$ be a large discrete series representation. Fix a representative  $\lambda\in \t^*$ of the Harish-Chandra parameter of $\pi$.
 Define $F_\theta=F_\pi$ as in \eqref{e:Fpi}, and choose  $E_\theta$, $H_\theta$ such that $(H_\theta,E_\theta,F_\theta)$ is an $\mathrm{SL}(2)$-triple with $\sigma(E_\theta)=F_\theta$.  Then
@@
 $$\end{lemma}
-Conversely, assume we are given an $L$-packet~$\Pi$ of generic discrete series, and consider a regular semisimple orbit~$\Omega$ in~$\Op \cap i\g(\R)^\ast$.
-We can determine the unique element~$\pi \in \Pi$ with $\WF(\pi)=\Omega$ as follows.
-Fix~$\xi_\R \in \Omega$, write $\xi_\R=F_\R^\ast$ with $F_\R \in \g$ and let $E_\R, H_\R \in \g$ be such that $(E_\R, H_\R, F_\R$ is an  $\mathrm{SL}(2)$-triple with $\theta(E_\R)=-F_\R$.
+There is a partial converse to this statement if we consider discrete series within a single $L$-packet.
+Fix an $L$-packet~$\Pi$ of discrete series, and consider a regular semisimple orbit~$\Omega$ in~$\Op \cap i\g(\R)^\ast$; then we can determine the generic representation~$\pi \in \Pi$ with $\WF(\pi)=\Omega$, as follows.
+Fix~$\xi_\R \in \Omega$, write $\xi_\R=F_\R^\ast$ with $F_\R \in \g$ and let $E_\R, H_\R \in \g$ be such that $(E_\R, H_\R, F_\R)$ is an  $\mathrm{SL}(2)$-triple with $\theta(E_\R)=-F_\R$.
 Set
-Let
 $$

### 2024-06-24 whittaker.tex
updated last (SL2) section

@@
 
-Suppose $\xi_\R\in \Op\cap i\g(\R)^\ast$, and write $\xi_\R = F_\R^\ast$ where $F_\R$ is a principal nilpotent element.
+Suppose $\xi_\R\in \Op\cap i\g(\R)^\ast$, and write $\xi_\R = E_\R^\ast$ where $E_\R$ is a principal nilpotent element.
 We may choose $H_\R, E_\R \in \g$ such that $(H_\R,E_\R,F_\R)$ is an $\mathrm{SL}(2)$-triple and  $E_\R$  contained in $i\g(\R)$,
@@
 After conjugating by~$G(\R)$ we may further assume $\theta(E_\R)=-F_\R$. Set 
-\[   F_\theta=\frac12(-E_\R+F_\R+H_\R).\]
-Then the Sekiguchi correspondence takes the $G(\R)$-orbit of~$\xi_\R$ to the $K$-orbit of $\xi_\theta=F_\theta^\ast$.
+\[   E_\theta=\frac12(E_\R-F_\R+H_\R)\quad
+F_\theta=\frac12(-E_\R+F_\R+H_\R)
+\]
+Then $E^\ast_\theta,F^\ast_\theta\in \Op\cap \s$, and the Sekiguchi correspondence takes the $G(\R)$-orbit of~$E^*_\R$ to the $K$-orbit of $E_\theta^\ast$. 
+Equivalently, it takes the $G(\R)$-orbit of $F^*_\R$ to the $K$-orbits of $F_\theta^\ast$.
 
 Computing the map in the other direction goes as follows.
-Suppose $\xi_\theta \in \Op\cap \s^\ast$, and let $F_\theta \in \s$ be such that $\xi_\theta=F_\theta^\ast$.
-Choose $E_\theta, H_\theta \in \g$ such that $(E_\theta, H_\theta, F_\theta)$ is an $SL(2)$-triple with $E_\theta \in \s$,  which implies $H_\theta\in\k$.
+Suppose $\xi_\theta \in \Op\cap \s^\ast$, and write $\xi_\theta=E_\theta^\ast$.
+Choose $F_\theta, H_\theta \in \g$ such that $(E_\theta, H_\theta, F_\theta)$ is an $SL(2)$-triple with $F_\theta \in \s$,  which implies $H_\theta\in\k$.
 After conjugating by $K$ we may further assume $\sigma(E_\theta)=F_\theta$.
@@
 \begin{equation}\label{def_F_R}
-  F_\R=\frac12(-E_\theta+F_\theta-H_\theta)\\
+E_\R=\frac12(E_\theta-F_\theta-H_\theta)\quad
+F_\R=\frac12(-E_\theta+F_\theta-H_\theta).
 \end{equation}
-Then the Sekiguchi correspondence takes the $K$-orbit of $\xi_\theta$ to the $G(\R)$-orbit of $\xi_\R = F_\R^\ast$.
+Then the Sekiguchi correspondence takes the $K$-orbit of $E^*_\theta$ (resp. $F^*_\theta$) to the $G(\R)$-orbit of $E_\R^\ast$ (resp. $F_\R^\ast$).
 
@@
 
-We know that  $\AV(\pi)=K \cdot F_\pi$, so the image of $\AV(\pi)$ by the Sekiguchi correspondence is 
+We know that  $\AV(\pi)=K \cdot F^*_\pi$, so the image of $\AV(\pi)$ by the Sekiguchi correspondence is 
  $G(\R)\cdot F_\R$. We want to check that this is equal to $\WF(\pi)$.
@@
 
-Then $\Wh(\pi)=\Wh(\pi')$ if and only if $\mathscr{C}, \mathscr{C}'$ are in the same $W_K$-orbit. 
+Then $\Wh(\pi)=\Wh(\pi')$ if and only if $\mathscr{C}, \mathscr{C}'$ are conjugate by $W_K$.
 \end{lemma}
@@
 
+\subsection{The example of $\text{SL}_2$}
+
+We illustrate the constructions of the previous section the case of $G=\SL(2,\R)$.
+
+The complexified Lie algebra $\g$ is the space of $2x2$ complex matrices of trace $0$. Let $\s(\C)=\{t_z\mid z\in\C\}\subset \g$ where
+$$
+t_z=\begin{pmatrix}0&z\\-z&0
+\end{pmatrix}
+$$
+Then $\s(\R)=\{t_x\mid x\in\R\}$.
+
+For $z\in \C$ define $\lambda_z\in \s(\C)^*$ by $\lambda_z(t_x)=xz$.
+The positive root can be taken to be   $\alpha(t_z)=2iz$, i.e.
+$\alpha=\lambda_{2i}$ so $\rho=\frac12\alpha=\lambda_i$.
+Note that $\alpha(\ch\alpha)=2$ gives
+$$
+\ch\alpha=t_{-i}
+$$
+i.e.
+$$
+\langle \lambda_{ik},\ch\alpha\rangle=\lambda_{ik}(t_{-i})=k
+$$
+Viewing $\ch\alpha$ as a map from $\C$ to $\ch{\mathfrak t}$ this says
+$$
+\ch\alpha(z)=t_{-iz}\quad (z\in \C).
+$$
+Also $\ch\rho=t_{-i/2}$
+and
+$$
+\ch\rho(-i)=t_{-\frac 12}=\begin{pmatrix}0&-\frac 12\\\frac 12&0
+\end{pmatrix}
+$$
+
+The Killing form satisfies
+$$
+\kappa(t_x,t_y)=-8xy.
+$$
+Define $H_{\lambda}\in \s(\C)$ so that $\kappa(H_\lambda,t_x)=\lambda(t_x)$. Then $H_\lambda=t_w$ for some $w$; so
+$$
+\kappa(H_{\lambda_z},t_x)=\lambda_z(t_x)=zx,\quad \kappa(t_w,t_x)=-8xw
+$$
+gives
+$$
+H_{\lambda_z}=t_{-\frac z8}.
+$$
+In particular
+$$
+H_{\pm \rho}=H_{\lambda_{\mp i}}=\begin{pmatrix}0&-\frac {\mp i}8\\\frac {\mp i}8&0
+\end{pmatrix}
+$$
+Let $\pi(\lambda_{ik})$ be the discrete series representation with Harish-Chandra parameter $\lambda_{ik}$ $(k\in \Z_{\ne 0})$, so
+$$
+H_{\pi(\lambda_{ik})}=H_{\lambda_{ik}}=
+\begin{pmatrix}0&-\frac{ik}8\\\frac{ik}8&0
+\end{pmatrix}
+$$
+For an $SL(2)$-triple we can take $\{X_\alpha,X_{-\alpha},t_{-i}\}$ where
+$$
+X_\alpha=\frac12\begin{pmatrix}1&i\\i&-1
+\end{pmatrix}, \quad X_{-\alpha}=\overline{X_\alpha}, \quad t_{-i}=\begin{pmatrix}0&-i\\i&0
+\end{pmatrix}
+$$
+That is
+$$
+[t_z,X_\alpha]=\alpha(t_z)X_\alpha=\lambda_{2i}(t_z)X_\alpha=2izX_\alpha
+$$
+In particular
+$$
+[t_{-i},X_\alpha]=2X_\alpha
+$$
+
+Let's compute $\AV(\pi(\lambda_{ik})$ using  \eqref{e:Fpi}.
+Suppose $k>0$. Then $\langle \lambda_{ik},\ch\alpha\rangle=k$, so $\Delta^+=\{\alpha\}$, and
+$F_{\pi_{ik}}=X_{-\alpha}$. 
+By \eqref{e:Fpi} $\AV(\pi_{ik})$ is the $K$-orbit of $X_{-\alpha}^\ast$.
+Thus in general
+$$
+\AV(\pi_{ik})=K\cdot X^*_{-\sgn(k)\alpha}
+$$
+Note: this only uses \eqref{e:Fpi}, which comes directly from \cite{AV1}.
+
+Conjugating $H_{\pi(\lambda_{ik})}$ by $\mathrm{diag}(x,\frac 1x)$ takes it to
+$\begin{pmatrix}0&-x^2\frac{ik}8\\\frac{ik}{x^2}&0
+\end{pmatrix}$,
+and taking the limit we see
+$$
+\WF(\pi(\lambda_{ik}))=\AC(G(\R)\cdot H_{\pi(\lambda_{ik}}))=
+G(\R)\cdot \begin{pmatrix}0&-\sgn(k)i\\0&0
+\end{pmatrix}
+$$
+Note: this only uses  \cite{HarrisHeOlafsson}.
+
+Note that the $G(\R)$ orbit of $\begin{pmatrix}0&i\\0&0
+\end{pmatrix}$ contains $\begin{pmatrix}0&i\R^+\\0&0
+\end{pmatrix}$,
+so in particular $G(\R)\cdot \begin{pmatrix}0&ix\\0&0
+\end{pmatrix}=G(\R)\cdot \begin{pmatrix}0&iy\\0&0
+\end{pmatrix}$ if and only if $\sgn(x)=\sgn(y)$.
+In particular
+$$
+\WF(\pi_{ik})=\WF(\pi_{i\ell})\Leftrightarrow \sgn(k)=\sgn(\ell)
+$$
+
+Finally let's compute $\Wh(\pi_{\lambda_{ik}})$ in two ways.
+First of all by Lemma \ref{lem:matumoto}, which comes directly from \cite[Theorem A]{matumoto}
+$$
+\Wh(\pi_{\lambda_{ik}})=\WF(\pi_{\lambda_{ik}})=G(\R)\cdot \begin{pmatrix}0&-\sgn(k)i\\0&0
+\end{pmatrix}
+$$
+
+Alternatively we apply Proposition \ref{JeffTasho_criterion}, which comes from 
+\cite{adams_kaletha}. Note that
+
+$$
+\O_{\pi_{\lambda_{ik}}}=G(\R)\cdot H_{\lambda_{ik}}=G(\R)\cdot \begin{pmatrix}0&-\frac{ik}8\\\frac{ik}8&0
+\end{pmatrix}
+$$
+
+Note that
+$$
+\K
+\begin{pmatrix}0&\pm i\\0&0
+\end{pmatrix}=\{\begin{pmatrix}0&\pm i\\z&0
+\end{pmatrix}\mid z\in\C\}
+$$
+so, with $\epsilon=\pm 1$, 
+$$
+H_{\lambda_{ik}}\in \K\begin{pmatrix}0&\epsilon i\\0&0
+\end{pmatrix}\Leftrightarrow \epsilon=\sgn(k).
+$$
+
+By Proposition \ref{JeffTasho_criterion}
+we conclude (again) that
+$$
+\Wh(\pi_{\lambda_{ik}})=G(\R)\cdot\begin{pmatrix}0&-\sgn(k)i\\0&0
+\end{pmatrix}
+$$
+
 \bibliographystyle{plain}

### 2024-06-26 whittaker.tex
Small edits

@@
 Suppose $\pi$ is a discrete series representation of~$G(\R)$, and let $\lambda\in\t^*$ be a representative of the Harish-Chandra parameter of $\pi$.
-Define\footnote{AA 2024-VI-14: should perhaps think about consistency in notation, and decide if we fix a large chamber from the start and take the HC parameter to live there, or add a few words about independence of choices...}
+Define
 \begin{equation} \label{semisimple_orbit_HC} \mathcal{O}_{\pi}=G(\R)\cdot\lambda.\end{equation}
+This depends only on~$\pi$, and not on the choice of representative~$\lambda$.
 
@@
 
-The complexified Lie algebra $\g$ is the space of $2x2$ complex matrices of trace $0$. Let $\s(\C)=\{t_z\mid z\in\C\}\subset \g$ where
+The complexified Lie algebra $\g$ is the space of $2\times 2$ complex matrices of trace~$0$. Let $\s(\C)=\{t_z\mid z\in\C\}\subset \g$ where
 $$
 t_z=\begin{pmatrix}0&z\\-z&0
-\end{pmatrix}
+\end{pmatrix}.
 $$
@@
 \begin{pmatrix}0&-\frac{ik}8\\\frac{ik}8&0
-\end{pmatrix}
+\end{pmatrix}.
 $$
@@
 \end{pmatrix}, \quad X_{-\alpha}=\overline{X_\alpha}, \quad t_{-i}=\begin{pmatrix}0&-i\\i&0
-\end{pmatrix}
+\end{pmatrix}.
 $$
@@
 $$
-[t_z,X_\alpha]=\alpha(t_z)X_\alpha=\lambda_{2i}(t_z)X_\alpha=2izX_\alpha
+[t_z,X_\alpha]=\alpha(t_z)X_\alpha=\lambda_{2i}(t_z)X_\alpha=2izX_\alpha.
 $$
@@
 $$
-[t_{-i},X_\alpha]=2X_\alpha
-$$
-
-Let's compute $\AV(\pi(\lambda_{ik})$ using  \eqref{e:Fpi}.
+[t_{-i},X_\alpha]=2X_\alpha.
+$$
+
+Let's compute $\AV(\pi(\lambda_{ik}))$ using  \eqref{e:Fpi}.
 Suppose $k>0$. Then $\langle \lambda_{ik},\ch\alpha\rangle=k$, so $\Delta^+=\{\alpha\}$, and
@@
 $$
-\WF(\pi(\lambda_{ik}))=\AC(G(\R)\cdot H_{\pi(\lambda_{ik}}))=
+\WF(\pi(\lambda_{ik}))=\AC(G(\R)\cdot H_{\pi(\lambda_{ik})})=
 G(\R)\cdot \begin{pmatrix}0&-\sgn(k)i\\0&0
@@
 $$
-\WF(\pi_{ik})=\WF(\pi_{i\ell})\Leftrightarrow \sgn(k)=\sgn(\ell)
+\WF(\pi_{ik})=\WF(\pi_{i\ell})\Leftrightarrow \sgn(k)=\sgn(\ell).
 $$
@@
 Finally let's compute $\Wh(\pi_{\lambda_{ik}})$ in two ways.
-First of all by Lemma \ref{lem:matumoto}, which comes directly from \cite[Theorem A]{matumoto}
+First of all by Lemma \ref{lem:matumoto}, which comes directly from \cite[Theorem A]{matumoto}:
 $$
 \Wh(\pi_{\lambda_{ik}})=\WF(\pi_{\lambda_{ik}})=G(\R)\cdot \begin{pmatrix}0&-\sgn(k)i\\0&0
-\end{pmatrix}
+\end{pmatrix}.
 $$
@@
 \O_{\pi_{\lambda_{ik}}}=G(\R)\cdot H_{\lambda_{ik}}=G(\R)\cdot \begin{pmatrix}0&-\frac{ik}8\\\frac{ik}8&0
-\end{pmatrix}
-$$
-
-Note that
+\end{pmatrix}.
+$$
+On the other hand
 $$
@@
 \Wh(\pi_{\lambda_{ik}})=G(\R)\cdot\begin{pmatrix}0&-\sgn(k)i\\0&0
-\end{pmatrix}
-$$
+\end{pmatrix}.
+$$
+Alexandre: the proof of Proposition~\ref{JeffTasho_criterion} uses Lemma~\ref{lem:matumoto}.
 

### 2024-06-26 whittaker.tex
Tiny edits

@@
 
-We consider pairs $(B,\eta)$ where 
+We are interested in representations of~$G(\R)$ which admit Whittaker models. For this we consider pairs $(B,\eta)$ where 
 \begin{enumerate}[(i)]
@@
 
-We recall what it means for a representation $\pi$ to have a $(B,\eta)$-Whittaker model in Section~\ref{sec:invariants}.
+Recall that a representation $\pi$ of~$G(\R)$ is said to {have a $(B,\eta)$-Whittaker model} if it has a nonzero distribution vector on which $N(\R)$ acts by $\eta$ (for a more careful statement of the definition see Section~\ref{sec:invariants}).
 This condition only depends on the conjugacy class of the pair, 
@@
 as a {\it Whittaker datum}.
-This is a small finite set.
 If $\w$ is a Whittaker datum, it makes sense to talk about $\pi$ having a $\w$-Whittaker model. We let $\Wh(\pi)$  be the set of
-Whittaker data $\w$ such that $\pi$ has a $\w$-Whittaker model. We say $\pi$ is {\it generic} if $\Wh(\pi)$ is non-empty.
+Whittaker data $\w$ such that $\pi$ has a $\w$-Whittaker model. This is a small finite set.
+We say $\pi$ is {\it generic} if $\Wh(\pi)$ is non-empty.
 
@@
 a useful invariant of generic representations.
-For instance if $\Pi$ is a tempered $L$-packet for $G(\R)$ and $\w$ is a Whittaker datum then $\Pi$ contains a unique representation $\pi$
+For instance if $\Pi$ is a tempered $L$-packet for $G(\R)$ and $\w$ is a Whittaker datum, then $\Pi$ contains a unique representation $\pi$
 having a $\w$-Whittaker model. This plays a role in describing the internal structure of $L$-packets.
@@
 case the invariants $\Wh(\pi), \WF(\pi)$ and $\AV(\pi)$ determine each
-other. This is well known to experts, but not so easy to to extract
+other. This is well known to experts, but not so easy to extract
 from the literature. The purpose
@@
 We say $\pi$ has a $(B,\eta)$-Whittaker model
-if there exists a nonzero element $v$ in $\mH^{-\infty}$ such that $\pi(n)(v)=\eta(n)v$ for all $n$ in the nilradical $N(\R)$ of $B(\R)$.See \cite{matumoto}.
+if there exists a nonzero element $v$ in $\mH^{-\infty}$ such that $\pi(n)(v)=\eta(n)v$ for all $n$ in the nilradical $N(\R)$ of $B(\R)$.
+See \cite{matumoto}.
 If~$\w$ is the corresponding Whittaker datum, i.e.

### 2024-06-26 whittaker.tex
added direct argument for Wh(pi), and removed a duplicate in Refs.bib

@@
 
-Finally let's compute $\Wh(\pi_{\lambda_{ik}})$ in two ways.
+Finally let's compute $\Wh(\pi_{\lambda_{ik}})$ in three ways.
+
+We can directly compute it as follows. Consider the  holomorphic discrete series $\pi_{in}$ with $n\ge 1$.
+This has a basis 
+ $\{v_j\}$ where $j=(n+1)+2i$ $(i\ge 0)$. 
+The complex Lie algebra acts on this basis by
+$$
+\begin{aligned}
+  H_\theta v_j&=jv_j\\
+  E_\theta v_j&= \frac 12(n+(j+1))v_{j+2}\\
+  F_\theta v_j&= \frac 12(n-(j-1))v_{j-2}\\
+\end{aligned}
+$$
+Change basis: let $w_i=v_{n+1}+2i$ $(0\le i)$. Then
+$$
+\begin{aligned}
+    H_\theta w_i&=(n+1+2i)w_i\\
+  E_\theta w_i&=(n+1+i)w_{i+1}\\
+  F_\theta w_i&= -iw_{i-1}
+\end{aligned}
+$$
+Let's try to find a $\lambda$-eigenvector for $F_\theta$.
+Solve
+$$
+F_\theta(\sum_{i=0}^\infty a_iw_i=\lambda\sum_{i=0}^\infty a_iw_i
+$$
+A short calculation gives
+$$
+a_{i+1}=-\frac{\lambda}{i+1}
+$$
+and this says that
+$$
+v=\sum_{i=0}^\infty \frac{\lambda^k}{(k+1)!}w_k
+$$
+is a $\lambda$-eigenvector.
+This is not an element of the $(\g,K)$-module, but lives in its completion.
+For details see [Howe-Tan].
+
+On the other hand an $E_\theta$-eigenvector would be something like (I'm not sure the calculation is correct in all details)
+$$
+v=\sum_{i=0}^\infty \frac{n^{\bar i}}{\lambda^i} w_i
+$$
+where $n^{\bar i}=(n+1)(n+2)\dots (n+i)$.
+This doesn't converge to give an element of any completion of $\pi$.
+
 First of all by Lemma \ref{lem:matumoto}, which comes directly from \cite[Theorem A]{matumoto}:
+
 $$

### 2024-07-03 whittaker.tex
New title and theorem numbering
Tiny edits to Introduction

@@
 \def\enddanger{\par\end{trivlist}}
+
+\numberwithin{equation}{section}
 
@@
 \begin{document}
-\title{Whittaker Models for Real Groups}
+\title{Nilpotent Invariants \\ for Generic Discrete Series of Real Groups}
 \author{Jeffrey Adams \& Alexandre Afgoustidis}
@@
 If $\Pi$ is a discrete series $L$-packet then each generic representation in the packet has a unique
-Whittaker model, so the generic representation in $\Pi$ are parametrized by their Whittaker models.
+Whittaker model, so the generic representations in $\Pi$ are parametrized by their Whittaker models.
 It is conjectured that these properties hold in the $p$-adic case as well, and this is known in many cases.
@@
 other. This is well known to experts, but not so easy to extract
-from the literature. The purpose
-of this paper is to give a self-contained account of these matters.
-
-More precisely, we will do two things:
+from the literature.
+
+The purpose
+of this paper is to give a self-contained account of these matters. More precisely, we will do two things:
 \begin{enumerate}
@@
 \end{enumerate}
-Many results in this note are well known. We have tried to give new and simplified proofs for as many of them as we could, and otherwise give convenient references.
+Many results in this note are well known.
+We  tried to give new and simplified proofs for as many of them as we could; for instance, Section~\ref{sec:Sekiguchi} contains a simple proof that $\WF(\pi)$ and $\AV(\pi)$ are exchanged by the Kostant--Sekiguchi correspondence.
+Otherwise we tried to give convenient references.
 
@@
 
-\subsection{Connection between ((3) $\leftrightarrow$ (4)) and the Kostant--Sekiguchi correspondence }
+\subsection{Connection between ((3) $\leftrightarrow$ (4)) and the Kostant--Sekiguchi correspondence } \label{sec:Sekiguchi}
 

### 2024-09-06 whittaker.tex
Many changes required to fix the issues with \g versus \g^*.

--- 2024-06-26 whittaker.tex
@@
 \newcommand{\g}{\mathfrak g}
+\newcommand{\gder}{\mathfrak g_{\mathrm{der}}}
 \newcommand\inv{^{-1}}
@@
 \newcommand{\AV}{\mathrm{AV}}
+\newcommand{\KS}{\mathcal{KS}}
 \newcommand{\Wh}{\mathrm{Wh}}
@@
 
-\subsubsection*{Nilpotent orbits} 
-\label{s:nilpotentorbits}
+\subsubsection*{Nilpotent orbits in $\g^*$} 
+\label{s:dual}
 Let $\N$ be the set of nilpotent elements of $\g$.
 
-We need to pass to the dual Lie algebra $\g^*$. We follow  \cite[Section 2]{AVAV}.
-Define $\N^*\subset \g^*$ to be the set of elements whose orbit is a cone.
-We identify $\g$ and $\g^*$ using  a non-degenerate invariant bilinear form on $\g$. Given an element~$X$ in $\g$ we sometimes write $X^\ast$ for the corresponding element of~$\g^\ast$.
-
-The identification $\g \simeq \g^\ast$ restricts to a bijection $\N\simeq \N^*$. Although this correspondence depends on the choice of form,
-the induced bijection on the level of $G$-orbits is canonical.
-
-We define $\O_p$ to be the \emph{principal nilpotent orbit} in $\N^*$: this is the unique orbit whose closure is  $\N^*$.
-
-We may assume the chosen bilinear form on~$\g$ is $\theta$-invariant.
-In this case the identification between $\g=\mathfrak k+\s$ and $\g^*=\mathfrak k^*\oplus \s^*$ determines a $K$-equivariant  (but non-canonical) isomorphism between $\s$ and $\s^\ast$.
-This induces
-a canonical bijection between $K$-orbits on $\s$ and on $\s^*$.
+We need to pass to the dual Lie algebra $\g^*$.
+We say an element of $\g^*$ is nilpotent if its $G$-orbit is a (weak) cone, i.e. closed under multiplication by $\C^*$,
+and \emph{regular} if $\dim_{\Cent(G)}(X)=\mathrm{rank}(G)$.  
+The principal nilpotent orbit $\O_p\in \g^*$ is the set of regular nilpotent elements.
+
+The statements of the main results do not require the choice of an isomorphism $\g\simeq \g^*$.
+In several places we do need to make such a choice;
+with the exception of (?) this choice will not matter.
+
+So we fix a non-degenerate, $G(\R)$-invariant bilinear form $\kappa$ on $\g(\R)$. This is equivalent to having a non-degenerate, $G(\C)$ and Galois invariant
+bilinear form on $\g$. The restriction of the form each simple factor
+is unique up to a non-zero constant. For example we can use the Killing form on $\gder$, extended arbitrarily by a non-degenerate form on the center.
+
+Given $\kappa$ we define
+$\psi_\kappa: \g\rightarrow \g^*$ as usual:
+$$
+\psi_\kappa(X)(Y)=\kappa(X,Y)\quad (X,Y\in\g).
+$$
+
+Using $\psi_\kappa$ we transfer the asymptotic cone, Kostant section, and Kostant Sekiguchi corresondence to $\g^*$. In each case these constructions are independent of the
+choice of $\kappa$. See (?).
+
+In Section \ref{s:AV} we need to be more precise: we choose  $\kappa$ to be the Killing form. (More generally, we could take any non-degenerate
+invariant form which is negative definite on the Lie algebra of a maximal compact subgroup.)
 
@@
 
-A slightly different invariant is the associated variety of the annihilator. Let $I_\pi$ be the annihlator of $\pi$ in the universal enveloping algebra.
-Let $\AVann(\pi)\subset\N^*\subset \g^*$ be the associated variety of $I_\pi$.
-This is the closure of a single complex nilpotent orbit: see \cite[Section 1, Theorem 4.7]{vogan_bowdoin}.
+A related invariant is the associated variety of the annihilator $I_\pi$ of $\pi$ in the universal enveloping algebra, 
+denoted $\AVann(\pi)$.
+This is a subset of $\N^*\subset\g^*$, and is the closure of a single complex nilpotent orbit: see \cite[Section 1, Theorem 4.7]{vogan_bowdoin}.
 
@@
 We write $\Wh(\pi)$ for the set of Whittaker data~$\w$ such that $\pi$ has a $\w$-Whittaker model.
+If $\pi$ has a unique Whittaker datum $\w$ we write $\Wh(\pi)=\w$.
 
@@
   \item $\pi$ is large;
+        \item $\pi$ is generic.
 \item $\AVann(\pi)=\N^*=\overline{\Op}$;
@@
   \item $\GK(\pi)=N/2$;
-    \item $\pi$ is generic.
-
 \end{enumerate}
@@
 See \cite{vogan_bowdoin}, in particular Corollary 4.7 and Theorem 8.4.
+
+From now on we use the terms {\it large} and {\it generic} interchangeably.
 
@@
 \end{enumerate}
-In particular if $\pi$ is a large discrete series representation then each of these three invariants of $\pi$ determines the other two. 
+In particular if $\pi$ is a generic discrete series representation then each of these three invariants of $\pi$ determines the other two. 
 \end{theorem}
 
-Before embarking on the proof, let us point out that the maps in the Theorem are defined using rather deep results of representation theory.
-However, we shall show in Section~\ref{sec:explicit} that all bijections $(i) \leftrightarrow (j)$, for $i,j \in \{(1), \dots, (4)\}$, can be spelled out in elementary terms.
-Furthermore we shall prove, using elementary arguments, that (3) $\leftrightarrow$ (4) coincides with the Kostant--Sekiguchi correspondence.
+Before embarking on the proof, let us point out that the maps in the
+Theorem are defined using rather deep results of representation
+theory. However, we shall show in Section~\ref{sec:explicit} that all
+bijections $(i) \leftrightarrow (j)$, for $i,j \in \{(1), \dots,
+(4)\}$, can be spelled out in elementary terms. Furthermore we shall
+prove, using elementary arguments, that (3) $\leftrightarrow$ (4)
+coincides with the Kostant--Sekiguchi correspondence.
 
@@
 Inspecting the definitions in \emph{loc.
-cit.} it becomes clear that the map $\pi \mapsto \AV(\pi)$, taking a large discrete series $(\g,K)$-module  (or rather its equivalence class) to its associated variety, is equivariant under~$Q_{\theta}(G)$, proving~(2).
+cit.} it becomes clear that the map $\pi \mapsto \AV(\pi)$, taking a generic discrete series $(\g,K)$-module  (or rather its equivalence class) to its associated variety, is equivariant under~$Q_{\theta}(G)$, proving~(2).
 \qed
@@
 
-\subsection{Whittaker data to real orbits ((2) $\leftrightarrow$ (4))}
-
-First we describe the set of Whittaker data more explicitly.
-Let $B$ be a Borel subgroup of $G$. Let $N$ be the nilradical of $B$, and $\overline N$ the opposite
-nilpotent subgroup. Let $\n,\overline\n$ be the Lie algebras of $N,\overline N$.
-If $B$ is defined over $\R$ we consider $N(\R),\n(\R), \overline\n(\R)$, etc.
-For $X\in i\overline \n(\R)^*$ define a unitary character $\psi_X$ of $N(\R)$ by:
-$$
-\psi_X(e^Y)=e^{X(Y)}\quad(Y\in \n(\R)).
-$$
-The map $X\rightarrow \psi_X$ is an isomorphism between $i\overline\n(\R)^*$ and the unitary characters of $N(\R)$.
-It is easy to see that $\psi_X$ is nondegenerate (i.e. satisfies condition~(ii) in the Introduction) if and only if $X\in i\g(\R)^*$ is a principal nilpotent element.
-Therefore the pair $(B(\R),X)$ determines a Whittaker datum $\mathfrak{w}_{X}$: the $G(\R)$-conjugacy class of $(B(\R),\psi_X)$.
-We do not keep track of~$B$ in the notation because~$\mathfrak{w}_X$ doesn't depend on this choice: see~\cite[Section~3.1]{adams_kaletha}.
-
-The correspondence $\mathfrak{w}_{X} \leftrightarrow G(\R)\cdot X$ defines a bijection between Whittaker data and
-$(\Op(\R)\cap i\g(\R)^*)/G(\R)$. The main result of \cite{matumoto} (Theorem A) says:
-
-\begin{lemma}\label{lem:matumoto}
-The bijection (2)$\leftrightarrow$(4) takes the Whittaker datum $\mathfrak{w}_{X}$ to
-the principal orbit $G(\R)\cdot X$. 
- \end{lemma}
-
-\subsection{Large discrete series to $K$-orbits ((1) $\leftrightarrow$ (3))}
+\subsection{Associated Variety of generic discrete series}
+\label{s:AV}
 
@@
 
-\begin{lemma}[(1)$\leftrightarrow$(3)]\label{l:pi_to_av}
-Suppose $\pi$ is a large discrete series representation with Harish-Chandra parameter $\lambda\in\t^*$.
+In this section only we need to  choose a particular an isomorphism $\gder\simeq \gder^*$.
+For this we let $\kappa$ be the killing form, and define $\psi:\gder\rightarrow \gder^*$ by
+$$
+\psi(X)(Y)=\kappa(X,Y)\quad (X,Y\in \gder).
+$$
+
+\begin{lemma}
+\label{l:pi_to_av}
+  \label{l:AV}
+Suppose $\pi$ is a generic discrete series representation with Harish-Chandra parameter $\lambda\in\t^*$.
 Set
@@
 
-Then $F_\pi\in\s$ is a regular nilpotent element. Let $F_\pi^\ast\in \N^*$ be the corresponding element (cf. Section \ref{s:nilpotentorbits}).
+Then $F_\pi\in\s$ is a regular nilpotent element.
 Then 
 $$
-\AV(\pi)=\overline{K\cdot F_\pi^\ast}.
+\AV(\pi)=K\cdot \psi(F_\pi).
 $$
@@
 
-\subsection{Large discrete series to real orbits ((1) $\leftrightarrow$ (4))}\label{sec:asymp_cone}
+\begin{remarkplain}
+Note that $\psi_{-\kappa}(F_\pi)=-\psi_{\kappa}(F_\pi)$, and these are not necessarily $K$-conjugate.
+  This is the reason we need to use (a positive multiple of) the Killing form for this formula.
+\end{remarkplain}
+
+\subsection{Wave front set of generic discrete series}\label{sec:asymp_cone}
 
@@
 
-For this see \cite{HarrisHeOlafsson}; in the special case considered here, the result is due to Rossmann and can be extracted from \cite{RossmannPicard}, Theorems B and C. \qed
-
-In Section~\ref{sec:alternate_WF} below we will  give another simple description of~$\WF(\pi)$, based on the description of $\AV(\pi)$ in the previous paragraph and on the Sekiguchi correspondence.
-
-\subsection{Large discrete series to Whittaker data ((1) $\leftrightarrow$ (2))}
-
-We recall a recent result of the first author and Tasho Kaletha, which spells out the connection between large discrete series and Whittaker data using  {\it Kostant sections}.
+For this see \cite{HarrisHeOlafsson}; in the special casea considered here, the result is due to Rossmann and can be extracted from \cite{RossmannPicard}, Theorems B and C. \qed
+
+In Section~\ref{sec:alternate_WF} below we will give another simple
+description of~$\WF(\pi)$, based on the description of $\AV(\pi)$ in
+the previous paragraph and on the Sekiguchi correspondence.
+
+\subsection{Whittaker data of generic discrete series}
+
+The following discussion is taken directly from \cite[Section~3.1]{adams_kaletha}.
+
+Suppose $X\in i\g(\R)^*\subset \g^*$ is a regular nilpotent element (see Section \ref{s:dual}).
+Let $\overline{\mathfrak b}(\R)$ be the kernel of $X$. 
+The corresponding Borel subgroup $B$ is defined over $\R$.
+Choose an $\R$-Cartan subgroup $T$ of
+$\overline B$, and let $B$ be the corresponding opposite Borel
+subgroup (characterized by $B\cap \overline B=T$). 
+Then $X$ defines a unitary
+character of the nilradical  $N(\R)$  of $B(\R)$ by
+\[ 
+\psi_X(\exp Y)=e^{X(Y)}\quad (Y\in\n(\R)).
+\] 
+We define $\w_X$ to be the $G(\R)$-conjugacy class of $(B(\R),\psi_X)$; as the notation indicates this is independent 
+of the choice of $T$.
+
+The correspondence $\mathfrak{w}_{X} \leftrightarrow G(\R)\cdot X$ defines a bijection between Whittaker data and
+$(\Op(\R)\cap i\g(\R)^*)/G(\R)$.
+
+We recall a recent result of the first author and Tasho Kaletha, which spells out the connection between generic discrete series and Whittaker data using  {\it Kostant sections}.
 Let~$X$ be a regular nilpotent element of~$\g$, and choose  $H, Y \in \g$ such that $(X,H,Y)$ is an  $\SL(2)$-triple.
@@
 
-Using the given identification $\g \simeq \g^\ast$, if $X \in i\g(\R)^\ast$ is a regular nilpotent element, then it makes sense to talk about the Kostant section $\Kostant{X} \subset \g^\ast$.
-The notation hides the dependence on a choice of $\mathrm{SL}(2)$-triple.
-
-\begin{proposition}[\cite{adams_kaletha}]\label{JeffTasho_criterion}
+We define the Kostant section in $\g^*$ using an identification $\g\simeq \g^*$ as discussed in Section \ref{s:dual}. That is we fix an equivariant isomorphism $\psi$, and define
+$$
+\K(X)=\psi(\K(\psi\inv(X))\quad (X\in \g^*)
+$$
+Since $\psi$ is unique on each simple factor up to non-zero scalar, it is easy to see this definition is independent of the choice of $\psi$. See \cite[Section 3.2]{adams_kaletha}.
+
+\begin{proposition}[\phantom{}{\cite[Proposition 3.3.3]{adams_kaletha}}]\label{JeffTasho_criterion}
+  \label{p:Kostant}
 Suppose $\pi$ is a generic discrete series representation of~$G(\R)$. Suppose~$\pi$ be a Whittaker datum for~$G(\R)$, and let~$X \in i\g(\R)^*$ be a regular nilpotent element such that $\w = \w_X$. 
@@
 
-\subsection{Connection between ((3) $\leftrightarrow$ (4)) and the Kostant--Sekiguchi correspondence }
-
-Theorem~\ref{th:main} gives a bijection between the set $(\Op \cap \s^*)/K$ of principal nilpotent~$K$-orbits and the set $(\Op \cap i\g(\R)^*)/G(\R)$ of principal nilpotent~$G(\R)$-orbits.
-
-It is well known that a natural bijection between nilpotent $K$-orbits and nilpotent $G(\R)$-orbits can be defined in more elementary terms.
-This is the Kostant--Sekiguchi correspondence~\cite{sekiguchi}.
-Furthermore, it is a deep theorem of Schmid and Vilonen (the main result of~\cite{SV1}) that the wavefront set and the associated variety are exchanged by this correspondence.
-(As a historical aside, the Kostant--Sekiguchi correspondence was discovered on the basis that the correspondence $\AV(\pi) \leftrightarrow \WF(\pi)$ might be expressed in elementary terms.)
-
-Therefore, a particular case of Schmid and Vilonen's theorem says: 
-\begin{proposition} \label{Sekiguchi_result} The bijection (3)--(4) is induced by the Kostant--Sekiguchi correspondence.
+\begin{lemma}[\phantom{}{\cite[Lemma 3.3.4]{adams_kaletha}}]
+\label{lem:Kost_and_AC}
+Let $\mathcal{O}$ be a regular semisimple orbit and  let $X$ be a regular nilpotent element. Then $\Kostant{X}$ meets~$\mathcal{O}$ if and only if $X$ is in the asymptotic cone~$\AC(\mathcal{O})$. 
+\end{lemma}
+
+For a closely related result see \cite[Proposition 3.5]{fm}.
+
+The Proposition, Lemma and Lemma \ref{lem:WF_and_AC} give the following result,
+which is a special case of the main result of \cite{matumoto} (Theorem A).
+
+\begin{corollary}\label{cor:matumoto}
+Suppose $\pi$ is a generic discrete series representation. Then
+$$
+\Wh(\pi)=\w_X\Leftrightarrow \WF(\pi)=G(\R)\cdot X.
+$$
+\end{corollary}
+
+\subsection{Geometry of Kostant sections and asymptotic cones}
+
+By Lemma \ref{l:pi_to_av} the associated variety of a discrete representation only depends on the Weyl chamber of its Harish-Chandra parameter. 
+The same holds for the wave front set and Whittaker data by Theorem \ref{th:main}. This can also be proved directly 
+using some geometric facts.
+
+Write $\O_H$ for the $G(\R)$-orbit of $H$.
+
+\begin{proposition}\label{prop:AC_chamber} Let $\mathcal{C} \subset \t$ be a large open Weyl chamber.
+  If $H,H'\in\mathcal{C}$  then $\AC(\mathcal{O}_H)=\AC(\mathcal{O}_{H'})$.
+
+  Suppose $X$ is a regular nilpotent element. Then $\K(X)\cap \O_H\ne \emptyset$ if and only if $\K(X)\cap \O_{H'}\ne\emptyset$.
 \end{proposition}
-We shall do two things here.
-First, we will quote a result of \cite{AVAV} which makes this case of the Kostant--Sekiguchi correspondence completely explicit.
-Second, we shall give a new and elementary proof of Proposition~\ref{Sekiguchi_result}: this avoids the use of Schmid and Vilonen's difficult results, and instead uses the results above (in particular Proposition~\ref{JeffTasho_criterion}) as the main ingredients.
-
-\subsubsection{The Sekiguchi correspondence for principal nilpotent orbits}\label{sec:concrete_sek}
-Let us spell out the special case of the Sekiguchi correspondence which is of interest here. We follow~\cite[Section~2]{AVAV}.
-
-Suppose $\xi_\R\in \Op\cap i\g(\R)^\ast$, and write $\xi_\R = E_\R^\ast$ where $E_\R$ is a principal nilpotent element.
-We may choose $H_\R, E_\R \in \g$ such that $(H_\R,E_\R,F_\R)$ is an $\mathrm{SL}(2)$-triple and  $E_\R$  contained in $i\g(\R)$,
-which implies $H_\R\in \g(\R)$. 
-After conjugating by~$G(\R)$ we may further assume $\theta(E_\R)=-F_\R$. Set 
-\[   E_\theta=\frac12(E_\R-F_\R+H_\R)\quad
-F_\theta=\frac12(-E_\R+F_\R+H_\R)
-\]
-Then $E^\ast_\theta,F^\ast_\theta\in \Op\cap \s$, and the Sekiguchi correspondence takes the $G(\R)$-orbit of~$E^*_\R$ to the $K$-orbit of $E_\theta^\ast$. 
-Equivalently, it takes the $G(\R)$-orbit of $F^*_\R$ to the $K$-orbits of $F_\theta^\ast$.
-
-Computing the map in the other direction goes as follows.
-Suppose $\xi_\theta \in \Op\cap \s^\ast$, and write $\xi_\theta=E_\theta^\ast$.
-Choose $F_\theta, H_\theta \in \g$ such that $(E_\theta, H_\theta, F_\theta)$ is an $SL(2)$-triple with $F_\theta \in \s$,  which implies $H_\theta\in\k$.
-After conjugating by $K$ we may further assume $\sigma(E_\theta)=F_\theta$.
-Define 
-\begin{equation}\label{def_F_R}
-E_\R=\frac12(E_\theta-F_\theta-H_\theta)\quad
-F_\R=\frac12(-E_\theta+F_\theta-H_\theta).
-\end{equation}
-Then the Sekiguchi correspondence takes the $K$-orbit of $E^*_\theta$ (resp. $F^*_\theta$) to the $G(\R)$-orbit of $E_\R^\ast$ (resp. $F_\R^\ast$).
-
-\subsubsection{A simple proof of Proposition~\ref{Sekiguchi_result}}\label{sec:sekiguchi_proof}
-
-Let us fix a generic discrete representation~$\pi$, a representative~$\lambda \in \t^\ast$ for the Harish-Chandra parameter, and we write~$H_\lambda$ for the element of~$\t$ such that $H_\lambda^\ast=\lambda$.
-In the rest of this section we use the identification $\g \simeq \g^\ast$ implicitly, and do not distinguish between adjoint and coadjoint orbits, Weyl chambers in $\t$ and $\t^\ast$, etc.
-
-Consider the principal nilpotent element~$F_\pi$ defined in~\eqref{e:Fpi}.
-Let us use this as~$F_\theta$ in the previous subsection: define $E_\theta = \sum_{\alpha \in S(\lambda)}X_\alpha$ and $H_\theta  = [E_\theta, F_\theta]$; then $E_\theta \in \s$ and $(E_\theta, H_\theta, F_\theta)$ is an $\mathrm{SL}(2)$-triple.
-Define another $\mathrm{SL}(2)$-triple $(E_\R, F_\R, H_\R)$ by
-\[ \begin{aligned}
-  F_\R&=\frac12(-E_\theta+F_\theta-H_\theta)\\
-  E_\R&=\frac12(E_\theta-F_\theta-H_\theta)\\
-  H_\R&=E_\theta+F_\theta.
-\end{aligned}\]
-
-We know that  $\AV(\pi)=K \cdot F^*_\pi$, so the image of $\AV(\pi)$ by the Sekiguchi correspondence is 
- $G(\R)\cdot F_\R$. We want to check that this is equal to $\WF(\pi)$.
-
-By Lemma~\ref{lem:matumoto} it is enough to check that $\pi$ is $\w$-generic for the Whittaker datum $\w$ corresponding to~$F_\R$.
-By Proposition~\ref{JeffTasho_criterion} this is the case if and only if the Kostant section $\Kostant{F_\R}$ meets $\mathcal{O}_\pi$.
-
-Now, we know that $\Kostant{F_\R}=F_\R+\mathrm{Cent}_\g(E_\R)$ contains $F_\R+E_\R = -H_\theta$.
-However, $H_\theta$ does not have to be on~$\mathcal{O}_\pi$: in general $\mathcal{O}_\pi=G(\R) \cdot H_\lambda$ and $G(\R) \cdot (-H_\theta)$ are disjoint orbits.
-Nevertheless $H_{\lambda}$ and $-H_\theta=[F_\theta, E_\theta] = \sum_{\alpha \in S(\lambda)} [X_{-\alpha,} X_\alpha]$ are in the same Weyl chamber.  Therefore the result follows from:
-
-\begin{proposition}\label{prop:AC_chamber} Let $\mathcal{C} \subset \t$ be a large open Weyl chamber.
-If $H$ and $H'$ are  points of~$\mathcal{C}$ and $\mathcal{O}, \mathcal{O}'$ are the   $G(\R)$-orbits of $H$ and $H'$, then $\AC(\mathcal{O})=\AC(\mathcal{O}')$.
-\end{proposition}
-
-We shall prove this in the rest of this section, based on the following lemma.
-
-\begin{lemma}\label{lem:Kost_and_AC} Let $\mathcal{O}$ be a regular semisimple orbit and  let $X$ be a regular nilpotent element.
-Then $\Kostant{X}$ meets~$\mathcal{O}$ if and only if $X$ is in the asymptotic cone~$\AC(\mathcal{O})$.
-
-Consequently each of the three invariants $\Wh(\pi),\AV(\pi)$ and $\WF(\pi)$ remain constant if $\pi=\pi_{\lambda, \zeta}$ is a large discrete series representation, and $\lambda$ varies in a fixed large Weyl chamber.
-\end{lemma}
-\begin{proof} 
-If $X\in \AC(\mathcal O)$ then $\Kostant{X}$ meets $\mathcal O$ by \cite[Lemma 3.2.3]{adams_kaletha}.
-
-Suppose $\Kostant{X}$ meets $\mathcal O$.
-This means there is an $SL(2)$-triple $(X,H,Y)$, and an element $Z\in \Cent_\g(Y)$ such that $W=X+Z \in \O$. 
-By \cite{Kostant59}, the centralizer  $\mathrm{Cent}_{\g}(Y)$ is abelian; furthermore there exists a Cartan subalgebra $\mathfrak{h} \subset \g$, and a positive system $\Delta$ for the roots of $\mathfrak{h}$ in $\g$, such that $E$ is contained in the sum of $\Delta$-positive root spaces, while $\mathrm{Cent}_{\g}(F)$ is contained in the sum of $\Delta$-negative roots.
-Therefore, if we set $h(t) = \exp(tH)$ for $t \in \R_+$, then
-\[\begin{cases} \mathrm{Ad}(h(t)) \cdot F \longrightarrow 0 & \text{as $t \to +\infty$, while} \\
- \mathrm{Ad}(h(t)) \cdot E = f(t) E & \text{ with $f(t) >0$ and $f(t)\to +\infty$ as $t \to \infty$.}\end{cases}\]
-Set $Y(t) = \mathrm{Ad}(h(t)) Y$; then $f(t) \left[ E + Y(t) \right] = \mathrm{Ad}(h(t)) W$ lies on the orbit~$\mathcal{O}$.
-Thus there exists a continuous path in $\R^+ \cdot \mathcal{O}$ with $E=X$ as a limit point; by definition this means $X \in \AC(\mathcal{O})$.%By the representation theory of $SL(2)$ we know that $Z=\sum_{j=0}^n Z_j$ with $[H,Z_j]=-jZ_j$.
-%Then 
-%$$
-%\Ad(e^{tH})(X+Z)=e^{2t}(X) + \sum_j e^{-tj}Z_j
-%$$
-%Taking the limit as $t\rightarrow 0$ gives $\Ad(e^{tH})(X+Z)\rightarrow e^{2t}X$. Therefore
-%$$
-%\lim_{t\rightarrow 0}e^{-2t}\Ad(e^{tH})(X+Z)=X
-%$$ which implies the result.
-\end{proof}
-
-For a closely related result see \cite[Proposition 3.5]{fm}.
-
-\medskip
-
-The connection between Lemma~\ref{lem:Kost_and_AC} and Proposition~\ref{prop:AC_chamber} is that Lemma~\ref{lem:Kost_and_AC}  implies the  following observation on the behavior of the asymptotic cone of regular semisimple orbits:
+
+Before giving the proof we need a Lemma.
 
@@
 \begin{proof}
+
 Let $F$ be an element of~$\Omega$, and let $\mathcal{O}$  be a regular semisimple orbit such that $\AC(\mathcal{O})$ contains~$\Omega$.
@@
 
-Let us prove Proposition~\ref{prop:AC_chamber}.
-Given an element $H$ of $\mathcal{C}$, we shall write $\mathcal{O}_H$ for the $G(\R)$-orbit of~$H$.
+\begin{proof}[proof of the  Proposition]
 For any regular nilpotent orbit~$\Omega$ let $\ECom$  denote the set of $H \in \mathcal{C}$ such that $\AC(\mathcal{O}_H)$ contains $\Omega$; by Lemma~\ref{lem:AC_containment}  we know that   $\ECom$ is an open subset of~$\mathcal{C}$.
@@
 
-Now consider the set $\Sigma$ of all points on $\mathcal{S} \cap \mathcal{C}$ which arise as the radial projection of the Harish-Chandra parameter~$H$ of some large discrete series representation.
+Now consider the set $\Sigma$ of all points on $\mathcal{S} \cap \mathcal{C}$ which arise as the radial projection of the Harish-Chandra parameter~$H$ of some generic discrete series representation.
 Since the Harish-Chandra parameters for discrete series are (a translate of) an integral lattice, the set $\Sigma$ is dense in $\mathcal{S} \cap \mathcal{C}$.
-Therefore if the open set $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$ is nonempty, there must exist at least one large discrete series representation~$\pi$ whose Harish-Chandra projects to $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$.
-By Lemma~\ref{lem:WF_and_AC} this means $\Omega$ and $\Omega'$ must be contained in $\WF(\pi)$, which implies $\Omega = \Omega'$ since the wavefront set is the closure of a single orbit if $\pi$ is a large discrete series.
+Therefore if the open set $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$ is nonempty, there must exist at least one generic discrete series representation~$\pi$ whose Harish-Chandra projects to $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$.
+By Lemma~\ref{lem:WF_and_AC} this means $\Omega$ and $\Omega'$ must be contained in $\WF(\pi)$, which implies $\Omega = \Omega'$ since the wavefront set is the closure of a single orbit if $\pi$ is a generic discrete series.
 
@@
 Since $\mathcal{C}$ is connected and equal to the union of all subsets $\mathcal{E}^{\mathcal{C}}_{\Omega}$, the chamber $\mathcal{C}$ must be equal to a single $\ECom$.
-This concludes the proof of Proposition~\ref{prop:AC_chamber}, and therefore also of Proposition~\ref{Sekiguchi_result}.
-
-\subsubsection{A simple description of the wavefront set}\label{sec:alternate_WF}
-
-As we saw the correspondence $\pi \leftrightarrow \WF(\pi)$ can be described using the asymptotic cone of the semisimple orbit of the Harish-Chandra parameter.
-We used this in the proof of Proposition~\ref{Sekiguchi_result}.
-Now, the results of Sections~\ref{sec:concrete_sek} and~\ref{sec:sekiguchi_proof} provide another description of $\WF(\pi)$ from the Harish-Chandra parameter: we can compose the maps (1)$\leftrightarrow$(3)$\leftrightarrow$(4).
-This gives the following rather concrete conclusion.
-
-\begin{lemma}\label{lem:explicit_WF}
-  Let $\pi$ be a large discrete series representation. Fix a representative  $\lambda\in \t^*$ of the Harish-Chandra parameter of $\pi$.
-Define $F_\theta=F_\pi$ as in \eqref{e:Fpi}, and choose  $E_\theta$, $H_\theta$ such that $(H_\theta,E_\theta,F_\theta)$ is an $\mathrm{SL}(2)$-triple with $\sigma(E_\theta)=F_\theta$.  Then
-$$
-\WF(\pi)=G(\R)\cdot F_\R^\ast, \quad \text{where $F_\R = \frac i2(-E_\theta+F_\theta-H_\theta)\in\N\cap i\g(\R)$.}
-$$\end{lemma}
-There is a partial converse to this statement if we consider discrete series within a single $L$-packet.
-Fix an $L$-packet~$\Pi$ of discrete series, and consider a regular semisimple orbit~$\Omega$ in~$\Op \cap i\g(\R)^\ast$; then we can determine the generic representation~$\pi \in \Pi$ with $\WF(\pi)=\Omega$, as follows.
-Fix~$\xi_\R \in \Omega$, write $\xi_\R=F_\R^\ast$ with $F_\R \in \g$ and let $E_\R, H_\R \in \g$ be such that $(E_\R, H_\R, F_\R)$ is an  $\mathrm{SL}(2)$-triple with $\theta(E_\R)=-F_\R$.
-Set
-$$
-H_\theta=E_\R-F_\R.
-$$
-Then $H_\theta$ is a regular semisimple element, and belongs to~$\k$.
-Define a Cartan subalgebra~$\t$ of~$\g$ by $\t=\Cent_{\g}(H_\theta)$, and a set of positive roots by
-$$
-\Delta^+=\{\alpha\in\Delta(\t,\g)\mid  \alpha(H_\theta)>0\}.
-$$
-Then $\pi$ is the discrete series representation in $\Pi$ whose Harish-Chandra parameter is dominant for $\Delta^+$.
-
-\subsection{Application: Whittaker model and Weyl chamber of the Harish-Chandra parameter}
-
-As an application of the above results, here is a simple proof of a fact which is well known to the experts, but not easy to locate in the literature.
-
-\begin{lemma}
+
+The second assertion is an immediate consequence of the first and Lemma \ref{lem:Kost_and_AC}
+
+\end{proof}
+
+\begin{corollary}
+\label{c:same}
+Suppose $\pi$ is a generic discrete series representation with Harish-Chandra parameter $\lambda$.
+Then $\AV(\pi)$, $\WF(\pi)$ and $\Wh(\pi)$ only depend on the Weyl chamber of $\lambda$.
+\end{corollary}
+
+\begin{proof}
+This follows from Lemma \ref{l:pi_to_av} for the associated variety;
+from Lemma \ref{lem:WF_and_AC} for the wave front set, and Lemma \ref{lem:Kost_and_AC} (or Corollary \ref{cor:matumoto})
+for the Whittaker model.
+\end{proof}
+
+Here is a slightly stronger statement.
+
+\begin{corollary}
 \label{l:equalWhittaker}
-Suppose $\pi$, $\pi'$ are large discrete series representations of~$G(\R)$.
+Suppose $\pi$, $\pi'$ are generic discrete series representations of~$G(\R)$.
 Let~$\lambda, \lambda'$ be representatives for the Harish-Chandra parameters of~$\pi, \pi'$ respectively, and let $\mathscr{C}, \mathscr{C}'$ be the corresponding Weyl chambers.
 
-Then $\Wh(\pi)=\Wh(\pi')$ if and only if $\mathscr{C}, \mathscr{C}'$ are conjugate by $W_K$.
-\end{lemma}
+Then $\WF(\pi)=\WF(\pi')$ if and only if $\mathscr{C}, \mathscr{C}'$ are conjugate by $W_K$.
+The same result holds for $\Wh(\pi)$ and $\AV(\pi)$. 
+\end{corollary}
 
 \begin{proof}
-If  $\mathscr{C}, \mathscr{C}'$ are in the same $W_K$-orbit, then the Harish-Chandra parameters of $\pi$, $\pi'$ have representatives in the same Weyl chamber; therefore $\Wh(\pi)=\Wh(\pi')$ by Lemma~\ref{lem:Kost_and_AC}.
-
-For the other direction, by Theorem \ref{th:main} we can replace
-$\Wh(\pi)$ in the statement with $\WF(\pi)$.  So suppose
-$\WF(\pi)=\WF(\pi')$. By Lemma \ref{lem:Kost_and_AC} we may assume
+If  $\mathscr{C}, \mathscr{C}'$ are in the same $W_K$-orbit, then the Harish-Chandra parameters of $\pi$, $\pi'$ have representatives in the same Weyl chamber; therefore $\Wh(\pi)=\Wh(\pi')$ by Corollary \ref{c:same}.
+
+Suppose $\WF(\pi)=\WF(\pi')$. By Lemma \ref{lem:Kost_and_AC} we may assume
 $\lambda=w\lambda'$ for some $w\in W$, i.e. $\pi,\pi'$ are contained
@@
 
+\subsection{$\AV(\pi)$ and $\WF(\pi)$: the Kostant--Sekiguchi correspondence } \label{sec:Sekiguchi}
+
+Theorem~\ref{th:main} gives a bijection between the set $(\Op \cap \s^*)/K$ of principal nilpotent~$K$-orbits and the set $(\Op \cap i\g(\R)^*)/G(\R)$ of principal nilpotent~$G(\R)$-orbits.
+
+It is well known that a natural bijection between nilpotent $G(\R)$-orbits on $\g(\R)$ and nilpotent $K$ orbits on $\s$. 
+This is the Kostant--Sekiguchi
+correspondence~\cite{sekiguchi}, which we write as $\KS(\O)$. It is a deep theorem of
+Schmid and Vilonen (the main result of~\cite{SV1}) that the wavefront
+set and the associated variety are exchanged by this
+correspondence. (As a historical aside, the Kostant--Sekiguchi
+correspondence was discovered on the basis that the correspondence
+$\AV(\pi) \leftrightarrow \WF(\pi)$ might be expressed in elementary
+terms.)
+
+As discussed in Section \ref{s:dual} we transfer the Kostant--Sekiguchi correspondence to $\g^*$ using  an isomorphism $\psi_\kappa$.
+Explicitly, suppose $\O$ is a $G(\R)$-orbit in $\O_p\cap i\g(\R)^*$.  Then $\KS(\O)$ is defined by:
+$$
+\KS(\O)=\psi_\kappa(\KS(\psi_\kappa\inv(\O)).
+$$
+Since $\O\subset \gder$, and $\psi_\kappa$ restricted to each simple factor is unique up to non-zero scalar, it is easy to see this definition
+is independent of the choice of $\kappa$.
+
+Here is a particular case of Schmid and Vilonen's theorem:
+
+\begin{proposition} \label{Sekiguchi_result}
+Suppose $\pi$ is a generic discrete series representation. Then
+$$
+\KS(\AV(\pi))=\WF(\pi)
+$$
+In other words the bijection (3)--(4) is induced by the Kostant--Sekiguchi correspondence.
+\end{proposition}
+
+We shall do two things here.
+First, we will quote a result of \cite{AVAV} which makes this case of the Kostant--Sekiguchi correspondence completely explicit.
+Second, we shall give a new and elementary proof of Proposition~\ref{Sekiguchi_result}: this avoids the use of Schmid and Vilonen's difficult results, and instead uses the results above (in particular Proposition~\ref{JeffTasho_criterion}) as the main ingredients.
+
+\subsubsection{The Sekiguchi correspondence for principal nilpotent orbits}\label{sec:concrete_sek}
+Let us spell out the special case of the Sekiguchi correspondence which is of interest here. We follow~\cite[Section~2]{AVAV}.
+
+Suppose $E_\R\in i\g(\R)$ is a principal nilpotent element.
+We may choose $H_\R, E_\R \in \g$ such that $(H_\R,E_\R,F_\R)$ is an $\mathrm{SL}(2)$-triple and  $E_\R$  contained in $i\g(\R)$,
+which implies $H_\R\in \g(\R)$. 
+After conjugating by~$G(\R)$ we may further assume $\theta(E_\R)=-F_\R$. Set 
+\[   E_\theta=\frac12(E_\R-F_\R+H_\R)\quad
+F_\theta=\frac12(-E_\R+F_\R+H_\R)
+\]
+Then
+$$
+\KS(G(\R)\cdot E_\R)=K\cdot E_\theta.
+$$
+Computing the map in the other direction is similar. Suppose $E_\theta\in \s$ is a principal nilpotent element. 
+Choose $F_\theta, H_\theta \in \g$ such that $(E_\theta, H_\theta, F_\theta)$ is an $SL(2)$-triple with $F_\theta \in \s$,  which implies $H_\theta\in\k$.
+After conjugating by $K$ we may further assume $\sigma(E_\theta)=F_\theta$.
+Define 
+\begin{equation}\label{def_F_R}
+E_\R=\frac12(E_\theta-F_\theta-H_\theta)\quad
+F_\R=\frac12(-E_\theta+F_\theta-H_\theta).
+\end{equation}
+Then
+\begin{equation}
+\label{e:KS}
+\KS(K\cdot E_\theta)=G(\R)\cdot E_\R\quad\KS(K\cdot F_\theta)=G(\R)\cdot(-E_\R)
+\end{equation}
+
+We need the corresponding result in $\g^*$. As discussed in Section \ref{s:dual} this uses a choice of an isomorphism $\g\simeq \g^*$, but the result is independent of this choice.
+That is for $X\in \O_p\subset \g^*$ we have
+$$
+\KS(K\cdot X)=\psi_c(\KS(K\cdot \psi_c\inv(X)),
+$$
+independent of the choice of $\psi$.
+
+\subsubsection{A simple proof of Proposition~\ref{Sekiguchi_result}}\label{sec:sekiguchi_proof}
+
+Let us fix a generic discrete representation~$\pi$ and let $\lambda$ be its Harish-Chandra parameter.
+As in Section \ref{s:AV} we let $\kappa$ be the Killing form and write $\psi:\gder\simeq \gder^*$ for the corresponding isomorphism.
+
+Consider the principal nilpotent element~$F_\pi$ defined in~\eqref{e:Fpi}, so by Lemma \ref{l:AV} $\AV(\pi)=K\cdot \psi(F_\pi)$. 
+We use this as~$F_\theta$ in the previous subsection: define $E_\theta = \sum_{\alpha \in S(\lambda)}X_\alpha$ and $H_\theta  = [E_\theta, F_\theta]$; then $E_\theta \in \s$ and $(E_\theta, H_\theta, F_\theta)$ is an $\mathrm{SL}(2)$-triple.
+Define another $\mathrm{SL}(2)$-triple $(E_\R, F_\R, H_\R)$ by
+\[ \begin{aligned}
+  F_\R&=\frac12(-E_\theta+F_\theta-H_\theta)\\
+  E_\R&=\frac12(E_\theta-F_\theta-H_\theta)\\
+  H_\R&=E_\theta+F_\theta.
+\end{aligned}\]
+By the discussion in the previous section $\KS(K\cdot \psi(F_\theta))=\psi(\KS(K\cdot F_\theta))=\psi(G(\R)\cdot (-E_\R))=G(\R)\cdot \psi(-E_\R)$.
+We need to show this equals $\WF(\pi)$. By Corollary \ref{cor:matumoto} it is enough to show $\Wh(\pi)=\w_{\psi(-E-\R)}$; by 
+  by Lemma \ref{lem:Kost_and_AC} this is equivalent to $\K(\psi(-E_\R))$ meets $G(\R)\cdot\lambda$.
+
+We compute $\K(\psi(-E_\R))=\psi(\K(-E_\R))\ni -E_\R-F_\R=H_\theta$ (by \eqref{def_F_R}).
+Thus $\K(\psi(-E_\R))$ meets $\psi(H_\theta)$. 
+Since  $\Psi(H_{\theta})$ and $\lambda$ are in the same Weyl chamber, by Proposition \ref{prop:AC_chamber} we conclude 
+$\K(\psi(-E_\R))$ meets $\lambda$ as required.
+
+\subsubsection{A simple description of the wavefront set}\label{sec:alternate_WF}
+
+As we saw the correspondence $\pi \leftrightarrow \WF(\pi)$ can be described using the asymptotic cone of the semisimple orbit of the Harish-Chandra parameter.
+We used this in the proof of Proposition~\ref{Sekiguchi_result}.
+Now, the results of Sections~\ref{s:AV}, \ref{sec:concrete_sek} and~\ref{sec:sekiguchi_proof} provide another description of $\WF(\pi)$ from the Harish-Chandra parameter: we can compose the maps (1)$\leftrightarrow$(3)$\leftrightarrow$(4).
+This gives the following rather concrete conclusion.
+As in Section \ref{s:AV} we define $\psi:\gder\simeq \gder^*$ using the Killing form.
+
+\begin{lemma}\label{lem:explicit_WF}
+  Let $\pi$ be a generic discrete series representation. Fix a representative  $\lambda\in \t^*$ of the Harish-Chandra parameter of $\pi$.
+Define $F_\theta=F_\pi$ as in \eqref{e:Fpi}, and choose  $E_\theta$, $H_\theta$ such that $(H_\theta,E_\theta,F_\theta)$ is an $\mathrm{SL}(2)$-triple with $\sigma(E_\theta)=F_\theta$.  Then
+$$
+\WF(\pi)=G(\R)\cdot \psi(F_\R), \quad \text{where $F_\R = \frac i2(-E_\theta+F_\theta-H_\theta)\in\N\cap i\g(\R)$.}
+$$\end{lemma}
+There is a partial converse to this statement if we consider discrete series within a single $L$-packet.
+Fix an $L$-packet~$\Pi$ of discrete series, and consider a regular semisimple orbit~$\Omega$ in~$\Op \cap i\g(\R)^\ast$; then we can determine the generic representation~$\pi \in \Pi$ with $\WF(\pi)=\Omega$, as follows.
+Fix~$\xi_\R \in \Omega$, write $\xi_\R=F_\R^\ast$ with $F_\R \in \g$ and let $E_\R, H_\R \in \g$ be such that $(E_\R, H_\R, F_\R)$ is an  $\mathrm{SL}(2)$-triple with $\theta(E_\R)=-F_\R$.
+Set
+$$
+H_\theta=E_\R-F_\R.
+$$
+Then $H_\theta$ is a regular semisimple element, and belongs to~$\k$.
+Define a Cartan subalgebra~$\t$ of~$\g$ by $\t=\Cent_{\g}(H_\theta)$, and a set of positive roots by
+$$
+\Delta^+=\{\alpha\in\Delta(\t,\g)\mid  \alpha(H_\theta)>0\}.
+$$
+Then $\pi$ is the discrete series representation in $\Pi$ whose Harish-Chandra parameter is dominant for $\Delta^+$.
+
 \subsection{Appendix: $SL(2,\R)$ calculation}
 
-This is not for publication, just to make sure we have the formulas in Section \ref{sec:concrete_sek} correct.
-These are:
-$$
-E_\theta=\frac12(E_\R-F_\R+H_\R)\in \N\cap \s.
-$$
-and
-$$
-E_\R=\frac 12(E_\theta-F_\theta-H_\theta)\in\N\cap i\g(\R).
-$$
-
-Recall $\sigma(X)=\overline X$ and $\theta(X)=-X^t$.
-
-Take
+The  Lie algebra $\g(\R)$  of $G=SL(2,\R)$  is the space of $2\times 2$  matrices of trace~$0$.
+Let $\g=\sl(2,\C)$ be the complexified Lie algebra.
+Then $\g(\R)=\g(\C)^\sigma$ where $\sigma(X)=\overline X$. 
+Set $\theta(X)=X^t$, so $\g(\C)^\theta$  is the complexified Lie algebra of a maximal compact subgroup of $SL(2,\R)$.
+
+Define the following basis of $\g$:
 $$
@@
 Furthermore $E_\R,F_\R$ are in the $-1$-eigenspace of $\sigma$,
-and  we have $\theta(E_\R)=F_\R$ and $\theta(H_\R)=-H_\R$.
+$\theta(E_\R)=F_\R$ and $\theta(H_\R)=-H_\R$.
+
+It is helpful to keep in mind that $E_\R,F_\R$ are $G(\R)$-conjugate,
+and for $c\in \R^*$ $cE_\R$ is $G(\R)$-conjugate to $E_\R$ if and only if $c>0$.
 
@@
 $$
-
-These satisfy the standard $SL(2)$ commutation relations, and $E_\theta,F_\theta$ are in the $-1$-eigenspace of $\theta$.
-Also $\sigma(E_\theta)=F_\theta,\sigma(H_\theta)=-H_\theta$.
-
-Furthermore:
+These also satisfy the standard $SL(2)$ commutation relations; $E_\theta,F_\theta$ are in the $-1$-eigenspace of $\theta$; 
+and  $\sigma(E_\theta)=F_\theta,\sigma(H_\theta)=-H_\theta$.
+
+The change of bases are given by:
 $$
@@
 
-\subsection{The example of $\text{SL}_2$}
-
-We illustrate the constructions of the previous section the case of $G=\SL(2,\R)$.
-
-The complexified Lie algebra $\g$ is the space of $2\times 2$ complex matrices of trace~$0$. Let $\s(\C)=\{t_z\mid z\in\C\}\subset \g$ where
+Let $\t(\C)=\{t_z\mid z\in\C\}$ where
 $$
@@
 $$
-Then $\s(\R)=\{t_x\mid x\in\R\}$.
-
-For $z\in \C$ define $\lambda_z\in \s(\C)^*$ by $\lambda_z(t_x)=xz$.
+Then $\t(\R)=\{t_x\mid x\in\R\}$ is the Lie algebra of a compact Cartan subalgebra of $G$ (this is also a maximal compact subgroup).
+
+Define the dual basis
+ $\{E_\R^*,F_\R^*,H_\R^*\}$ of $\g^*$ as usual,  i.e. $E_\R^*(E_\R)=1$, $E_\R^*(F_\R)=E_\R^*(H_\R)=0$, etc. Define 
+ $\{E_\theta^*,F_\theta^*,H_\theta^*\}$ similarly.
+
+For $z\in \C$ define $\lambda_z\in \t(\C)^*$ by $\lambda_z(t_x)=xz$.
+Note that $t_i=-H_\theta$, $\lambda_z(t_i)=iz$ and $H_\theta^*(t_i)=-1$.
+Write $\lambda_z=cH_\theta^*$ for some $c$. Evaluating both sides on $t_i=-H_\theta$ gives
+$c=-iz$:
+\begin{equation}
+\label{e:lambdaz}
+\lambda_z=-izH_\theta^*.
+\end{equation}
+In particular
+\begin{equation}
+\label{e:lambdai}
+\lambda_{ik}=kH_\theta^*
+\end{equation}
+
 The positive root can be taken to be   $\alpha(t_z)=2iz$, i.e.
@@
 $$
-Also $\ch\rho=t_{-i/2}$
+
+Let $\pi(\lambda_{ik})$ be the discrete series representation with Harish-Chandra parameter $\lambda_{ik}$ $(k\in \Z_{\ne 0})$.
+
+\subsection{Identifying  $\g$ and $\g^*$}
+
+For $c\in \R^*$ define
+$$
+\kappa_c(X,Y)=c\mathrm{Tr}(XY)\quad (X,Y\in \g(\R)).
+$$
+This is a non-degenerate, $G(\R)$ invariant bilinear form on $\g(\R)$, and extends to a $\sigma$-invariant, $G(\C)$-invariant bilinear form on $\g$. 
+It is well known that every such form arises this way.
+The Killing form $\kappa$ is equal to $\kappa_4$, 
+as is checked by computing  $\mathrm{tr}(\ad(t_z)\ad(t_w))=-8zw$, and 
+ $\kappa_c(t_z,t_w)=-2czw$.
+
+Given $\kappa_c$ we obtain an isomorphism $\g(\R)\simeq \g(\R)^*$:
+$$
+\psi_c(X)(Y)=\kappa_c(X,Y)\quad (X,Y\in \g(\R))
+$$
+and this extends to an isomorphism $\psi_c: \g\rightarrow \g^*$.
+
+Explicitly we compute
+$$
+\psi_c(H_\R)(H_\R)=2c, \psi_c(H_\R)(E_\R)= \psi_c(H_\R)(F_\R)=0
+$$
+so  $\psi_c(H_\R)=2cH_\R^*$.
+The result is
+\begin{equation}
+\label{e:psic1}
+\begin{aligned}
+\psi_c(H_\R)&=2cH_\R^*\\
+\psi_c(E_\R)&=cF_\R^*\\
+\psi_c(F_\R)&=cE_\R^*
+\end{aligned}
+\end{equation}
+Since we obtained the $\theta$ basis by conjugating, the formulas in this basis are the same:
+\begin{equation}
+\label{e:psic2}
+\begin{aligned}
+\psi_c(H_\theta)&=2cH_\theta^*\\
+\psi_c(E_\theta)&=cF_\theta^*\\
+\psi_c(F_\theta)&=cE_\theta^*
+\end{aligned}
+\end{equation}
+
+Recall that for $\mu\in \g^*$
+$$
+\AC(\mu)=\psi_c^{-1}(\AC(\psi_c(\mu)))
+$$
 and
 $$
-\ch\rho(-i)=t_{-\frac 12}=\begin{pmatrix}0&-\frac 12\\\frac 12&0
+\K(\mu)=\psi_c^{-1}(\K(\psi_c(\mu))),
+$$
+independent of $c$.
+
+\subsection{$\WF(\pi)$}
+
+Let's compute $\WF(\pi_{\lambda_{ik}})$ by  \cite{HarrisHeOlafsson}, which says:
+$$
+\WF(\pi(\lambda_{ik}))=\AC(G(\R)\cdot \lambda_{ik}).
+$$
+
+First let's compute $\AC(G(\R)\cdot kH_\theta)=\AC(G(\R)\cdot\begin{pmatrix}0&-ik\\ik&0
+\end{pmatrix})$ for $k\in \Z_{\ne 0}$.
+Here we're taking the real asymptotic cone; since $kH_\theta\in i\g(\R)$ this is a subset of $i\g(\R)$. 
+Taking the limit as $x\rightarrow \infty$ in 
+$$
+\begin{pmatrix}
+x&0\\0&\frac 1x
 \end{pmatrix}
-$$
-
-The Killing form satisfies
-$$
-\kappa(t_x,t_y)=-8xy.
-$$
-Define $H_{\lambda}\in \s(\C)$ so that $\kappa(H_\lambda,t_x)=\lambda(t_x)$. Then $H_\lambda=t_w$ for some $w$; so
-$$
-\kappa(H_{\lambda_z},t_x)=\lambda_z(t_x)=zx,\quad \kappa(t_w,t_x)=-8xw
-$$
-gives
-$$
-H_{\lambda_z}=t_{-\frac z8}.
-$$
-In particular
-$$
-H_{\pm \rho}=H_{\lambda_{\mp i}}=\begin{pmatrix}0&-\frac {\mp i}8\\\frac {\mp i}8&0
+\begin{pmatrix}0&-ik\\ik&0
+\end{pmatrix}\begin{pmatrix}
+\frac 1x&0\\0&x
+\end{pmatrix}=
+\begin{pmatrix}0&-ikx^2\\\frac{ik}{x^2}&0
 \end{pmatrix}
 $$
-Let $\pi(\lambda_{ik})$ be the discrete series representation with Harish-Chandra parameter $\lambda_{ik}$ $(k\in \Z_{\ne 0})$, so
-$$
-H_{\pi(\lambda_{ik})}=H_{\lambda_{ik}}=
-\begin{pmatrix}0&-\frac{ik}8\\\frac{ik}8&0
-\end{pmatrix}.
-$$
-For an $SL(2)$-triple we can take $\{X_\alpha,X_{-\alpha},t_{-i}\}$ where
-$$
-X_\alpha=\frac12\begin{pmatrix}1&i\\i&-1
-\end{pmatrix}, \quad X_{-\alpha}=\overline{X_\alpha}, \quad t_{-i}=\begin{pmatrix}0&-i\\i&0
-\end{pmatrix}.
+we see
+$$
+\AC(G(\R)\cdot kH_\theta)=-G(\R)\cdot\sgn(k)E_\R.
+$$
+
+Now we carry out this computation over to $i\g(\R)^*$:
+$$
+\begin{aligned}
+\AC(G(\R)\cdot\lambda_{ik})&=\AC(G(\R)\cdot kH_\theta^*)\\
+&=\psi_c(\AC(G(\R)\cdot \psi_c\inv(kH_\theta^*))\\
+&=\psi_c(-G(\R)\cdot\sgn(\frac k{2c})E_\R)\\
+&=-G(\R)\cdot\sgn(\frac k{2c})cF_\R^*\\
+&=-G(\R)\cdot\sgn(k)F_\R^*\\
+&=G(\R)\cdot(-\sgn(k)E_\R^*)\\
+\end{aligned}
+$$
+Note that $c$ canceled as expected.
+In the last line we've used that $E_\R^*,F_\R^*$ are $G(\R)$-conjugate.
+
+Therefore by 
+\cite{HarrisHeOlafsson} we have
+\begin{equation}
+\label{e:WF}
+\WF(\pi(\lambda_{ik}))=G(\R)\cdot (-\sgn(k)E_\R^*).
+\end{equation}
+In particular note that $\WF(\pi_{ik})=\WF(\pi_{i\ell})\Leftrightarrow \sgn(k)=\sgn(\ell)$.
+We also conclude
+$$
+\Wh(\pi(\lambda_{ik}))=\w_X\Leftrightarrow X\sim_{G(\R)} -\sgn(k)E_\R^*.
+$$
+
+\subsection{$\AV(\pi(\lambda_{ik}))$}
+
+We apply Lemma \ref{l:AV}. It is easy to see
+$$
+F_{\pi(\lambda_{ik})}=
+\begin{cases} F_\theta&k>0\\
+  E_\theta&k<0
+\end{cases}
+$$
+Recall (Section \ref{s:AV}) $\psi$ is defined using the Killing form $\kappa_4$, which satisfies
+$\psi(F_\theta)=4E^*_\theta, \psi(E_\theta)=4F^*_\theta$. 
+Therefore
+\begin{equation}
+  \label{e:AV}
+\AV(\pi(\lambda_{ik}))=
+\begin{cases}K\cdot E_\theta^*&k>0\\
+  K\cdot F_\theta^*&k<0\\
+\end{cases}
+\end{equation}
+
+Let's check Proposition \ref{Sekiguchi_result} in this case.
+Suppose $\pi=\pi(\lambda_{ik})$. First assume $k>0$ and compute
+$$
+\begin{aligned}
+\KS(\AV(\pi))&=  \KS(K\cdot E_\theta^*)\quad \text{by \eqref{e:AV}}\\
+&=  \psi_c(\KS(K\cdot \psi_c\inv (E_\theta^*)))\\
+  &=  \psi_c(\KS(K\cdot \frac 1c F_\theta))\\
+&=\psi_C(G(\R)\cdot \frac 1c(-E_\R))\quad\text{(by \eqref{e:KS})}\\
+&=  G(\R)\cdot \psi_c(\frac{-1}c F_\R))\\
+&=G(\R)\cdot (-E_\R^*)\\
+&=\WF(\pi)\quad \text{(by \ref{e:WF})}
+\end{aligned}
+$$
+which agrees with 
+Proposition \ref{Sekiguchi_result}.
+
+Next, let's check Proposition \ref{p:Kostant}, 
+which says $\Wh(\pi)=\w_X\Leftrightarrow \K(X)\cap\O_\pi\ne \emptyset$. 
+Assume $k>0$. Then 
+$$
+\Wh(\pi(\lambda_{ik}))=G(\R)\cdot(-E_\R^*).
+$$
+So we compute
+$$
+\begin{aligned}
+\K(-E_\R^*)&=\psi_c(\K(\psi_c\inv(-E_\R^*)))\\
+&=\psi_c(\K( -\frac 1cF_\R))\\
+&\ni \psi_c\frac 1c(-F_\R-E_\R)\\
+&=\psi_c(\frac 1cH_\theta)=2H_\theta^*
+\end{aligned}
 $$
@@
 $$
-[t_z,X_\alpha]=\alpha(t_z)X_\alpha=\lambda_{2i}(t_z)X_\alpha=2izX_\alpha.
-$$
-In particular
-$$
-[t_{-i},X_\alpha]=2X_\alpha.
-$$
-
-Let's compute $\AV(\pi(\lambda_{ik}))$ using  \eqref{e:Fpi}.
-Suppose $k>0$. Then $\langle \lambda_{ik},\ch\alpha\rangle=k$, so $\Delta^+=\{\alpha\}$, and
-$F_{\pi_{ik}}=X_{-\alpha}$. 
-By \eqref{e:Fpi} $\AV(\pi_{ik})$ is the $K$-orbit of $X_{-\alpha}^\ast$.
-Thus in general
-$$
-\AV(\pi_{ik})=K\cdot X^*_{-\sgn(k)\alpha}
-$$
-Note: this only uses \eqref{e:Fpi}, which comes directly from \cite{AV1}.
-
-Conjugating $H_{\pi(\lambda_{ik})}$ by $\mathrm{diag}(x,\frac 1x)$ takes it to
-$\begin{pmatrix}0&-x^2\frac{ik}8\\\frac{ik}{x^2}&0
-\end{pmatrix}$,
-and taking the limit we see
-$$
-\WF(\pi(\lambda_{ik}))=\AC(G(\R)\cdot H_{\pi(\lambda_{ik})})=
-G(\R)\cdot \begin{pmatrix}0&-\sgn(k)i\\0&0
-\end{pmatrix}
-$$
-Note: this only uses  \cite{HarrisHeOlafsson}.
-
-Note that the $G(\R)$ orbit of $\begin{pmatrix}0&i\\0&0
-\end{pmatrix}$ contains $\begin{pmatrix}0&i\R^+\\0&0
-\end{pmatrix}$,
-so in particular $G(\R)\cdot \begin{pmatrix}0&ix\\0&0
-\end{pmatrix}=G(\R)\cdot \begin{pmatrix}0&iy\\0&0
-\end{pmatrix}$ if and only if $\sgn(x)=\sgn(y)$.
-In particular
-$$
-\WF(\pi_{ik})=\WF(\pi_{i\ell})\Leftrightarrow \sgn(k)=\sgn(\ell).
-$$
-
-Finally let's compute $\Wh(\pi_{\lambda_{ik}})$ in two ways.
-First of all by Lemma \ref{lem:matumoto}, which comes directly from \cite[Theorem A]{matumoto}:
-$$
-\Wh(\pi_{\lambda_{ik}})=\WF(\pi_{\lambda_{ik}})=G(\R)\cdot \begin{pmatrix}0&-\sgn(k)i\\0&0
-\end{pmatrix}.
-$$
-
-Alternatively we apply Proposition \ref{JeffTasho_criterion}, which comes from 
-\cite{adams_kaletha}. Note that
-
-$$
-\O_{\pi_{\lambda_{ik}}}=G(\R)\cdot H_{\lambda_{ik}}=G(\R)\cdot \begin{pmatrix}0&-\frac{ik}8\\\frac{ik}8&0
-\end{pmatrix}.
-$$
-On the other hand
-$$
-\K
-\begin{pmatrix}0&\pm i\\0&0
-\end{pmatrix}=\{\begin{pmatrix}0&\pm i\\z&0
-\end{pmatrix}\mid z\in\C\}
-$$
-so, with $\epsilon=\pm 1$, 
-$$
-H_{\lambda_{ik}}\in \K\begin{pmatrix}0&\epsilon i\\0&0
-\end{pmatrix}\Leftrightarrow \epsilon=\sgn(k).
-$$
-
-By Proposition \ref{JeffTasho_criterion}
-we conclude (again) that
-$$
-\Wh(\pi_{\lambda_{ik}})=G(\R)\cdot\begin{pmatrix}0&-\sgn(k)i\\0&0
-\end{pmatrix}.
-$$
-Alexandre: the proof of Proposition~\ref{JeffTasho_criterion} uses Lemma~\ref{lem:matumoto}.
+\K(-E_\R^*)\cap G(\R)\cdot 2H_{\theta}^*\ne\emptyset
+$$
 

### 2024-09-10 whittaker.tex
some proofreading

@@
 
-We need to pass to the dual Lie algebra $\g^*$.
+We need to pass to the dual Lie algebra $\g^*$, and it is important to do this as canonically as possible, i.e. independent of a choice
+of isomorphism $\g\simeq\g^*$. First we define the nilpotent cone in $\g^*$ as follows. 
 We say an element of $\g^*$ is nilpotent if its $G$-orbit is a (weak) cone, i.e. closed under multiplication by $\C^*$,
 and \emph{regular} if $\dim_{\Cent(G)}(X)=\mathrm{rank}(G)$.
-The principal nilpotent orbit $\O_p\in \g^*$ is the set of regular nilpotent elements.
-
-The statements of the main results do not require the choice of an isomorphism $\g\simeq \g^*$.
-In several places we do need to make such a choice;
-with the exception of (?) this choice will not matter.
-
-So we fix a non-degenerate, $G(\R)$-invariant bilinear form $\kappa$ on $\g(\R)$. This is equivalent to having a non-degenerate, $G(\C)$ and Galois invariant
+Let $\N^*$ be the set of nilpotent elements.
+The principal nilpotent orbit $\O_p\in \N^*$ is the set of regular nilpotent elements, and $\overline{\O_p}=\N^*$.
+
+The statements of the main results do not require the choice of an isomorphism $\g\simeq \g^*$. However such a choice appears in the proofs so we spell this out.
+Having a $G(\R)$-invariant bilinear form on $\g(\R)$ is equivalent to having a $G(\R)$-equivariant isomorphism $\g(\R)\simeq \g^*(\R)$. 
+Suppose we fix a non-degenerate, $G(\R)$-invariant bilinear form $\kappa$ on $\g(\R)$. This is equivalent to having a non-degenerate, $G(\C)$ and Galois invariant
 bilinear form on $\g$. The restriction of the form each simple factor
@@
 Using $\psi_\kappa$ we transfer the asymptotic cone, Kostant section, and Kostant Sekiguchi corresondence to $\g^*$. In each case these constructions are independent of the
-choice of $\kappa$. See (?).
-
+choice of $\kappa$. See Section \ref{sec:Sekiguchi}.
 In Section \ref{s:AV} we need to be more precise: we choose  $\kappa$ to be the Killing form. (More generally, we could take any non-degenerate
@@
 
-It is well known that a natural bijection between nilpotent $G(\R)$-orbits on $\g(\R)$ and nilpotent $K$ orbits on $\s$. 
+It is well known that there is a natural bijection between nilpotent $G(\R)$-orbits on $\g(\R)$ and nilpotent $K$ orbits on $\s$. 
 This is the Kostant--Sekiguchi
@@
 Schmid and Vilonen (the main result of~\cite{SV1}) that the wavefront
-set and the associated variety are exchanged by this
+set and the associated variety are related by this
 correspondence. (As a historical aside, the Kostant--Sekiguchi
@@
 $$
-In other words the bijection (3)--(4) is induced by the Kostant--Sekiguchi correspondence.
 \end{proposition}
@@
 By the discussion in the previous section $\KS(K\cdot \psi(F_\theta))=\psi(\KS(K\cdot F_\theta))=\psi(G(\R)\cdot (-E_\R))=G(\R)\cdot \psi(-E_\R)$.
-We need to show this equals $\WF(\pi)$. By Corollary \ref{cor:matumoto} it is enough to show $\Wh(\pi)=\w_{\psi(-E-\R)}$; by 
+We need to show this equals $\WF(\pi)$. By Corollary \ref{cor:matumoto} it is enough to show $\Wh(\pi)=\w_{\psi(-E_
+  \R)}$; by 
   by Lemma \ref{lem:Kost_and_AC} this is equivalent to $\K(\psi(-E_\R))$ meets $G(\R)\cdot\lambda$.
@@
 Thus $\K(\psi(-E_\R))$ meets $\psi(H_\theta)$. 
-Since  $\Psi(H_{\theta})$ and $\lambda$ are in the same Weyl chamber, by Proposition \ref{prop:AC_chamber} we conclude 
+Since  $\psi(H_{\theta})$ and $\lambda$ are in the same Weyl chamber, by Proposition \ref{prop:AC_chamber} we conclude 
 $\K(\psi(-E_\R))$ meets $\lambda$ as required.
@@
 \subsection{Appendix: $SL(2,\R)$ calculation}
+
+We illustrate these results with the illustrative example of $SL(2,\R)$,.
 
@@
 
-Let's check Proposition \ref{Sekiguchi_result} in this case.
+Let's check Proposition \ref{Sekiguchi_result} in this case, which says $\KS(\AV(\pi))=\WF(\pi)$.
 Suppose $\pi=\pi(\lambda_{ik})$. First assume $k>0$ and compute
@@
   &=  \psi_c(\KS(K\cdot \frac 1c F_\theta))\\
-&=\psi_C(G(\R)\cdot \frac 1c(-E_\R))\quad\text{(by \eqref{e:KS})}\\
+&=\psi_c(G(\R)\cdot \frac 1c(-E_\R))\quad\text{(by \eqref{e:KS})}\\
 &=  G(\R)\cdot \psi_c(\frac{-1}c F_\R))\\
@@
 which agrees with 
+Proposition \ref{Sekiguchi_result}. If $k<0$ replace $E_\theta^*$ with $F_\theta^*$, and conclude $\KS(\AV(\pi))=G(\R)\cdot E_\R^*$, in accordance with
 Proposition \ref{Sekiguchi_result}.
@@
 $$
-\K(-E_\R^*)\cap G(\R)\cdot 2H_{\theta}^*\ne\emptyset
-$$
+\K(-E_\R^*)\cap G(\R)\cdot 2H_{\theta}^*\ne\emptyset\quad (k<0).
+$$
+The case $k<0$ is similar; we conclude
+$\Wh(\pi_{\lambda_ik})=G(\R)E_\R^*$, and $\K(E_\R^*)\cap G(\R)\cdot (-2H_\theta)\ne \emptyset$.
 

### 2024-09-18 whittaker.tex
More proofreading

@@
 \newcommand{\AV}{\mathrm{AV}}
-\newcommand{\KS}{\mathcal{KS}}
+\newcommand{\KS}{\mathrm{KS}}
 \newcommand{\Wh}{\mathrm{Wh}}
@@
 This condition only depends on the conjugacy class of the pair, 
-so we  consider pairs $(B,\eta)$ modulo conjugation by $G(\R)$, and refer to such a conjugacy class as a 
+so we  consider pairs $(B,\eta)$ modulo conjugation by $G(\R)$, and refer to such a conjugacy class
 as a {\it Whittaker datum}.
@@
 a useful invariant of generic representations.
-For instance if $\Pi$ is a tempered $L$-packet for $G(\R)$ and $\w$ is a Whittaker datum, then $\Pi$ contains a unique representation $\pi$
+For instance, in the local Langlands correspondence, if $\Pi$ is a tempered $L$-packet for $G(\R)$ and $\w$ is a Whittaker datum, then $\Pi$ contains a unique representation
 having a $\w$-Whittaker model. This plays a role in describing the internal structure of $L$-packets.
@@
 irreducible representation $\pi$.  We will be concerned with two of
-them, defined very differently. The first is the \emph{wavefront set} $\WF(\pi)$
+them, defined very differently. The first is the \emph{wavefront set} $\WF(\pi)$,
 which is an analytic invariant.
@@
 Let~$\sigma$ be the anti-holomorphic involution defining~$G(\R)$.
-Let $\g=\Lie(G), \g(\R)=\Lie(G(\R))$. 
+Set $\g=\Lie(G)$ and $\g(\R)=\Lie(G(\R))$. 
 Choose a Cartan involution $\theta$ for $G$. This means:
 $\theta$ is an algebraic involution, commuting with~$\sigma$,
-and $G(\R)^\theta$ is a maximal compact subgroup of~$G(\R)$. Set $K=G^\theta$, $K(\R)=G(\R)^\theta=K^\sigma$.
-Let $\s$ be the $-1$ eigenspace of $\theta$ acting on~$\g$
-(we use the same notation for $\sigma,\theta$ lifted to $\g$).
+and $G(\R)^\theta$ is a maximal compact subgroup of~$G(\R)$. Set $K=G^\theta$ and $K(\R)=G(\R)^\theta=K^\sigma$.
+Let $\s$ be the $-1$ eigenspace of $\theta$ acting on~$\g$, where we use the notation $\sigma, \theta$ also for the automorphisms of~$\g$ induced by the above involutions.
 
@@
 \label{s:dual}
-Let $\N$ be the set of nilpotent elements of $\g$.
-
-We need to pass to the dual Lie algebra $\g^*$, and it is important to do this as canonically as possible, i.e. independent of a choice
-of isomorphism $\g\simeq\g^*$. First we define the nilpotent cone in $\g^*$ as follows. 
-We say an element of $\g^*$ is nilpotent if its $G$-orbit is a (weak) cone, i.e. closed under multiplication by $\C^*$,
+Let $\N$ be the set of nilpotent elements of $\g$. Several of the invariants below are related to~$\N$, but are more naturally defined as subsets of the dual vector space~$\g^\ast$.
+Therefore we need to pass to the dual Lie algebra $\g^*$, and it is important to do this as canonically as possible, i.e. in a manner as independent as possible of a choice
+of isomorphism $\g\simeq\g^*$.
+
+First we define the nilpotent cone in $\g^*$ as follows. 
+We say an element of~$\g^*$ is \emph{nilpotent} if its $G$-orbit is a (weak) cone, i.e. closed under multiplication by~$\C^*$,
 and \emph{regular} if $\dim_{\Cent(G)}(X)=\mathrm{rank}(G)$.
@@
 
-The statements of the main results do not require the choice of an isomorphism $\g\simeq \g^*$. However such a choice appears in the proofs so we spell this out.
+The statements of the main results below do not require the choice of an isomorphism $\g\simeq \g^*$. However such a choice appears in the proofs, so we spell this out.
 Having a $G(\R)$-invariant bilinear form on $\g(\R)$ is equivalent to having a $G(\R)$-equivariant isomorphism $\g(\R)\simeq \g^*(\R)$. 
-Suppose we fix a non-degenerate, $G(\R)$-invariant bilinear form $\kappa$ on $\g(\R)$. This is equivalent to having a non-degenerate, $G(\C)$ and Galois invariant
-bilinear form on $\g$. The restriction of the form each simple factor
-is unique up to a non-zero constant. For example we can use the Killing form on $\gder$, extended arbitrarily by a non-degenerate form on the center.
-
-Given $\kappa$ we define
+Suppose we fix a non-degenerate, $G(\R)$-invariant bilinear form $\kappa$ on $\g(\R)$.
+This is equivalent to having a non-degenerate bilinear form on~$\g$ which is both $G(\C)$- and Galois-invariant.
+The restriction of the form to each simple factor
+is unique up to a nonzero constant. For example we can use the Killing form on $\gder=[\g, \g]$, extended arbitrarily by a non-degenerate form on the center.
+
+Given such a non-degenerate bilinear form $\kappa$, we define
 $\psi_\kappa: \g\rightarrow \g^*$ as usual:
@@
 
-Using $\psi_\kappa$ we transfer the asymptotic cone, Kostant section, and Kostant Sekiguchi corresondence to $\g^*$. In each case these constructions are independent of the
-choice of $\kappa$. See Section \ref{sec:Sekiguchi}.
-In Section \ref{s:AV} we need to be more precise: we choose  $\kappa$ to be the Killing form. (More generally, we could take any non-degenerate
+Using $\psi_\kappa$ we shall transfer to $\g^\ast$ several notions usually defined on $\g$: the asymptotic cone, the Kostant section, and the Kostant--Sekiguchi corresondence.
+In each case the resulting notions are independent of the
+choice of $\kappa$. See Section~\ref{sec:Sekiguchi}.
+In Section~\ref{s:AV} we need to be more precise: we choose  $\kappa$ to be the Killing form. (More generally, we could take any non-degenerate
 invariant form which is negative definite on the Lie algebra of a maximal compact subgroup.)
@@
 This is a subset of $\N^*\subset\g^*$, and is the closure of a single complex nilpotent orbit: see \cite[Section 1, Theorem 4.7]{vogan_bowdoin}.
+Both $\AV(\pi)$ and $\AVann(\pi)$ depend only on the equivalence class of~$\pi$.
 
@@
 The set~$\WF(\pi)$  is a closed $G(\R)$-invariant subset of the nilpotent cone in
-$i\g(\R)^*$. As such it is the union of a finite number of nilpotent $G(\R)$-orbits.
+$i\g(\R)^*$. As such it is the union of a finite number of nilpotent $G(\R)$-orbits. Again, this depends only on the equivalence class of~$\pi$.
 
@@
 Suppose again that $\pi$ is an irreducible admissible representation of $G(\R)$ on a Hilbert space $\mH$.
-We consider the attached representations of~$\pi$ on the space $\mH^\infty$ of smooth vectors in $\mH$, and on its dual $\mH^{-\infty}$.
+We consider the corresponding actions of $G(\R)$ on the space~$\mH^\infty$ of smooth vectors in $\mH$, and on its dual $\mH^{-\infty}$; and we still denote them by~$\pi$.
 Let~$(B, \eta)$ be a pair satisfying conditions (i)-(ii) of the Introduction.
 We say $\pi$ has a $(B,\eta)$-Whittaker model
-if there exists a nonzero element $v$ in $\mH^{-\infty}$ such that $\pi(n)(v)=\eta(n)v$ for all $n$ in the nilradical $N(\R)$ of $B(\R)$.
-See \cite{matumoto}.
+if there exists a nonzero element $v$ in~$\mH^{-\infty}$ such that $\pi(n)(v)=\eta(n)v$ for all $n$ in the nilradical $N(\R)$ of $B(\R)$.
+See~\cite{matumoto}.
 If~$\w$ is the corresponding Whittaker datum, i.e.
@@
   \begin{enumerate}
-  \item $\pi$ is large;
-        \item $\pi$ is generic.
-\item $\AVann(\pi)=\N^*=\overline{\Op}$;
-\item $\dim(\AVann(\pi))=N$;
-  \item $\dim(\AV(\pi))=N/2$;
-  \item $\GK(\pi)=N/2$;
+  \item $\pi$ is large\textup{;}
+        \item $\pi$ is generic\textup{;}
+\item $\AVann(\pi)=\N^*=\overline{\Op}$\textup{;}
+\item $\dim(\AVann(\pi))=N$\textup{;}
+  \item $\dim(\AV(\pi))=N/2$\textup{;}
+  \item $\GK(\pi)=N/2$.
 \end{enumerate}
@@
 Then any discrete series representation of~$G(\R)$ has a \emph{Harish-Chandra parameter}, which is an element of~$\Lambda/W_K$.
-In fact, suppose~$\lambda$ is an element of~$\Lambda$ and $\zeta$ is a character of the center~$Z(\R)$ of~$G(\R)$ whose differential agrees with~$\lambda-\rho$ on the intersection $T(\R) \cap Z(\R)$; then the pair $(\lambda, \zeta)$  determines a discrete series representation~$\pi_{\lambda, \zeta}$ of~$G(\R)$.
+In fact, suppose~$\lambda$ is an element of~$\Lambda$ and suppose $\zeta$ is a character of the center~$Z(\R)$ of~$G(\R)$ whose differential agrees with~$\lambda-\rho$ on the intersection $T(\R) \cap Z(\R)$; then the pair $(\lambda, \zeta)$  determines a discrete series representation~$\pi_{\lambda, \zeta}$ of~$G(\R)$.
 Every discrete series representation arises in this way, and $\pi_{\lambda, \zeta}=\pi_{\lambda', \zeta'}$ if and only if $\zeta=\zeta'$ and $\lambda, \lambda'$ are $W_K$-conjugate.
@@
 \begin{proposition} \label{invariants_ds}
-  Suppose $\pi$ is a generic discrete series representation of $G(\R)$. Then:
+  Suppose $\pi$ is a generic discrete series representation of $G(\R)$. Then\textup{:}
 \begin{enumerate}[(a)]
-\item $\Wh(\pi)$ is a single Whittaker datum;
-\item $\AV(\pi)$ is the closure of a single $K$-orbit on~$\mathcal{O}_p \cap \s^*$;
-\item  $\WF(\pi)$ is the closure of a single $G(\R)$-orbit on $\mathcal{O}_p \cap  i \g(\R)^*$.
+\item $\Wh(\pi)$ is a single Whittaker datum\textup{;}
+\item $\AV(\pi)$ is the closure of a single $K$-orbit on~$\mathcal{O}_p \cap \s^*$\textup{;}
+\item  $\WF(\pi)$ is the closure of a single $G(\R)$-orbit on $\mathcal{O}_p \cap  i \g(\R)^*$\textup{.}
 \end{enumerate}
@@
 Because of Proposition~\ref{invariants_ds} we will abuse notation slightly, as follows.
-If~$\pi$ is a generic discrete series representation of~$G(\R)$, we write $AV(\pi)=\O$ to indicate that $AV(\pi)$ is the closure of the $K$-orbit $\O\subset \s^*$.
-Similarly we write $\WF(\pi)=\O$ to indicate that $\WF(\pi)$ is the closure of the $G(\R)$-orbit $\O\subset i\g(\R)^*$.
+If~$\pi$ is a generic discrete series representation of~$G(\R)$ and~$\O$ is a $K$-orbit in~$\s^\ast$, we write $AV(\pi)=\O$ to indicate that $AV(\pi)$ is the closure of the $K$-orbit $\O$.
+Similarly, if $\O\subset i\g(\R)^*$ is a $G(\R)$-orbit, we write $\WF(\pi)=\O$ to indicate that $\WF(\pi)$ is the closure of~$\O$.
 
@@
 
-\begin{lemma} Suppose a group $Q$ acts on two sets $A, B$ and let $f\colon A \to B$ be a~$Q$-equivariant map. 
+\begin{lemma} Suppose a group $Q$ acts on two sets $A, B$ and let $f\colon A \to B$ be a $Q$-equivariant map. 
 \begin{itemize}
@@
 
-The adjoint action of $\Gad^\sigma$ on~$G(\R)$ induces an action on $G(\R)$-representations, which descends to an action of  $Q_\sigma(G)$ on equivalence class of $G(\R)$-reoresentations.
+The adjoint action of $\Gad^\sigma$ on~$G(\R)$ induces an action on $G(\R)$-representations, which descends to an action of  $Q_\sigma(G)$ on equivalence class of $G(\R)$-representations.
 If~$q$ is an element of~$Q_\sigma(G)$, we write $\pi \mapsto \pi^q$ for the action of~$q$ on equivalence classes of $G(\R)$-representations.
@@
 
-These two actions are intertwined by the isomorphism of Lemma~\ref{lem:iso_q}:
+These two actions are intertwined by the isomorphism of Lemma~\ref{lem:iso_q} (this follows immediately from the definitions of the actions and of that isomorphism):
 
@@
 Suppose $q\in Q_\sigma(G)$. 
-Then $(\pi^q)_K\simeq (\pi_K)^{\phi(g)}$.
+Then $(\pi^q)_K\simeq (\pi_K)^{\varphi(g)}$.
 \end{lemma}
-
-\begin{proof}
-Immediate from Lemma~\ref{lem:iso_q} and the definition of the actions.
-\end{proof}
 
@@
 and choose $X\in \omega,X'\in\omega'$. Then there exists $g\in G$ such that $\Ad(g)(X)=X'$. Since $X\in \g(\R)^*$ the condition $X'\in i\g(\R)^*$ 
-is $g\inv \sigma(g)\in \Stab_G(X)$.  Since $X$ is principal $\Stab_G(X)=ZU$ where $U$ is a unipotent group. 
-A standard fact is that $H^1(\sigma, U)=1$ \cite[Chap.~III, Proposition~6]{Serre_Galois}, and from this we see that, after multiplying $g$ on the right by an element of $u$, we can assume $g\inv \sigma(g)\in Z$.
+is $g\inv \sigma(g)\in \Stab_G(X)$.  Since $X$ is principal, we have $\Stab_G(X)=ZU$ where $U$ is a unipotent group. 
+A standard fact is that $H^1(\sigma, U)=1$ \cite[Chap.~III, Proposition~6]{Serre_Galois}, and from this we see that, after multiplying $g$ on the right by an element of $u$, we may assume $g\inv \sigma(g)\in Z$.
 This is equivalent to: the image of $g$ in $\Gad$ is in $\Gad(\R)$.
@@
 
-On the other hand $Q(G)$, realized as $Q_\theta(G)$ is a group of automorphisms of $(\g,K)$.
+On the other hand $Q(G)$, realized as $Q_\theta(G)$, is a group of automorphisms of $(\g,K)$.
 It induces actions on $\s^*$, $\Op$ and $\Op\cap\s^*$, and on $(\g,K)$-modules.
@@
 In this section only we need to  choose a particular an isomorphism $\gder\simeq \gder^*$.
-For this we let $\kappa$ be the killing form, and define $\psi:\gder\rightarrow \gder^*$ by
-$$
-\psi(X)(Y)=\kappa(X,Y)\quad (X,Y\in \gder).
+For this we let $\kappa$ be the killing form, and define $\psi_\kappa:\gder\rightarrow \gder^*$ by
+$$
+\psi_\kappa(X)(Y)=\kappa(X,Y)\quad (X,Y\in \gder).
 $$
@@
   \label{e:Fpi}
-  F_\pi=\sum_{\alpha\in S(\lambda)}X_{-\alpha}\in \N.
+  F_\pi=\sum_{\alpha\in S(\lambda)}X_{-\alpha}
 \end{equation}
-
-Then $F_\pi\in\s$ is a regular nilpotent element.
-Then 
-$$
-\AV(\pi)=K\cdot \psi(F_\pi).
+Then $F_\pi\in\s$ is a regular nilpotent element, belongs to~$\gder$, and satisfies: 
+$$
+\AV(\pi)=K\cdot \psi_\kappa(F_\pi).
 $$
@@
 
-For this see \cite{HarrisHeOlafsson}; in the special casea considered here, the result is due to Rossmann and can be extracted from \cite{RossmannPicard}, Theorems B and C. \qed
+For this see \cite{HarrisHeOlafsson}; in the special case considered here, the result is due to Rossmann and can be extracted from \cite{RossmannPicard}, Theorems B and C. \qed
 
@@
 
-The following discussion is taken directly from \cite[Section~3.1]{adams_kaletha}.
+The following discussion summarizes results from \cite[Section~3]{adams_kaletha}.
 
 Suppose $X\in i\g(\R)^*\subset \g^*$ is a regular nilpotent element (see Section \ref{s:dual}).
-Let $\overline{\mathfrak b}(\R)$ be the kernel of $X$. 
-The corresponding Borel subgroup $B$ is defined over $\R$.
+Let $\overline{\mathfrak b}(\R)$ be the kernel of $X$. This is the Lie algebra of~$\overline{B}(\R)$, where$\overline{B}$ is a Borel subgroup of~$G$ defined over $\R$.
 Choose an $\R$-Cartan subgroup $T$ of
-$\overline B$, and let $B$ be the corresponding opposite Borel
-subgroup (characterized by $B\cap \overline B=T$). 
+$\overline B$, and let~$B$ be the  Borel
+subgroup opposite to~$\overline{B}$, characterized by $B\cap \overline B=T$.
 Then $X$ defines a unitary
@@
 $$
-\K(X)=\psi(\K(\psi\inv(X))\quad (X\in \g^*)
-$$
-Since $\psi$ is unique on each simple factor up to non-zero scalar, it is easy to see this definition is independent of the choice of $\psi$. See \cite[Section 3.2]{adams_kaletha}.
+\K(X)=\psi(\K(\psi\inv(X))\quad (X\in \g^*).
+$$
+Since $\psi$ is unique on each simple factor up to a non-zero scalar, it is easy to see this definition is independent of the choice of $\psi$. See \cite[Section 3.2]{adams_kaletha}.
 
@@
 \label{lem:Kost_and_AC}
-Let $\mathcal{O}$ be a regular semisimple orbit and  let $X$ be a regular nilpotent element. Then $\Kostant{X}$ meets~$\mathcal{O}$ if and only if $X$ is in the asymptotic cone~$\AC(\mathcal{O})$. 
+Let $\mathcal{O} \subset i\g(\R)^\ast$ be a regular semisimple orbit and  let~$X \in \g^\ast$ be a regular nilpotent element.
+Then $\Kostant{X}$ meets~$\mathcal{O}$ if and only if $X$ is in the asymptotic cone~$\AC(\mathcal{O})$.
 \end{lemma}
@@
 
-The Proposition, Lemma and Lemma \ref{lem:WF_and_AC} give the following result,
-which is a special case of the main result of \cite{matumoto} (Theorem A).
+The two statements above, combined with Lemma \ref{lem:WF_and_AC}, give the following result,
+which is a special case of the main result of \cite{matumoto} (Theorem A):
 
@@
 
-Write $\O_H$ for the $G(\R)$-orbit of $H$.
+If~$H$ is an element of~$\g$, write $\O_H$ for the $G(\R)$-orbit of $H$.
 
@@
 
-\begin{proof}[proof of the  Proposition]
+\begin{proof}[Proof of the  Proposition]
 For any regular nilpotent orbit~$\Omega$ let $\ECom$  denote the set of $H \in \mathcal{C}$ such that $\AC(\mathcal{O}_H)$ contains $\Omega$; by Lemma~\ref{lem:AC_containment}  we know that   $\ECom$ is an open subset of~$\mathcal{C}$.
@@
 
-The second assertion is an immediate consequence of the first and Lemma \ref{lem:Kost_and_AC}
-
-\end{proof}
+This proves the first assertion in the Proposition; the second assertion follows from the first and Lemma~\ref{lem:Kost_and_AC}.\end{proof}
 
@@
 
-\subsection{$\AV(\pi)$ and $\WF(\pi)$: the Kostant--Sekiguchi correspondence } \label{sec:Sekiguchi}
+\subsection{$\AV$ and $\WF$: the Kostant--Sekiguchi correspondence } \label{sec:Sekiguchi}
 
@@
 This is the Kostant--Sekiguchi
-correspondence~\cite{sekiguchi}, which we write as $\KS(\O)$. It is a deep theorem of
+correspondence~\cite{sekiguchi}, which we write as $\O \mapsto \KS(\O)$. It is a deep theorem of
 Schmid and Vilonen (the main result of~\cite{SV1}) that the wavefront
@@
 
-We need the corresponding result in $\g^*$. As discussed in Section \ref{s:dual} this uses a choice of an isomorphism $\g\simeq \g^*$, but the result is independent of this choice.
+We need the corresponding result in $\g^*$. As discussed in Section \ref{s:dual} this uses a choice of an isomorphism $\psi\colon \g\to \g^*$, but the result is independent of this choice.
 That is for $X\in \O_p\subset \g^*$ we have
 $$
-\KS(K\cdot X)=\psi_c(\KS(K\cdot \psi_c\inv(X)),
+\KS(K\cdot X)=\psi(\KS(K\cdot \psi\inv(X)),
 $$
@@
 Let us fix a generic discrete representation~$\pi$ and let $\lambda$ be its Harish-Chandra parameter.
-As in Section \ref{s:AV} we let $\kappa$ be the Killing form and write $\psi:\gder\simeq \gder^*$ for the corresponding isomorphism.
-
-Consider the principal nilpotent element~$F_\pi$ defined in~\eqref{e:Fpi}, so by Lemma \ref{l:AV} $\AV(\pi)=K\cdot \psi(F_\pi)$. 
+As in Section \ref{s:AV} we let $\kappa$ be the Killing form and $\psi\colon\gder\to \gder^*$ be the corresponding isomorphism.
+
+Consider the principal nilpotent element~$F_\pi$ defined in~\eqref{e:Fpi}, so by Lemma~\ref{l:AV} $\AV(\pi)=K\cdot \psi(F_\pi)$. 
 We use this as~$F_\theta$ in the previous subsection: define $E_\theta = \sum_{\alpha \in S(\lambda)}X_\alpha$ and $H_\theta  = [E_\theta, F_\theta]$; then $E_\theta \in \s$ and $(E_\theta, H_\theta, F_\theta)$ is an $\mathrm{SL}(2)$-triple.
@@
   \R)}$; by 
-  by Lemma \ref{lem:Kost_and_AC} this is equivalent to $\K(\psi(-E_\R))$ meets $G(\R)\cdot\lambda$.
+   Lemma \ref{lem:Kost_and_AC} this is equivalent to $\K(\psi(-E_\R))$ meets $G(\R)\cdot\lambda$.
 
@@
 
-\subsection{Appendix: $SL(2,\R)$ calculation}
-
-We illustrate these results with the illustrative example of $SL(2,\R)$,.
+\section{Appendix: the case of $SL(2,\R)$}
+
+We illustrate the results of Section~\ref{sec:explicit} by making the case of $SL(2,\R)$ fully explicit.
+
+\subsection{Notation}
 
@@
 Let $\g=\sl(2,\C)$ be the complexified Lie algebra.
-Then $\g(\R)=\g(\C)^\sigma$ where $\sigma(X)=\overline X$. 
+Then $\g(\R)=\g(\C)^\sigma$ where $\sigma\colon X \to \overline X$ is complex conjugation. 
 Set $\theta(X)=X^t$, so $\g(\C)^\theta$  is the complexified Lie algebra of a maximal compact subgroup of $SL(2,\R)$.
 
-Define the following basis of $\g$:
+We begin by defining different bases of~$\g$. Start with the following basis:
 $$
@@
 $$
-These satisfy the standard $SL(2)$ commutation relations: 
+These elements satisfy the standard $SL(2)$ commutation relations: 
 \[ [E_\R, F_\R] = H_\R, \quad [H_\R, E_\R] = 2E_\R, \quad [H_\R, F_\R] = -2F_\R. \]
 
-Furthermore $E_\R,F_\R$ are in the $-1$-eigenspace of $\sigma$,
+Furthermore $E_\R,F_\R$ are in the $-1$-eigenspace of $\sigma$, and we have
 $\theta(E_\R)=F_\R$ and $\theta(H_\R)=-H_\R$.
@@
   F_\R&=\frac12(-E_\theta+F_\theta-H_\theta)\\
-  H_\R&=E_\theta+F_\theta
+  H_\R&=E_\theta+F_\theta.
 \end{aligned}
 $$
-
-Let $\t(\C)=\{t_z\mid z\in\C\}$ where
-$$
-t_z=\begin{pmatrix}0&z\\-z&0
-\end{pmatrix}.
-$$
-Then $\t(\R)=\{t_x\mid x\in\R\}$ is the Lie algebra of a compact Cartan subalgebra of $G$ (this is also a maximal compact subgroup).
 
@@
  $\{E_\theta^*,F_\theta^*,H_\theta^*\}$ similarly.
+
+\medskip
+
+We now introduce notation for tori and roots. Let $\t(\C)=\{t_z\mid z\in\C\}$ where
+$$
+t_z=\begin{pmatrix}0&z\\-z&0
+\end{pmatrix}.
+$$
+Then $\t(\R)=\{t_x\mid x\in\R\}$ is the Lie algebra of a compact Cartan subalgebra of $\g$ (the corresponding Cartan subgroup of~$G(\R)$ is also a maximal compact subgroup).
 
@@
 \end{equation}
-In particular
+In particular, for $k \in \Z$ we have
 \begin{equation}
 \label{e:lambdai}
-\lambda_{ik}=kH_\theta^*
+\lambda_{ik}=kH_\theta^*.
 \end{equation}
 
-The positive root can be taken to be   $\alpha(t_z)=2iz$, i.e.
-$\alpha=\lambda_{2i}$ so $\rho=\frac12\alpha=\lambda_i$.
-Note that $\alpha(\ch\alpha)=2$ gives
+The positive root can be taken to be   $\alpha\colon t_z \to 2iz$, i.e.
+$\alpha=\lambda_{2i}$; therefore $\rho=\frac12\alpha$ is~$\lambda_i$.
+Since the coroot~$\ch\alpha$ satisfies $\alpha(\ch\alpha)=2$, we have
 $$
@@
 $$
-i.e.
+therefore
 $$
@@
 $$
+for $k \in \Z$.
+
 Viewing $\ch\alpha$ as a map from $\C$ to $\ch{\mathfrak t}$ this says
@@
 \psi_c(E_\R)&=cF_\R^*\\
-\psi_c(F_\R)&=cE_\R^*
+\psi_c(F_\R)&=cE_\R^*.
 \end{aligned}
 \end{equation}
-Since we obtained the $\theta$ basis by conjugating, the formulas in this basis are the same:
+Since we obtained the ``$\theta$-basis" by conjugating, the formulas in this basis are the same:
 \begin{equation}
@@
 \psi_c(E_\theta)&=cF_\theta^*\\
-\psi_c(F_\theta)&=cE_\theta^*
+\psi_c(F_\theta)&=cE_\theta^*.
 \end{aligned}
@@
 
-Recall that for $\mu\in \g^*$
+Recall that for $\mu\in \g^*$, we have
 $$
@@
 
-\subsection{$\WF(\pi)$}
-
-Let's compute $\WF(\pi_{\lambda_{ik}})$ by  \cite{HarrisHeOlafsson}, which says:
+\subsection{Wave-front set}
+
+Suppose~$k \in \Z_{\neq 0}$. Let us compute $\WF(\pi_{\lambda_{ik}})$ by  \cite{HarrisHeOlafsson}, which says:
 $$
@@
 
-First let's compute $\AC(G(\R)\cdot kH_\theta)=\AC(G(\R)\cdot\begin{pmatrix}0&-ik\\ik&0
+First let us compute $\AC(G(\R)\cdot kH_\theta)=\AC(G(\R)\cdot\begin{pmatrix}0&-ik\\ik&0
 \end{pmatrix})$ for $k\in \Z_{\ne 0}$.
-Here we're taking the real asymptotic cone; since $kH_\theta\in i\g(\R)$ this is a subset of $i\g(\R)$. 
+Here we are taking the real asymptotic cone; since $kH_\theta\in i\g(\R)$ this is a subset of $i\g(\R)$. 
 Taking the limit as $x\rightarrow \infty$ in 
@@
 $$
-
 Now we carry out this computation over to $i\g(\R)^*$:
@@
 &=-G(\R)\cdot\sgn(k)F_\R^*\\
-&=G(\R)\cdot(-\sgn(k)E_\R^*)\\
+&=G(\R)\cdot(-\sgn(k)E_\R^*).
 \end{aligned}
 $$
-Note that $c$ canceled as expected.
-In the last line we've used that $E_\R^*,F_\R^*$ are $G(\R)$-conjugate.
+In the last line we used the fact that $E_\R^*,F_\R^*$ are $G(\R)$-conjugate.
+Note that $c$ disappeared from the end result, as expected.
 
@@
 
-\subsection{$\AV(\pi(\lambda_{ik}))$}
+\subsection{Associated variety}
 
@@
 F_{\pi(\lambda_{ik})}=
-\begin{cases} F_\theta&k>0\\
-  E_\theta&k<0
+\begin{cases} F_\theta&\text{ if $k>0$;}\\
+  E_\theta& \text{ if $k<0$.}
 \end{cases}
 $$
-Recall (Section \ref{s:AV}) $\psi$ is defined using the Killing form $\kappa_4$, which satisfies
+Recall that in Section \ref{s:AV} we use the isomorphism $\psi$ defined using the Killing form $\kappa_4$, which satisfies
 $\psi(F_\theta)=4E^*_\theta, \psi(E_\theta)=4F^*_\theta$. 
@@
 
-Let's check Proposition \ref{Sekiguchi_result} in this case, which says $\KS(\AV(\pi))=\WF(\pi)$.
+Let us see that this computation and that of the previous section agree with Proposition \ref{Sekiguchi_result}, which says $\KS(\AV(\pi))=\WF(\pi)$ in that case.
+
 Suppose $\pi=\pi(\lambda_{ik})$. First assume $k>0$ and compute
@@
 which agrees with 
-Proposition \ref{Sekiguchi_result}. If $k<0$ replace $E_\theta^*$ with $F_\theta^*$, and conclude $\KS(\AV(\pi))=G(\R)\cdot E_\R^*$, in accordance with
+Proposition \ref{Sekiguchi_result}. If $k<0$, replace $E_\theta^*$ with $F_\theta^*$, and conclude $\KS(\AV(\pi))=G(\R)\cdot E_\R^*$, in accordance with
 Proposition \ref{Sekiguchi_result}.
 
-Next, let's check Proposition \ref{p:Kostant}, 
+\subsection{Whittaker model}
+
+Finally, let us check Proposition \ref{p:Kostant}, 
 which says $\Wh(\pi)=\w_X\Leftrightarrow \K(X)\cap\O_\pi\ne \emptyset$. 
@@
 $$
-So we compute
+On the other hand, we can compute
 $$
@@
 \K(-E_\R^*)&=\psi_c(\K(\psi_c\inv(-E_\R^*)))\\
-&=\psi_c(\K( -\frac 1cF_\R))\\
-&\ni \psi_c\frac 1c(-F_\R-E_\R)\\
-&=\psi_c(\frac 1cH_\theta)=2H_\theta^*
-\end{aligned}
-$$
-That is 
-$$
-\K(-E_\R^*)\cap G(\R)\cdot 2H_{\theta}^*\ne\emptyset\quad (k<0).
-$$
-The case $k<0$ is similar; we conclude
+&=\psi_c(\K( -\frac 1cF_\R)).\end{aligned}$$
+This contains
+$$ \psi_c\left(\frac 1c(-F_\R-E_\R)\right)=\psi_c(\frac 1cH_\theta)=2H_\theta^*.
+$$
+So we do have
+$$
+\K(-E_\R^*)\cap G(\R)\cdot 2H_{\theta}^*\ne\emptyset\quad (k>0).
+$$
+The case $k<0$ is similar; in that case we conclude
 $\Wh(\pi_{\lambda_ik})=G(\R)E_\R^*$, and $\K(E_\R^*)\cap G(\R)\cdot (-2H_\theta)\ne \emptyset$.

### 2024-09-25 whittaker.tex
Fixing tiny typos

@@
 $$
-E_\R=\begin{pmatrix}0&i\\0&0\end{pmatrix},
-F_\R=\begin{pmatrix}0&0\\-i&0\end{pmatrix},
-H_\R=\begin{pmatrix}1&0\\0&-1\end{pmatrix}
+E_\R=\begin{pmatrix}0&i\\0&0\end{pmatrix},\quad 
+F_\R=\begin{pmatrix}0&0\\-i&0\end{pmatrix},\quad
+H_\R=\begin{pmatrix}1&0\\0&-1\end{pmatrix}.
 $$
@@
 $$
-E_\theta=\frac12\begin{pmatrix}1&i\\i&-1\end{pmatrix},
-F_\theta=\frac12\begin{pmatrix}1&-i\\-i&-1\end{pmatrix},
-H_\theta=\begin{pmatrix}0&-i\\i&0\end{pmatrix},
+E_\theta=\frac12\begin{pmatrix}1&i\\i&-1\end{pmatrix}, \quad
+F_\theta=\frac12\begin{pmatrix}1&-i\\-i&-1\end{pmatrix},\quad
+H_\theta=\begin{pmatrix}0&-i\\i&0\end{pmatrix}.
 $$
@@
 $$
-Now we carry out this computation over to $i\g(\R)^*$:
+Now we carry this computation over to $i\g(\R)^*$:
 $$
@@
 \AV(\pi(\lambda_{ik}))=
-\begin{cases}K\cdot E_\theta^*&k>0\\
-  K\cdot F_\theta^*&k<0\\
+\begin{cases}K\cdot E_\theta^*&k>0;\\
+  K\cdot F_\theta^*&k<0.\\
 \end{cases}
@@
 &=G(\R)\cdot (-E_\R^*)\\
-&=\WF(\pi)\quad \text{(by \ref{e:WF})}
+&=\WF(\pi)\quad \text{(by \eqref{e:WF})}
 \end{aligned}

### 2024-10-02 whittaker.tex
minor proofreading changes

@@
 \begin{enumerate}[(i)]
-\item $B$ is a Borel subgroup of~$G$ defined over~$\R$, with real points $B(\R)$,
+\item $B$ is a Borel subgroup of~$G$ defined over~$\R$,
 \item $\eta$ is a character of the nilpotent radical~$N(\R)$ of~$B(\R)$, subject to the condition that~$\eta$ is nontrivial on each simple root space.
@@
 defined  algebraically.
-Both consist of nilpotent elements of the dual of the Lie algebra of~$G$, and are defined as
-coadjoint orbits (of two different kinds).
+Both consist of nilpotent elements of the dual of the Lie algebra of~$G$.
 The invariants $\Wh(\pi), \WF(\pi)$ and $\AV(\pi)$ are closely related to each other.
@@
 Many results in this note are well known.
-We  tried to give new and simplified proofs for as many of them as we could; for instance, Section~\ref{sec:Sekiguchi} contains a simple proof that $\WF(\pi)$ and $\AV(\pi)$ are exchanged by the Kostant--Sekiguchi correspondence.
-Otherwise we tried to give convenient references.
+We give new and simplified proofs for as many of them as we could; for instance, Section~\ref{sec:Sekiguchi} contains a simple proof that $\WF(\pi)$ and $\AV(\pi)$ are exchanged by the Kostant--Sekiguchi correspondence.
+Otherwise we give convenient references.
 
@@
 Let $\N$ be the set of nilpotent elements of $\g$. Several of the invariants below are related to~$\N$, but are more naturally defined as subsets of the dual vector space~$\g^\ast$.
-Therefore we need to pass to the dual Lie algebra $\g^*$, and it is important to do this as canonically as possible, i.e. in a manner as independent as possible of a choice
+Therefore we need to pass to the dual Lie algebra $\g^*$, and it is important to do this as independently as possible of a choice
 of isomorphism $\g\simeq\g^*$.
@@
 In each case the resulting notions are independent of the
-choice of $\kappa$. See Section~\ref{sec:Sekiguchi}.
-In Section~\ref{s:AV} we need to be more precise: we choose  $\kappa$ to be the Killing form. (More generally, we could take any non-degenerate
+choice of $\kappa$. See Sections~\ref{s:gds} and \ref{sec:Sekiguchi}.
+In Section~\ref{s:AV} we need to be more precise: we choose  $\kappa$ to be the Killing form  (or any non-degenerate
 invariant form which is negative definite on the Lie algebra of a maximal compact subgroup.)
@@
 $(\g,K)$-module is on the space of $K$-finite vectors in
-$V$; we will denote it by~$\pi_K$ in this paper.
+$V$; we will denote it by~$\pi_K$.
 
@@
   set} $\WF(\pi)$ is an analytic invariant determined by the
-singularities of the global character of $\pi$ near the identity. See \cite{howe_wave_front, bv_local_structure, HarrisHeOlafsson} for the definition. 
+singularity of the global character of $\pi$ near the identity. See \cite{howe_wave_front, bv_local_structure, HarrisHeOlafsson} for the definition. 
 The set~$\WF(\pi)$  is a closed $G(\R)$-invariant subset of the nilpotent cone in
@@
 Suppose again that $\pi$ is an irreducible admissible representation of $G(\R)$ on a Hilbert space $\mH$.
-We consider the corresponding actions of $G(\R)$ on the space~$\mH^\infty$ of smooth vectors in $\mH$, and on its dual $\mH^{-\infty}$; and we still denote them by~$\pi$.
+We consider the corresponding actions of $G(\R)$ on the space~$\mH^\infty$ of smooth vectors in $\mH$, and on its dual $\mH^{-\infty}$.
 Let~$(B, \eta)$ be a pair satisfying conditions (i)-(ii) of the Introduction.
@@
 We now take~$A=G$, and continue to assume~$\tau$ is an involutive automorphism. Then the short exact sequence $1\rightarrow Z \rightarrow G \rightarrow \Gad\rightarrow 1$ 
-gives rise to a ``long" exact sequence of pointed sets:
+gives rise to a long exact sequence of pointed sets:
 \begin{equation} \label{long_ptset}
@@
 
+\qed
+
 %where $\varphi_{\sigma}$ and $\varphi_{\theta}$ are induced by the inclusion $Z \hookrightarrow G$.
@@
 \subsection{Whittaker data of generic discrete series}
+\label{s:gds}
 
@@
 Suppose $X\in i\g(\R)^*\subset \g^*$ is a regular nilpotent element (see Section \ref{s:dual}).
-Let $\overline{\mathfrak b}(\R)$ be the kernel of $X$. This is the Lie algebra of~$\overline{B}(\R)$, where$\overline{B}$ is a Borel subgroup of~$G$ defined over $\R$.
+Let $\overline{\mathfrak b}(\R)$ be the kernel of $X$. This is the Lie algebra of~$\overline{B}(\R)$, where
+$\overline{B}$ is an $\R$-Borel subgroup of~$G$.
 Choose an $\R$-Cartan subgroup $T$ of
@@
 \end{proposition}
-
-This confirms that  the corresponding statement  in the $p$-adic case \cite{debacker_reeder_generic, kaletha_epipelagic}
-applies to the real case as well.
 
@@
 
-We begin by defining different bases of~$\g$. Start with the following basis:
+We begin by defining two  bases of~$\g$. Start with the following basis:
 $$
@@
 
-First let us compute $\AC(G(\R)\cdot kH_\theta)=\AC(G(\R)\cdot\begin{pmatrix}0&-ik\\ik&0
+First we compute $\AC(G(\R)\cdot kH_\theta)=\AC(G(\R)\cdot\begin{pmatrix}0&-ik\\ik&0
 \end{pmatrix})$ for $k\in \Z_{\ne 0}$.

### 2024-10-02 whittaker.tex
almost finished

@@
 \begin{document}
+%Jeffrey Adams University of Maryland/IDA Center for Computing Sciences
+%jda@math.umd.edu
 \title{Nilpotent Invariants \\ for Generic Discrete Series of Real Groups}
@@
   \label{l:AV}
-Suppose $\pi$ is a generic discrete series representation with Harish-Chandra parameter $\lambda\in\t^*$.
+Suppose $\pi$ is a generic discrete series representation and $\lambda\in\t^*$ is a representative of its  Harish-Chandra parameter.
 Set
@@
 \label{c:same}
-Suppose $\pi$ is a generic discrete series representation with Harish-Chandra parameter $\lambda$.
-Then $\AV(\pi)$, $\WF(\pi)$ and $\Wh(\pi)$ only depend on the Weyl chamber of $\lambda$.
+Suppose $\pi,\pi'$ are generic discrete series representations. Let  $\lambda,\lambda'$ be representatives
+for the Harish-Chandra parameters of $\pi,\pi'$. If 
+$\lambda,\lambda'$ are in the same  Weyl chamber then
+$\pi,\pi'$ have the same associated variety, wave-front set, and Whittaker models.
 \end{corollary}
@@
 \begin{proof}
-If  $\mathscr{C}, \mathscr{C}'$ are in the same $W_K$-orbit, then the Harish-Chandra parameters of $\pi$, $\pi'$ have representatives in the same Weyl chamber; therefore $\Wh(\pi)=\Wh(\pi')$ by Corollary \ref{c:same}.
+If  $\mathscr{C}, \mathscr{C}'$ are in the same $W_K$-orbit, then the Harish-Chandra parameters of $\pi$, $\pi'$ have representatives in the same Weyl chamber; therefore $\Wh(\pi)=\Wh(\pi')$ by Corollary~\ref{c:same}.
 

### 2024-10-02 whittaker.tex
Affiliations and typography

@@
-%edited starting 8/27/17 for re-submission to Duke
 \documentclass[10pt,leqno]{article}
+
 \usepackage{verbatim}
@@
 \usepackage{mathtools}
-%\usepackage{amsrefs}
 \usepackage{rotating}
@@
 
-%\usepackage{showkeys}
 \usepackage{tabularx}
@@
 \begin{document}
-%Jeffrey Adams University of Maryland/IDA Center for Computing Sciences
-%jda@math.umd.edu
+
 \title{Nilpotent Invariants \\ for Generic Discrete Series of Real Groups}
-\author{Jeffrey Adams \& Alexandre Afgoustidis}
+\author{Jeffrey Adams\footnote{University of Maryland \& IDA Center for Computing Sciences ; \url{jda@math.umd.edu}} {} \& Alexandre Afgoustidis\footnote{CNRS \& Université de Lorraine, Nancy \& Metz ; \url{alexandre.afgoustidis@math.cnrs.fr}}}
+%\email{alexandre.afgoustidis@math.cnrs.fr}
+
 \maketitle
@@
 If $\Pi$ is a discrete series $L$-packet then each generic representation in the packet has a unique
-Whittaker model, so the generic representations in $\Pi$ are parametrized by their Whittaker models.
+Whittaker model, so the generic representations in~$\Pi$ are parametrized by their Whittaker models.
 It is conjectured that these properties hold in the $p$-adic case as well, and this is known in many cases.
@@
 Both consist of nilpotent elements of the dual of the Lie algebra of~$G$.
-The invariants $\Wh(\pi), \WF(\pi)$ and $\AV(\pi)$ are closely related to each other.
+The invariants $\Wh(\pi), \WF(\pi)$ and~$\AV(\pi)$ are closely related to each other.
 
@@
 and $G(\R)^\theta$ is a maximal compact subgroup of~$G(\R)$. Set $K=G^\theta$ and $K(\R)=G(\R)^\theta=K^\sigma$.
-Let $\s$ be the $-1$ eigenspace of $\theta$ acting on~$\g$, where we use the notation $\sigma, \theta$ also for the automorphisms of~$\g$ induced by the above involutions.
+Let $\s$ be the $(-1)$-eigenspace of $\theta$ acting on~$\g$, where we use the notation $\sigma, \theta$ also for the automorphisms of~$\g$ induced by the above involutions.
 
@@
 denoted $\AVann(\pi)$.
-This is a subset of $\N^*\subset\g^*$, and is the closure of a single complex nilpotent orbit: see \cite[Section 1, Theorem 4.7]{vogan_bowdoin}.
+This is a subset of $\N^*$ of~$\g^*$, and is the closure of a single complex nilpotent orbit: see \cite[Section 1, Theorem~4.7]{vogan_bowdoin}.
 Both $\AV(\pi)$ and $\AVann(\pi)$ depend only on the equivalence class of~$\pi$.
@@
 When~$A$ is a group and $\tau$ is an involutive automorphism of~$A$, consider the cohomology sets $H^0(\tau, A)$ and $H^1(\tau, A)$ attached to the action of $\Z/2\Z$ on~$A$ by~$\tau$.
-We shall view   $H^0(\tau, A)$ as the fixed-point-set $A^{\tau}$, and $H^1(\tau,A)$ as the quotient of $A^{-\tau} = \{ a \in A, \tau(a)=a^{-1}\}$ by the equivalence relation $a \sim x a \tau(x^{-1})$ for all $x \in A$.
+We shall view   $H^0(\tau, A)$ as the fixed-point-set $A^{\tau}$, and $H^1(\tau,A)$ as the quotient of \mbox{$A^{-\tau} = \{ a \in A, \tau(a)=a^{-1}\}$} by the equivalence relation $a \sim x a \tau(x^{-1})$ for all $x \in A$.
 The set $H^1(\tau, A)$ has a distinguished point $1$, coming from the identity of~$A$; but in general it is just a pointed set, and not a group if~$A$ is nonabelian.
@@
 
-Because of Lemmas~\ref{lem:iso_q} and \ref{lem:action_q}, we write $Q(G)$ for the group $Q_\sigma(G)$ or $Q_\theta(G)$, depending on the situation.
+Because of Lemmas~\ref{lem:iso_q} and \ref{lem:action_q}, we write $Q(G)$ for the group $Q_\sigma(G)$ or~$Q_\theta(G)$, depending on the situation.
 
@@
 
-In this section only we need to  choose a particular an isomorphism $\gder\simeq \gder^*$.
+In this section only we need to  choose a particular an isomorphism \mbox{$\gder\simeq \gder^*$}.
 For this we let $\kappa$ be the killing form, and define $\psi_\kappa:\gder\rightarrow \gder^*$ by
@@
 This follows from Lemma \ref{l:pi_to_av} for the associated variety;
-from Lemma \ref{lem:WF_and_AC} for the wave front set, and Lemma \ref{lem:Kost_and_AC} (or Corollary \ref{cor:matumoto})
+from Lemma~\ref{lem:WF_and_AC} and Proposition~\ref{prop:AC_chamber} for the wave front set, and Lemma \ref{lem:Kost_and_AC} (or Corollary \ref{cor:matumoto})
 for the Whittaker model.
@@
 
-Furthermore $E_\R,F_\R$ are in the $-1$-eigenspace of $\sigma$, and we have
+Furthermore $E_\R,F_\R$ are in the $(-1)$-eigenspace of $\sigma$, and we have
 $\theta(E_\R)=F_\R$ and $\theta(H_\R)=-H_\R$.
@@
 $$
-These also satisfy the standard $SL(2)$ commutation relations; $E_\theta,F_\theta$ are in the $-1$-eigenspace of $\theta$; 
+These also satisfy the standard $SL(2)$ commutation relations; $E_\theta,F_\theta$ are in the $(-1)$-eigenspace of $\theta$; 
 and  $\sigma(E_\theta)=F_\theta,\sigma(H_\theta)=-H_\theta$.

### 2024-10-04 whittaker.tex
Removed the date because arXiv adds one
Done?

@@
 \author{Jeffrey Adams\footnote{University of Maryland \& IDA Center for Computing Sciences ; \url{jda@math.umd.edu}} {} \& Alexandre Afgoustidis\footnote{CNRS \& Université de Lorraine, Nancy \& Metz ; \url{alexandre.afgoustidis@math.cnrs.fr}}}
-%\email{alexandre.afgoustidis@math.cnrs.fr}
+\date{}
 
@@
 
-By Lemma \ref{l:pi_to_av} the associated variety of a discrete representation only depends on the Weyl chamber of its Harish-Chandra parameter. 
+By Lemma \ref{l:pi_to_av} the associated variety of a discrete representation only depends on the $W_K$-orbit of any Weyl chamber containing a representative of its Harish-Chandra parameter. 
 The same holds for the wave front set and Whittaker data by Theorem \ref{th:main}. This can also be proved directly 
@@
 
-Now consider the set $\Sigma$ of all points on $\mathcal{S} \cap \mathcal{C}$ which arise as the radial projection of the Harish-Chandra parameter~$H$ of some generic discrete series representation.
-Since the Harish-Chandra parameters for discrete series are (a translate of) an integral lattice, the set $\Sigma$ is dense in $\mathcal{S} \cap \mathcal{C}$.
-Therefore if the open set $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$ is nonempty, there must exist at least one generic discrete series representation~$\pi$ whose Harish-Chandra projects to $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$.
+Now consider the set $\Sigma$ of all points on $\mathcal{S} \cap \mathcal{C}$ which arise as the radial projection of an element~$H$ corresponding to a representative in $\t^\ast$ for the Harish-Chandra parameter of some generic discrete series representation.
+Since the representatives for Harish-Chandra parameters of discrete series are (a translate of) an integral lattice, the set $\Sigma$ is dense in $\mathcal{S} \cap \mathcal{C}$.
+Therefore if the open set $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$ is nonempty, there must exist at least one generic discrete series representation~$\pi$ with a Harish-Chandra parameter representative which projects to $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$.
 By Lemma~\ref{lem:WF_and_AC} this means $\Omega$ and $\Omega'$ must be contained in $\WF(\pi)$, which implies $\Omega = \Omega'$ since the wavefront set is the closure of a single orbit if $\pi$ is a generic discrete series.
@@
 which says $\Wh(\pi)=\w_X\Leftrightarrow \K(X)\cap\O_\pi\ne \emptyset$. 
-Assume $k>0$. Then 
-$$
-\Wh(\pi(\lambda_{ik}))=G(\R)\cdot(-E_\R^*).
+Assume $k>0$. Then by~\eqref{e:WF} and Corollary~\ref{cor:matumoto} we have
+$$
+\Wh(\pi(\lambda_{ik}))=\mathfrak{w}_{-E_\R^*}.
 $$
@@
 The case $k<0$ is similar; in that case we conclude
-$\Wh(\pi_{\lambda_ik})=G(\R)E_\R^*$, and $\K(E_\R^*)\cap G(\R)\cdot (-2H_\theta)\ne \emptyset$.
+$\Wh(\pi_{\lambda_{ik}})=\mathfrak{w}_{E_\R^\ast}$, and $\K(E_\R^*)\cap G(\R)\cdot (-2H_\theta)\ne \emptyset$.
 

### 2025-02-18 whittaker_JIMJ.tex
Files for submission to Jussieu

--- 2024-10-04 whittaker.tex
@@
-\documentclass[10pt,leqno]{article}
-
-\usepackage{verbatim}
-\usepackage{amssymb, amscd}
-\usepackage{mathtools}
+\documentclass[cupthm]{CUP-JNL-JMJ}
+
+%%%% Packages
+\usepackage{latexsym}
+\usepackage{graphicx}
+\usepackage{multicol,multirow}
+\usepackage{amsmath,amssymb,amsfonts, amscd}
+\usepackage{mathrsfs}
+\usepackage{amsthm}
 \usepackage{rotating}
-\usepackage{xcolor}
-\usepackage{amsmath}
-\usepackage{mathrsfs}
+\usepackage{appendix}
+\usepackage[numbers]{natbib}
 \usepackage{enumerate}
-\usepackage[colorlinks=true, linktoc=page, citecolor=blue, linkcolor=blue, urlcolor=blue]{hyperref}
-
-\usepackage{tabularx}
-\setlength\extrarowheight{4pt}   %spacing in tables
-\usepackage{theorem}
-\usepackage[matrix,tips,frame,color,line,poly,curve]{xy}
-\renewcommand{\labelenumi}{(\arabic{enumi})}
-\newcommand\kappaarrow[2]{#1\overset\kappa\rightarrow#2}
-\newtheorem{theorem}[equation]{Theorem}
-\newtheorem{corollary}[equation]{Corollary}
-\newtheorem{definition}[equation]{Definition}
-\newtheorem{lemma}[equation]{Lemma}
-\newtheorem{desideratum}[equation]{Desideratum}
-\newtheorem{conjecture}[equation]{Conjecture}
-\newtheorem{proposition}[equation]{Proposition}
-\newtheorem{remark}[equation]{Remark}
-{\theorembodyfont{\rmfamily}\newtheorem{theoremplain}[equation]{Theorem}
-\newtheorem{remarkplain}[equation]{Remark}
-\newtheorem{editorialremarkplain}[equation]{Editorial Remark}
-\newtheorem{exampleplain}[equation]{Example}
-\newtheorem{corollaryplain}[equation]{Corollary}
-\newtheorem{mytable}[equation]{Table}
-}
-
-\renewcommand{\sec}[1]{\section{#1}
-\renewcommand{\theequation}{\thesection.\arabic{equation}}
-  \setcounter{equation}{0}}
-\newcommand{\subsec}[1]{\subsection{#1}
-\renewcommand{\theequation}{\thesubsection.\arabic{equation}}
-  \setcounter{equation}{0}}
-
-\newcommand{\subsubsec}[1]{\subsubsection{#1}
-\renewcommand{\theequation}{\thesubsection.\arabic{equation}}
-  \setcounter{equation}{0}}
-
-% Danger, Will Robinson!
-\def\danger{\begin{trivlist}\item[]\noindent%
-\begingroup\hangindent=3pc\hangafter=-2%\clubpenalty=10000%
-\def\par{\endgraf\endgroup}%
-\hbox to0pt{\hskip-\hangindent\dbend\hfill}\ignorespaces}
-\def\enddanger{\par\end{trivlist}}
+
+%%%%
 
 \numberwithin{equation}{section}
+
+\articletype{RESEARCH ARTICLE}
+\jname{J. Inst. Math. Jussieu}
+%\artid{20}
+\jyear{2025}
+\jvol{1}
+%\jissue{1}
+\jdoi{10.1017/S1474748020000237}
+
+\DeclareGraphicsRule{.tif}{eps}{.tif.bb}{`tiff2ps #1}
+
+\theoremstyle{cupplain}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{proposition}{Proposition}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{corollary}[theorem]{Corollary}
+
+\theoremstyle{cupdefinition}
+\newtheorem{definition}{Definition}[section]
+
+\theoremstyle{cupremark}
+\newtheorem{remark}[theorem]{Remark}
+\newtheorem{example}[theorem]{Example}
+
+\theoremstyle{cupproof}
+\newtheorem{proof}{Proof}
 
@@
 \newcommand{\thetaK}{\negthinspace\negthinspace\phantom{a}^\theta K(\C)}
-\newcommand{\qed}{\hfill $\square$ \medskip}
-\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\qed}
 \newcommand\exact[3]{1\rightarrow #1\rightarrow #2\rightarrow #3\rightarrow1}
@@
 \newcommand{\ECom}{\mathcal{E}^{\mathcal{C}}_\Omega}
+
 \begin{document}
 
-\title{Nilpotent Invariants \\ for Generic Discrete Series of Real Groups}
-\author{Jeffrey Adams\footnote{University of Maryland \& IDA Center for Computing Sciences ; \url{jda@math.umd.edu}} {} \& Alexandre Afgoustidis\footnote{CNRS \& Université de Lorraine, Nancy \& Metz ; \url{alexandre.afgoustidis@math.cnrs.fr}}}
-\date{}
+\title[Nilpotent Invariants for Generic Discrete Series of Real Groups]{NILPOTENT INVARIANTS  \\ FOR GENERIC DISCRETE SERIES OF REAL GROUPS}
+\author[1]{JEFFREY ADAMS}
+
+\address[1]{\orgname{University of Maryland \& IDA Center for Computing Sciences}\\ \email{jda@math.umd.edu}\\}
+
+ \author[2]{ALEXANDRE AFGOUSTIDIS}
+ \address[2]{\orgname{CNRS \& Université de Lorraine,} \city{Nancy \& Metz,} \country{France} \\ \email{alexandre.afgoustidis@math.cnrs.fr}}
+
+\received{\today}
 
@@
 
+\abstract{Let $G(\mathbb{R})$ be a real reductive group.
+Suppose $\pi$ is an irreducible representation of $G(\mathbb{R})$ having a Whittaker model, and consider three invariants of~$\pi$ related to nilpotents elements of the Lie algebra of~$G$ (or its dual): the associated variety, the wave-front set, and the set of Whittaker data for which $\pi$ has a Whittaker model.
+If $\pi$ is a discrete series representation, these invariants are known to determine each other.
+We provide a self-contained account of this and related matters.
+Many of the results were known: we give simplified proofs for several of them, for instance a simple proof (for generic discrete series) that the associated variety and the wave-front set are related by the Kostant--Sekiguchi correspondence.}
+
 Let $G$ be a connected complex reductive group, defined over $\R$, and consider the group $G(\R)$ of real points. 
-
 We are interested in representations of~$G(\R)$ which admit Whittaker models. For this we consider pairs $(B,\eta)$ where 
 \begin{enumerate}[(i)]
-\item $B$ is a Borel subgroup of~$G$ defined over~$\R$,
-\item $\eta$ is a character of the nilpotent radical~$N(\R)$ of~$B(\R)$, subject to the condition that~$\eta$ is nontrivial on each simple root space.
+\item[(i)] $B$ is a Borel subgroup of~$G$ defined over~$\R$;
+\item[(ii)] $\eta$ is a character of the nilpotent radical~$N(\R)$ of~$B(\R)$, subject to the condition that~$\eta$ is nontrivial on each simple root space.
 \end{enumerate}
-The existence of a Borel subgroup satisfying (i) is the definition of $G$ being quasisplit, which we assume holds from now on.
+The existence of a Borel subgroup satisfying (i) is the definition of $G$ being quasisplit over~$\R$, which we assume holds from now on.
 
@@
 Whittaker data $\w$ such that $\pi$ has a $\w$-Whittaker model. This is a small finite set.
-We say $\pi$ is {\it generic} if $\Wh(\pi)$ is non-empty.
+We say $\pi$ is {\it generic} if $\Wh(\pi)$ is nonempty.
 
@@
 \end{enumerate}
-Many results in this note are well known.
-We give new and simplified proofs for as many of them as we could; for instance, Section~\ref{sec:Sekiguchi} contains a simple proof that $\WF(\pi)$ and $\AV(\pi)$ are exchanged by the Kostant--Sekiguchi correspondence.
+Many results in this note were known.
+We gave new and simplified proofs for as many of them as we could; for instance, Section~\ref{sec:Sekiguchi} contains a simple proof that $\WF(\pi)$ and $\AV(\pi)$ are exchanged by the Kostant--Sekiguchi correspondence.
 Otherwise we give convenient references.
@@
 
-\subsubsection*{Involutions}
-
-Let~$\sigma$ be the anti-holomorphic involution defining~$G(\R)$.
-Set $\g=\Lie(G)$ and $\g(\R)=\Lie(G(\R))$. 
-Choose a Cartan involution $\theta$ for $G$. This means:
+\subsubsection{Involutions}~
+ By definition there exists an anti-holomorphic involution~$\sigma$ of~$G$ such that $G(\R) = G^\sigma$. Fix such an involution~$\sigma$, and choose a Cartan involution $\theta$ for $G$. This means:
 $\theta$ is an algebraic involution, commuting with~$\sigma$,
 and $G(\R)^\theta$ is a maximal compact subgroup of~$G(\R)$. Set $K=G^\theta$ and $K(\R)=G(\R)^\theta=K^\sigma$.
-Let $\s$ be the $(-1)$-eigenspace of $\theta$ acting on~$\g$, where we use the notation $\sigma, \theta$ also for the automorphisms of~$\g$ induced by the above involutions.
-
-\subsubsection*{Nilpotent orbits in $\g^*$} 
+Set $\g=\Lie(G)$, and let $\s$ be the $(-1)$-eigenspace of $\theta$ acting on~$\g$, where we use the notation $\sigma, \theta$ also for the automorphisms of~$\g$ induced by the above involutions.
+Set $\g(\R)=\Lie(G(\R))$.
+
+\subsubsection{Nilpotent orbits in $\g^*$}~
 \label{s:dual}
@@
 First we define the nilpotent cone in $\g^*$ as follows. 
-We say an element of~$\g^*$ is \emph{nilpotent} if its $G$-orbit is a (weak) cone, i.e. closed under multiplication by~$\C^*$,
-and \emph{regular} if $\dim_{\Cent(G)}(X)=\mathrm{rank}(G)$.
+We say an element~$X$ of~$\g^*$ is \emph{nilpotent} if its $G$-orbit is a (weak) cone, i.e. closed under multiplication by~$\C^*$,
+and we say~$X$ is \emph{regular} if $\dim_{\Cent(G)}(X)=\mathrm{rank}(G)$.
 Let $\N^*$ be the set of nilpotent elements.
@@
 Having a $G(\R)$-invariant bilinear form on $\g(\R)$ is equivalent to having a $G(\R)$-equivariant isomorphism $\g(\R)\simeq \g^*(\R)$. 
-Suppose we fix a non-degenerate, $G(\R)$-invariant bilinear form $\kappa$ on $\g(\R)$.
-This is equivalent to having a non-degenerate bilinear form on~$\g$ which is both $G(\C)$- and Galois-invariant.
+Suppose we fix a nondegenerate, $G(\R)$-invariant bilinear form $\kappa$ on $\g(\R)$.
+This is equivalent to having a nondegenerate bilinear form on~$\g$ which is both $G(\C)$- and Galois-invariant.
 The restriction of the form to each simple factor
-is unique up to a nonzero constant. For example we can use the Killing form on $\gder=[\g, \g]$, extended arbitrarily by a non-degenerate form on the center.
-
-Given such a non-degenerate bilinear form $\kappa$, we define
+is unique up to a nonzero constant. For example we can use the Killing form on $\gder=[\g, \g]$, extended arbitrarily by a nondegenerate form on the center.
+
+Given such a nondegenerate bilinear form $\kappa$, we define
 $\psi_\kappa: \g\rightarrow \g^*$ as usual:
@@
 $$
-
 Using $\psi_\kappa$ we shall transfer to $\g^\ast$ several notions usually defined on $\g$: the asymptotic cone, the Kostant section, and the Kostant--Sekiguchi corresondence.
@@
 choice of $\kappa$. See Sections~\ref{s:gds} and \ref{sec:Sekiguchi}.
-In Section~\ref{s:AV} we need to be more precise: we choose  $\kappa$ to be the Killing form  (or any non-degenerate
+In Section~\ref{s:AV} we need to be more precise: we choose  $\kappa$ to be the Killing form  (or any nondegenerate
 invariant form which is negative definite on the Lie algebra of a maximal compact subgroup.)
 
-\subsubsection*{Representations} 
+\subsubsection{Representations}~
 We need to pass back and forth between representations of $G(\R)$ and $(\g,K)$-modules.
-See \cite{greenbook} for details.
+See \cite[Chapter~0]{greenbook} for details.
 
@@
 
-Conversely if $\pi$ is an irreducible $(\g,K)$-module it can be
+Conversely, if $\pi$ is an irreducible $(\g,K)$-module, it can be
 realized as the $K$-finite vectors of a Hilbert space representation, which we
-refer to as the Hilbert space globalization of $\pi$.
+refer to as the Hilbert space globalization of~$\pi$.
 
@@
 
-\subsubsection*{Associated variety and Gelfand--Kirillov dimension}
-
+\subsubsection{Associated variety and Gelfand--Kirillov dimension}~
 Suppose $\pi$ is an irreducible $(\g,K)$-module.
-
 The associated variety of $\pi$, denoted $\AV(\pi)$, is a closed, $K$-invariant set in~$\s^*$; so it is a finite union of
@@
 
-The Gelfand--Kirillov dimension~$\GK(\pi)$ of~$\pi$ can be defined in several different ways~\cite{vogan-gelfand-kirillov}; but one of them is
+The Gelfand--Kirillov dimension~$\GK(\pi)$ of~$\pi$ can be defined in several different ways~\cite{vogan-gelfand-kirillov}; one of them is
 $$
@@
 
-\subsubsection*{Wavefront set}
-
+\subsubsection{Wavefront set}~
 Now suppose $\pi$ is an irreducible admissible representation of $G(\R)$ on a Hilbert space $\mH$. 
@@
 singularity of the global character of $\pi$ near the identity. See \cite{howe_wave_front, bv_local_structure, HarrisHeOlafsson} for the definition. 
-The set~$\WF(\pi)$  is a closed $G(\R)$-invariant subset of the nilpotent cone in
-$i\g(\R)^*$. As such it is the union of a finite number of nilpotent $G(\R)$-orbits. Again, this depends only on the equivalence class of~$\pi$.
+The set~$\WF(\pi)$  is a closed $G(\R)$-invariant subset of the nilpotent cone in~$i\g(\R)^*$.
+As such, it is the union of a finite number of nilpotent $G(\R)$-orbits.
+Again, this depends only on the equivalence class of~$\pi$.
 
@@
 
-\subsubsection*{Whittaker models}
-
+\subsubsection{Whittaker models}~
 Suppose again that $\pi$ is an irreducible admissible representation of $G(\R)$ on a Hilbert space $\mH$.
@@
 
-\subsection{Large representations} Set $N=\dim(G)-\mathrm{rank}(G)$. This is the dimension of the nilpotent cone~$\N$. The maximal Gelfand--Kirillov dimension of a representation is $N/2$.
+\subsection{Large representations} Set $N=\dim(G)-\mathrm{rank}(G)$. This is the dimension of the nilpotent cone~$\N$. The maximal possible Gelfand--Kirillov dimension of a representation is $N/2$.
 We say $\pi$ is {\it large} if $\GK(\pi)=N/2$. See \cite[Section~6]{vogan-gelfand-kirillov}.
@@
   The following conditions are equivalent.
-  \begin{enumerate}
+  \begin{enumerate}[(i)]
   \item $\pi$ is large\textup{;}
@@
 Then any discrete series representation of~$G(\R)$ has a \emph{Harish-Chandra parameter}, which is an element of~$\Lambda/W_K$.
-In fact, suppose~$\lambda$ is an element of~$\Lambda$ and suppose $\zeta$ is a character of the center~$Z(\R)$ of~$G(\R)$ whose differential agrees with~$\lambda-\rho$ on the intersection $T(\R) \cap Z(\R)$; then the pair $(\lambda, \zeta)$  determines a discrete series representation~$\pi_{\lambda, \zeta}$ of~$G(\R)$.
+In fact, suppose~$\lambda \in \Lambda$ and suppose $\zeta$ is a character of the center~$Z(\R)$ of~$G(\R)$ whose differential agrees with~$\lambda-\rho$ on the intersection $T(\R) \cap Z(\R)$; then the pair $(\lambda, \zeta)$  determines a discrete series representation~$\pi_{\lambda, \zeta}$ of~$G(\R)$.
 Every discrete series representation arises in this way, and $\pi_{\lambda, \zeta}=\pi_{\lambda', \zeta'}$ if and only if $\zeta=\zeta'$ and $\lambda, \lambda'$ are $W_K$-conjugate.
@@
 \subsection{The invariants for generic discrete series}
+\medskip
 
@@
 Before embarking on the proof, let us point out that the maps in the
-Theorem are defined using rather deep results of representation
+Theorem are defined using deep results of representation
 theory. However, we shall show in Section~\ref{sec:explicit} that all
@@
 \end{itemize}
-The theorem follows immediately from these two observations, and from the following basic fact on group actions.
-
-\begin{lemma} Suppose a group $Q$ acts on two sets $A, B$ and let $f\colon A \to B$ be a $Q$-equivariant map. 
+The theorem follows immediately from these two observations, plus the following basic fact on group actions.
+
+\begin{lemma} Suppose a group $Q$ acts on two sets $A$ and~$B$. Let $f\colon A \to B$ be a $Q$-equivariant map. 
 \begin{itemize}
@@
 
-\subsubsection{Definition of the two groups, and canonical isomorphism}
+\subsubsection{Definition of the two groups, and canonical isomorphism}~
 
@@
 
-\begin{lemma}\label{lem:iso_q}
+\begin{lemma}\label{lem:iso_q}~
 \begin{itemize}
@@
 
-\subsubsection{Connection with group cohomology}
-
+\subsubsection{Connection with group cohomology}~
 The groups $Q_{\sigma}(G)$ and $Q_{\theta}(G)$ are instances of the following construction: if~$\tau$ is an involutive automorphism of~$G$, then it preserves~$Z$ and induces an involution of~$\Gad$, still denoted $\tau$; we may then set $Q_{\tau}(G)=(\Gad)^{\tau}/(G^{\tau})_{\ad}$, where $(G^{\tau})_{\ad}$ is the image of~$G^{\tau}$ in~$\Gad$.
@@
 
-\subsubsection{Proof of Lemma~\ref{lem:iso_q}}
+\subsubsection{Proof of Lemma~\ref{lem:iso_q}}~
 
 The proof of Lemma~\ref{lem:iso_q} uses Galois cohomology for the compact real form.  Recall $\theta\sigma = \sigma\theta$, and $G^{\sigma\theta}$ is a compact real form of~$G$. 
-The involutions $\sigma$ and $\theta$ coincide on $G^{\sigma\theta}$,
+The involutions $\sigma$ and $\theta$ coincide on~$G^{\sigma\theta}$,
 therefore  $H^1(\sigma, G^{\sigma\theta})$ and  $H^1(\theta, G^{\sigma\theta})$ are the same set,
@@
 By \cite[Corollary~4.4 and Corollary 4.7]{galois}, both of these maps are \emph{bijections}.
-Replacing~$G$ by $Z$ we get bijections $H^{1}(\sigma, Z) \leftarrow H(\ast, Z^{\sigma\theta}) \rightarrow H^{1}_{\theta}(\Gamma, Z)$.
+Replacing~$G$ by~$Z$ we get bijections $H^{1}(\sigma, Z) \leftarrow H(\ast, Z^{\sigma\theta}) \rightarrow H^{1}_{\theta}(\Gamma, Z)$.
 These fit with the bijections~\eqref{bij_cohom} into a commutative diagram
@@
 
-Let $g$ be an element of $G$ such that $\gamma = gZ$; then $z=g \sigma(g^{-1})$ is an element of $Z^{-\sigma}$.
+Let $g$ be an element of $G$ such that $\gamma = gZ$; then $z=g \sigma(g^{-1})$ is an element of~$Z^{-\sigma}$.
 Let $\zeta$ be its class in $H^{1}(\theta, Z)$.
@@
 Then $\gamma_0 \in (G^{\sigma})_\ad$, and $\gamma_0$ is equal to the image of $k^{-1} g$ in $\Gad$.
-The element $\kappa=\gamma \gamma_0^{-1}$ of $\Gad$  is therefore $\sigma$-invariant, and since $\kappa=kZ$, we also have $(\theta\sigma)(\kappa)=\kappa$; we conclude that $\theta(\kappa) = \kappa$, q.e.d.
-
-Let us prove~(b).
+The element $\kappa=\gamma \gamma_0^{-1}$ of $\Gad$  is therefore $\sigma$-invariant, and since $\kappa=kZ$, we also have $(\theta\sigma)(\kappa)=\kappa$; we deduce that $\theta(\kappa) = \kappa$, which concludes the proof of~(a).
+
 To show that when $g\in (\Gad)^\sigma \cap (\Gad)^\theta$ is a representative of $x \in Q_{\sigma}(G)$,  the image of~$g$ in  $Q_\theta(G)$ depends only on~$x$, it is enough to show that  $(G^\sigma)_\ad \cap (\Gad)^\theta \subset (G^\theta)_{\ad}$.
@@
 Exchanging the roles of $\sigma$ and $\theta$, we get a well-defined map $Q_{\theta}(G) \to Q_{\sigma}(G)$, which is the inverse of $\varphi$; therefore $\varphi$ is an isomorphism.
+Assertion~(b) follows.
 
@@
 
-\subsubsection*{On representations}
-
-The adjoint action of $\Gad^\sigma$ on~$G(\R)$ induces an action on $G(\R)$-representations, which descends to an action of  $Q_\sigma(G)$ on equivalence class of $G(\R)$-representations.
+\subsubsection{On representations}~The adjoint action of $\Gad^\sigma$ on~$G(\R)$ induces an action on $G(\R)$-representations, which descends to an action of  $Q_\sigma(G)$ on equivalence class of $G(\R)$-representations.
 If~$q$ is an element of~$Q_\sigma(G)$, we write $\pi \mapsto \pi^q$ for the action of~$q$ on equivalence classes of $G(\R)$-representations.
@@
 
-\subsubsection*{On real nilpotent orbits}
-
-To define the action of~$Q_{\sigma}(G)$ on~(4), first observe that~$\Gad$ acts on~$\g$ by the adjoint action.
+\subsubsection{On real nilpotent orbits}~To define the action of~$Q_{\sigma}(G)$ on~(4), first observe that~$\Gad$ acts on~$\g$ by the adjoint action.
 This action preserves~$\Op$, and its restriction to~$\Gad(\R)$ preserves~$\Op\cap i\g(\R)^*$.
@@
 
-\begin{proposition}\label{prop:action_on_real_orbits}
-\begin{enumerate} 
+\begin{proposition}\label{prop:action_on_real_orbits}~
+\begin{enumerate}[(a)] 
 \item The action of~$Q_{\sigma}(G)$ on $(\Op\cap i\g(\R)^*)/G(\R)$ is simply transitive.
@@
 \begin{proof}
-The proof of~(1) is a standard argument in group cohomology. Suppose $\omega,\omega'$ are $G(\R)$ orbits in $\Op\cap i\g(\R)^*$,
+The proof of~(a) is a standard argument in group cohomology. Suppose $\omega,\omega'$ are $G(\R)$ orbits in $\Op\cap i\g(\R)^*$,
 and choose $X\in \omega,X'\in\omega'$. Then there exists $g\in G$ such that $\Ad(g)(X)=X'$. Since $X\in \g(\R)^*$ the condition $X'\in i\g(\R)^*$ 
@@
 On the other hand $\omega=\omega'$
-if and only if $X'=\Ad(g)X$ for some $g\in G(\R)$. This competes the proof of (1).
-
-Part~(2) of the proposition is comes from general properties of the wavefront set in microlocal analysis, and from the fact that the action of $Q_{\sigma}(G)$ comes from automorphisms of~$G(\R)$.
+if and only if $X'=\Ad(g)X$ for some $g\in G(\R)$. This competes the proof of (a).
+
+Part~(b) of the proposition is comes from general properties of the wavefront set in microlocal analysis, and from the fact that the action of $Q_{\sigma}(G)$ comes from automorphisms of~$G(\R)$.
 More precisely, if~$q$ is an element of~$Q_{\sigma}(G)$ and $\tilde{q}$ is a representative of~$q$ in $\Gad(\R)$, then the action of~$q$ on equivalence classes of $(\g, K)$-modules comes from the action of the automorphism $\mathrm{int}(\tilde{q})$ of~$G(\R)$ on $(\g, K)$-modules.
 Now the wavefront set of a distribution on a manifold satisfies general covariance properties under diffeomorphisms of the manifold: this follows from Hörmander's original definitions, see e.g.
-\cite[Section 2, p.~800]{HarrisHeOlafsson}.
-Applying this to the present situation, and going through the basics as in   \cite[Section~2]{HarrisHeOlafsson}, it follows that $\pi \mapsto \WF(\pi)$ is equivariant under $Q_{\sigma}(G)$.
+\cite[Sect.~2, p.~800]{HarrisHeOlafsson}.
+Applying this to the present situation, and going through the basics as in   \cite[Sect.~2]{HarrisHeOlafsson}, it follows that $\pi \mapsto \WF(\pi)$ is equivariant under $Q_{\sigma}(G)$.
 \end{proof}
@@
 
-\begin{proposition}\label{prop:action_on_K_orbits}
-\begin{enumerate} 
+\begin{proposition}\label{prop:action_on_K_orbits}~
+\begin{enumerate}[(a)]
 \item The action of~$Q(G)$ on $(\Op \cap \s^*)/K$ is simply transitive.
@@
 
-The proof of~(1) is exactly the same as that  to that of Proposition~\ref{prop:action_on_real_orbits}(1), replacing~$\sigma$ by the Cartan involution $\theta$.
-
-As for~(2), it follows directly from the definition of the associated variety.
+The proof of~(a) is exactly the same as that  to that of Proposition~\ref{prop:action_on_real_orbits}(a), replacing~$\sigma$ by the Cartan involution $\theta$.
+
+As for~(b), it follows directly from the definition of the associated variety.
 This uses filtrations of the universal enveloping algebra of~$\g$ which are all invariant under $\Gad^{\theta_{\ad}}$: see for instance the Introduction of~\cite{vogan_bowdoin}.
 Inspecting the definitions in \emph{loc.
-cit.} it becomes clear that the map $\pi \mapsto \AV(\pi)$, taking a generic discrete series $(\g,K)$-module  (or rather its equivalence class) to its associated variety, is equivariant under~$Q_{\theta}(G)$, proving~(2).
+cit.} it becomes clear that the map $\pi \mapsto \AV(\pi)$, taking a generic discrete series $(\g,K)$-module  (or rather its equivalence class) to its associated variety, is equivariant under~$Q_{\theta}(G)$, proving~(b).
 \qed
@@
 and let $S(\lambda)\subset\Delta^+(\lambda)$ be the simple roots.
-For $\alpha\in \Delta$, let $\g_\alpha$ be the corresponding root space, and choose a non-zero element $X_\alpha\in\g_\alpha$ for each $\alpha$.
+For $\alpha\in \Delta$, let $\g_\alpha$ be the corresponding root space, and choose a nonzero element $X_\alpha\in\g_\alpha$ for each $\alpha$.
 
@@
   \label{e:Fpi}
-  F_\pi=\sum_{\alpha\in S(\lambda)}X_{-\alpha}
+  F_\pi=\sum_{\alpha\in S(\lambda)}X_{-\alpha}.
 \end{equation}
@@
 
-\begin{remarkplain}
+\begin{remark}
 Note that $\psi_{-\kappa}(F_\pi)=-\psi_{\kappa}(F_\pi)$, and these are not necessarily $K$-conjugate.
   This is the reason we need to use (a positive multiple of) the Killing form for this formula.
-\end{remarkplain}
+\end{remark}
 
@@
 Consider the \emph{asymptotic cone} of $\mathcal{O}_\pi$ (see e.g. \cite[Section 3]{AVAV}) :
-\[ \AC(\mathcal{O}_\pi) = \left\{ v \in \g^* \ : \ \text{$\exists (\varepsilon_n, x_n)\in (\R_+ \times \mathcal{O}_\pi)^\mathbb{N}$ such that $\varepsilon_n \to 0$ and $\varepsilon_n x_n \to v$}\}  \right\}.
-\]
+\[ \AC(\mathcal{O}_\pi) = \left\{ v \in \g^*  :\ \text{$\exists (\varepsilon_n, x_n)\in (\R_+ \times \mathcal{O}_\pi)^\mathbb{N}$, $\varepsilon_n \to 0$ and $\varepsilon_n x_n \to v$}  \right\}. \]
 This is a union of nilpotent $G(\R)$-orbits on $i\g(\R)^*$.
@@
 
-Suppose $X\in i\g(\R)^*\subset \g^*$ is a regular nilpotent element (see Section \ref{s:dual}).
+Suppose $X\in i\g(\R)^*\subset \g^*$ is a regular nilpotent element (see \S\,{}\ref{s:dual}).
 Let $\overline{\mathfrak b}(\R)$ be the kernel of $X$. This is the Lie algebra of~$\overline{B}(\R)$, where
@@
 $$
-Since $\psi$ is unique on each simple factor up to a non-zero scalar, it is easy to see this definition is independent of the choice of $\psi$. See \cite[Section 3.2]{adams_kaletha}.
+Since $\psi$ is unique on each simple factor up to a nonzero scalar, it is easy to see this definition is independent of the choice of $\psi$. See \cite[Section 3.2]{adams_kaletha}.
 
@@
   \label{p:Kostant}
-Suppose $\pi$ is a generic discrete series representation of~$G(\R)$. Suppose~$\pi$ be a Whittaker datum for~$G(\R)$, and let~$X \in i\g(\R)^*$ be a regular nilpotent element such that $\w = \w_X$. 
-Then $\pi$ is $\w$-generic if and only if $\Kostant{X}$ meets $\mathcal{O}_\pi$. 
+Suppose $\pi$ is a generic discrete series representation of~$G(\R)$. Let~$\w$ be a Whittaker datum for~$G(\R)$, and let~$X \in i\g(\R)^*$ be a regular nilpotent element with $\w = \w_X$. 
+Then $\pi$ is $\w$-generic if and only if $\Kostant{X}$ meets~$\mathcal{O}_\pi$. 
 \end{proposition}
@@
 For a closely related result see \cite[Proposition 3.5]{fm}.
+\medskip
 
@@
 which is a special case of the main result of \cite{matumoto} (Theorem A):
-
 \begin{corollary}\label{cor:matumoto}
@@
 
-By Lemma \ref{l:pi_to_av} the associated variety of a discrete representation only depends on the $W_K$-orbit of any Weyl chamber containing a representative of its Harish-Chandra parameter. 
+By Lemma \ref{l:pi_to_av} the associated variety of a discrete series representation only depends on the $W_K$-orbit of any Weyl chamber containing a representative of its Harish-Chandra parameter. 
 The same holds for the wave front set and Whittaker data by Theorem \ref{th:main}. This can also be proved directly 
@@
 
-If~$H$ is an element of~$\g$, write $\O_H$ for the $G(\R)$-orbit of $H$.
+If~$H \in \g$, write $\O_H$ for the $G(\R)$-orbit of~$H$.
 
 \begin{proposition}\label{prop:AC_chamber} Let $\mathcal{C} \subset \t$ be a large open Weyl chamber.
-  If $H,H'\in\mathcal{C}$  then $\AC(\mathcal{O}_H)=\AC(\mathcal{O}_{H'})$.
-
-  Suppose $X$ is a regular nilpotent element. Then $\K(X)\cap \O_H\ne \emptyset$ if and only if $\K(X)\cap \O_{H'}\ne\emptyset$.
+\begin{enumerate}[(a)]
+\item  If $H,H'\in\mathcal{C}$  then $\AC(\mathcal{O}_H)=\AC(\mathcal{O}_{H'})$.
+
+\item  Suppose $X$ is a regular nilpotent element. Then $\K(X)\cap \O_H\ne \emptyset$ if and only if $\K(X)\cap \O_{H'}\ne\emptyset$.
+\end{enumerate}
 \end{proposition}
@@
 
-Given regular nilpotent orbits $\Omega$ and $\Omega'$, we deduce that $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$ is an open subset of the $\mathcal{S} \cap \mathcal{C}$.
+Given regular nilpotent orbits $\Omega$, $\Omega'$, we deduce that $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$ is an open subset of~$\mathcal{S} \cap \mathcal{C}$.
 
@@
 Therefore if the open set $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$ is nonempty, there must exist at least one generic discrete series representation~$\pi$ with a Harish-Chandra parameter representative which projects to $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$.
-By Lemma~\ref{lem:WF_and_AC} this means $\Omega$ and $\Omega'$ must be contained in $\WF(\pi)$, which implies $\Omega = \Omega'$ since the wavefront set is the closure of a single orbit if $\pi$ is a generic discrete series.
+By Lemma~\ref{lem:WF_and_AC} this means $\Omega$ and $\Omega'$ must be contained in~$\WF(\pi)$, which implies $\Omega = \Omega'$ since the wavefront set is the closure of a single orbit if $\pi$ is a generic discrete series.
 
@@
 $\lambda,\lambda'$ are in the same  Weyl chamber then
-$\pi,\pi'$ have the same associated variety, wave-front set, and Whittaker models.
+$\pi,\pi'$ have the same associated variety, wave-front set, and Whittaker model.
 \end{corollary}
@@
 This follows from Lemma \ref{l:pi_to_av} for the associated variety;
-from Lemma~\ref{lem:WF_and_AC} and Proposition~\ref{prop:AC_chamber} for the wave front set, and Lemma \ref{lem:Kost_and_AC} (or Corollary \ref{cor:matumoto})
+from Lemma~\ref{lem:WF_and_AC} and Proposition~\ref{prop:AC_chamber} for the wavefront set; and from Lemma \ref{lem:Kost_and_AC} (or Corollary \ref{cor:matumoto})
 for the Whittaker model.
@@
 \begin{proof}
-If  $\mathscr{C}, \mathscr{C}'$ are in the same $W_K$-orbit, then the Harish-Chandra parameters of $\pi$, $\pi'$ have representatives in the same Weyl chamber; therefore $\Wh(\pi)=\Wh(\pi')$ by Corollary~\ref{c:same}.
+If  $\mathscr{C}, \mathscr{C}'$ are in the same $W_K$-orbit, then the Harish-Chandra parameters of $\pi$, $\pi'$ have representatives in the same Weyl chamber, and $\Wh(\pi)=\Wh(\pi')$ by Corollary~\ref{c:same}.
 
@@
 $$
-Since $\O\subset \gder$, and $\psi_\kappa$ restricted to each simple factor is unique up to non-zero scalar, it is easy to see this definition
+Since $\O\subset \gder$, and $\psi_\kappa$ restricted to each simple factor is unique up to nonzero scalar, it is easy to see this definition
 is independent of the choice of $\kappa$.
@@
 $$
-\KS(\AV(\pi))=\WF(\pi)
+\KS(\AV(\pi))=\WF(\pi).
 $$
@@
 \[   E_\theta=\frac12(E_\R-F_\R+H_\R)\quad
-F_\theta=\frac12(-E_\R+F_\R+H_\R)
+F_\theta=\frac12(-E_\R+F_\R+H_\R).
 \]
@@
 \label{e:KS}
-\KS(K\cdot E_\theta)=G(\R)\cdot E_\R\quad\KS(K\cdot F_\theta)=G(\R)\cdot(-E_\R)
+\KS(K\cdot E_\theta)=G(\R)\cdot E_\R\quad\KS(K\cdot F_\theta)=G(\R)\cdot(-E_\R).
 \end{equation}
@@
 \end{aligned}\]
-By the discussion in the previous section $\KS(K\cdot \psi(F_\theta))=\psi(\KS(K\cdot F_\theta))=\psi(G(\R)\cdot (-E_\R))=G(\R)\cdot \psi(-E_\R)$.
-We need to show this equals $\WF(\pi)$. By Corollary \ref{cor:matumoto} it is enough to show $\Wh(\pi)=\w_{\psi(-E_
-  \R)}$; by 
-   Lemma \ref{lem:Kost_and_AC} this is equivalent to $\K(\psi(-E_\R))$ meets $G(\R)\cdot\lambda$.
+By the discussion in the previous section we have 
+$$\KS(K\cdot \psi(F_\theta))=\psi(\KS(K\cdot F_\theta))=\psi(G(\R)\cdot (-E_\R))=G(\R)\cdot \psi(-E_\R).$$
+We need to show this equals $\WF(\pi)$. By Corollary \ref{cor:matumoto}, proving $\Wh(\pi)=\w_{\psi(-E_
+  \R)}$ is enough; by 
+   Lemma \ref{lem:Kost_and_AC} this is equivalent to: $\K(\psi(-E_\R))$ meets $G(\R)\cdot\lambda$.
 
@@
 
-\subsubsection{A simple description of the wavefront set}\label{sec:alternate_WF}
-
-As we saw the correspondence $\pi \leftrightarrow \WF(\pi)$ can be described using the asymptotic cone of the semisimple orbit of the Harish-Chandra parameter.
+\subsubsection{A simple description of the wavefront set}\label{sec:alternate_WF}~
+As we saw the correspondence \mbox{$\pi \leftrightarrow \WF(\pi)$} can be described using the asymptotic cone of the semisimple orbit of the Harish-Chandra parameter.
 We used this in the proof of Proposition~\ref{Sekiguchi_result}.
@@
 This gives the following rather concrete conclusion.
-As in Section \ref{s:AV} we define $\psi:\gder\simeq \gder^*$ using the Killing form.
+As in Sect. \ref{s:AV} we define $\psi:\gder\simeq \gder^*$ using the Killing~form.
 
@@
 These also satisfy the standard $SL(2)$ commutation relations; $E_\theta,F_\theta$ are in the $(-1)$-eigenspace of $\theta$; 
-and  $\sigma(E_\theta)=F_\theta,\sigma(H_\theta)=-H_\theta$.
-
-The change of bases are given by:
-$$
-\begin{aligned}
-  E_\theta&=\frac12(E_\R-F_\R+H_\R)\\
-  F_\theta&=\frac12(-E_\R+F_\R+H_\R)\\
-  H_\theta&=-E_\R-F_\R
-\end{aligned}
+and  $\sigma(E_\theta)=F_\theta,\sigma(H_\theta)=-H_\theta$. The change of bases are given by:
+$$
+  E_\theta=\frac12(E_\R-F_\R+H_\R), \quad 
+  F_\theta=\frac12(-E_\R+F_\R+H_\R), \quad
+  H_\theta=-E_\R-F_\R
 $$
@@
 $$
-\begin{aligned}
-  E_\R&=\frac12(E_\theta-F_\theta-H_\theta)\\
-  F_\R&=\frac12(-E_\theta+F_\theta-H_\theta)\\
-  H_\R&=E_\theta+F_\theta.
-\end{aligned}
+   E_\R=\frac12(E_\theta-F_\theta-H_\theta), \quad 
+  F_\R=\frac12(-E_\theta+F_\theta-H_\theta), \quad 
+  H_\R=E_\theta+F_\theta.
 $$
@@
 Define the dual basis
- $\{E_\R^*,F_\R^*,H_\R^*\}$ of $\g^*$ as usual,  i.e. $E_\R^*(E_\R)=1$, $E_\R^*(F_\R)=E_\R^*(H_\R)=0$, etc. Define 
+ $\{E_\R^*,F_\R^*,H_\R^*\}$ of $\g^*$ as usual: $E_\R^*(E_\R)=1$, $E_\R^*(F_\R)=E_\R^*(H_\R)=0$, etc. Define 
  $\{E_\theta^*,F_\theta^*,H_\theta^*\}$ similarly.
@@
 $$
-\langle \lambda_{ik},\ch\alpha\rangle=\lambda_{ik}(t_{-i})=k
-$$
-for $k \in \Z$.
+\langle \lambda_{ik},\ch\alpha\rangle=\lambda_{ik}(t_{-i})=k,\quad \text{for } k \in \Z.
+$$
 
@@
 $$
-This is a non-degenerate, $G(\R)$ invariant bilinear form on $\g(\R)$, and extends to a $\sigma$-invariant, $G(\C)$-invariant bilinear form on $\g$. 
-It is well known that every such form arises this way.
+This is a nondegenerate, $G(\R)$ invariant bilinear form on $\g(\R)$, and extends to a $\sigma$-invariant, $G(\C)$-invariant bilinear form on $\g$. 
+Every such form arises in this way.
 The Killing form $\kappa$ is equal to $\kappa_4$, 
@@
 and this extends to an isomorphism $\psi_c: \g\rightarrow \g^*$. 
-
 Explicitly we compute
@@
 \begin{aligned}
-\psi_c(H_\R)&=2cH_\R^*\\
-\psi_c(E_\R)&=cF_\R^*\\
+\psi_c(H_\R)&=2cH_\R^*, \quad
+\psi_c(E_\R)&=cF_\R^*, \quad
 \psi_c(F_\R)&=cE_\R^*.
@@
 \begin{aligned}
-\psi_c(H_\theta)&=2cH_\theta^*\\
-\psi_c(E_\theta)&=cF_\theta^*\\
+\psi_c(H_\theta)&=2cH_\theta^*, \quad
+\psi_c(E_\theta)&=cF_\theta^*, \quad
 \psi_c(F_\theta)&=cE_\theta^*.
@@
 \AC(\mu)=\psi_c^{-1}(\AC(\psi_c(\mu)))
-$$
-and
-$$
+\quad \text{and} \quad 
 \K(\mu)=\psi_c^{-1}(\K(\psi_c(\mu))),
@@
 
-First we compute $\AC(G(\R)\cdot kH_\theta)=\AC(G(\R)\cdot\begin{pmatrix}0&-ik\\ik&0
-\end{pmatrix})$ for $k\in \Z_{\ne 0}$.
+First we compute $\AC(G(\R)\cdot kH_\theta)=\AC\left(G(\R)\cdot\big(\begin{smallmatrix}0&-ik\\ik&0
+\end{smallmatrix}\big)\right)$ for $k\in \Z_{\ne 0}$.
 Here we are taking the real asymptotic cone; since $kH_\theta\in i\g(\R)$ this is a subset of $i\g(\R)$. 
@@
 \begin{aligned}
-\K(-E_\R^*)&=\psi_c(\K(\psi_c\inv(-E_\R^*)))\\
-&=\psi_c(\K( -\frac 1cF_\R)).\end{aligned}$$
+\K(-E_\R^*)&=\psi_c(\K(\psi_c\inv(-E_\R^*))) =\psi_c(\K( -\frac 1cF_\R)).\end{aligned}$$
 This contains
@@
 The case $k<0$ is similar; in that case we conclude
-$\Wh(\pi_{\lambda_{ik}})=\mathfrak{w}_{E_\R^\ast}$, and $\K(E_\R^*)\cap G(\R)\cdot (-2H_\theta)\ne \emptyset$.
+\[ \Wh(\pi_{\lambda_{ik}})=\mathfrak{w}_{E_\R^\ast} \quad \text{and}\quad \K(E_\R^*)\cap G(\R)\cdot (-2H_\theta)\ne \emptyset.\]
 
 \bibliographystyle{plain}
-\bibliography{Refs}
+\bibliography{Refs_JIMJ}
 

### 2025-03-06 whittaker_JIMJ.tex
Small changes after Jeff's round

@@
 \end{enumerate}
-Many results in this note were known.
+Many results in this note are known.
 We gave new and simplified proofs for as many of them as we could; for instance, Section~\ref{sec:Sekiguchi} contains a simple proof that $\WF(\pi)$ and $\AV(\pi)$ are exchanged by the Kostant--Sekiguchi correspondence.
@@
 \subsubsection{Involutions}~
- By definition there exists an anti-holomorphic involution~$\sigma$ of~$G$ such that $G(\R) = G^\sigma$. Fix such an involution~$\sigma$, and choose a Cartan involution $\theta$ for $G$. This means:
+ In our setting we may view $G(\R)$ as the fixed-point group $G^\sigma$, where $\sigma$ is an anti-holomorphic involution~$\sigma$ of~$G$ such that $G(\R) = G^\sigma$.
+Fix such an involution~$\sigma$, and choose a compatible Cartan involution~$\theta$ for $G$.
+This means:
 $\theta$ is an algebraic involution, commuting with~$\sigma$,
 and $G(\R)^\theta$ is a maximal compact subgroup of~$G(\R)$. Set $K=G^\theta$ and $K(\R)=G(\R)^\theta=K^\sigma$.
-Set $\g=\Lie(G)$, and let $\s$ be the $(-1)$-eigenspace of $\theta$ acting on~$\g$, where we use the notation $\sigma, \theta$ also for the automorphisms of~$\g$ induced by the above involutions.
+Set $\g=\Lie(G)$, and let $\s$ be the $(-1)$-eigenspace of~$\theta$ acting on~$\g$, where we use the notation $\sigma, \theta$ also for the automorphisms of~$\g$ induced by the above involutions.
 Set $\g(\R)=\Lie(G(\R))$.
@@
 there exists a $\theta$-stable Cartan subgroup~$T$ of~$G$  such that~$T(\R) \cap G_d$ is  compact, where $G_d$ is the derived group of~$G$.
-Throughout the paper, we assume $G(\R)$ does have discrete series representation, we fix  a Cartan subgroup $T \subset G$ satisfying the conditions above, and we let~$\mathfrak{t}$ denote the Lie algebra of~$T$, which is a Cartan subalgebra of~$\g$.
+Throughout the paper, we assume $G(\R)$ does have relative discrete series representation, we fix  a Cartan subgroup $T \subset G$ satisfying the conditions above, and we let~$\mathfrak{t}$ denote the Lie algebra of~$T$, which is a Cartan subalgebra of~$\g$.
 
@@
 
+We encourage the reader to consult the example of $\mathrm{SL}(2,\R)$ in the Appendix (\S\,\ref{sec:appendix}) when reading this section.
+
 \subsection{Associated Variety of generic discrete series}
@@
 
-\section{Appendix: the case of $SL(2,\R)$}
+\section{Appendix: the case of $SL(2,\R)$}\label{sec:appendix}
 

### 2025-03-07 whittaker_JIMJ.tex
Typographical trick, now 21 pages

@@
 \subsubsection{Involutions}~
- In our setting we may view $G(\R)$ as the fixed-point group $G^\sigma$, where $\sigma$ is an anti-holomorphic involution~$\sigma$ of~$G$ such that $G(\R) = G^\sigma$.
+ In our setting we may view $G(\R)$ as the fixed-point group $G^\sigma$, where $\sigma$ is an anti-holomorphic involution~$\sigma$ of~$G$.
 Fix such an involution~$\sigma$, and choose a compatible Cartan involution~$\theta$ for $G$.
@@
 $V$; we will denote it by~$\pi_K$. 
-
 Conversely, if $\pi$ is an irreducible $(\g,K)$-module, it can be
@@
 
-The proof of Lemma~\ref{lem:iso_q} uses Galois cohomology for the compact real form.  Recall $\theta\sigma = \sigma\theta$, and $G^{\sigma\theta}$ is a compact real form of~$G$. 
+The proof of the Lemma uses Galois cohomology for the compact real form.  Recall $\theta\sigma = \sigma\theta$, and $G^{\sigma\theta}$ is a compact real form of~$G$. 
 The involutions $\sigma$ and $\theta$ coincide on~$G^{\sigma\theta}$,
@@
 In this section only we need to  choose a particular an isomorphism \mbox{$\gder\simeq \gder^*$}.
-For this we let $\kappa$ be the killing form, and define $\psi_\kappa:\gder\rightarrow \gder^*$ by
+For this we let $\kappa$ be the Killing form, and define $\psi_\kappa:\gder\rightarrow \gder^*$ by
 $$
@@
 
+\small
+
 \bibliographystyle{plain}

### 2025-12-15 revision_whittaker.tex
Adds revision file

--- 2024-10-04 whittaker.tex
@@
 \begin{enumerate}[(i)]
-\item $B$ is a Borel subgroup of~$G$ defined over~$\R$,
+\item $B$ is a Borel subgroup of~$G$ defined over~$\R$;
 \item $\eta$ is a character of the nilpotent radical~$N(\R)$ of~$B(\R)$, subject to the condition that~$\eta$ is nontrivial on each simple root space.
@@
 \end{itemize}
-The theorem follows immediately from these two observations, and from the following basic fact on group actions.
+The theorem follows immediately from these two observations, and from the following basic fact on group actions, whose proof is left to the reader.
 
@@
 \end{lemma}
+
+\begin{center} \textcolor{red}{TODO : indicate in which sections of the paper we prove each of the statements in (i)-(ii) about the actions of $Q(G)$. }\end{center}
+
+\begin{remark} \textcolor{red}{\textup{TODO : add a remark about the case of fundamental series packets, in case there is no DS. }}\end{remark}
+
+\begin{remark} \textcolor{red}{\textup{TODO : say what this looks like when $G$ is adjoint, or simply connected, and add a remark on the general case.}  }\end{remark}
 
@@
 
+\begin{center} \textcolor{red}{TO DO : explain that this preserves generic representations, and  DS representations within a single $L$-packet.\\ Then explain why the action is transitive.
+}\end{center}
+
 \subsubsection*{On real nilpotent orbits}

### 2025-12-22 revision_whittaker.tex
Adds discussion on the size of Q(R) and placeholders for other stuff

@@
 \end{itemize}
-The theorem follows immediately from these two observations, and from the following basic fact on group actions, whose proof is left to the reader.
+
+For the action on~(1) see Section~\ref{sec:action_DS}.
+For the action on~(2) and the equivariance of $\pi \mapsto \Wh(\pi)$, see Section~\ref{sec:action_whitt}.
+For the action on~(4) and the equivariance of the map $\pi \mapsto \AV(\pi)$, see Section~\ref{sec:action_AV}.
+For the action on~(3) and the equivariance of $\pi \mapsto \WF(\pi)$ see Section~\ref{sec:action_WF}.
+
+The theorem then follows immediately from observations (i)-(ii), and from the following basic fact on group actions, whose proof is left to the reader.
 
@@
 
-\begin{center} \textcolor{red}{TODO : indicate in which sections of the paper we prove each of the statements in (i)-(ii) about the actions of $Q(G)$. }\end{center}
-
-\begin{remark} \textcolor{red}{\textup{TODO : add a remark about the case of fundamental series packets, in case there is no DS. }}\end{remark}
-
-\begin{remark} \textcolor{red}{\textup{TODO : say what this looks like when $G$ is adjoint, or simply connected, and add a remark on the general case.}  }\end{remark}
+\begin{remarkplain} \textup{The group $Q$ is a finite abelian group, in fact an elementary abelian $2$-group.
+It is trivial when $G$ is adjoint, and when $G$ is a simple group the cardinal of~$Q$ is at most~$4$.
+See Remark~\ref{rk:size_Q} for a more precise discussion.} \end{remarkplain}
+
+\begin{remarkplain} \textcolor{red}{\textup{TODO : add a remark about the case of fundamental series packets, in case there is no DS. }}\end{remarkplain}
 
@@
 This finite group may be viewed as a group of outer automorphisms of~$G(\R)$.
+
+\begin{remarkplain} \label{rk:size_Q} When $G$ is adjoint, it immediately follows from the definitions that $(G_\ad)^\sigma = (G^\sigma)_{\ad}$, therefore $Q_\sigma(G)$ is trivial in that case.
+
+In general, the group $G(\R)_{\ad}=(G^\sigma)_{\ad}$ contains the identity component of~$\Gad(\R)$, because the above injection $(G^\sigma)_{\ad} \hookrightarrow (\Gad)^\sigma$ is an isomorphism on the Lie algebra level.
+Therefore  $Q_\sigma(G)$ may be viewed as a quotient of the component group of $\Gad(\R)$, and is an elementary abelian $2$-group.
+
+When $G(\R)$ is connected, which happens for instance if $G$ is simply connected, the group $G(\R)_{\ad}$ is itself connected, and therefore equal to the identity component of $\Gad(\R)$.
+In that case $Q_\sigma(\R)$ is isomorphic with the component group of $\Gad(\R)$.
+
+For the concrete computation of this component group in case  $G$ is simple, see the tables in \cite[Section~10]{galois}. In particular  $Q_\sigma(\R)$ has at most four elements in that case.
+\end{remarkplain}
 
@@
 
-\subsubsection*{On representations}
+\subsubsection{On representations} \label{sec:action_DS}
 
@@
 
-\subsubsection*{On real nilpotent orbits}
+\subsubsection{\textcolor{red}{(NEW)} On Whittaker data}\label{sec:action_whitt}
+
+\begin{center} \textcolor{red}{TO DO : explain how $Q_\sigma(G)$ acts on Whittaker data, and refer to \cite[Lemma 3.1.3]{adams_kaletha} for the simple transitivity; point out that $\pi \mapsto \Wh(\pi)$ is equivariant.
+}\end{center}
+
+\subsubsection{On real nilpotent orbits} \label{sec:action_WF}
 
@@
 The resulting bijection  $(\Op\cap i\g(\R))/G(\R)\simeq Q_\sigma(\R)$ is equivariant (for the actions of $Q_\sigma(G)$ on $(\Op\cap i\g(\R))/G(\R)$ described above, and the action of  $Q_\sigma(G)$ on itself by multiplication), and this gives another proof of~(1).
+
+\subsubsection{On regular nilpotent $K$-orbits} \label{sec:action_AV}
 

### 2025-12-22 revision_whittaker.tex
Adds [new] and [/new] for clarity

@@
 
-For the action on~(1) see Section~\ref{sec:action_DS}.
+\textcolor{red}{[NEW]} For the action on~(1) see Section~\ref{sec:action_DS}.
 For the action on~(2) and the equivariance of $\pi \mapsto \Wh(\pi)$, see Section~\ref{sec:action_whitt}.
@@
 For the action on~(3) and the equivariance of $\pi \mapsto \WF(\pi)$ see Section~\ref{sec:action_WF}.
+\textcolor{red}{[/NEW]}
 
@@
 
-\begin{remarkplain} \textup{The group $Q$ is a finite abelian group, in fact an elementary abelian $2$-group.
-It is trivial when $G$ is adjoint, and when $G$ is a simple group the cardinal of~$Q$ is at most~$4$.
-See Remark~\ref{rk:size_Q} for a more precise discussion.} \end{remarkplain}
+\begin{remarkplain} \textcolor{red}{[NEW]} {The group $Q$ is a finite abelian group, in fact an elementary abelian $2$-group.
+It is trivial when $G$ is adjoint, and when $G$ is simple  the cardinal of~$Q$ is at most~$4$.
+See Remark~\ref{rk:size_Q} for a more precise discussion.} \textcolor{red}{[/NEW]}\end{remarkplain}
 
@@
 
-\begin{remarkplain} \label{rk:size_Q} When $G$ is adjoint, it immediately follows from the definitions that $(G_\ad)^\sigma = (G^\sigma)_{\ad}$, therefore $Q_\sigma(G)$ is trivial in that case.
+\begin{remarkplain} \textcolor{red}{(NEW)} \label{rk:size_Q} When $G$ is adjoint, it immediately follows from the definitions that $(G_\ad)^\sigma = (G^\sigma)_{\ad}$, therefore $Q_\sigma(G)$ is trivial in that case.
 
@@
 
-For the concrete computation of this component group in case  $G$ is simple, see the tables in \cite[Section~10]{galois}. In particular  $Q_\sigma(\R)$ has at most four elements in that case.
+For the concrete computation of this component group in case  $G$ is simple, see the tables in \cite[Section~10]{galois}.
+In particular  $Q_\sigma(\R)$ has at most four elements in that case.\textcolor{red}{[/NEW]}
 \end{remarkplain}

### 2025-12-22 revision_whittaker.tex
Cuts a few useless words
One more small cut

@@
 
-\begin{remarkplain} \textcolor{red}{[NEW]} {The group $Q$ is a finite abelian group, in fact an elementary abelian $2$-group.
+\begin{remarkplain} \textcolor{red}{[NEW]} {The group $Q$ is an elementary abelian $2$-group.
 It is trivial when $G$ is adjoint, and when $G$ is simple  the cardinal of~$Q$ is at most~$4$.
@@
 When $G(\R)$ is connected, which happens for instance if $G$ is simply connected, the group $G(\R)_{\ad}$ is itself connected, and therefore equal to the identity component of $\Gad(\R)$.
-In that case $Q_\sigma(\R)$ is isomorphic with the component group of $\Gad(\R)$.
+In that case $Q_\sigma(\R)$ is the component group of $\Gad(\R)$.
 

### 2025-12-22 revision_whittaker.tex
Adds a remark on Shelstad's terminology and another on fundamental series

@@
 Recall that the \emph{Weyl chambers} of~$\mathfrak{t}^\ast$ are the connected components of the set of regular elements.
-Each Weyl chamber specifies a positive root system for the roots of $\mathfrak{t}$ in~$\g$, and we say a Weyl chamber is \emph{large} if the corresponding simple roots are all noncompact.
+Each Weyl chamber specifies a positive root system for the roots of $\mathfrak{t}$ in~$\g$, \textcolor{red}{[new]} and a Borel subgroup of~$G$ containing~$T$ and defined over~$\R$ \textcolor{red}{[/new]}.
+We say a Weyl chamber is \emph{large} if the corresponding simple roots are all noncompact.
 
@@
 See~\cite[Section 6]{vogan-gelfand-kirillov}.
+\textcolor{red}{[new]} In the terminology of Shelstad~\cite[Section 2.3]{shelstad}, if $B$~is the corresponding Borel subgroup of~$G$, then $(B, T)$ is a fundamental Borel pair of Whittaker type.\textcolor{red}{[/new]}
 
@@
 
-\begin{remarkplain} \textcolor{red}{\textup{TODO : add a remark about the case of fundamental series packets, in case there is no DS. }}\end{remarkplain}
+\begin{remarkplain} 
+ \textcolor{red}{[NEW]} Not all quasi-split real groups have discrete series representations.
+But if $G(\R)$ is a quasi-split real group, then the  \emph{fundamental series} representations that are generic are irreducibly induced from generic discrete series of a maximal cuspidal Levi subgroup $M(\R)$ of $G(\R)$.
+Using \cite[Chapter~14]{abv}, especially Lemma 14.11 there, one may relate Whittaker data for $G(\R)$ with Whittaker data for $M(\R)$, and the generic fundamental series representations in a given $L$-packet for $G(\R)$ (together with the attached Whittaker data) with  generic discrete series representations for maximal cuspidal Levi subgroups.
+We shall not pursue this here.
+\textcolor{red}{[/NEW]}
+ \end{remarkplain}
 

### 2025-12-22 revision_whittaker.tex
Adds the comparison with Moeglin-Renard

@@
 It is trivial when $G$ is adjoint, and when $G$ is simple  the cardinal of~$Q$ is at most~$4$.
-See Remark~\ref{rk:size_Q} for a more precise discussion.} \textcolor{red}{[/NEW]}\end{remarkplain}
+See Remark~\ref{rk:size_Q} for a more precise discussion.} \end{remarkplain}
+
+\begin{exampleplain} If $G(\R)$ is the symplectic group $\mathrm{Sp}(2n, \R)$, then $Q \simeq \Z/2\Z$ and there are two distinct Whittaker data for $G(\R)$.
+If $\Pi$ is the $L$-packet of discrete series with the same infinitesimal character as the trivial representation, then $\Pi_{\mathrm{gen}}$ has two elements, and the correspondence $\pi \mapsto \Wh(\pi)$ in Theorem~\ref{th:main} was made explicit by Mœglin and Renard \cite[Proposition~4.1]{moeglin_renard} following work of Wallach~\cite{wallach} and Oda~\cite{oda}.
+As we shall see their result agrees with the description in Section~\ref{sec:alternate_WF} below.
+\textcolor{red}{[/NEW]}\end{exampleplain}
 
@@
 $$\end{lemma}
-There is a partial converse to this statement if we consider discrete series within a single $L$-packet.
+
+\begin{exampleplain} \textcolor{red}{[NEW]} Suppose $G(\R) = \mathrm{Sp}(2n, \R)$ and ~$\pi$ is the generic discrete series representation denoted  $\pi_{\mathbf{B}_+, \mathbf{T}}$ in \cite[Section~4.2]{moeglin_renard}.
+Take up the notation above and use the discussion in Section~\ref{s:AV} to define a pinning $\mathcal{P}$ of~$G$; then the corresponding Borel subgroup is the subgroup $\textbf{B}_{+}$ of \cite{moeglin_renard}.
+If $X_\mathcal{P}$ is the principal nilpotent element defined in \cite[Section 3.1]{adams_kaletha}, then the Whittaker data $\mathfrak{w}_{\psi(F_\R)}$  coincides with  $\mathfrak{w}_{X_\mathcal{P}}$: see \cite[Lemma 3.1.2]{adams_kaletha}.
+By Lemma~\ref{lem:explicit_WF} and Corollary~\ref{cor:matumoto} above we deduce that $\Wh(\pi)$ is the Whittaker datum attached to the pinning~$\mathcal{P}$ and the additive character  $\Lambda\colon x \mapsto e^{ix}$ of~$\R$.
+This is the Whittaker datum denoted by $\Wh_1$ in \cite[loc.
+cit.]{moeglin_renard}, therefore our results are consistent with \cite[Proposition~4.1]{moeglin_renard}.
+\textcolor{red}{[/NEW]} 
+\end{exampleplain}
+
+\begin{remarkplain} There is a partial converse to this statement if we consider discrete series within a single $L$-packet.
 Fix an $L$-packet~$\Pi$ of discrete series, and consider a regular semisimple orbit~$\Omega$ in~$\Op \cap i\g(\R)^\ast$; then we can determine the generic representation~$\pi \in \Pi$ with $\WF(\pi)=\Omega$, as follows.
@@
 Then $\pi$ is the discrete series representation in $\Pi$ whose Harish-Chandra parameter is dominant for $\Delta^+$. 
-
+\end{remarkplain}
 \section{Appendix: the case of $SL(2,\R)$}

### 2025-12-22 revision_whittaker.tex
Adds missing references

@@
 
-\begin{exampleplain} If $G(\R)$ is the symplectic group $\mathrm{Sp}(2n, \R)$, then $Q \simeq \Z/2\Z$ and there are two distinct Whittaker data for $G(\R)$.
-If $\Pi$ is the $L$-packet of discrete series with the same infinitesimal character as the trivial representation, then $\Pi_{\mathrm{gen}}$ has two elements, and the correspondence $\pi \mapsto \Wh(\pi)$ in Theorem~\ref{th:main} was made explicit by Mœglin and Renard \cite[Proposition~4.1]{moeglin_renard} following work of Wallach~\cite{wallach} and Oda~\cite{oda}.
+\begin{exampleplain} \textcolor{red}{[NEW]} If $G(\R)$ is the symplectic group $\mathrm{Sp}(2n, \R)$, then $Q \simeq \Z/2\Z$ and there are two distinct Whittaker data for $G(\R)$.
+If $\Pi$ is the $L$-packet of discrete series with the same infinitesimal character as the trivial representation, then $\Pi_{\mathrm{gen}}$ has two elements, and the correspondence $\pi \mapsto \Wh(\pi)$ in Theorem~\ref{th:main} was made explicit by Mœglin and Renard \cite[Proposition~4.1]{moeglin_renard}, based on work of Wallach~\cite{wallach} and Oda~\cite{oda} for $n=1,2$.
 As we shall see their result agrees with the description in Section~\ref{sec:alternate_WF} below.

### 2025-12-22 revision_whittaker.tex
Fixes the typos mentioned in the report

@@
 Suppose $X\in i\g(\R)^*\subset \g^*$ is a regular nilpotent element (see Section \ref{s:dual}).
-Let $\overline{\mathfrak b}(\R)$ be the kernel of $X$. This is the Lie algebra of~$\overline{B}(\R)$, where
+Let $\overline{\mathfrak b}(\R)$ be the kernel of $X$ in $\g(\R)$. This is the Lie algebra of~$\overline{B}(\R)$, where
 $\overline{B}$ is an $\R$-Borel subgroup of~$G$.
@@
 \subsubsection{The Sekiguchi correspondence for principal nilpotent orbits}\label{sec:concrete_sek}
+
 Let us spell out the special case of the Sekiguchi correspondence which is of interest here. We follow~\cite[Section~2]{AVAV}.
@@
 Suppose $E_\R\in i\g(\R)$ is a principal nilpotent element.
-We may choose $H_\R, E_\R \in \g$ such that $(H_\R,E_\R,F_\R)$ is an $\mathrm{SL}(2)$-triple and  $E_\R$  contained in $i\g(\R)$,
+We may choose $H_\R, F_\R \in \g$ such that $(H_\R,E_\R,F_\R)$ is an $\mathrm{SL}(2)$-triple and  $E_\R$  contained in $i\g(\R)$,
 which implies $H_\R\in \g(\R)$. 

### 2025-12-22 revision_whittaker.tex
Adds the requested remark on whittaker model terminology

@@
 
-Recall that a representation $\pi$ of~$G(\R)$ is said to {have a $(B,\eta)$-Whittaker model} if it has a nonzero distribution vector on which $N(\R)$ acts by $\eta$ (for a more careful statement of the definition see Section~\ref{sec:invariants}).
+Recall that a representation $\pi$ of~$G(\R)$ is said to {have a $(B,\eta)$-Whittaker model} if it has a nonzero distribution vector on which $N(\R)$ acts by $\eta$ (for a more careful statement of the definition and terminology see Section~\ref{sec:invariants}).
 This condition only depends on the conjugacy class of the pair, 
@@
 See~\cite{matumoto}.
-If~$\w$ is the corresponding Whittaker datum, i.e.
-the $G(\R)$-conjugacy class of the pair $(B, \eta)$, we say~$\pi$ has a $\w$-Whittaker model.
+\textcolor{red}{[NEW]} This condition depends only on the $G(\R)$-conjugacy class of the pair $(B, \eta)$.
+It is equivalent to the existence of a $G$-equivariant embedding of $\mH^\infty$ into the space of smooth sections of the equivariant line bundle over $G(\R)/N(\R)$ determined by $\eta$ (for the quasi-regular action of~$G$ on sections); the image of that embedding is a geometric realization of (the smooth vectors of)~$\pi$ which is the origin of the terminology ``Whittaker model for~$\pi$''.
+\textcolor{red}{[/NEW]}
+
+ If~$\w$ is the corresponding Whittaker datum, i.e. the $G(\R)$-conjugacy class of the pair $(B, \eta)$, we say~$\pi$ has a $\w$-Whittaker model.
 

### 2025-12-22 revision_whittaker.tex
Adds discussion of the action on Whittaker data

@@
 
-\subsubsection*{Whittaker models}
+\subsubsection*{Whittaker models}\label{sec:whittaker_defs}
 
@@
 We consider the corresponding actions of $G(\R)$ on the space~$\mH^\infty$ of smooth vectors in $\mH$, and on its dual $\mH^{-\infty}$.
-Let~$(B, \eta)$ be a pair satisfying conditions (i)-(ii) of the Introduction.
-We say $\pi$ has a $(B,\eta)$-Whittaker model
+Let~$(B, \eta)$ be a pair satisfying conditions (i)-(ii) of the Introduction; we shall say $(B, \eta)$ is a \emph{Whittaker pair}.
+We say $\pi$ has a \emph{$(B,\eta)$-Whittaker model}
 if there exists a nonzero element $v$ in~$\mH^{-\infty}$ such that $\pi(n)(v)=\eta(n)v$ for all $n$ in the nilradical $N(\R)$ of $B(\R)$.
@@
 
- If~$\w$ is the corresponding Whittaker datum, i.e. the $G(\R)$-conjugacy class of the pair $(B, \eta)$, we say~$\pi$ has a $\w$-Whittaker model.
+ If~$\w$ is the corresponding Whittaker datum, i.e. the $G(\R)$-conjugacy class of the pair $(B, \eta)$, we say~$\pi$ has a \emph{$\w$-Whittaker model}.
 
@@
 Each Weyl chamber specifies a positive root system for the roots of $\mathfrak{t}$ in~$\g$, \textcolor{red}{[new]} and a Borel subgroup of~$G$ containing~$T$ and defined over~$\R$ \textcolor{red}{[/new]}.
-We say a Weyl chamber is \emph{large} if the corresponding simple roots are all noncompact.
+We say a Weyl chamber is \emph{large}, or that the corresponding Borel subgroup is large, if the corresponding simple roots are all noncompact.
 
@@
 
-\textcolor{red}{[NEW]} For the action on~(1) see Section~\ref{sec:action_DS}.
+\textcolor{red}{[NEW]} For the action on~(1) see Sections~\ref{sec:action_DS} and~\ref{sec:action_transitivity}.
 For the action on~(2) and the equivariance of $\pi \mapsto \Wh(\pi)$, see Section~\ref{sec:action_whitt}.
@@
 
-\begin{remarkplain} \textcolor{red}{(NEW)} \label{rk:size_Q} When $G$ is adjoint, it immediately follows from the definitions that $(G_\ad)^\sigma = (G^\sigma)_{\ad}$, therefore $Q_\sigma(G)$ is trivial in that case.
+\begin{remarkplain} \textcolor{red}{[NEW]} \label{rk:size_Q} When $G$ is adjoint, it immediately follows from the definitions that $(G_\ad)^\sigma = (G^\sigma)_{\ad}$, therefore $Q_\sigma(G)$ is trivial in that case.
 
@@
 
-\begin{center} \textcolor{red}{TO DO : explain that this preserves generic representations, and  DS representations within a single $L$-packet.\\ Then explain why the action is transitive.
-}\end{center}
-
-\subsubsection{\textcolor{red}{(NEW)} On Whittaker data}\label{sec:action_whitt}
-
-\begin{center} \textcolor{red}{TO DO : explain how $Q_\sigma(G)$ acts on Whittaker data, and refer to \cite[Lemma 3.1.3]{adams_kaletha} for the simple transitivity; point out that $\pi \mapsto \Wh(\pi)$ is equivariant.
-}\end{center}
+\subsubsection{\textcolor{red}{(NEW SEC.)} On Whittaker data and generic representations}\label{sec:action_whitt}
+
+Suppose $\tilde{q} \in \Gad^\sigma$.
+For every Whittaker pair $(B, \eta)$ as in Section~\ref{sec:whittaker_defs}, the pair $q\cdot (B, \eta)=\big(\tilde{q} B \tilde{q}^{-1}, \eta \circ (x \mapsto \tilde{q} x \tilde{q}^{-1})\big)$ is again a Whittaker pair, which is conjugate to $(B, \eta)$ if and only if $\tilde{q} \in (G^\sigma)_{\ad}$.
+This determines an action of $Q_\sigma(G)$ on the set of Whittaker data for~$G(\R)$, which we shall denote by $(q, \mathfrak{w}) \mapsto q \cdot \mathfrak{w}$.
+This action is simply transitive: see \cite[Lemma 3.1.3]{adams_kaletha} for an elementary argument.
+
+Now let $\pi$ be a generic discrete series representation of~$G(\R)$.
+Let $q$ be an element of $Q_\sigma(G)$, with a representative $\tilde{q}$ in $\Gad^\sigma$.
+For every Whittaker pair $(B, \eta)$ such that $\pi$ has a $(B, \eta)$-Whittaker model, it is immediate from the definitions that the representation $\pi \circ (x \mapsto \tilde{q} x\tilde{q}^{-1})$ is again a discrete series, and that it has a $\tilde{q}\cdot (B, \eta)$-Whittaker model.
+Passing to equivalence classes we see that $\pi^q$ is generic, and satisfies $\Wh(\pi^q)=q \cdot \Wh(\pi)$.
+Therefore the map $\pi \mapsto \Wh(\pi)$ is $Q_\sigma(G)$-equivariant.
+
+\subsubsection{On generic discrete series in a single $L$-packet}\label{sec:action_transitivity}
+
+\begin{center} \textcolor{red}{TO DO : explain that the action of $Q_\sigma$ on generic DS preserves $L$-packets.\\ Then explain why the action on is transitive.\\
+Perhaps adding something about $L$-packets in \S~\ref{sec:discrete_series} would be useful. }\end{center}
 
